### 2021-05-27 papers/white-cycle-modeling/content.tex
adding template files

\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{wagner2017optimization} . Now citing a book reference \cite{blair2005sam} or other reference types \cite{hirsch2011standardization}. %Please use the command \citep{} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}

% The MDPI table float is called specialtable
\begin{specialtable}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabular}
\end{specialtable}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{equation}
a = 1,
\end{equation}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\end{paracol}
\nointerlineskip
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}

% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
\begin{figure}[H]	
\widefigure
\includegraphics[width=15 cm]{Definitions/logo-mdpi}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

\begin{paracol}{2}
\linenumbers
\switchcolumn

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

\end{paracol}

### 2021-06-16 simulations/modules/GenericSSCModule.py
adding documentation
much needed comments for GenericSSCModule class

@@ -17,15 +17,39 @@ from util.SSCHelperMethods import SSCHelperMethods
 from dispatch.GeneralDispatch import GeneralDispatch as GD
 from dispatch.GeneralDispatch import GeneralDispatchParamWrap as GDP
 from dispatch.GeneralDispatch import GeneralDispatchOutputs as GDO
-import pyomo.environ as pe
 import numpy as np
 import copy
 from abc import ABC
 
 class GenericSSCModule(ABC):
     
+    """
+    The GenericSSCModule class works as a way to intialize, update, and
+    run SSC simulations through PySAM. 
+    
+    This class is not meant to be run, but instead work as a parent class
+    for all other models including NuclearTES, a future CSP class, etc. 
+    
+    NOTE: I over-use the word "module" because everything is apparently a module.
+    There are three hierarchies of modules at play here:
+        - SSC modules   : these are the cmod_<name>.cpp files from the SSC repository written in C++
+        - PySAM modules : these are PySAM wrappers for the SSC modules (also Grid, Financial modules, etc.)
+        - NE2 modules   : these are Python classes that create PySAM modules (e.g., *THIS* class)
+    
+    TODO: can we convert this to an abstract class in Python?
+    
+    """
+    
     def __init__(self, plant_name="nuclear_tes", json_name="model1", 
                        is_dispatch=False, dispatch_time_step=1):
+        """ Initializes the GenericSSCModules
+        
+        Inputs:
+            plant_name (str)         : name of SSC module to run 
+            json_name (str)          : name of JSON script with input data for module
+            is_dispatch (bool)       : boolean, if True runs Pyomo dispatch optimization
+            dispatch_time_step (int) : time step for dispatch (hours)
+        """
         
         # grab names, either default here or from child class
         self.json_name  = json_name
@@ -69,6 +93,15 @@ class GenericSSCModule(ABC):
 
     def run_sim(self, run_loop=False, export=False, filename='temp.csv'):
         """ Method to run single simulation for Generic System
+        
+        This method handles the creating and execution of Plant, Grid, and Financial objects to
+        run through SSC. The Plant has an optional boolean input to allow the running of a full
+        simulation in a segmented loop.
+        
+        Inputs:
+            run_loop (bool) : if true, runs simulation in segments. else, runs simulation all at once
+            export (bool)   : if true, exports results to an Excel sheet
+            filename (str)  : name for Excel sheet saved to the /outputs directory
[…]

### 2021-06-16 simulations/util/FileMethods.py

@@ -87,9 +87,9 @@ class FileMethods(object):
             
         """
         
-        params_dataframe = pandas.DataFrame(data_list,columns=columns)
+        params_dataframe = pandas.DataFrame(data_list, columns=columns)
         
         filepath = "../outputs/" + filename
-        params_dataframe.to_csv(filepath,index=False)
+        params_dataframe.to_csv(filepath, index=False)
 
         

### 2021-06-16 simulations/modules/GenericSSCModule.py
streamlined the logging array methods

@@ -521,24 +521,35 @@ class GenericSSCModule(ABC):
         # size of simulation arrays
         N_sim = int( i_end - i_start )
         
-        # setting each logging array to zero
-        self.time_log          = np.zeros(N_sim)   # logging time
-        self.gen_log           = np.zeros(N_sim)   # electricity generation log
-        self.q_thermal_log     = np.zeros(N_sim)   # thermal power from nuclear to HTF log
-        self.p_cycle_log       = np.zeros(N_sim)   # PC electrical power output (gross)
-        self.q_dot_rec_inc_log = np.zeros(N_sim)   # Nuclear incident thermal power
-        self.q_pb_log          = np.zeros(N_sim)   # PC input energy
-        self.q_dot_pc_su_log   = np.zeros(N_sim)   # PC startup thermal power
-        self.m_dot_pc_log      = np.zeros(N_sim)   # PC HTF mass flow rate
-        self.m_dot_rec_log     = np.zeros(N_sim)   # Nuc mass flow rate
-        self.T_pc_in_log       = np.zeros(N_sim)   # PC HTF inlet temperature 
-        self.T_pc_out_log      = np.zeros(N_sim)   # PC HTF outlet temperature
-        self.T_tes_cold_log    = np.zeros(N_sim)   # TES cold temperature
-        self.T_tes_hot_log     = np.zeros(N_sim)   # TES hot temperature
-        self.T_cond_out_log    = np.zeros(N_sim)   # PC condenser water outlet temperature
-        self.e_ch_tes_log      = np.zeros(N_sim)   # TES charge state
-        self.op_mode_1_log     = np.zeros(N_sim)   # Operating Mode
-        self.defocus_log       = np.zeros(N_sim)   # Nuclear "Defocus" fraction
+        # dictionary of output variable names to log after each segment simulation
+        self.Log_Arrays = {
+        #    name of NE2 variable || name of SSC module variable
+                'time_log':          'time_hr',          # logging time
+                'gen_log':           'gen',              # electricity generation log
+                'q_thermal_log':     'Q_thermal',        # thermal power from nuclear to HTF 
+                'p_cycle_log' :      'P_cycle',          # PC electrical power output (gross)
+                'q_dot_rec_inc_log': 'q_dot_rec_inc',    # Nuclear incident thermal power
+                'q_pb_log':          'q_pb',             # PC input energy
[…]

### 2021-06-17 simulations/dispatch/GeneralDispatch.py
more documentation
documenting the rest of the modules and multiple Dispatch classes

@@ -24,7 +24,24 @@ from pyomo.util.check_units import assert_units_consistent, assert_units_equival
 
 
 class GeneralDispatch(object):
+    """
+    The GeneralDispatch class is meant to set up and run Dispatch
+    optimization as a mixed integer linear program problem using Pyomo.
+    It creates a ConcreteModel in Pyomo with Parameters, Variables,
+    Objectives, and Constraints. The ConcreteModel can then be solved. 
+    
+    This is the base/parent class and should not be run by itself.
+    
+    TODO: can we convert this to an abstract class in Python?
+    """
+    
     def __init__(self, params, unitRegistry):
+        """ Initializes the GeneralDispatch module
+        
+        Inputs:
+            params (dict)                : dictionary of Pyomo dispatch parameters
+            unitRegistry (pint.registry) : unique unit Pint unit registry
+        """
         
         self.model = pe.ConcreteModel()
         self.generate_params(params)
@@ -36,11 +53,11 @@ class GeneralDispatch(object):
     def generate_params(self,params):
         
         time_range = range(1,params["T"]+1)
-        # this is a lambda function to grab Pint Quantity magntitude if it has one
+        # this is a lambda function to grab Pint Quantity magntitude if it has one (gm = get magnitude)
         gm = lambda param_str: params[param_str].m if hasattr(params[param_str],'m') else params[param_str]
-        # creates dictionary if parameter happens to be a time-indexed parameter
+        # creates dictionary if parameter happens to be a time-indexed parameter (gd = get dictionary)
         gd = lambda param_str: {ind:val for (ind,val) in zip(time_range, gm(param_str))} if type(gm(param_str)) is np.ndarray else gm(param_str)
-        # shortening definition name for converting Pint units to pyomo units
+        # shortening definition name for converting Pint units to pyomo units (gu = get unit)
         gu = lambda param_str: SSCHelperMethods.convert_to_pyomo_unit(params, param_str)
         
         ### Sets and Indices ###
@@ -474,9 +491,24 @@ class GeneralDispatch(object):
 # =============================================================================
 
 class GeneralDispatchParamWrap(object):
+    """
+    The GeneralDispatchParamWrap class is meant to be the staging area for the 
+    creation of Parameters ONLY. It communicates with the NE2 modules, receiving
[…]

### 2021-06-17 simulations/dispatch/NuclearDispatch.py

@@ -20,8 +20,19 @@ from util.SSCHelperMethods import SSCHelperMethods
 import copy
 
 class NuclearDispatch(GeneralDispatch):
+    """
+    The NuclearDispatch class is meant to set up and run Dispatch
+    optimization as a mixed integer linear program problem using Pyomo,
+    specifically for the NuclearTES NE2+SSC module.
+    """
     
     def __init__(self, params, unitRegistry):
+        """ Initializes the NuclearDispatch module
+        
+        Inputs:
+            params (dict)                : dictionary of Pyomo dispatch parameters
+            unitRegistry (pint.registry) : unique unit Pint unit registry
+        """
         
         # initialize Generic module, csv data arrays should be saved here
         GeneralDispatch.__init__( self, params, unitRegistry )
@@ -31,15 +42,41 @@ class NuclearDispatch(GeneralDispatch):
 # =============================================================================
 
 class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
+    """
+    The NuclearDispatchParamWrap class is meant to be the staging area for the 
+    creation of Parameters ONLY for the NuclearDispatch class. It communicates 
+    with the NE2 modules, receiving SSC and PySAM input dictionaries to calculate 
+    both static parameters used for every simulation segment AND initial conditions 
+    that can be updated.
+    """
     
     def __init__(self, unit_registry, SSC_dict=None, PySAM_dict=None, pyomo_horizon=48, 
                    dispatch_time_step=1):
+        """ Initializes the NuclearDispatchParamWrap module
+        
+        Inputs:
+            unitRegistry (pint.registry)   : unique unit Pint unit registry
+            SSC_dict (dict)                : dictionary of SSC inputs needed to run modules
+            PySAM_dict (dict)              : dictionary of PySAM inputs + file names
+            pyomo_horizon (int Quant)      : length of Pyomo simulation segment (hours)
+            dispatch_time_step (int Quant) : length of each Pyomo time step (hours)
+        """
         
         GeneralDispatchParamWrap.__init__( self, unit_registry, SSC_dict, PySAM_dict, 
                             pyomo_horizon, dispatch_time_step )
 
 
     def set_fixed_cost_parameters(self, param_dict):
+        """ Method to set fixed costs of the Plant
+        
+        This method calculates some fixed costs for the Plant operations, startup,
+        standby, etc. 
+        
+        Inputs:
[…]

### 2021-06-17 simulations/modules/GenericSSCModule.py

@@ -22,7 +22,6 @@ import copy
 from abc import ABC
 
 class GenericSSCModule(ABC):
-    
     """
     The GenericSSCModule class works as a way to intialize, update, and
     run SSC simulations through PySAM. 
@@ -487,6 +486,9 @@ class GenericSSCModule(ABC):
         
         ** self.is_dispatch == True 
         (Called within simulation)
+        
+        Outputs:
+            dispatch_wrap (obj) : wrapper object for the class that creates dispatch parameters
         
         This method is creates the Dispatch Parameter dictionary that will be 
         populated with static inputs from SSC_dict as well as initial conditions

### 2021-06-17 simulations/modules/NuclearTES.py

@@ -16,9 +16,20 @@ import PySAM.PySSC as pssc
 from util.FileMethods import FileMethods
 import copy
 
-class NuclearTES(GenericSSCModule):
+class NuclearTES(GenericSSCModule): 
+    """
+    The NuclearTES class intializes, updates, and runs SSC simulations through PySAM,
+    specifically for the SSC NuclearTES module. 
+    """
     
     def __init__(self, plant_name="nuclear_tes", json_name="model1", is_dispatch=False):
+        """ Initializes the NuclearTES module
+        
+        Inputs:
+            plant_name (str)         : name of SSC module to run 
+            json_name (str)          : name of JSON script with input data for module
+            is_dispatch (bool)       : boolean, if True runs Pyomo dispatch optimization
+        """
         
         # initialize Generic module, csv data arrays should be saved here
         GenericSSCModule.__init__( self, plant_name, json_name, is_dispatch )
@@ -27,8 +38,14 @@ class NuclearTES(GenericSSCModule):
     def store_csv_arrays(self, input_dict):
         """ Method to get data from specified csv files and store in class
         
+        This method uses the designated PySAM inputs from a JSON script to extract
+        csv arrays for use in SSC. The PySAM inputs used here are relative filepaths
+        to find the respective csv files. We then either save the filepath as a variable
+        or extract the data from the named csv file and save it to as a member attribute
+        of this NE2 module class.
+        
         Inputs:
-            input_dict (dict) : dictionary with csv file names
+            input_dict (dict) : dictionary with csc relative filepaths
         """
         
         # saving location of solar resource file for SSC input using parent class def
@@ -47,6 +64,12 @@ class NuclearTES(GenericSSCModule):
         
     def create_Plant(self):
         """ Method to create Plant object for the first time
+        
+        This method creates a Plant object using built-in PySAM functionalities
+        (including some former PySSC structures). Essentially, it creates some
+        sort of data structure (pointer?) from SSC inputs found in the SSC_dict
+        and the specified SSC module. That data structure is then used to create
+        a PySAM module for the specified SSC Plant module (TCSMolten_Salt, etc.). 
         """
         
         # create plant data encoding for generic system
@@ -69,8 +92,11 @@ class NuclearTES(GenericSSCModule):
     def create_Grid(self):
         """ Method to create Grid object for the first time
         
-        Inputs:
-            plant (obj) : object representing Plant
[…]

### 2021-06-17 simulations/util/FileMethods.py
even more documentation

@@ -9,6 +9,10 @@ Created on Fri Apr  2 09:23:58 2021
 import pandas, os, json
 
 class FileMethods(object):
+    """
+    The FileMethods class is a util class used generally to read and write data
+    from and to files. This can be csv, text, maybe LaTeX files in the future. 
+    """
     
     #defining directory where this particular file is located and other useful directories
     util_dir     = os.path.dirname(os.path.realpath(__file__))
@@ -25,6 +29,7 @@ class FileMethods(object):
         Outputs:
             data_array (list) : data in either list (SSC_ARRAY) or nested list (SSC_MATRIX) form
         """
+        
         dataframe = pandas.read_csv(filepath,header=None) #important: No Header assumed
         
         #recasting dataframe to a 1D numpy array if there is only 1 columnn in csv (SSC ARRAY)
@@ -38,14 +43,25 @@ class FileMethods(object):
 
 
     def read_solar_resource_file(filepath, unit_registry):
+        """ Method to read csv file and return data array
+        
+        Inputs:
+            filepath (str)               : full path to file
+            unitRegistry (pint.registry) : unique unit Pint unit registry
+        Outputs:
+            t_dry (float Quant) : dry bulb temperature (in deg K)
+        """
         
         # setting a standard unit registry
         u = unit_registry 
         
+        # import csv dataframe
         dataframe = pandas.read_csv(filepath,header=2)
         
+        # extract Temperature from dataframe
         data = dataframe['Temperature']
         
+        # convert to proper data structure with units in deg C
         t_dry = data.to_numpy() * u.degC
         
         return t_dry.to('kelvin')
@@ -61,6 +77,7 @@ class FileMethods(object):
             ssc_dict (dict) : dictionary of SSC inputs needed to run modules
             out_dict (dict) : dictionary of PySAM output keywords for extraction
         """
+        
         #defining filepath for JSON script (FUTURE: add non-default functionality to input whole path)
         samsim_dir = FileMethods.samsim_dir
         json_filepath = os.path.join( samsim_dir, "json", json_name)
@@ -76,6 +93,7 @@ class FileMethods(object):
         out_dict   = D['PySAM_outputs']
         
         return pysam_dict, ssc_dict, out_dict
+
 
     def write_csv(data_list, columns, filename):
         """ Method to write csv file 

### 2021-06-17 simulations/util/FileParser.py

@@ -11,6 +11,12 @@ from util.FileMethods import FileMethods
 import pyomo as pyo
 
 class FileParser(object):
+    """
+    The FileParser class is a util class used generally to manipulate text data
+    in files. Some main features is the ability to search existing Python class
+    files for particular strings. Currently using regex to search for complex
+    strings, don't yell at me please.
+    """
     
     # Regex rules for parsing through dispatch files (e.g. GeneralDispatch, NuclearDispatch)
     param_latex_regex  = r'\s#([\w+\d+\{\}\^\\\,-]+):\s'           # Matches parameter names in LaTeX form
@@ -278,6 +284,8 @@ class FileParser(object):
         Excel sheet called "Raw Data" in an xlsx file specified by the user input.
         Output file will be written in the simulations/outputs folder. Excel sheet 
         will have three columns: Parameter name, its value, and a txt description.
+        
+        TODO: perhaps this method belongs in FileMethods?
         
         Inputs:
             model (PyomoModel)  : Pyomo model after execution

### 2021-06-17 simulations/util/PySSCWrapper.py

@@ -12,7 +12,35 @@ import os, json
 import numpy as np
 
 class PySSCWrapper(object):
+    """
+    The PySSCWrapper class is a util class used to run PySSC from a given JSON
+    script (similar to what we're doing in the PySAM NE2 modules). The main 
+    use-case for this method is mixed-mode debugging:
+        (1) choose an existing script from the /scripts directory that calls this method
+        (2) run the script
+        (3) PySSCWrapper class is initialized
+        (4) PySSCWrapper creates PySSC data structures and modules
+        (5) PySSC calls SSC
+        (6) We can debug SSC if we're running it through CodeLite or Eclipse
+    
+    For more information: https://github.com/uw-esolab/docs/blob/main/sam/debugSSCwithPySSC_Linux_CodeLiteIDE.md
+    
+    To ensure the debug version of SSC, look into the https://github.com/uw-esolab/neup-ies/build_debug_SAM bash script
+    """
+    
     def __init__(self, json_name='model1', is_debug=True):
+        """ Initializes the PySSCWrapper module
+        
+        This method initialized the PySSCWrapper module. If we intend to run
+        in debug mode, the flag used as input ensures we point to the correct
+        version of the SSC library (libSSCd.so file which is the Debug version
+        rather than the Release version). The method also finds and extracts
+        information from the specified JSON script. 
+        
+        Inputs:
+            json_name (str)  : name of JSON script with input data for module
+            is_debug (bool)  : flag to determine if running in debug mode
+        """
         
         self.is_debug = is_debug
         
@@ -30,10 +58,17 @@ class PySSCWrapper(object):
         
         #extracting specific dicts nested inside the JSON script
         self.pysam_dict = D['PySAM_inputs']
-        self.sscdict   = D['SSC_inputs']
+        self.sscdict    = D['SSC_inputs']
 
 
     def run_sim(self):
+        """ Method to run full SSC simulation through PySSC
+        
+        This method creates an SSC API, saves input data from the specified
+        JSON script to it and runs a full SSC simulation through PySSC. Much
+        like PySAM, it creates a Plant, Grid, and Financial module and runs
+        each in order. 
+        """
         
         # creating SSC API and Data object(?) for PySSC
         self.create_API()
@@ -58,12 +93,27 @@ class PySSCWrapper(object):
 
     
     def create_API(self):
+        """ Method to create and save a unique SSC API to self
+        
+        This method also ensures we use the correct SSC library file, whether
[…]

### 2021-06-17 simulations/util/SSCHelperMethods.py

@@ -11,6 +11,12 @@ import pint
 from pyomo.environ import units
 
 class SSCHelperMethods(object):
+    """
+    The SSCHelperMethods class is a util class for any auxilliary methods that 
+    help us link up better with SSC or create better inputs for SSC. Typically
+    for methods that can be used across all modules and dispatchers, so better
+    to keep in one designated area. 
+    """
     
     def define_unit_registry():
         """ Method to define unique unit registry from Pint

### 2021-06-17 simulations/modules/GenericSSCModule.py
new variable and fewer inputs to log_arrays
storing slice objects for the normal SSC Horizon and the moving SSC Horizon relative to the simulation time

@@ -246,6 +246,10 @@ class GenericSSCModule(ABC):
         # setting index for subsequent calls, it's just a static index for log arrays
         self.t_ind = int(time_next.to('hr').m)
         
+        # slice for the first indeces of the SSC Horizon, also initializing current Horizon (updated in loop)
+        self.sscFirstHorizon   = slice( 0, self.t_ind,1)
+        self.sscCurrentHorizon = slice( int( time_start.to('hr').m ), self.t_ind, 1)  
+        
         # setting up empty log array for log arrays
         self.initialize_arrays()
         
@@ -266,13 +270,17 @@ class GenericSSCModule(ABC):
         # this loop should only be entered if run_loop == True
         while (time_next < time_end):
             
-            # time-printer
-            print_time = int(time_next.to('d').magnitude)
-            if not print_time % 10: print('   [%s / %s] completed.' % (print_time, np.round(time_end.to('d').m)) )
-            
             # update time
             time_start += self.ssc_horizon.to('s')
             time_next  += self.ssc_horizon.to('s')
+            
+            # update the current slice of SSC Horizon relative to full simulation
+            self.sscCurrentHorizon = slice( int( time_start.to('hr').m ), 
+                                            int( time_next.to('hr').m  ), 1)  
+        
+            # time-printer
+            print_time = int(time_next.to('d').magnitude)
+            if not print_time % 10: print('   [%s / %s] completed.' % (print_time, np.round(time_end.to('d').m)) )
             
             # update Plant parameters after previous run
             self.update_Plant_after_SSC( )
@@ -309,18 +317,19 @@ class GenericSSCModule(ABC):
             end_hr (float Quant)   : ending time for next simulation (hours)
         """
         
-        # start and end times for full simulation
+        
         i_start = int( start_hr.to('hr').m )
         i_end   = int( end_hr.to('hr').m )
         
+        # start and end times for full simulation
         self.Plant.SystemControl.time_start = start_hr.to('s').magnitude
-        self.Plant.SystemControl.time_stop = end_hr.to('s').magnitude
+        self.Plant.SystemControl.time_stop  = end_hr.to('s').magnitude
         
         self.Plant.execute()
         
         # logging SSC outputs to arrays that have already been initialized
         if self.run_loop:
-            self.log_SSC_arrays(i_start, i_end)
+            self.log_SSC_arrays()
         else:
[…]

### 2021-06-17 simulations/modules/GenericSSCModule.py
new slice feature for indexing current segment
adding this slice object as inputs to methods intended to update PySAM parameters with time series data

@@ -247,8 +247,9 @@ class GenericSSCModule(ABC):
         self.t_ind = int(time_next.to('hr').m)
         
         # slice for the first indeces of the SSC Horizon, also initializing current Horizon (updated in loop)
-        self.sscFirstHorizon   = slice( 0, self.t_ind,1)
-        self.sscCurrentHorizon = slice( int( time_start.to('hr').m ), self.t_ind, 1)  
+        self.slice_ssc_firstH   = slice( 0, self.t_ind,1)
+        self.slice_ssc_currentH = slice( int( time_start.to('hr').m ), self.t_ind, 1)  
+        self.slice_pyo_currentH = slice( int( time_start.to('hr').m ), int( self.pyomo_horizon.to('hr').m ), 1) 
         
         # setting up empty log array for log arrays
         self.initialize_arrays()
@@ -256,12 +257,12 @@ class GenericSSCModule(ABC):
         # run dispatch optimization for the first time
         if self.is_dispatch:
             # create dispatch parameters for the first time
-            disp_params = self.create_dispatch_params()
+            disp_params = self.create_dispatch_params( self.slice_pyo_currentH )
             
             # run pyomo optimization
             self.run_pyomo(disp_params)
             
-            # updating SSC inputs using Pyomo outputs
+            # update: Pyomo(t) -> Plant(t) 
             self.update_Plant_after_Pyomo()
         
         # first execution of Plant through SSC
@@ -275,30 +276,33 @@ class GenericSSCModule(ABC):
             time_next  += self.ssc_horizon.to('s')
             
             # update the current slice of SSC Horizon relative to full simulation
-            self.sscCurrentHorizon = slice( int( time_start.to('hr').m ), 
-                                            int( time_next.to('hr').m  ), 1)  
-        
+            self.slice_ssc_currentH = slice( int( time_start.to('hr').m ), 
+                                             int( time_next.to('hr').m  ), 1)  
+            # update the current slice of Pyomo Horizon relative to full simulation
+            self.slice_pyo_currentH = slice( int( time_start.to('hr').m ), 
+                                             int( (time_start + self.pyomo_horizon).to('hr').m  ), 1)  
+            
             # time-printer
             print_time = int(time_next.to('d').magnitude)
             if not print_time % 10: print('   [%s / %s] completed.' % (print_time, np.round(time_end.to('d').m)) )
             
-            # update Plant parameters after previous run
+            # update: SSC(t) -> Plant(t+1)
             self.update_Plant_after_SSC( )
             
[…]

### 2021-06-17 simulations/modules/NuclearTES.py

@@ -166,31 +166,32 @@ class NuclearTES(GenericSSCModule):
         return dispatch_wrap
 
     
-    def create_dispatch_params(self):
+    def create_dispatch_params(self, current_pyomo_slice):
         """ Populating a dictionary with dispatch parameters before optimization
         
         ** self.is_dispatch == True 
         (Called within simulation)
-
-        Outputs:
-            dispatch_wrap (obj) : wrapper object for the class that creates dispatch parameters
         
         This method is creates the Dispatch Parameter dictionary that will be 
         populated with static inputs from SSC_dict as well as initial conditions
         for Dispatch optimization. The initial conditions are continuously updated
         if simulation is segmented.
+
+        Inputs:
+            current_pyomo_slice (slice) : range of current pyomo horizon (ints representing hours)
+        Outputs:
+            dispatch_wrap (obj) : wrapper object for the class that creates dispatch parameters
         """
         
         # get the object
         DW = self.dispatch_wrap
         
         # run the setters from the GenericSSCModule parent class
-        params = GenericSSCModule.create_dispatch_params(self)
+        params = GenericSSCModule.create_dispatch_params(self, current_pyomo_slice)
         
         # these are NuclearTES-specific setters
         params = DW.set_nuclear_parameters( params )
-        params = DW.set_time_series_nuclear_parameters( params, self.solar_resource_file, 
-                                                       self.df_array, self.ud_array )
+        params = DW.set_time_series_nuclear_parameters( params, self.df_array, self.ud_array, current_pyomo_slice )
         
         # this sets the initial set for the NuclearTES
         params = DW.set_initial_state( params )
@@ -198,7 +199,7 @@ class NuclearTES(GenericSSCModule):
         return params
 
 
-    def update_Pyomo_after_SSC(self, params):
+    def update_Pyomo_after_SSC(self, params, current_pyomo_slice):
         """ Update Pyomo inputs with SSC outputs from previous segment simulation
         
         ** self.run_loop    == True
@@ -210,7 +211,8 @@ class NuclearTES(GenericSSCModule):
         of the Dispatch parameter dictionary. 
         
         Inputs:
-            params (dict) : dictionary of Pyomo dispatch parameters
+            params (dict)               : dictionary of Pyomo dispatch parameters
+            current_pyomo_slice (slice) : range of current pyomo horizon (ints representing hours)
         Outputs:
[…]

### 2021-06-17 simulations/dispatch/GeneralDispatch.py
updates dry bulb temperature and price at each segment
time series was not indexed correctly before, now price and tdry get updated for each new simulation segment

@@ -12,7 +12,7 @@ Model authors:
 Pyomo code by Alex Zolan
 Modified by Gabriel Soto
 """
-import pyomo
+import os
 import pyomo.environ as pe
 import numpy as np
 from util.FileMethods import FileMethods
@@ -517,6 +517,11 @@ class GeneralDispatchParamWrap(object):
         
         # setting a standard unit registry
         self.u = unit_registry 
+        
+        # retrieving the dry bulb temperature values in the SAM directory
+        parent_dir = FileMethods.parent_dir
+        self.solar_resource_file = os.path.join(parent_dir, self.PySAM_dict['solar_resource_rel_parent']) 
+        self.Tdry = FileMethods.read_solar_resource_file(self.solar_resource_file, self.u) 
         
         self.set_design()
         

### 2021-06-17 simulations/dispatch/NuclearDispatch.py

@@ -17,7 +17,7 @@ from dispatch.GeneralDispatch import GeneralDispatchParamWrap
 import numpy as np
 from util.FileMethods import FileMethods
 from util.SSCHelperMethods import SSCHelperMethods
-import copy
+import os, copy
 
 class NuclearDispatch(GeneralDispatch):
     """
@@ -146,7 +146,7 @@ class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
         return param_dict
     
     
-    def set_time_series_nuclear_parameters(self, param_dict, solar_resource_filepath, df_array, ud_array):
+    def set_time_series_nuclear_parameters(self, param_dict, df_array, ud_array, current_pyomo_slice):
         """ Method to set fixed costs of the Plant for Dispatch optimization
         
         This method calculates some time series parameters for the Plant operations, startup,
@@ -156,9 +156,9 @@ class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
         
         Inputs:
             param_dict (dict)             : dictionary of Pyomo dispatch parameters
-            solar_resource_filepath (str) : filepath to the solar resource file (typically in SAM)
             df_array (array)              : array of user defined dispatch factors over simulation time
             ud_array (list of list)       : table of user defined data as nested lists
+            current_pyomo_slice (slice)   : range of current pyomo horizon (ints representing hours)
         Outputs:
             param_dict (dict) : updated dictionary of Pyomo dispatch parameters
         """
@@ -167,8 +167,7 @@ class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
         u = self.u
         
         self.Drsu       = self.PySAM_dict['Dnsu']*u.hr   # Minimum time to start the receiver (hr)
-        self.P          = df_array*u.USD/u.kWh
-        self.Qin        = np.array([self.q_rec_design.magnitude]*self.T)*self.q_rec_design.units
+        self.Qin        = np.array([self.q_rec_design.magnitude]*self.T)*self.q_rec_design.units #TODO: update at each segment
         self.Qc         = self.Ec / np.ceil(self.SSC_dict['startup_time']*u.hr / np.min(self.Delta)) / np.min(self.Delta) #TODO: make sure Ec is called correctly
         self.Wdotnet    = [1.e10 for j in range(self.T)] *u.kW
[…]

### 2021-06-17 simulations/data/ARMA/extract_data.py
Creating new data parser script for temperature

@@ -3,11 +3,13 @@ import pandas as pd
 import datetime
 
 # Open  data file
-data_file_name = "tucson_az_32.116521_-110.933042_psmv3_60_tmy.csv"
+data_file_name = "862903_43.09_-89.42_2018.csv"
 data_file = pd.read_csv(data_file_name, header=2).astype(int)
 
 # Extract DHI solar data
-target_data = data_file["Temperature"]
+target_data = data_file["Temperature"].astype(float)
+
+print(target_data.loc[[0]])
 
 # Extract time data
 date=pd.to_datetime(data_file[['Year', 'Month', 'Day', 'Hour', 'Minute']])
@@ -21,4 +23,4 @@ time_data=delta.dt.total_seconds().abs() //60
 full_data = pd.concat([time_data, target_data], axis=1, ignore_index=True)
 
 # Write to a new .csv file
-full_data.to_csv(r'/home/una/github/postdoc_uw_madison/NE2/sam_dev/neup-ies/simulations/data/ARMA/temp_parsed_data.csv', header=["Time", "Temperature"], index = False)
+full_data.to_csv(r'/home/una/github/postdoc_uw_madison/NE2/sam_dev/neup-ies/simulations/data/ARMA/parsed_data.csv', header=["Time", "Temperature"], index = False)

### 2021-06-17 simulations/data/ARMA/solar_data.py

@@ -3,11 +3,11 @@ import pandas as pd
 import datetime
 
 # Open  data file
-data_file_name = "tucson_az_32.116521_-110.933042_psmv3_60_tmy.csv"
+data_file_name = "862903_43.09_-89.42_2018.csv"
 data_file = pd.read_csv(data_file_name, header=2).astype(int)
 
 # Extract DHI solar data
-target_data = data_file["Temperature"]
+solar_data = data_file["DHI"]
 
 # Extract time data
 date=pd.to_datetime(data_file[['Year', 'Month', 'Day', 'Hour', 'Minute']])
@@ -18,7 +18,8 @@ delta=(pd.to_datetime(data_file['Year'].astype(str)+'-01-01')-date)
 time_data=delta.dt.total_seconds().abs() //60
 
 # Concatenate time data and solar data
-full_data = pd.concat([time_data, target_data], axis=1, ignore_index=True)
+full_data = pd.concat([time_data, solar_data], axis=1, ignore_index=True)
 
 # Write to a new .csv file
-full_data.to_csv(r'/home/una/github/postdoc_uw_madison/NE2/sam_dev/neup-ies/simulations/data/ARMA/temp_parsed_data.csv', header=["Time", "Temperature"], index = False)
+full_data.to_csv(r'/home/una/github/postdoc_uw_madison/NE2/sam_dev/neup-ies/simulations/data/solar_data_parsed.csv', header=["Time", "DHI"], index = False)
+# Write solar data with new time points

### 2021-06-25 simulations/modules/GenericSSCModule.py
moving instantiation of dictionaries in init
making it easier to reassign values after running init

@@ -61,15 +61,16 @@ class GenericSSCModule(ABC):
         
         # read in dictionaries from json script
         PySAM_dict, SSC_dict, output_keys = FileMethods.read_json( self.json_name )
+
+        # save SSC_dict for usage later
+        self.SSC_dict = SSC_dict
+        self.PySAM_dict = PySAM_dict
         
         # storing SSC and Pyomo time horizons, inputs are in unit of hours
         self.ssc_horizon   = PySAM_dict['ssc_horizon'] * u.hr
         self.pyomo_horizon = PySAM_dict['pyomo_horizon'] * u.hr
         self.output_keys   = output_keys
         self.dispatch_time_step = dispatch_time_step * u.hr
-        
-        # save SSC_dict for usage later
-        self.SSC_dict = SSC_dict
         
         # save csv arrays to class 
         self.store_csv_arrays( PySAM_dict )
@@ -88,7 +89,7 @@ class GenericSSCModule(ABC):
             self.disp_results = {}
             
             # initialize dispatch wrap class
-            self.dispatch_wrap = self.create_dispatch_wrapper( PySAM_dict )
+            self.dispatch_wrap = self.create_dispatch_wrapper( self.PySAM_dict )
 
 
     def run_sim(self, run_loop=False, export=False, filename='temp.csv'):

### 2021-06-25 simulations/util/PostProcessing.py
fix in plotting and new method to calculate rho
new helper method to calculate rho of HTF based on temperature

@@ -241,7 +241,7 @@ class Plots(object):
         ax.legend(loc=self.loc, fontsize=self.fsl)
 
         # plot Defocus array
-        ax2 = self.plot_SSC_generic(ax2, ['defocus'], ['Defocus'], 'Defocus (fraction)', None, \
+        ax2 = self.plot_SSC_generic(ax2, ['defocus'], ['Defocus'], 'Defocus', None, \
                                             plot_all_time, start_hr, end_hr )
         
         # plot legend for Energy arrays and also set line color to default C3 (reddish)

### 2021-06-25 simulations/util/SSCHelperMethods.py

@@ -205,14 +205,49 @@ class SSCHelperMethods(object):
         
         T = T.to('kelvin')
         
-        a = -1.0e-10*u.J/u.g/u.kelvin**4
-        b = 2.0e-7*u.J/u.g/u.kelvin**3
-        c = 5.0e-6*u.J/u.g/u.kelvin**2
-        d = 1.4387*u.J/u.g/u.kelvin
+        a = -1.0e-10 * u.J/u.g/u.kelvin**4
+        b =  2.0e-7  * u.J/u.g/u.kelvin**3
+        c =  5.0e-6  * u.J/u.g/u.kelvin**2
+        d =  1.4387  * u.J/u.g/u.kelvin
         
         cp = (a*T**3 + b*T**2 + c*T + d).to('J/g/kelvin')
         
         return cp 
+
+
+    def get_rho_htf( u, T, rec_htf):
+        """ Method to calculate density of some heat transfer fluid 
+        
+        This method calculates density at average temperature for a heat transfer
+        fluid. In our case, we use molten salt. This method is copied from SSC,
+        specifically the htf_props cpp method. 
+        
+        Inputs:
+            u (unitRegistry) : Pint unit registry
+            T (float Quant)  : Temperature at which to find specific heat of HTF, in units of Kelvin
+            rec_htf (int)    : integer value representing HTF in SSC table
+        Outputs:
+            rho (float Quant) : fluid density value in kg/m^3
+            
+        """
+        
+        # HTF: 17 = Salt (60% NaNO3, 40% KNO3)
+        if rec_htf != 17:
+            print ('HTF %d not recognized'%rec_htf)
+            return 0.0
+        
+        T = T.to('kelvin')
+
+        a = -1.0e-07 * u.kg/u.m**3/u.kelvin**3
+        b =  0.0002  * u.kg/u.m**3/u.kelvin**2
+        c = -0.7875  * u.kg/u.m**3/u.kelvin
+        d =  2299.4  * u.kg/u.m**3
+        
+        rho = (a*T**3 + b*T**2 + c*T + d).to('kg/m^3')
+        
+        # rho = np.max(rho, 1000.0*u.kg/u.m**3)
+        
+        return rho 
 
 
     def get_ambient_T_corrections_from_udpc_inputs( u, Tamb, ud_array):

### 2021-06-25 simulations/scripts/output_scripts/psweep_nucTES_sizingTES.py
new subdirectory and parameter sweep for TES size
new subdirectory for scripts, meant to just generate output data, media, etc. This one sweeps through NucTES and tries to size the TES

@@ -1,0 +1,174 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Jun 24 14:05:11 2021
+
+@author: gabrielsoto
+"""
+
+
+import modules.NuclearTES as NuclearTES
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+from pylab import rc
+rc('axes', linewidth=2)
+rc('font', weight='bold',size=12)
+from util.SSCHelperMethods import SSCHelperMethods
+
+pid = os.getpid()
+print("PID = ", pid)
+
+
+# =============================================================================
+#     Set Up
+# =============================================================================
+
+nuctes = NuclearTES.NuclearTES(is_dispatch=True)
+u = nuctes.u
+
+T_tes_hot  = (nuctes.SSC_dict['T_tank_hot_init']  * u.degC ).to('degK')
+T_tes_cold = (nuctes.SSC_dict['T_tank_cold_init'] * u.degC ).to('degK')
+tshours       = nuctes.SSC_dict['tshours'] * u.hr
+q_nuc_thermal = nuctes.SSC_dict['q_dot_nuclear_des'] * u.MW
+h_min   = nuctes.SSC_dict['h_tank_min'] * u.m
+h_tank  = nuctes.SSC_dict['h_tank'] * u.m
+n_tanks = nuctes.SSC_dict['tank_pairs']
+u_tank  = nuctes.SSC_dict['u_tank'] * u.W / (u.m**2 * u.K)
+
+# =============================================================================
+#    Run Simulation
+# =============================================================================
+
+# setting up arrays to cycle through
+tshours   = np.array([ 5., 7.5, 10., 12.5, 15.]) * u.hr
+num_tanks = np.array([  1,   5,  10,   15, 20])
+
+iterator1 = tshours
+iterator2 = num_tanks
+
+empty = np.zeros([  len(iterator1), len(iterator2) ])
+
+dtank_array    = empty.copy()
+qdotLoss_array = empty.copy() 
+
+for i,th in enumerate(iterator1):
+    for j,N in enumerate(iterator2):
+        
+        # print current position in loop
+        print("tshours :         ", th)
+        print("number of tanks : ", N)
+        
[…]

### 2021-07-13 simulations/scripts/output_scripts/ANS2021Winter/generate_psweep_nucTES_powerProductionCurve.py
fixed top x-axis

@@ -105,7 +105,7 @@ start = 0
 end   = 48*4
 
 # calling plots
-upl.plot_SSC_power_and_energy(ax=ax1, plot_all_time=fullTime, start_hr=start, end_hr=end, x_legend=1.175, y_legend_L=1.0, y_legend_R=0.2 )
+upl.plot_SSC_power_and_energy(ax=ax1, plot_all_time=fullTime, start_hr=start, end_hr=end, x_legend=1.175, y_legend_L=1.0, y_legend_R=0.2, hide_x=True )
 upl.plot_SSC_op_modes(        ax=ax2, plot_all_time=fullTime, start_hr=start, end_hr=end, x_legend=1.175, y_legend_L=1.0)
 
 

### 2021-07-13 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py
updating plotting of 2D pricing heatmap
also uploading a file of data that took me 6 hrs to make, kind of annoying to re-run

@@ -52,94 +52,116 @@ lcoe_nom_array      = Storage['lcoe_nom_array']
 # Plots
 # =============================================================================
 
-wiPyomo24 = tuple( [0,range(len(iterator1)),range(len(iterator2))] )
-wiPyomo48 = tuple( [1,range(len(iterator1)),range(len(iterator2))] )
-woPyomo   = tuple( [2,range(len(iterator1)),range(len(iterator2))] )
+## can we automate this:
+    # look through types of dispatch
+    #     find optimal value in each run
+    #     compare between each
+    #     print out optimum
+    # plot 2D map of dispatch type that lead to optimum
+    # plot the other two as contours
 
-x_array = P_ref*iterator2
+# creating figure object
+fig = plt.figure(constrained_layout=True)
+ax = fig.gca()
 
-array_list = [ ppa_array,
-               lcoe_nom_array ]
+#===================================
+# plotting 2D heat map for Qdot losses, with interpolation
+im = ax.imshow(lcoe_nom_array[2].T, origin='lower', interpolation='bicubic')
 
-colormarkers = ['C1', 'C2']
+# creating colorbar for the 2D heatmap with label
+cb = fig.colorbar(im, ax=ax)
+# cb.set_label(r'$\dot{q}^{L}_{TES}$ (MW)', fontweight = 'bold')
 
-label_list = [ 'PPA Price',
-               'LCOE Nom' ]
+# setting tick marks for x and y axes
+ax.set_xticks(range(len(iterator1)))
+ax.set_xticklabels(iterator1)
+ax.set_yticks(range(len(iterator2)))
+ax.set_yticklabels(iterator2)
 
-lw = 2
+# x_array = P_ref*iterator2
 
-# Energy Outputs
-fig = plt.figure(figsize=(12,8))
-ax1 = fig.add_subplot(211)
-ax2 = fig.add_subplot(212)
-# ax = fig.gca()
-ax1.plot( x_array, annual_energy_array[woPyomo] , 'C0',    linewidth = lw,  label='No Pyomo'  )
-ax1.plot( x_array, annual_energy_array[wiPyomo48] , 'C0--',  linewidth = lw,  label='w/ Pyomo 48 hr'  )
[…]

### 2021-07-14 papers/white-cycle-modeling/modeling-of-combined-lfr-csp-sco2-paper/content.tex
uploading paper LaTex files
Updates to Paper 6-25-21
Paper edits and adding-organizing the cycle ees models

--- 2021-05-27 papers/white-cycle-modeling/content.tex
@@
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
+%\section{How to Use this Template}
 
-The template details the sections that can be used in a manuscript.
+%The template details the sections that can be used in a manuscript.
 Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
@@
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
+%The introduction should briefly place the study in a broad context and highlight why it is important.
 It should define the purpose of the work and its significance.
@@
 As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{wagner2017optimization} .
-Now citing a book reference \cite{blair2005sam} or other reference types \cite{hirsch2011standardization}.
 %Please use the command \citep{} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.
@@
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+%Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
 Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
@@
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
+%Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
 If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
@@
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+%Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+%\begin{quote}
+%This is an example of a quote.
+%\end{quote}
+
+\subsection{Cycle Component Modeling}
+
+\subsubsection{Heat Exchangers}
+\subsubsection{Turbines}
+\subsubsection{Compressors}
+\subsubsection{Concentrating Solar Power Cycle}
+
+\subsection{Cycle Models}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
+%This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+
+\subsection{Cycle Configurations} %========================================
+
+\begin{specialtable}[H] 
+    \caption{Constant cycle parameters with definition, variable and set value. The variables with (*) have changing labels depending on the specific cycle diagram. \label{cycle-constants}}
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
+    \midrule
+    \textit{Efficiencies}\\
+    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
+    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
+    Turbine & $\eta_{T}$		& 0.90 (-)\\
+    Pump & $\eta_{P}$      & 0.90 (-)\\
+    \midrule
+    \textit{Approach Temperatures}\\
+    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
+    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
+    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
+    \midrule
+    \textit{Pressures}\\
+    Pressure Ratio & $PR$ & 3.27 (-)\\
+    High Side Pressure & (*) & 2.88e7 (Pa)\\
+    \midrule
+    \textit{Heat Into System}\\
+    Lead-Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
+    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
+    \midrule
+    \textit{Temperature}\\
+    Main Compressor Inlet & (*) & 313.2 (K)\\
+    Lead-Fast Reactor Low Temperature & (*) & 673.2 (K)\\
+    \midrule
+    \textit{Pumps}\\
+    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
+    Pump Low Side Pressure & (*) & 3.0e6 (Pa)\\ 
+    \bottomrule
+    \end{tabular}
+\end{specialtable}
+
+\subsubsection{C-LFR-ON} %--------------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
+    \caption{Diagram for C-LFR-ON with focus on electricity generation\label{c-lfr-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\begin{specialtable}[H] 
+    \caption{State points calculated at steady state operation and LFR low temperature constrained to 673.2 K for C-LFR-ON cycle. \label{c-lfr-on-tab-cons}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Diagram}	& \textbf{Temperature}	& \textbf{Pressure} &\textbf{Mass Flow} & \textbf{Enthalpy}\\
+    \textbf{Label} & \textbf{(K)} & \textbf{(Pa)} &\textbf{(kg/s)} & \textbf{(J/kg)}\\
+    \midrule
+    1a-A		& 313.2  & 8.807e6  & 3029  & -149660\\
+    1b-A		& 313.2  & 8.807e6  & 3029  & -149660\\
+    2a-A		& 374.2  & 2.88e7  & 3029  & -110393\\
+    2b-A		& 374.2  & 2.88e7  & 3029  & -110393\\
+    3a-A		& 438.2  & 2.88e7  & 3029  & 10618\\
+    3a-B		& 506.4  & 2.88e7  & 832.4  & 114847\\
+    3b  		& 451.9  & 2.88e7  & 3861  & 33089\\
+    3b-A		& 451.9  & 2.88e7  & 3861  & 33089\\
+    4a-A		& 673.2  & 2.88e7  & 3861  & 333669\\
+    4b  		& 673.2  & 2.88e7  & 3861  & 333669\\
+    5a  		& 868.2  & 2.88e7  & 3861  & 579720\\
+    5b  		& 868.2  & 2.88e7  & 3861  & 579720\\
+    6a  		& 722.8  & 8.807e6  & 3861  & 417482\\
+    6b  		& 722.8  & 8.807e6  & 3861  & 417482\\
+    7a  		& 722.8  & 8.807e6  & 3861  & 417482\\
+    7b  		& 722.8  & 8.807e6  & 3861  & 417482\\
+    8a  		& 461.9  & 8.807e6  & 3861  & 116902\\
+    8b  		& 461.9  & 8.807e6  & 3861  & 116902\\
+    9a  		& 384.2  & 8.807e6  & 3861  & 21981\\
+    9b-A		& 384.2  & 8.807e6  & 3029  & 21981\\
+    9b-B		& 384.2  & 8.807e6  & 834.2  & 21981\\
+    \bottomrule
+    \end{tabular}
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{Calculated Value}\\
+    \midrule
+    Cycle Efficiency (\%) & $\eta_{cycle}$ & 45.28\\
+    Alternator Power (W) & $\dot{W}_{A}$ & 4.302e8\\
+    PreCooler Heat Transfer (W) & $\dot{Q}_{PC}$ & 5.198e8\\
+    Main Compressor Power (W) & $\dot{W}_{MC}$ & 1.189e8\\ 
+    ReCompressor Power (W) & $\dot{W}_{RC}$ & 7.730e7\\ 
+    Turbine Power (W) & $\dot{W}_{T}$ & 6.264e8\\
+    Main Compressor Mass Flow Fraction (-) & $y_{1}$ & 0.7844\\
+    LTR UA Value (W/K) & $UA_{LTR}$ & 2.284e7\\
+    LTR Capacitance Ratio (-) & $CR_{LTR}$ & 0.8473\\
+    LTR Heat Transfer Rate (W) & $\dot{Q}_{LTR}$ & 3.665e8\\
+    LTR Effectiveness (-) & $\varepsilon_{LTR}$ & 0.8742\\
+    HTR UA Value (W/K) & $UA_{HTR}$ & 4.271e7\\
+    HTR Capacitance Ratio (-) & $CR_{HTR}$ & 0.9627\\
+    HTR Heat Transfer Rate (W) & $\dot{Q}_{HTR}$ & 1.161e9\\
+    HTR Effectiveness (-) & $\varepsilon_{HTR}$ & 0.9627\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\begin{specialtable}[H] 
+    \caption{State points calculated at steady state operation with LFR low temperature unconstrained and cycle efficiency maximized for C-LFR-ON cycle. \label{c-lfr-on-tab-unconst}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Diagram}	& \textbf{Temperature}	& \textbf{Pressure} &\textbf{Mass Flow} & \textbf{Enthalpy}\\
+    \textbf{Label} & \textbf{(K)} & \textbf{(Pa)} &\textbf{(kg/s)} & \textbf{(J/kg)}\\
+    \midrule
+    1a-A		& 313.2  & 8.807e6  & 2929  & -149660\\
+    1b-A		& 313.2  & 8.807e6  & 2929  & -149660\\
+    2a-A		& 374.2  & 2.88e7  & 2929  & -110393\\
+    2b-A		& 374.2  & 2.88e7  & 2929  & -110393\\
+    3a-A		& 505.7  & 2.88e7  & 2929  & 113832\\
+    3a-B		& 506.4  & 2.88e7  & 1255  & 114847\\
+    3b  		& 505.9  & 2.88e7  & 4184  & 114137\\
+    3b-A		& 505.9  & 2.88e7  & 4184  & 114137\\
+    4a-A		& 688.3  & 2.88e7  & 4184  & 352679\\
+    4b  		& 688.3  & 2.88e7  & 4184  & 352679\\
+    5a  		& 868.2  & 2.88e7  & 4184  & 579720\\
+    5b  		& 868.2  & 2.88e7  & 4184  & 579720\\
+    6a  		& 722.8  & 8.807e6  & 4184  & 417482\\
+    6b  		& 722.8  & 8.807e6  & 4184  & 417482\\
+    7a  		& 722.8  & 8.807e6  & 4184  & 417482\\
+    7b  		& 722.8  & 8.807e6  & 4184  & 417482\\
+    8a  		& 515.9  & 8.807e6  & 4184  & 178939\\
+    8b  		& 515.9  & 8.807e6  & 4184  & 178939\\
+    9a  		& 384.2  & 8.807e6  & 4184  & 21981\\
+    9b-A		& 384.2  & 8.807e6  & 2929  & 21981\\
+    9b-B		& 384.2  & 8.807e6  & 1255  & 21981\\
+    \bottomrule
+    \end{tabular}
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{Calculated Value}\\
+    \midrule
+    Cycle Efficiency (\%) & $\eta_{cycle}$ & 47.08\\
+    Alternator Power (W) & $\dot{W}_{A}$ & 4.473e8\\ 
+    PreCooler Heat Transfer (W) & $\dot{Q}_{PC}$ & 5.027e8\\
+    Main Compressor Power (W) & $\dot{W}_{MC}$ & 1.150e8\\ 
+    ReCompressor Power (W) & $\dot{W}_{RC}$ & 1.166e8\\ 
+    Turbine Power (W) & $\dot{W}_{T}$ & 6.789e8\\
+    Main Compressor Mass Flow Fraction (-) & $y_{1}$ & 0.7000\\
+    LTR UA Value (W/K) & $UA_{LTR}$ & 5.468e7\\
+    LTR Capacitance Ratio (-) & $CR_{LTR}$ & 0.9867\\
+    LTR Heat Transfer Rate (W) & $\dot{Q}_{LTR}$ & 6.568e8\\
+    LTR Effectiveness (-) & $\varepsilon_{LTR}$ & 0.92\\
+    HTR UA Value (W/K) & $UA_{HTR}$ & 4.829e7\\
+    HTR Capacitance Ratio (-) & $CR_{HTR}$ & 0.8657\\
+    HTR Heat Transfer Rate (W) & $\dot{Q}_{HTR}$ & 9.981e8\\
+    HTR Effectiveness (-) & $\varepsilon_{HTR}$ & 0.9544\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\subsubsection{C-CSP-ON} %--------------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-csp-on.pdf}
+    \caption{Diagram for C-CSP-ON with focus on electricity generation\label{c-csp-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsubsection{C-1HTR1T-ON} %-----------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
+    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsubsection{C-2HTR3T-ON} %-----------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-2htr3t-on.pdf}
+    \caption{Diagram for C-2HTR3T-ON with focus on electricity generation\label{c-2htr3t-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsection{Thermal Energy Storage Charging Techniques} %=========================
+
+\subsubsection{C-LFR-PRE} %-------------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-pre.pdf}
+    \caption{Diagram for C-LFR-PRE thermal energy storage charging orientation\label{c-lfr-pre}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsubsection{C-LFR-POST} %------------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-post.pdf}
+    \caption{Diagram for C-LFR-POST thermal energy storage charging orientation\label{c-lfr-post}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsubsection{C-LFR-PAR} %-------------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-par.pdf}
+    \caption{Diagram for C-LFR-PAR thermal energy storage charging orientation\label{c-lfr-par}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsubsection{C-LFR-CIRC} %------------------------------------------------------
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-circ.pdf}
+    \caption{Full diagram for C-LFR-CIRC thermal energy storage charging orientation\label{c-lfr-circ}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=10 cm]{Definitions/c-lfr-circ-sub.pdf}
+    \caption{Diagram for C-LFR-CIRC subcycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Discussion}
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{how to use}
+
 \subsection{Subsection}
+Citing a journal paper \cite{wagner2017optimization} . Now citing a book reference \cite{blair2005sam} or other reference types \cite{hirsch2011standardization}. \cite{nellis_klein_2008}
 \subsubsection{Subsubsection}
@@
 \nointerlineskip
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
+\begin{eqnarray}
+a &=& b + c + d + e + f + g + h + i + j + k + l\nonumber \\
+ &+& m + n + o + p + q + r + s + t + u + v + w + x + y + z %\nonumber
+\end{eqnarray}
 
 % Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
-\begin{figure}[H]	
-\widefigure
-\includegraphics[width=15 cm]{Definitions/logo-mdpi}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}
+%\begin{figure}[H]	
+%\widefigure
+%\includegraphics[width=15 cm]{Definitions/logo-mdpi}
+%\caption{This is a wide figure.\label{fig2}}
+%\end{figure}
 
@@
 \switchcolumn
-
 Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
-
 \end{paracol}

### 2021-07-14 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py
now plots multiple 2D heatmaps with additional contours
the heatmaps represent the results of a specific performance metrics, the contours show differences between that metric and the others

@@ -16,6 +16,7 @@ rc('font', weight='bold',size=12)
 u = pint.UnitRegistry()
 import pickle
 from util.FileMethods import FileMethods
+import matplotlib.cm as cm
 
 pid = os.getpid()
 print("PID = ", pid)
@@ -49,119 +50,158 @@ lcoe_nom_array      = Storage['lcoe_nom_array']
 
     
 # =============================================================================
-# Plots
+# Set Up Figures and Initialize Lists
 # =============================================================================
 
-## can we automate this:
-    # look through types of dispatch
-    #     find optimal value in each run
-    #     compare between each
-    #     print out optimum
-    # plot 2D map of dispatch type that lead to optimum
-    # plot the other two as contours
+# creating figure
+fig = plt.figure(figsize=[18.5,6])
+ax1 = fig.add_subplot(131)
+ax2 = fig.add_subplot(132)
+ax3 = fig.add_subplot(133)
 
-# creating figure object
-fig = plt.figure(constrained_layout=True)
-ax = fig.gca()
+# adjusting space between 
+plt.subplots_adjust(wspace=0.4)
 
-#===================================
-# plotting 2D heat map for Qdot losses, with interpolation
-im = ax.imshow(lcoe_nom_array[2].T, origin='lower', interpolation='bicubic')
+# names of dispatch scenarios
+dispatch_scenarios  = ['Pyomo - 24hr Horizon', 'Pyomo - 48hr Horizon', 'No Pyomo - SSC Only ']  
 
-# creating colorbar for the 2D heatmap with label
-cb = fig.colorbar(im, ax=ax)
-# cb.set_label(r'$\dot{q}^{L}_{TES}$ (MW)', fontweight = 'bold')
+# specific performance metrics to plot 
+performance_metrics = [annual_energy_array, ppa_array, lcoe_nom_array]
+N              = len(performance_metrics)
+get_max        = [True, False, False] # whether each performance is optimized with max or min
+axes           = [ax1,ax2,ax3] # list of axes
+heat_cmap_list = ['Blues', 'Blues_r', 'Blues_r'] # colormaps used for each performance metric
+metric_labels  = ['Annual Energy Production \n(TWh)',
+                  'PPA Price \n(cents/kWh)',
[…]

### 2021-07-14 simulations/scripts/output_scripts/generate_psweep_nucTES_pricePerformance_wDispatch.py
new financial outputs saved after running script
perhaps we want to save the final NE2 modules to the pickle file as well? would increase overhead but you'd have all the information available. need to delete them immediately as well to prevent memory leak

@@ -24,14 +24,14 @@ print("PID = ", pid)
 # setting up arrays to cycle through
 dispatch  = np.array([ True, True, False ])
 tshours   = np.array([ 10, 12, 14, 16, 18])
-p_mult    = np.array([ 1.05, 1.1, 1.15, 1.25, 1.35, 1.45])
+p_mult    = np.array([ 1.05, 1.15, 1.25, 1.35, 1.45])
+
+# SSC and dispatch horizons for each dispatch element above ^
+sscH = np.array([12, 24, 24])
+pyoH = np.array([24, 48, 48])
 
 # baseline cycle power output
 P_ref = 465
-
-# SSC and dispatch horizons
-sscH = np.array([12, 24, 24])
-pyoH = np.array([24, 48, 48])
 
 # formally defining the iterator arrays
 iterator1 = tshours 
@@ -44,6 +44,14 @@ empty = np.zeros([  len(dispatch) , len(iterator1), len(iterator2) ])
 annual_energy_array = empty.copy()
 ppa_array           = empty.copy()
 lcoe_nom_array      = empty.copy()
+npv_aftertax        = empty.copy()
+flip_actual_irr     = empty.copy()
+flip_actual_year    = empty.copy()
+irr_aftertax        = empty.copy()
+cost_installed      = empty.copy()
+size_of_equity      = empty.copy()
+size_of_debt        = empty.copy()
+
 
 # starting the time counter
 tic = time.perf_counter()
@@ -81,9 +89,16 @@ for d,dp in enumerate(dispatch): #over dispatch type
             
             # log outputs
             annual_energy_array[d,i,j] = (nt.Outputs.annual_energy*u.kWh).to('TWh').m
-            ppa_array[d,i,j] = so.Outputs.ppa
-            lcoe_nom_array[d,i,j]  = so.Outputs.lcoe_nom
-            
+            ppa_array[d,i,j]         = so.Outputs.ppa           # in cents/kWh
+            lcoe_nom_array[d,i,j]    = so.Outputs.lcoe_nom      # in cents/kWh
+            npv_aftertax[d,i,j]      = so.Outputs.project_return_aftertax_npv/1e6 #in million $
+            flip_actual_irr[d,i,j]   = so.Outputs.flip_actual_irr   # in %
+            flip_actual_year[d,i,j]  = so.Outputs.flip_actual_year  # in yr
+            irr_aftertax[d,i,j]      = so.Outputs.project_return_aftertax_irr  # in %
[…]

### 2021-07-16 simulations/scripts/output_scripts/generate_psweep_nucTES_pricePerformance_wDispatch.py
new metrics saved in generate script, specifying irr

@@ -82,6 +82,9 @@ for d,dp in enumerate(dispatch): #over dispatch type
             nuctes.SSC_dict['P_ref'] = fm*P_ref
             nuctes.SSC_dict['tshours'] = th
             
+            # update target IRR, nominal was 11% for CSP
+            nuctes.SSC_dict['flip_target_percent'] = 11
+            
             # run simulation
             nuctes.run_sim( run_loop=True )
             nt = nuctes.Plant

### 2021-07-16 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py

@@ -27,7 +27,7 @@ print("PID = ", pid)
 
 # locating output directory
 output_dir = FileMethods.output_dir
-filename   = 'pricePerfvsDispatch_sizingTESandCycle.nuctes' 
+filename   = 'pricePerfvsDispatch_sizingTESandCycle_irr11pct.nuctes' 
 NTPath = os.path.join(output_dir, filename)
 
 # pickling
@@ -47,7 +47,9 @@ pyoH         = Storage['pyoH']
 annual_energy_array = Storage['annual_energy_array'] 
 ppa_array           = Storage['ppa_array']
 lcoe_nom_array      = Storage['lcoe_nom_array']
-
+npv_aftertax = Storage['npv_aftertax']
+irr = Storage['irr_aftertax']
+irr_mean = np.mean(irr)
     
 # =============================================================================
 # Set Up Figures and Initialize Lists
@@ -55,6 +57,7 @@ lcoe_nom_array      = Storage['lcoe_nom_array']
 
 # creating figure
 fig = plt.figure(figsize=[18.5,6])
+fig.suptitle("IRR: {0:.1f}".format(irr_mean), fontsize=14)
 ax1 = fig.add_subplot(131)
 ax2 = fig.add_subplot(132)
 ax3 = fig.add_subplot(133)
@@ -66,14 +69,14 @@ plt.subplots_adjust(wspace=0.4)
 dispatch_scenarios  = ['Pyomo - 24hr Horizon', 'Pyomo - 48hr Horizon', 'No Pyomo - SSC Only ']  
 
 # specific performance metrics to plot 
-performance_metrics = [annual_energy_array, ppa_array, lcoe_nom_array]
+performance_metrics = [annual_energy_array, ppa_array, npv_aftertax]
 N              = len(performance_metrics)
 get_max        = [True, False, False] # whether each performance is optimized with max or min
 axes           = [ax1,ax2,ax3] # list of axes
 heat_cmap_list = ['Blues', 'Blues_r', 'Blues_r'] # colormaps used for each performance metric
 metric_labels  = ['Annual Energy Production \n(TWh)',
                   'PPA Price \n(cents/kWh)',
-                  'LCOE \n(cents/kWh)' ] # labels for each performance metric
+                  'NPV \n($M)' ] # labels for each performance metric
 
 # colormap for contours
 cmap_contour = cm.RdBu
@@ -136,72 +139,76 @@ for n in range(N):
[…]

### 2021-07-16 simulations/modules/NuclearTES.py
fixing plots and generalizing creating of PySAM plants

@@ -33,7 +33,9 @@ class NuclearTES(GenericSSCModule):
         
         # initialize Generic module, csv data arrays should be saved here
         GenericSSCModule.__init__( self, plant_name, json_name, is_dispatch )
-
+        
+        # define specific PySAM module to be called later
+        self.PySAM_Module = NuclearTes
         
     def store_csv_arrays(self, input_dict):
         """ Method to get data from specified csv files and store in class
@@ -76,7 +78,7 @@ class NuclearTES(GenericSSCModule):
         plant_dat = pssc.dict_to_ssc_table( self.SSC_dict, self.plant_name )
         
         # create new Plant object
-        self.Plant = NuclearTes.wrap(plant_dat)
+        self.Plant = self.PySAM_Module.wrap(plant_dat)
         
         # manually setting data arrays from csv files
         self.Plant.SolarResource.solar_resource_file         = self.solar_resource_file

### 2021-07-16 simulations/scripts/PySAM_model1.py

@@ -87,11 +87,11 @@ ax1 = fig.add_subplot(311)
 ax2 = fig.add_subplot(312)
 ax3 = fig.add_subplot(313)
 
-plot_full_time = True
+plot_all_time = True
 
-upl.plot_SSC_power_and_energy(ax1 )#, plot_full_time=plot_full_time, title_label='SSC Results - 48 hrs')
-upl.plot_SSC_op_modes(ax2) #, plot_full_time=plot_full_time)
-upl.plot_SSC_massflow(ax3) #, plot_full_time=plot_full_time)
+upl.plot_SSC_power_and_energy(ax1 , plot_all_time=plot_all_time, title_label='SSC Results - 48 hrs')
+upl.plot_SSC_op_modes(ax2, plot_all_time=plot_all_time)
+upl.plot_SSC_massflow(ax3, plot_all_time=plot_all_time)
 
 # full 1 year plot
 # figF = plt.figure(figsize=[10,8])

### 2021-07-16 simulations/modules/SolarTES.py
adding an NE2 module for CSP+TES
this includes the NE2 module that creates a PySAM module and executes through SSC, a corresponding JSON script, and a plotting utility called SolarPlots

@@ -1,0 +1,38 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jul 16 13:49:24 2021
+
+@author: gabrielsoto
+"""
+
+import sys
+sys.path.append('..')
+import PySAM.TcsmoltenSalt as TcsmoltenSalt
+from modules.NuclearTES import NuclearTES
+# from dispatch.NuclearDispatch import NuclearDispatch as ND
+# from dispatch.NuclearDispatch import NuclearDispatchParamWrap as NDP
+import PySAM.PySSC as pssc
+from util.FileMethods import FileMethods
+import copy
+
+class SolarTES(NuclearTES): 
+    """
+    The SolarTES class intializes, updates, and runs SSC simulations through PySAM,
+    specifically for the SSC tcsmolten_salt module. 
+    """
+    
+    def __init__(self, plant_name="tcsmolten_salt", json_name="model_solarTES", is_dispatch=False):
+        """ Initializes the SolarTES module
+        
+        Inputs:
+            plant_name (str)         : name of SSC module to run 
+            json_name (str)          : name of JSON script with input data for module
+            is_dispatch (bool)       : boolean, if True runs Pyomo dispatch optimization
+        """
+        
+        # initialize Generic module, csv data arrays should be saved here
+        NuclearTES.__init__( self, plant_name, json_name, is_dispatch )
+        
+        # define specific PySAM module to be called later
+        self.PySAM_Module = TcsmoltenSalt

### 2021-07-16 simulations/util/SolarPlots.py

@@ -1,0 +1,142 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jul 16 16:15:50 2021
+
+@author: gabrielsoto
+"""
+
+from pylab import rc
+import matplotlib.pyplot as plt
+import pyomo.environ as pe
+import numpy as np
+import pint
+u = pint.UnitRegistry(autoconvert_offset_to_baseunit=True)
+rc('axes', linewidth=2)
+rc('font', weight='bold', size=12)
+from util.PostProcessing import Plots
+
+class SolarPlots(Plots):
+    """
+    The Plots class is a part of the PostProcessing family of classes. It can 
+    output results from SSCmodels. This might be a 
+    Sisyphus-ian task as some of the parameters are very unique to whatever 
+    plot you are trying to make, but will do my best to provide basic structures
+    and templates to work off of. 
+
+    Note that the Plots class must be initialized before using. 
+    """
+
+    def __init__(self, module, fsl='x-small', loc='best', legend_offset=False,
+                 lp=16, lps=12, fs=12, lw=2, x_shrink=0.85, x_legend=12):
+        """ Initializes the Plots module
+
+        The instantiation of this class receives a full module object, the module
+        being one of the NE2 modules in the /neup-ies/simulations/modules directory.
+        It also contains various inputs relating to cosmetic parameters for
+        matplotlib plots. 
+
+        Inputs:
+            module (object)     : object representing NE2 module class after simulations
+            fsl (str)           : fontsize for legend
+            loc (str)           : location of legend
+            legend_offset(bool) : are we plotting legends off-axis?
+            lp (int)            : labelpad for axis labels
+            lps (int)           : labelpad for axis labels - short version
+            fs (int)            : fontsize for labels, titles, etc.
+            lw (int)            : linewidth for plotting
+            x_shrink (float)    : (legend_offset==True) amount to shrink axis to make room for legend
+        """
+        
[…]

### 2021-07-21 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py
consolidated a bunch of if statements, better output print statements

@@ -62,7 +62,7 @@ def print_string_header(header):
 
 # creating figure
 fig = plt.figure(figsize=[18.5,6])
-fig.suptitle("IRR: {0:.1f}".format(irr_mean), fontsize=14)
+fig.suptitle("IRR: {0:.1f}".format(irr_mean), fontsize=14, fontweight='bold')
 ax1 = fig.add_subplot(131)
 ax2 = fig.add_subplot(132)
 ax3 = fig.add_subplot(133)
@@ -76,30 +76,26 @@ dispatch_scenarios  = ['Pyomo - 24hr Horizon', 'Pyomo - 48hr Horizon', 'No Pyomo
 # specific performance metrics to plot 
 performance_metrics = [annual_energy_array, ppa_array, npv_aftertax]
 N              = len(performance_metrics)
-get_max        = [True, False, False] # whether each performance is optimized with max or min
+get_max        = [True, False, True] # whether each performance is optimized with max or min
 axes           = [ax1,ax2,ax3] # list of axes
 heat_cmap_list = ['Blues', 'Blues_r', 'Blues_r'] # colormaps used for each performance metric
 metric_labels  = ['Annual Energy Production \n(TWh)',
                   'PPA Price \n(cents/kWh)',
                   'NPV \n($M)' ] # labels for each performance metric
 
-# colormap for contours
-cmap_contour = cm.RdBu
-
 # some other arrays
 P_array  = P_ref * p_mult #actual power cycle reference outputs
 lp = 12 #labelpad
 
-
-
 # ========================================   
 # Looping!
 # ========================================     
-
+print("\n\nBlue -> Better Performance in the 2D Heatmaps")
+print("Red  -> Better Performance in the Comparison Contours")
 for n in range(N):
 
     # indeces for dispatch scenarios
-    dispatch_series  = list( range(N) ) # declare this every loop
+    dispatch_series  = list( range(len(dispatch_scenarios) ) ) # declare this every loop
     
     #extracting specific performance metric
     performance_metric = performance_metrics[n]
@@ -109,14 +105,14 @@ for n in range(N):
             else np.amin(performance_metric)
 
     # indeces for this maximum value - { D=Dispatch_Type, T=tshours, P=power_cycle }
-    [Opt_D, Opt_T, Opt_P] = [np.where(performance_metric == Opt)[d][0] for d in range(N)]
+    [Opt_D, Opt_T, Opt_P] = [np.where(performance_metric == Opt)[d][0] for d in range(len(performance_metric.shape))]
     
[…]

### 2021-07-21 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py
fixing logic for determining colormaps

@@ -190,15 +190,31 @@ for n in range(N):
     # define contour levels
     if np.sign(diffmin_pct) == np.sign(diffmax_pct):
         # difference has only one sign, so optimal is strictly better
-        cmap_contour = cm.Reds_r # colormap for contours
+        cmap_contour = cm.Reds_r if Opt_D != 2 else cm.Reds # colormap for contours
         strictly_better = True
         if Opt_D == 2:
             levels = [diffmin_pct, 0.75*diffmin_pct, 0.3*diffmin_pct, diffmax_pct]
         else:
             levels = np.linspace(diffmin_pct, diffmax_pct, 5).tolist()
     else:
-        # difference changes signs, so sometimes the Dispatch type behaves worse
-        cmap_contour = cm.RdBu_r  if get_max[n] and Opt_D != 2 else cm.RdBu # colormap for contours
+        # difference changes signs, so sometimes the Dispatch type behaves worse in some regions
+        #
+        # red values represent better relative performance
+        # RdBu_r => red is higher value
+        # RdBu   => red is lower value
+        
+        #                       |  max = True    |  max = False 
+        # ---------------------------------------------------------
+        # Opt_D != 2            | higher => red  |   lower => red
+        # [compare              |   (RdBu_r)     |     (RdBu)
+        #  relative to SSC]     |                |
+        # ---------------------------------------------------------
+        # Opt_D == 2            | lower => red   |   higher => red
+        # [compare              |   (RdBu)       |     (RdBu_r)
+        #  relative to non-SSC] |                
+        #
+        cmap_contour = cm.RdBu_r if (get_max[n]     and Opt_D != 2) \
+                                 or (not get_max[n] and Opt_D == 2) else cm.RdBu # colormap for contours
         strictly_better = False
         if Opt_D == 2:
             levels = [diffmin_pct, 0.7*diffmin_pct, 0.4*diffmin_pct, 0, 0.4*diffmax_pct, 0.9*diffmax_pct, diffmax_pct]

### 2021-07-22 simulations/util/PostProcessing.py
new output extraction class, gets called by Plotting classes

@@ -15,12 +15,157 @@ u = pint.UnitRegistry(autoconvert_offset_to_baseunit=True)
 rc('axes', linewidth=2)
 rc('font', weight='bold', size=12)
 
+class OutputExtraction(object):
+    """
+    The OutputExtraction class is a part of the PostProcessing family of classes.
+    It extracts outputs from SSC or Dispatch models. Can be called from other 
+    plotting classes to extract outputs.  
+    """
+    
+    def __init__(self, module):
+        """ Initializes the OutputExtraction module
 
-# BIG difference here is that the Plots class gets initialized
+        The instantiation of this class receives a full module object, the module
+        being one of the NE2 modules in the /neup-ies/simulations/modules directory.
+        or a Dispatch module. 
+
+        Inputs:
+            module (object)     : object representing NE2 module class after simulations
+        """
+        
+        # module class name
+        mod_class = module.__class__.__module__
+        self.mod_class_name = mod_class.split('.')[0]
+
+        # continuing with SSC plots
+        if self.mod_class_name == 'modules':
+            
+            # full PySAM module
+            self.mod = module.Plant
+            
+            # define an Output object to extract information from SSC
+            Outputs = self.mod.PySAM_Outputs if module.run_loop else self.mod.Outputs
+            
+            self.t_full = np.asarray(Outputs.time_hr)*u.hr
+            
+            # extracting outputs
+            self.set_ssc_outputs( Outputs )
+        
+        elif self.mod_class_name == 'dispatch':
+            
+            # saving module to self
+            self.dm = module
+            
+            # extract outputs from Dispatch model
+            self.set_pyomo_outputs()
+
+    
+    def set_ssc_outputs(self, mod_out):
+        """ Method to set SSC outputs from module
+        
+        The method extracts SSC outputs and save them to arrays. The input to this
+        method is a subclass to an NE2 class holding all outputs to simulations.          
+        
+        Inputs:
+            mod_out (object)  : object representing Outputs subclass of NE2 module
+        """
+        # saving some outputs for plotting
[…]

### 2021-07-22 simulations/scripts/PySAM_model1.py
tidying up the plotting scripts

@@ -28,9 +28,9 @@ print("PID = ", pid)
 # =============================================================================
 
 # defining directories
-nuctes = NuclearTES.NuclearTES()
+nuctes = NuclearTES.NuclearTES(is_dispatch=False)
 output_file = 'output.csv'
-nuctes.run_sim( run_loop=False, export=True, filename=output_file )
+nuctes.run_sim( run_loop=True, export=False, filename=output_file )
 nt = nuctes.Plant
 so = nuctes.SO
 
@@ -93,94 +93,5 @@ upl.plot_SSC_power_and_energy(ax1 )#, plot_full_time=plot_full_time, title_label
 upl.plot_SSC_op_modes(ax2) #, plot_full_time=plot_full_time)
 upl.plot_SSC_massflow(ax3) #, plot_full_time=plot_full_time)
 
-# full 1 year plot
-# figF = plt.figure(figsize=[10,8])
-# ax1F = figF.add_subplot(311)
-# ax2F = figF.add_subplot(312)
-# ax3F = figF.add_subplot(313)
 
-# upl.plot_SSC_power_and_energy(ax1F, True, title_label='SSC Results - Full Year')
-# upl.plot_SSC_op_modes(ax2F, True)
-# upl.plot_SSC_massflow(ax3F, True)
-
-
-# upl.plot_SSC_op_modes(False)
-# upl.plot_SSC_op_modes(True)
-# upl.plot_SSC_power_and_energy(False)
-# upl.plot_SSC_power_and_energy(True)
-# upl.plot_SSC_massflow(False)
-# upl.plot_SSC_massflow(True)
-
-
-# plt.figure()
-# plt.plot(t_plot,nuctes.df_array)
-
-
-# fig = plt.figure(figsize=[10,8])
-# ax1 = fig.gca()
-# # ax1 = fig.add_subplot(311)
-# # ax2 = fig.add_subplot(312)
-# # ax3 = fig.add_subplot(313)
-
-# # Energy plot
-# ax1.plot(t_plot, e_ch_tes, linewidth = lw, label='Salt Charge Level (MWht)')
-# ax1.plot(t_plot, p_cycle, linewidth = lw, label='P_cycle (Electric)')
-# ax1.plot(t_plot, q_dot_rec_in, linewidth = lw, label='Q_dot to Salt (Thermal)')
[…]

### 2021-07-22 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py
new revenue metric

@@ -27,7 +27,7 @@ print("PID = ", pid)
 
 # locating output directory
 output_dir = FileMethods.output_dir
-filename   = 'pricePerfvsDispatch_sizingTESandCycle_irr11pct.nuctes' 
+filename   = 'pricePerfvsDispatch_sizingTESandCycle_irr11pct_simplerevenue.nuctes' 
 NTPath = os.path.join(output_dir, filename)
 
 # pickling
@@ -49,6 +49,7 @@ ppa_array           = Storage['ppa_array']
 lcoe_nom_array      = Storage['lcoe_nom_array']
 npv_aftertax = Storage['npv_aftertax']
 irr          = Storage['irr_aftertax']
+revenue      = Storage['simple_revenue'] * 1e-9
 irr_mean     = np.mean(irr)
     
 # =============================================================================
@@ -74,14 +75,14 @@ plt.subplots_adjust(wspace=0.4)
 dispatch_scenarios  = ['Pyomo - 24hr Horizon', 'Pyomo - 48hr Horizon', 'No Pyomo - SSC Only']  
 
 # specific performance metrics to plot 
-performance_metrics = [annual_energy_array, ppa_array, npv_aftertax]
+performance_metrics = [annual_energy_array, ppa_array, revenue]
 N              = len(performance_metrics)
 get_max        = [True, False, True] # whether each performance is optimized with max or min
 axes           = [ax1,ax2,ax3] # list of axes
-heat_cmap_list = ['Blues', 'Blues_r', 'Blues_r'] # colormaps used for each performance metric
+heat_cmap_list = ['Blues', 'Blues_r', 'Blues'] # colormaps used for each performance metric
 metric_labels  = ['Annual Energy Production \n(TWh)',
                   'PPA Price \n(cents/kWh)',
-                  'NPV \n($M)' ] # labels for each performance metric
+                  'Revenue - Simple Calculation \n($B)' ] # labels for each performance metric
 
 # some other arrays
 P_array  = P_ref * p_mult #actual power cycle reference outputs
@@ -190,7 +191,8 @@ for n in range(N):
     # define contour levels
     if np.sign(diffmin_pct) == np.sign(diffmax_pct):
         # difference has only one sign, so optimal is strictly better
-        cmap_contour = cm.Reds_r if Opt_D != 2 else cm.Reds # colormap for contours
+        cmap_contour = cm.Reds if (get_max[n]     and Opt_D != 2) \
[…]

### 2021-07-22 papers/white-cycle-modeling/modeling-of-combined-lfr-csp-sco2-paper/content.tex
added results section

@@
 
-\subsection{Cycle Configurations} %========================================
+There are various cycles that have been modeled to test their advantages and disadvantages.
+These various models cycles two different categories: non-charging and charging.
+The non-charging category will decide the configuration of the cycle with a focus on generating electricity.
+This includes the number of turbines, recuperators, and where heat is put into the system by the CSP and LFR.
+The charging category tests different locations of where heat is drawn from the LFR to be stored in the CSP's TES for later use.
+
+\subsection{Non-Charging Cycle Configurations}%===================================
+
+The cycles presented are generalized in order to draw a more direct comparison between cycles.
+These general parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
+These values are summarized in Table \ref{cycle-constants}.
 
 \begin{specialtable}[H] 
-    \caption{Constant cycle parameters with definition, variable and set value. The variables with (*) have changing labels depending on the specific cycle diagram. \label{cycle-constants}}
+    \caption{Constant cycle parameters with definition, variable and set value. \label{cycle-constants}}
     \begin{tabular}{lcc}
@@
     Pressure Ratio & $PR$ & 3.27 (-)\\
-    High Side Pressure & (*) & 2.88e7 (Pa)\\
+    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
     \midrule
@@
     \textit{Temperature}\\
-    Main Compressor Inlet & (*) & 313.2 (K)\\
-    Lead-Fast Reactor Low Temperature & (*) & 673.2 (K)\\
+    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
+    Lead-Fast Reactor Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
     \midrule
@@
     Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
-    Pump Low Side Pressure & (*) & 3.0e6 (Pa)\\ 
+    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
     \bottomrule
@@
 
-\subsubsection{C-LFR-ON} %--------------------------------------------------------
+The values displayed in Table \ref{cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Corporation.
+
+\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON} %--------------------------------------------------------
+
+The first cycle that will be tested has independent sCO$_{2}$ loops bridged by the CSP.
+This cycle has two Brayton Cycles: a LFR cycle and a CSP cycle.
+These two cycles individually operate when the focus of plant operation is primarily electricity generation.
+
+The LFR cycle for this two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.
+
 \end{paracol}
@@
 
+Modeling the C-LFR-ON cycle in EES yeilded the results in Table \ref{tab-c-lfr-on}.
+Two seperate sensitivity studies were completed on the LFR inlet temperature.
+The unconstrained (\textit{U}) values were from parametric studies on mass flow to the main compressor while maximizing cycle efficiency.
+The constrained (\textit{C}) values were calculated by setting the LFR inlet temperature to the design value of 673.2 K.
+
 \begin{specialtable}[H] 
-    \caption{State points calculated at steady state operation and LFR low temperature constrained to 673.2 K for C-LFR-ON cycle. \label{c-lfr-on-tab-cons}}
-    \begin{tabular}{lcccc}
+    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-on}}
+    \begin{tabular}{lccc}
     \toprule
-    \textbf{Diagram}	& \textbf{Temperature}	& \textbf{Pressure} &\textbf{Mass Flow} & \textbf{Enthalpy}\\
-    \textbf{Label} & \textbf{(K)} & \textbf{(Pa)} &\textbf{(kg/s)} & \textbf{(J/kg)}\\
+    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
     \midrule
-    1a-A		& 313.2  & 8.807e6  & 3029  & -149660\\
-    1b-A		& 313.2  & 8.807e6  & 3029  & -149660\\
-    2a-A		& 374.2  & 2.88e7  & 3029  & -110393\\
-    2b-A		& 374.2  & 2.88e7  & 3029  & -110393\\
-    3a-A		& 438.2  & 2.88e7  & 3029  & 10618\\
-    3a-B		& 506.4  & 2.88e7  & 832.4  & 114847\\
-    3b  		& 451.9  & 2.88e7  & 3861  & 33089\\
-    3b-A		& 451.9  & 2.88e7  & 3861  & 33089\\
-    4a-A		& 673.2  & 2.88e7  & 3861  & 333669\\
-    4b  		& 673.2  & 2.88e7  & 3861  & 333669\\
-    5a  		& 868.2  & 2.88e7  & 3861  & 579720\\
-    5b  		& 868.2  & 2.88e7  & 3861  & 579720\\
-    6a  		& 722.8  & 8.807e6  & 3861  & 417482\\
-    6b  		& 722.8  & 8.807e6  & 3861  & 417482\\
-    7a  		& 722.8  & 8.807e6  & 3861  & 417482\\
-    7b  		& 722.8  & 8.807e6  & 3861  & 417482\\
-    8a  		& 461.9  & 8.807e6  & 3861  & 116902\\
-    8b  		& 461.9  & 8.807e6  & 3861  & 116902\\
-    9a  		& 384.2  & 8.807e6  & 3861  & 21981\\
-    9b-A		& 384.2  & 8.807e6  & 3029  & 21981\\
-    9b-B		& 384.2  & 8.807e6  & 834.2  & 21981\\
-    \bottomrule
-    \end{tabular}
-    \begin{tabular}{lcc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{Calculated Value}\\
-    \midrule
-    Cycle Efficiency (\%) & $\eta_{cycle}$ & 45.28\\
-    Alternator Power (W) & $\dot{W}_{A}$ & 4.302e8\\
-    PreCooler Heat Transfer (W) & $\dot{Q}_{PC}$ & 5.198e8\\
-    Main Compressor Power (W) & $\dot{W}_{MC}$ & 1.189e8\\ 
-    ReCompressor Power (W) & $\dot{W}_{RC}$ & 7.730e7\\ 
-    Turbine Power (W) & $\dot{W}_{T}$ & 6.264e8\\
-    Main Compressor Mass Flow Fraction (-) & $y_{1}$ & 0.7844\\
-    LTR UA Value (W/K) & $UA_{LTR}$ & 2.284e7\\
-    LTR Capacitance Ratio (-) & $CR_{LTR}$ & 0.8473\\
-    LTR Heat Transfer Rate (W) & $\dot{Q}_{LTR}$ & 3.665e8\\
-    LTR Effectiveness (-) & $\varepsilon_{LTR}$ & 0.8742\\
-    HTR UA Value (W/K) & $UA_{HTR}$ & 4.271e7\\
-    HTR Capacitance Ratio (-) & $CR_{HTR}$ & 0.9627\\
-    HTR Heat Transfer Rate (W) & $\dot{Q}_{HTR}$ & 1.161e9\\
-    HTR Effectiveness (-) & $\varepsilon_{HTR}$ & 0.9627\\
+    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	&	Data	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	\\
+    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
+    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
+    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
+    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
+    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
+    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
+    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
+    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
+    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
     \bottomrule
@@
 
-\begin{specialtable}[H] 
-    \caption{State points calculated at steady state operation with LFR low temperature unconstrained and cycle efficiency maximized for C-LFR-ON cycle. \label{c-lfr-on-tab-unconst}}
-    \begin{tabular}{lcccc}
-    \toprule
-    \textbf{Diagram}	& \textbf{Temperature}	& \textbf{Pressure} &\textbf{Mass Flow} & \textbf{Enthalpy}\\
-    \textbf{Label} & \textbf{(K)} & \textbf{(Pa)} &\textbf{(kg/s)} & \textbf{(J/kg)}\\
-    \midrule
-    1a-A		& 313.2  & 8.807e6  & 2929  & -149660\\
-    1b-A		& 313.2  & 8.807e6  & 2929  & -149660\\
-    2a-A		& 374.2  & 2.88e7  & 2929  & -110393\\
-    2b-A		& 374.2  & 2.88e7  & 2929  & -110393\\
-    3a-A		& 505.7  & 2.88e7  & 2929  & 113832\\
-    3a-B		& 506.4  & 2.88e7  & 1255  & 114847\\
-    3b  		& 505.9  & 2.88e7  & 4184  & 114137\\
-    3b-A		& 505.9  & 2.88e7  & 4184  & 114137\\
-    4a-A		& 688.3  & 2.88e7  & 4184  & 352679\\
-    4b  		& 688.3  & 2.88e7  & 4184  & 352679\\
-    5a  		& 868.2  & 2.88e7  & 4184  & 579720\\
-    5b  		& 868.2  & 2.88e7  & 4184  & 579720\\
-    6a  		& 722.8  & 8.807e6  & 4184  & 417482\\
-    6b  		& 722.8  & 8.807e6  & 4184  & 417482\\
-    7a  		& 722.8  & 8.807e6  & 4184  & 417482\\
-    7b  		& 722.8  & 8.807e6  & 4184  & 417482\\
-    8a  		& 515.9  & 8.807e6  & 4184  & 178939\\
-    8b  		& 515.9  & 8.807e6  & 4184  & 178939\\
-    9a  		& 384.2  & 8.807e6  & 4184  & 21981\\
-    9b-A		& 384.2  & 8.807e6  & 2929  & 21981\\
-    9b-B		& 384.2  & 8.807e6  & 1255  & 21981\\
-    \bottomrule
-    \end{tabular}
-    \begin{tabular}{lcc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{Calculated Value}\\
-    \midrule
-    Cycle Efficiency (\%) & $\eta_{cycle}$ & 47.08\\
-    Alternator Power (W) & $\dot{W}_{A}$ & 4.473e8\\ 
-    PreCooler Heat Transfer (W) & $\dot{Q}_{PC}$ & 5.027e8\\
-    Main Compressor Power (W) & $\dot{W}_{MC}$ & 1.150e8\\ 
-    ReCompressor Power (W) & $\dot{W}_{RC}$ & 1.166e8\\ 
-    Turbine Power (W) & $\dot{W}_{T}$ & 6.789e8\\
-    Main Compressor Mass Flow Fraction (-) & $y_{1}$ & 0.7000\\
-    LTR UA Value (W/K) & $UA_{LTR}$ & 5.468e7\\
-    LTR Capacitance Ratio (-) & $CR_{LTR}$ & 0.9867\\
-    LTR Heat Transfer Rate (W) & $\dot{Q}_{LTR}$ & 6.568e8\\
-    LTR Effectiveness (-) & $\varepsilon_{LTR}$ & 0.92\\
-    HTR UA Value (W/K) & $UA_{HTR}$ & 4.829e7\\
-    HTR Capacitance Ratio (-) & $CR_{HTR}$ & 0.8657\\
-    HTR Heat Transfer Rate (W) & $\dot{Q}_{HTR}$ & 9.981e8\\
-    HTR Effectiveness (-) & $\varepsilon_{HTR}$ & 0.9544\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
+\textbf{Discussion of Results}
 
-\subsubsection{C-CSP-ON} %--------------------------------------------------------
+The CSP cycle for this two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
+The CSP is shown in this diagram with the necessary pumps, TES tanks, and salt heat exchanger.
+
 \end{paracol}
@@
 
+ C-CSP-ON is not directly impacted by constrained or unconstrained LFR low temperatures because it is an independent cycle while focused on electricity generation.
+Instead a sensitivity study was done on the temperature of the cold TES.
+Two temperatures were tested, 663.2 K and 713.2 K, to observe the impacts on cycle efficiency.
+The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
+
+\begin{specialtable}[H] 
+    \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
+    \begin{tabular}{lccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} &  &\\
+    \midrule
+    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	\\
+    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
+    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
+    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
+    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
+    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
+    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
+    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
+    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
+    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
+    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
 \subsubsection{C-1HTR1T-ON} %-----------------------------------------------------
+
+One of the drawbacks of having a two-cycle design as seen in the C-LFR-ON and C-CSP-ON is the number of system components is essentially doubled.
+Combining the two cycles into one would reduce this redundancy.
+Heat addition from the CSP and LFR in parallel orientation was therefore studied in the C-1HTR1T-ON model.
+This model is important to study the impact on cycle efficiency when mixing different temperature flows prior to the turbine.
+The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.
+
 \end{paracol}
@@
 
+In this cycle the LFR and CSP are linked due to the parallel orientation.
+Therefore, three sensitivity studies were done on the C-1HTR1T-ON EES model.
+The initial two studies had the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency.
+The two tested values for cold CSP TES with constrained LFR low temperature were 683.2 K and 713.2 K.
+The desired cold CSP TES temperature of 663.2 K was not possible with the constraint on the LFR low temperature.
+To obtain the desired cold CSP TES temperature, the constraint was removed droping the temperature of the LFR inlet to 653.2 K.
+These values are displayed in Table \ref{tab-c-1htr1t-on}.
+
+\begin{specialtable}[H] 
+    \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.
+Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
+    & & \textit{U} & \textit{C} & \textit{C}\\
+    \midrule
+    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	&	Data	\\
+    LFR Inlet Temperature (K)	&	$T_{4C}$	&	Data	&	Data	&	Data	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	&	Data	\\
+    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	&	Data	\\
+    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	&	Data	\\
+    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	&	Data	\\
+    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	&	Data	\\
+    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	&	Data	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	&	Data	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	Data	&	Data	&	Data	\\
+    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	&	Data	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	&	Data	\\
+    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	&	Data	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	&	Data	\\
+    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	&	Data	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	&	Data	\\
+    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	&	Data	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	&	Data	\\
+    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
 \subsubsection{C-2HTR3T-ON} %-----------------------------------------------------
+
+Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency.
+To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine was desired.
+This cycle is labeled at C-2HTR3T-ON.
+This cycle, seen in Figure \ref{c-2htr3t-on}, has two high temperature recuperators and three turbines.
+
 \end{paracol}
@@
 
+Three sensitivity studies were done on the C-2HTR3T-ON model.
+Two with the LFR low temperature constrained and one without this constraint.
+The two constrained studies had varied cold CSP TES temperature with the lowest temperautre of 663.2 K and highest temperature of 713.2 K.
+The unconstrained low LFR inlet study was done at a cold CSP TES temperature of 663.2 K.
+The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
+
+\begin{specialtable}[H]
+    \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-2htr3t-on}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
+    & & \textit{U} & \textit{C} & \textit{C}\\
+    \midrule	
+    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	&	Data	\\
+    LFR Inlet Temperature (K)	&	$T_{5A}$	&	Data	&	Data	&	Data	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	&	Data	\\
+    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	&	Data	\\
+    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	&	Data	\\
+    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	&	Data	\\
+    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	&	Data	\\
+    T1 Power (W)	&	$\dot{W}_{T1}$	&	Data	&	Data	&	Data	\\
+    T2 Power (W)	&	$\dot{W}_{T2}$	&	Data	&	Data	&	Data	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	&	Data	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	Data	&	Data	&	Data	\\
+    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	&	Data	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	&	Data	\\
+    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	&	Data	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	&	Data	\\
+    HTR1 UA Value (W/K)	&	$UA_{HTR1}$	&	Data	&	Data	&	Data	\\
+    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	Data	&	Data	&	Data	\\
+    HTR1 Heat Transfer Rate (W)	&	$\dot{Q}_{HTR1}$	&	Data	&	Data	&	Data	\\
+    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	Data	&	Data	&	Data	\\
+    HTR2 UA Value (W/K)	&	$UA_{HTR2}$	&	Data	&	Data	&	Data	\\
+    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	Data	&	Data	&	Data	\\
+    HTR2 Heat Transfer Rate (W)	&	$\dot{Q}_{HTR2}$	&	Data	&	Data	&	Data	\\
+    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	Data	&	Data	&	Data	\\
+    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
 \subsection{Thermal Energy Storage Charging Techniques} %=========================
 
+When the grid demand is not high, the non-charging cycle configurations focus on an energy storage operating mode.
+Alternator power is set to zero and power from the turbine is solely powering the two compressors.
+The excess energy from the LFR is thermally stored in the TES for later use instead of generating electricity.
+Comparison of where thermal energy is drawn from the cycle is done by using the same recompression cycle and configuring the salt heat exchanger in different locations around the turbine.
+
 \subsubsection{C-LFR-PRE} %-------------------------------------------------------
+
+Flow leaves the turbine with excess thermal energy that was not transformed into mechanical energy.
+This thermal energy can be used to charge the hot CSP TES.
+The diagram outlining this process is C-LFR-PRE in Figure \ref{c-lfr-pre}.
+
 \end{paracol}
@@
 
+Problems arise with this salt charging configuration.
+The primary issue is that the temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of 833.2 K.
+To raise the temperature, some of the high temperature flow before the turbine is redirected through a valve and combined after the turbine.
+This combination of different temperature flows has a large impact on heat storage efficiency.
+The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
+
+\begin{specialtable}[H]
+    \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
+    & & \textit{C}\\
+    \midrule	
+    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	\\
+    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	Data	\\
+    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	\\
+    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	\\
+    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	\\
+    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	\\
+    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	Data	\\
+    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	\\
+    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	\\
+    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	\\
+    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	\\
+    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	\\
+    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
 \subsubsection{C-LFR-POST} %------------------------------------------------------
+
+Moving the heat extraction prior to the turbine was qualitatively analyzed in C-LFR-POST. This diagram is seen in Figure \ref{c-lfr-post}.
+
 \end{paracol}
@@
 
+This TES charging cycle was extracting heat before the turbine and therefore would have a large negative effect on the amount of work that the turbine could produce.
+The turbine needs to offset the requirements of both compressors and this would require the inlet temperature to be high.
+The amount of energy that could be extracted before the turbine would be small and therefore the heat storage efficiency would be small.
+There was no quantitative study done on this diagram because it theoreticaly would be non-viable.
+
 \subsubsection{C-LFR-PAR} %-------------------------------------------------------
+
+The requirement of the turbine and hot CSP TES temperature could be accomplished by splitting the flow before the turbine.
+The flow through the salt heat exchanger would therefore be seperate from the turbine.
+After the salt heat exchanger a valve would need to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
+
 \end{paracol}
@@
 
+This cycle had two sensitivity studies done with varying cold CSP TES.
+The low temperature study was done at 663.2 K and the high temperature study was done at 713.2 K.
+The results from this study are displayed in Table \ref{tab-c-lfr-par}.
+
+\begin{specialtable}[H]
+    \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
+    \begin{tabular}{lccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
+    & & \textit{C} & \textit{C}\\
+    \midrule	
+    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	\\
+    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	&	Data	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	Data	&	Data	\\
+    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
+    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
+    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
+    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
+    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
+    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	Data	&	Data	\\
+    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
+    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
+    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
+    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
+    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	\\
+    CSPHX Approach Temperature (K)	&	$\delta_{CSPHX}$	&	Data	&	Data	\\
+
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
+The CSP salt mass flow rate and approach temperature of the SALT HX would adjust according to the temperature difference in the TES and keep the efficiency constant.
+
 \subsubsection{C-LFR-CIRC} %------------------------------------------------------
+
+The full diagram for C-LFR-CIRC is shown in Figure \ref{c-lfr-circ}.
+
 \end{paracol}
@@
 
+The charging subsection of this diagram is composed of a circulation cycle that has heat inputed through the LFR heat exchanger. This subsection is seen in Figure \ref{c-lfr-circ-sub}.
+
 \end{paracol}
@@
 \switchcolumn
+
+The flow then continues through a circulator which has neglegible pressure rise.
+A heat exchanger then extracts heat from the flow, transfering into the hot TES for later use.
+Excess heat that is not extracted is then dumped into a reservior through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of 673.2 K.
+Three different temperatures; 663.2 K, 683.2 K, and 713.2 K, are compared in Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.\\
+
+\begin{specialtable}[H]
+    \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-circ}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
+    \midrule	
+    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	&	Data	\\
+    LFR Inlet Temperature (K)	&	$T_{1C}$	&	Data	&	Data	&	Data	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	Data	&	Data	&	Data	\\
+    Chiller Heat Transfer (W)	&	$\dot{Q}_{chill}$	&	Data	&	Data	&	Data	\\
+    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
 

### 2021-07-22 simulations/util/SolarPlots.py
fixing calls to SolarOutputExtract class

@@ -14,43 +14,30 @@ import pint
 u = pint.UnitRegistry(autoconvert_offset_to_baseunit=True)
 rc('axes', linewidth=2)
 rc('font', weight='bold', size=12)
+from util.PostProcessing import OutputExtraction
 from util.PostProcessing import Plots
 from util.PostProcessing import DispatchPlots
 
-class SolarPlots(Plots):
-    """
-    The Plots class is a part of the PostProcessing family of classes. It can 
-    output results from SSCmodels. This might be a 
-    Sisyphus-ian task as some of the parameters are very unique to whatever 
-    plot you are trying to make, but will do my best to provide basic structures
-    and templates to work off of. 
 
-    Note that the Plots class must be initialized before using. 
+class SolarOutputExtraction(OutputExtraction):
     """
-
-    def __init__(self, module, fsl='x-small', loc='best', legend_offset=False,
-                 lp=16, lps=12, fs=12, lw=2, x_shrink=0.85, x_legend=12):
-        """ Initializes the Plots module
+    The OutputExtraction class is a part of the PostProcessing family of classes.
+    It extracts outputs from SSC or Dispatch models. Can be called from other 
+    plotting classes to extract outputs.  
+    """
+    
+    def __init__(self, module):
+        """ Initializes the OutputExtraction module
 
         The instantiation of this class receives a full module object, the module
         being one of the NE2 modules in the /neup-ies/simulations/modules directory.
-        It also contains various inputs relating to cosmetic parameters for
-        matplotlib plots. 
+        or a Dispatch module. 
 
         Inputs:
             module (object)     : object representing NE2 module class after simulations
-            fsl (str)           : fontsize for legend
-            loc (str)           : location of legend
-            legend_offset(bool) : are we plotting legends off-axis?
-            lp (int)            : labelpad for axis labels
-            lps (int)           : labelpad for axis labels - short version
-            fs (int)            : fontsize for labels, titles, etc.
-            lw (int)            : linewidth for plotting
-            x_shrink (float)    : (legend_offset==True) amount to shrink axis to make room for legend
         """
         
-        Plots.__init__(self, module, fsl=fsl, loc=loc, legend_offset=legend_offset,
-                 lp=lp, lps=lps, fs=fs, lw=lw, x_shrink=x_shrink, x_legend=x_legend)
[…]

### 2021-07-28 simulations/modules/GenericSSCModule.py
streamlining log_SSC_arrays so it works when run_loop is false
also ensuring safe deletion of things in reset_all

@@ -35,8 +35,6 @@ class GenericSSCModule(ABC):
     - PySAM modules : these are PySAM wrappers for the SSC modules (also Grid, Financial modules, etc.)
     - NE2 modules   : these are Python classes that create PySAM modules (e.g., *THIS* class)
     
-    TODO: can we convert this to an abstract class in Python?
-    
     """
     
     @abstractmethod
@@ -114,30 +112,20 @@ class GenericSSCModule(ABC):
             
         """
         
-        u = self.u
-        
         self.run_loop = run_loop
-        SSC_dict = self.SSC_dict
         
         #--- create Plant object and execute it
         self.create_Plant( )
         self.simulate_Plant( )
         
         # log final results from looping simulations
-        if self.run_loop:
-            self.log_SSC_arrays(log_final=True)
-        
-        #logging annual energy and capacity factor (sometimes doesn't get calculated)
-        annual_energy = np.sum(self.gen_log)*u.kWh
-        if 'P_ref' in SSC_dict.keys():
-            ref_energy    = SSC_dict['P_ref']*u.MW * SSC_dict['gross_net_conversion_factor']
-            self.capacity_factor = (annual_energy / (ref_energy * 1*u.yr) ).to(' ')
+        self.log_SSC_arrays(log_final=True)
         
         #--- use executed Plant object to create Grid object and execute it
         self.create_Grid( )
         # update gen and annual energy so SystemOutput is consistent, carried over to SO object
         self.Grid.SystemOutput.gen = tuple(self.gen_log)
-        self.Grid.SystemOutput.annual_energy = np.sum(annual_energy.magnitude)
+        self.Grid.SystemOutput.annual_energy = np.sum(self.annual_energy.magnitude)
         self.Grid.execute( )
         
         #--- use executed Plant object to create SingleOwner object and execute it
@@ -284,6 +272,7 @@ class GenericSSCModule(ABC):
         
         # first execution of Plant through SSC
         self.run_Plant_through_SSC( time_start , time_next )
+        self.log_SSC_arrays()
         
         # this loop should only be entered if run_loop == True
         while (time_next < time_end):
@@ -320,6 +309,7 @@ class GenericSSCModule(ABC):
             
             # run Plant again
             self.run_Plant_through_SSC( time_start, time_next )
+            self.log_SSC_arrays()
         
         print(' Plant Simulation successfully completed.')
         
[…]

### 2021-07-28 simulations/tests/test_modules.py
rearranging tests, updating log array tests

@@ -125,7 +125,124 @@ class TestPySAMModules(unittest.TestCase):
             self.assertTrue(hasattr(mod,'SO') ,
                             "SO object not created for {0}".format(mod.__class__.__name__) )
             
+
+    def test_initialize_arrays(self):
+        """ Testing the initialize_arrays method
+        """
+        
+        # running in time segments versus running full year at once
+        loop_modes = [True, False]
+
+        # looping through all modules
+        for mod in self.mod_list:
+            for mode in loop_modes:
+                
+                # =====================================================
+                # run the method for given looping mode
+                mod.run_loop = mode
+                mod.initialize_arrays()
     
+                # assert that a Log dictionary was created
+                self.assertTrue( hasattr(mod, 'Log_Arrays') , 
+                                "Log_Arrays dictionary not created in {0} module.".format(mod.__class__.__name__ ) )
+    
+                # check that individual log arrays were saved to the NE2 module
+                keys = mod.Log_Arrays.keys()
+                
+                # if NOT running time segments, should only be saving the 'gen_long' array
+                condition = len(keys) == 1 if mode is False else len(keys) > 1
+                
+                self.assertTrue( condition , 
+                                "Improper amount of keys created in {0} module when run_loop is {1}.".format(mod.__class__.__name__ , mode ) )
+                
+                for k in keys:
+                    self.assertTrue( hasattr(mod, k) , 
+                                    "{0} Plant module doesn't have Output {1}.".format(mod.__class__.__name__ , k) )
+                
+                mod.reset_all()
+
+
+    def test_reset_all(self):
+        """ Testing the reset_all method
+        """
+        
+        try_all_PySAM_mods = [True, False]
+        
+        # looping through all modules
+        for mod in self.mod_list:
+            for try_all in try_all_PySAM_mods:
+                
+                # create PySAM modules
+                mod.create_Plant()
+                
+                # testing safe deletion, will it throw error if Grid was never created?
+                if try_all:
+                    mod.create_Grid()
+                    mod.create_SO()
+                
+                # initialize arrays
+                mod.run_loop = True
+                mod.initialize_arrays()
+                keys = mod.Log_Arrays.keys()
+                
+                # run the method
+                mod.reset_all()
+                
+                # check that method deleted PySAM modules
+                self.assertFalse( hasattr(mod,"Plant") ,
[…]

### 2021-07-28 simulations/dispatch/GeneralDispatch.py
defining units for variables in dispatch and converting Nuc O&M cost to thermal

@@ -55,11 +55,15 @@ class GeneralDispatch(ABC):
             unitRegistry (pint.registry) : unique unit Pint unit registry
         """
         
+        self.u_pyomo = u_pyomo
+        
         self.model = pe.ConcreteModel()
         self.generate_params(params)
         self.generate_variables()
         self.add_objective()
         self.generate_constraints()
+        
+        # assert_units_consistent(self.model)
 
 
     def generate_params(self, params):
@@ -152,18 +156,18 @@ class GeneralDispatch(ABC):
         parameters. Here we define continuous and binary variables for the 
         Power Cycle. 
         """
-        
+        u = self.u_pyomo
         ### Decision Variables ###
         #------- Variables ---------
-        self.model.ucsu = pe.Var(self.model.T, domain=pe.NonNegativeReals)                             #u^{csu}: Cycle start-up energy inventory at period $t$ [kWt$\cdot$h]
-        self.model.wdot = pe.Var(self.model.T, domain=pe.NonNegativeReals)                             #\dot{w}: Power cycle electricity generation at period $t$ [kWe]
-        self.model.wdot_delta_plus = pe.Var(self.model.T, domain=pe.NonNegativeReals)	               #\dot{w}^{\Delta+}: Power cycle ramp-up in period $t$ [kWe]
-        self.model.wdot_delta_minus = pe.Var(self.model.T, domain=pe.NonNegativeReals)	               #\dot{w}^{\Delta-}: Power cycle ramp-down in period $t$ [kWe]
-        self.model.wdot_v_plus = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.W_v_plus))      #\dot{w}^{v+}: Power cycle ramp-up beyond designed limit in period $t$ [kWe]
-        self.model.wdot_v_minus = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.W_v_minus)) 	 #\dot{w}^{v-}: Power cycle ramp-down beyond designed limit in period $t$ [kWe]
-        self.model.wdot_s = pe.Var(self.model.T, domain=pe.NonNegativeReals)	                       #\dot{w}^s: Energy sold to grid in time t [kWe]
-        self.model.wdot_p = pe.Var(self.model.T, domain=pe.NonNegativeReals)	                       #\dot{w}^p: Energy purchased from the grid in time t [kWe]
[…]

### 2021-07-28 simulations/dispatch/NuclearDispatch.py

@@ -109,12 +109,13 @@ class NuclearDispatch(GeneralDispatch):
         # generating GeneralDispatch variables first (PowerCycle, etc.)
         GeneralDispatch.generate_variables(self)
         
+        u = self.u_pyomo
         ### Decision Variables ###
         #------- Variables ---------
-        self.model.s = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.Eu))    #s: TES reserve quantity at period $t$  [kWt$\cdot$h]
-        self.model.unsu = pe.Var(self.model.T, domain=pe.NonNegativeReals)     #u^{nsu}: Nuclear start-up energy inventory at period $t$ [kWt$\cdot$h]
-        self.model.xn = pe.Var(self.model.T, domain=pe.NonNegativeReals)	   #x^n: Thermal power delivered by the nuclear at period $t$ [kWt]
-        self.model.xnsu = pe.Var(self.model.T, domain=pe.NonNegativeReals)     #x^{nsu}: Nuclear start-up power consumption at period $t$ [kWt]
+        self.model.s = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.Eu), units=u.kWh)    #s: TES reserve quantity at period $t$  [kWt$\cdot$h]
+        self.model.unsu = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kWh)     #u^{nsu}: Nuclear start-up energy inventory at period $t$ [kWt$\cdot$h]
+        self.model.xn = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW)	    #x^n: Thermal power delivered by the nuclear at period $t$ [kWt]
+        self.model.xnsu = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW)      #x^{nsu}: Nuclear start-up power consumption at period $t$ [kWt]
         
         #------- Binary Variables ---------
         self.model.yn = pe.Var(self.model.T, domain=pe.Binary)        #y^r: 1 if nuclear is generating ``usable'' thermal power at period $t$; 0 otherwise
@@ -142,10 +143,10 @@ class NuclearDispatch(GeneralDispatch):
                     - (model.Ccsu*model.ycsup[t] + 0.1*model.Cchsp*model.ychsp[t] + model.alpha*model.ycsd[t])
[…]

### 2021-07-28 simulations/tests/test_modules.py
more module testing

@@ -8,6 +8,7 @@ Created on Thu Apr  1 14:36:02 2021
 
 from modules.NuclearTES import NuclearTES
 import unittest, os, math
+import numpy as np
 
 
 class TestPySAMModules(unittest.TestCase):
@@ -175,7 +176,7 @@ class TestPySAMModules(unittest.TestCase):
                 # create PySAM modules
                 mod.create_Plant()
                 
-                # testing safe deletion, will it throw error if Grid was never created?
+                # testing safe deletion, will it throw error if Grid/SO was never created?
                 if try_all:
                     mod.create_Grid()
                     mod.create_SO()
@@ -207,42 +208,166 @@ class TestPySAMModules(unittest.TestCase):
                                     "{0} Plant module still has Output {1}".format(mod.__class__.__name__ , k) )
             
             
-    # def test_log_SSC_arrays(self):
-    #     """ Testing the log_SSC_arrays method
+    def test_log_SSC_arrays(self):
+        """ Testing the log_SSC_arrays method
         
-    #     Here we test both instances of the method call, during simulations and
-    #     during the last simulation segment. 
-    #     """
+        Here we test both instances of the method call, during simulations and
+        during the last simulation segment. 
+        """
         
-    #     # running in time segments versus running full year at once
-    #     loop_modes = [True, False]
-    #     final_attrs = ['gen_log', 'capacity_factor', 'annual_energy']
+        # running in time segments versus running full year at once
+        loop_modes = [True, False]
+        final_attrs = ['gen_log', 'capacity_factor', 'annual_energy']
         
-    #     # looping through all modules
-    #     for mod in self.mod_list:
-    #         # looping through all loop modes for log_final being true
-    #         for mode in loop_modes: 
-                
-    #             # ================================================================
-    #             # test that method behaves correctly for given loop mode
-    #             mod.run_sim(run_loop=False)
-                
-                
-    #             # check attributes 
-    #             for f in final_attrs:
-                    
-    #                 # check that attributes exist
-    #                 self.assertTrue( hasattr(mod, f) , 
-    #                                 "{0} Plant module does not have output {1}".format(mod.__class__.__name__ , f) )
-                    
-    #                 # check that attribute is non-zero
-    #                 self.assertTrue( getattr(mod, f).sum() != 0 ,
-    #                                 "Output {0} sums up to 0 in module {1}".format(f, mod.__class__.__name__ ) )
-                
-    #             mod.reset_all()
+        # looping through all modules
[…]

### 2021-07-28 simulations/dispatch/NuclearDispatch.py
some unit fixes for constraints

@@ -204,13 +204,15 @@ class NuclearDispatch(GeneralDispatch):
         """
         def nuc_production_rule(model,t):
             """ Upper bound on thermal energy produced by NP """
-            return model.xn[t] + model.xnsu[t] + model.Qnsd*model.ynsd[t] <= model.Qin_nuc[t]
+            u = self.u_pyomo
+            return model.xn[t] + model.xnsu[t] + model.Qnsd*model.ynsd[t]/(1*u.hr) <= model.Qin_nuc[t]
         def nuc_generation_rule(model,t):
             """ Thermal energy production by NP only when operating """
             return model.xn[t] <= model.Qin_nuc[t] * model.yn[t]
         def min_generation_rule(model,t):
             """ Lower bound on thermal energy produced by NP """
-            return model.xn[t] >= model.Qnl * model.yn[t]
+            u = self.u_pyomo
+            return model.xn[t] >= model.Qnl/(1*u.hr) * model.yn[t]
         def nuc_gen_persist_rule(model,t):
             """ NP not able to operate if no thermal power (adapted from CSP) """
             return model.yn[t] <= model.Qin_nuc[t]/model.Qnl
@@ -315,9 +317,10 @@ class NuclearDispatch(GeneralDispatch):
         """
         def grid_sun_rule(model, t):
             """ Balance of power flow, i.e. sold vs purchased """
+            u = self.u_pyomo
             return (
                     model.wdot_s[t] - model.wdot_p[t] == (1-model.etac[t])*model.wdot[t]
-                		- model.Ln*(model.xn[t] + model.xnsu[t] + model.Qnl*model.ynsb[t])
+                		- model.Ln*(model.xn[t] + model.xnsu[t] + model.Qnl*model.ynsb[t]/(1*u.hr))
                 		- model.Lc*model.x[t] 
                         - model.Wb*model.ycsb[t] - model.Wnht*(model.ynsb[t]+model.ynsu[t])		#Is Wrsb energy [kWh] or power [kW]?  [az] Wrsb = Wht in the math?
             )

### 2021-07-28 simulations/modules/GenericSSCModule.py
adding new progress tracker when running loop

@@ -17,6 +17,7 @@ from util.SSCHelperMethods import SSCHelperMethods
 from dispatch.GeneralDispatch import GeneralDispatch as GD
 from dispatch.GeneralDispatch import GeneralDispatchParamWrap as GDP
 from dispatch.GeneralDispatch import GeneralDispatchOutputs as GDO
+from tqdm import tqdm
 import numpy as np
 import copy
 from abc import ABC, abstractmethod
@@ -274,12 +275,21 @@ class GenericSSCModule(ABC):
         self.run_Plant_through_SSC( time_start , time_next )
         self.log_SSC_arrays()
         
+        # setting up iterable time to cycle thorugh in for loop
+        p_time_next = int(np.round(time_next.to('d').m) )
+        p_time_end  = int(np.round(time_end.to('d').m) )
+        remaining_sim_time = range(p_time_next, p_time_end) if self.run_loop else range(0)
+        
         # this loop should only be entered if run_loop == True
-        while (time_next < time_end):
-            
+        for t in tqdm(remaining_sim_time):
+        
             # update time
             time_start += self.ssc_horizon.to('s')
             time_next  += self.ssc_horizon.to('s')
+            
+            # make sure we don't go over-time
+            if time_next > time_end:
+                time_next = time_end
             
             # update the current slice of SSC Horizon relative to full simulation
             self.slice_ssc_currentH = slice( int( time_start.to('hr').m ), 
@@ -287,10 +297,6 @@ class GenericSSCModule(ABC):
             # update the current slice of Pyomo Horizon relative to full simulation
             self.slice_pyo_currentH = slice( int( time_start.to('hr').m ), 
                                              int( (time_start + self.pyomo_horizon).to('hr').m  ), 1)  
-            
-            # time-printer
-            print_time = int(time_next.to('d').magnitude)
-            if not print_time % 10: print('   [%s / %s] completed.' % (print_time, np.round(time_end.to('d').m)) )
             
             # update: SSC(t) -> Plant(t+1)
             self.update_Plant_after_SSC( )
@@ -311,7 +317,7 @@ class GenericSSCModule(ABC):
             self.run_Plant_through_SSC( time_start, time_next )
             self.log_SSC_arrays()
         
-        print(' Plant Simulation successfully completed.')
+        print('\n Plant Simulation successfully completed.')
         
         
     def run_Plant_through_SSC(self, start_hr, end_hr):
@@ -600,6 +606,7 @@ class GenericSSCModule(ABC):
         
         # ==========================================================================
[…]

### 2021-07-28 simulations/tests/test_nuctes.py
testing dispatch parameters and literal unit testing

@@ -7,7 +7,10 @@ Created on Thu Apr  1 14:36:02 2021
 """
 
 from modules.NuclearTES import NuclearTES
+from dispatch.NuclearDispatch import NuclearDispatch
 import unittest
+from pyomo.util.check_units import assert_units_consistent, assert_units_equivalent, check_units_equivalent
+
 
 class TestNuclearTES(unittest.TestCase):
     """
@@ -24,7 +27,7 @@ class TestNuclearTES(unittest.TestCase):
         """
         
         # creating instance of module
-        self.nuctes = NuclearTES(json_name='tests/test_nuctes')
+        self.nuctes = NuclearTES(json_name='tests/test_nuctes', is_dispatch=True)
         self.nuctes_name = self.nuctes.__class__.__name__
         
     
@@ -56,7 +59,63 @@ class TestNuclearTES(unittest.TestCase):
             # checking that the attribute exists
             self.assertTrue(hasattr(self.nuctes,attr) ,
                             "Something went wrong when {0} called 'store_csv_arrays method, {1} does not exist".format(self.nuctes_name, attr) )
+
+
+    def test_create_dispatch_params(self):
+        """ Testing the creation of a parameter dictionary for NuclearDispatch
+        """
+        
+        attr_list = ['Ec',        # from GeneralDispatch.set_power_cycle_parameters()
+                     'P',         # from GeneralDispatch.set_time_indexed_parameters()
+                     'Cpc',       # from GeneralDispatch.set_fixed_cost_parameters()
+                     'Cnuc',      # from NuclearDispatch.set_fixed_cost_parameters()
+                     'En',        # from NuclearDispatch.set_nuclear_parameters()
+                     'Qin_nuc',   # from NuclearDispatch.set_time_series_nuclear_parameters()
+                     'y0',        # from GeneralDispatch.set_initial_state()
+                     'yn0' ]      # from NuclearDispatch.set_initial_state()
+                 
+        
+        # feigning a pyomo horizon slice
+        time_slice = slice(0,48,1)
+        
+        # create the dictionary
+        params_dict = self.nuctes.create_dispatch_params( time_slice )
+        
+        # looping through all defined attributes
+        for attr in attr_list:
             
+            # checking that the attribute exists
+            self.assertIn( attr, params_dict.keys() ,
+                            "Parameter {0} is not found in dispatch parameter dictionary for {1}".format(attr, self.nuctes_name) )
+
+
[…]

### 2021-07-29 simulations/dispatch/NuclearDispatch.py
fixing unit definitions in constraints

@@ -185,7 +185,8 @@ class NuclearDispatch(GeneralDispatch):
             return model.xnsu[t] <= model.Qnu*model.ynsu[t]
         def nontrivial_solar_rule(model,t):
             """ NP trivial power prevents startup """
-            return model.ynsu[t] <= model.Qin_nuc[t]
+            u = self.u_pyomo
+            return model.ynsu[t] <= model.Qin_nuc[t] / (1*u.kW)
         
         self.model.nuc_inventory_con = pe.Constraint(self.model.T,rule=nuc_inventory_rule)
         self.model.nuc_inv_nonzero_con = pe.Constraint(self.model.T,rule=nuc_inv_nonzero_rule)
@@ -215,7 +216,8 @@ class NuclearDispatch(GeneralDispatch):
             return model.xn[t] >= model.Qnl/(1*u.hr) * model.yn[t]
         def nuc_gen_persist_rule(model,t):
             """ NP not able to operate if no thermal power (adapted from CSP) """
-            return model.yn[t] <= model.Qin_nuc[t]/model.Qnl
+            u = self.u_pyomo
+            return model.yn[t] <= model.Qin_nuc[t]/model.Qnl * (1*u.hr)
         
         self.model.nuc_production_con = pe.Constraint(self.model.T,rule=nuc_production_rule)
         self.model.nuc_generation_con = pe.Constraint(self.model.T,rule=nuc_generation_rule)
@@ -284,9 +286,10 @@ class NuclearDispatch(GeneralDispatch):
         """
         def tes_balance_rule(model, t):
             """ Balance of energy to and from TES """
+            u = self.u_pyomo
             if t == 1:
-                return model.s[t] - model.s0 == model.Delta[t] * (model.xn[t] - (model.Qc[t]*model.ycsu[t] + model.Qb*model.ycsb[t] + model.x[t] + model.Qnsb*model.ynsb[t]))
-            return model.s[t] - model.s[t-1] == model.Delta[t] * (model.xn[t] - (model.Qc[t]*model.ycsu[t] + model.Qb*model.ycsb[t] + model.x[t] + model.Qnsb*model.ynsb[t]))
+                return model.s[t] - model.s0 == model.Delta[t] * (model.xn[t] - (model.Qc[t]*model.ycsu[t] + model.Qb*model.ycsb[t] + model.x[t] + model.Qnsb*model.ynsb[t]/(1*u.hr)))
[…]

### 2021-07-29 simulations/tests/test_dispatch.py

@@ -1,0 +1,39 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jul 28 16:54:26 2021
+
+@author: gabrielsoto
+"""
+
+
+from dispatch.GeneralDispatch import GeneralDispatch
+import unittest
+
+class TestGeneralDispatch(unittest.TestCase):
+    """
+    Unit tests for General Dispatch module
+    
+    This testing suite is meant to test the general Dispatch module of 
+    the NE2 architecture. Here we have 
+    """
+
+    def setUp(self):
+        """ Creating instance of GeneralDispatch upon start of each test
+        """
+        
+        # creating instance of module
+        self.dispatch = GeneralDispatch({})
+        
+    
+    def tearDown(self):
+        """ Deleting instance of GeneralDispatch at end of each test
+        """
+        
+        # deleting each module
+        del self.dispatch
+    
+
+if __name__ == "__main__":
+    unittest.main()
+            

### 2021-07-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Uploading paper for methods and material section review

--- 2021-07-22 papers/white-cycle-modeling/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 \subsection{Cycle Component Modeling}
+\subsubsection{Counter Flow and Black Box Heat Exchangers}
 
-\subsubsection{Heat Exchangers}
 \subsubsection{Turbines}
+
 \subsubsection{Compressors}
+
+\subsubsection{Lead-Fast Reactor}
+
 \subsubsection{Concentrating Solar Power Cycle}
 
-\subsection{Cycle Models}
+The CSP cycles modeled in this paper are composed of the hot and cold thermal energy storage, pumps to move the molten salt, and a black box heat input.
+The diagram for this CSP cycle is seen in Figure \ref{csp}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\end{paracol}
+\begin{figure}[H] 
+    \widefigure
+    \includegraphics[width=10 cm]{Definitions/csp.pdf}
+    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
 
-%This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+The salt CSP cycle can be either in charging mode or electrical generation mode.
+When the CSP cycle is in charging mode, excess heat is transfered from the sCO$_{2}$ Brayton cycle through the SALT HX.
+The heated salt is then stored in the hot storage until grid demand increases.
 
-There are various cycles that have been modeled to test their advantages and disadvantages.
-These various models cycles two different categories: non-charging and charging.
-The non-charging category will decide the configuration of the cycle with a focus on generating electricity.
-This includes the number of turbines, recuperators, and where heat is put into the system by the CSP and LFR.
-The charging category tests different locations of where heat is drawn from the LFR to be stored in the CSP's TES for later use.
+When electrical generation is occuring, the heat input in this cycle is accomplished through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
+The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
+The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the heliostat field is added.
 
-\subsection{Non-Charging Cycle Configurations}%===================================
+\subsection{Generalization of Cycle Modeling}
 
-The cycles presented are generalized in order to draw a more direct comparison between cycles.
-These general parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
+The cycles presented are generalized in order to draw a more direct comparison.
+The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
 These values are summarized in Table \ref{cycle-constants}.
@@
     Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
-    Lead-Fast Reactor Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
+    %Lead-Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
+    Lead-Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
     \midrule
@@
 
+In addition to generalized parameters, all cycles have identical recompression sides.
+The recompression side contains a PreCooler, Low Temperature Recuperator, and two compressors; Main Compressor and ReCompressor.
+
+\subsection{Non-Charging Cycle Configurations}%===================================
+Various cycles are modeled to test their advantages and disadvantages.
+These cycle models fall into two categories: non-charging and charging.
+The non-charging category decides the configuration of the cycle with a focus on electricity generation.
+This includes the number and location of turbines, recuperators, and heat input to the system by the CSP and LFR.
+To quantify the effectiveness of the non-charging configurations, a cycle efficiency, $\eta_{cycle}$, is defined in Equation \ref{eq-eta-cycle}.
+
+\begin{equation}
+    \label{eq-eta-cycle}
+    \eta_{heatstorage} = \frac{\dot{W}_{T}-\dot{W}_{MC}-\dot{W}_{RC}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
+\end{equation}
+
+The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$.
+The denominator is the total power input into the system from the LFR, $\dot{Q}_{LFRHX}$, and CSP, $\dot{Q}_{CSPHX}$.
+
 \subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON} %--------------------------------------------------------
 
-The first cycle that will be tested has independent sCO$_{2}$ loops bridged by the CSP.
-This cycle has two Brayton Cycles: a LFR cycle and a CSP cycle.
+The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a salt CSP cycle.
+This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON.
+Configuration of components for these two cycles is identical with the exception of heat inputs.
+C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from a CSP.
 These two cycles individually operate when the focus of plant operation is primarily electricity generation.
@@
 
+Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
+The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency.
+The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K.
+
+The CSP cycle for this two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
+The diagram has the necessary pumps, TES tanks, and salt heat exchangers to be representative of a relizable salt CSP cycle.
+
+\end{paracol}
+\begin{figure}[H] 
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-csp-on.pdf}
+    \caption{Diagram for C-CSP-ON with focus on electricity generation\label{c-csp-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+ Due to the individual operation while the cycles are generating electricity, C-CSP-ON is not directly impacted by the LFR low end temperatures.
+Instead, a sensitivity study is done on the temperature of the cold TES.
+Two temperatures are tested, 663.2 K and 713.2 K, to observe the impact of cold TES temperature on cycle efficiency.
+
+\subsubsection{C-1HTR1T-ON} %-----------------------------------------------------
+
+One drawback of having a two-cycle design, as seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components.
+Combining the two cycles into one would reduce redundancy and complexity.
+Heat addition from the CSP and LFR in parallel orientation is therefore studied in the C-1HTR1T-ON model.
+This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency.
+The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.
+
+\end{paracol}
+\begin{figure}[H] 
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
+    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+In this cycle, the LFR and CSP have identical inlet temperatures due to splitting the flow prior to their parallel orientation.
+Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model.
+The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency.
+The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K.
+The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature.
+To obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K.
+
+\subsubsection{C-2HTR3T-ON} %-----------------------------------------------------
+
+Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency.
+To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired.
+This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
+The LFR is powering one turbine, T1, and recuperating heat through a dedicated high temperature recuperator, HTR1.
+The CSP cycle also contains two seperate turbines, T2, while having a dedicated high temperature recuperator, HTR2.
+After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-2htr3t-on.pdf}
+    \caption{Diagram for C-2HTR3T-ON with focus on electricity generation\label{c-2htr3t-on}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+Three sensitivity studies are done on the C-2HTR3T-ON model.
+Two with the LFR low temperature constrained and one without this constraint.
+The two constrained studies had varied cold CSP TES temperature with the lowest temperature of 663.2 K and highest temperature of 713.2 K.
+The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of 663.2 K.
+
+\subsection{Thermal Energy Storage Charging Techniques} %=========================
+
+Charging cycle configurations focus on an energy storage operating mode.
+These configurations test the optimal location of LFR heat extraction through the SALT HX.
+To maximize the available heat for extraction, alternator power is set to zero and turbine power is therefore equal to the compressors' demand.
+The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases.
+Comparison of where thermal energy is extracted in the cycle is done by using the same Brayton cycle, C-LFR-ON, and configuring the salt heat exchanger in different locations around the turbine.
+To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
+
+\begin{equation}
+    \label{eq-eta-heatstorage}
+    \eta_{heatstorage} = \frac{\dot{Q}_{SALT}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
+\end{equation}
+
+Whereas $\dot{Q}_{SALT}$ is the amount of heat transfered through the SALT HX and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR and CSP.
+
+\subsubsection{C-LFR-PRE} %-------------------------------------------------------
+
+Flow leaving the turbine contains excess thermal energy that is not transformed into electrical energy.
+This excess thermal energy is stored in the hot CSP TES.
+The diagram outlining this process is C-LFR-PRE in Fig.
+\ref{c-lfr-pre}.
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-pre.pdf}
+    \caption{Diagram for C-LFR-PRE thermal energy storage charging orientation\label{c-lfr-pre}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+Problems arise with this salt charging configuration.
+The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of 833.2 K.
+To raise the temperature, some of the high temperature flow before the turbine is redirected through a valve and combined after the turbine.
+Combining different temperature flows and reducing the flow through the turbine has a large impact on heat storage efficiency.
+
+\subsubsection{C-LFR-POST} %------------------------------------------------------
+
+Moving the heat extraction prior to the turbine is analyzed in C-LFR-POST. This diagram is seen in Figure \ref{c-lfr-post}.
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-post.pdf}
+    \caption{Diagram for C-LFR-POST thermal energy storage charging orientation\label{c-lfr-post}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+This TES charging cycle extracts heat before the turbine and therefore would have a large negative effect on the amount of work that the turbine could produce.
+The turbine needs to offset the requirements of both compressors and this would require the inlet temperature to be high.
+The amount of energy that could be extracted before the turbine would be small and therefore the heat storage efficiency would be small.
+There is no quantitative study done on this diagram because, due to the efficiency losses, it is non-viable.
+
+\subsubsection{C-LFR-PAR} %-------------------------------------------------------
+
+The requirement of the turbine and CSP hot TES temperature can be accomplished by splitting the flow before the turbine.
+The flow through the salt heat exchanger in this cycle is therefore seperate from the turbine.
+After the salt heat exchanger a valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-par.pdf}
+    \caption{Diagram for C-LFR-PAR thermal energy storage charging orientation\label{c-lfr-par}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+Two sensitivity studies with varying cold CSP TES are desired to see the impact on heat storage efficiency.
+The TES temperature study is calculated with a low TES temperature of 663.2 K and a high TES temperature of 713.2 K.
+
+\subsubsection{C-LFR-CIRC} %------------------------------------------------------
+
+The full diagram for C-LFR-CIRC is shown in Figure \ref{c-lfr-circ}.
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-lfr-circ.pdf}
+    \caption{Full diagram for C-LFR-CIRC thermal energy storage charging orientation\label{c-lfr-circ}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+The charging subsection of this diagram is composed of a circulation cycle that has heat inputed through the LFR heat exchanger.
+This subsection is encircled in blue and can be seen in Figure \ref{c-lfr-circ-sub}.
+
+\end{paracol}
+\begin{figure}[H]
+    \widefigure
+    \includegraphics[width=10 cm]{Definitions/c-lfr-circ-sub.pdf}
+    \caption{Diagram for C-LFR-CIRC subcycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+The flow continues through a circulator which is assumed to have neglegible pressure rise.
+A heat exchanger, SALT HX, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
+Excess heat that is not extracted is then dumped into a reservior through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of 673.2 K.
+Three different temperatures; 663.2 K, 683.2 K, and 713.2 K, are compared in a sensitivity study.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
+\subsection{Non-Charging Cycle Configurations}
+
+\subsubsection{C-LFR-ON and C-CSP-ON}
+
 Modeling the C-LFR-ON cycle in EES yeilded the results in Table \ref{tab-c-lfr-on}.
-Two seperate sensitivity studies were completed on the LFR inlet temperature.
-The unconstrained (\textit{U}) values were from parametric studies on mass flow to the main compressor while maximizing cycle efficiency.
-The constrained (\textit{C}) values were calculated by setting the LFR inlet temperature to the design value of 673.2 K.
 
@@
 
-The CSP cycle for this two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
-The CSP is shown in this diagram with the necessary pumps, TES tanks, and salt heat exchanger.
-
-\end{paracol}
-\begin{figure}[H] 
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-csp-on.pdf}
-    \caption{Diagram for C-CSP-ON with focus on electricity generation\label{c-csp-on}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
- C-CSP-ON is not directly impacted by constrained or unconstrained LFR low temperatures because it is an independent cycle while focused on electricity generation.
-Instead a sensitivity study was done on the temperature of the cold TES.
-Two temperatures were tested, 663.2 K and 713.2 K, to observe the impacts on cycle efficiency.
 The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
@@
 
-\subsubsection{C-1HTR1T-ON} %-----------------------------------------------------
+\subsubsection{C-1HTR1T-ON}
 
-One of the drawbacks of having a two-cycle design as seen in the C-LFR-ON and C-CSP-ON is the number of system components is essentially doubled.
-Combining the two cycles into one would reduce this redundancy.
-Heat addition from the CSP and LFR in parallel orientation was therefore studied in the C-1HTR1T-ON model.
-This model is important to study the impact on cycle efficiency when mixing different temperature flows prior to the turbine.
-The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.
-
-\end{paracol}
-\begin{figure}[H] 
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
-    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-In this cycle the LFR and CSP are linked due to the parallel orientation.
-Therefore, three sensitivity studies were done on the C-1HTR1T-ON EES model.
-The initial two studies had the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency.
-The two tested values for cold CSP TES with constrained LFR low temperature were 683.2 K and 713.2 K.
-The desired cold CSP TES temperature of 663.2 K was not possible with the constraint on the LFR low temperature.
-To obtain the desired cold CSP TES temperature, the constraint was removed droping the temperature of the LFR inlet to 653.2 K.
 These values are displayed in Table \ref{tab-c-1htr1t-on}.
@@
 
-\subsubsection{C-2HTR3T-ON} %-----------------------------------------------------
+\subsubsection{C-2HTR3T-ON}
 
-Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency.
-To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine was desired.
-This cycle is labeled at C-2HTR3T-ON.
-This cycle, seen in Figure \ref{c-2htr3t-on}, has two high temperature recuperators and three turbines.
-
-\end{paracol}
-\begin{figure}[H]
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-2htr3t-on.pdf}
-    \caption{Diagram for C-2HTR3T-ON with focus on electricity generation\label{c-2htr3t-on}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-Three sensitivity studies were done on the C-2HTR3T-ON model.
-Two with the LFR low temperature constrained and one without this constraint.
-The two constrained studies had varied cold CSP TES temperature with the lowest temperautre of 663.2 K and highest temperature of 713.2 K.
-The unconstrained low LFR inlet study was done at a cold CSP TES temperature of 663.2 K.
 The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
@@
 
-\subsection{Thermal Energy Storage Charging Techniques} %=========================
+\subsection{Thermal Energy Storage Charging Techniques}
 
-When the grid demand is not high, the non-charging cycle configurations focus on an energy storage operating mode.
-Alternator power is set to zero and power from the turbine is solely powering the two compressors.
-The excess energy from the LFR is thermally stored in the TES for later use instead of generating electricity.
-Comparison of where thermal energy is drawn from the cycle is done by using the same recompression cycle and configuring the salt heat exchanger in different locations around the turbine.
+\subsubsection{C-LFR-PRE}
 
-\subsubsection{C-LFR-PRE} %-------------------------------------------------------
-
-Flow leaves the turbine with excess thermal energy that was not transformed into mechanical energy.
-This thermal energy can be used to charge the hot CSP TES.
-The diagram outlining this process is C-LFR-PRE in Figure \ref{c-lfr-pre}.
-
-\end{paracol}
-\begin{figure}[H]
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-lfr-pre.pdf}
-    \caption{Diagram for C-LFR-PRE thermal energy storage charging orientation\label{c-lfr-pre}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-Problems arise with this salt charging configuration.
-The primary issue is that the temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of 833.2 K.
-To raise the temperature, some of the high temperature flow before the turbine is redirected through a valve and combined after the turbine.
-This combination of different temperature flows has a large impact on heat storage efficiency.
 The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
@@
 
-\subsubsection{C-LFR-POST} %------------------------------------------------------
+\subsubsection{C-LFR-POST}
 
-Moving the heat extraction prior to the turbine was qualitatively analyzed in C-LFR-POST. This diagram is seen in Figure \ref{c-lfr-post}.
+\subsubsection{C-LFR-PAR}
 
-\end{paracol}
-\begin{figure}[H]
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-lfr-post.pdf}
-    \caption{Diagram for C-LFR-POST thermal energy storage charging orientation\label{c-lfr-post}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-This TES charging cycle was extracting heat before the turbine and therefore would have a large negative effect on the amount of work that the turbine could produce.
-The turbine needs to offset the requirements of both compressors and this would require the inlet temperature to be high.
-The amount of energy that could be extracted before the turbine would be small and therefore the heat storage efficiency would be small.
-There was no quantitative study done on this diagram because it theoreticaly would be non-viable.
-
-\subsubsection{C-LFR-PAR} %-------------------------------------------------------
-
-The requirement of the turbine and hot CSP TES temperature could be accomplished by splitting the flow before the turbine.
-The flow through the salt heat exchanger would therefore be seperate from the turbine.
-After the salt heat exchanger a valve would need to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
-
-\end{paracol}
-\begin{figure}[H]
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-lfr-par.pdf}
-    \caption{Diagram for C-LFR-PAR thermal energy storage charging orientation\label{c-lfr-par}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-This cycle had two sensitivity studies done with varying cold CSP TES.
-The low temperature study was done at 663.2 K and the high temperature study was done at 713.2 K.
 The results from this study are displayed in Table \ref{tab-c-lfr-par}.
@@
 
-\subsubsection{C-LFR-CIRC} %------------------------------------------------------
+\subsubsection{C-LFR-CIRC}
 
-The full diagram for C-LFR-CIRC is shown in Figure \ref{c-lfr-circ}.
-
-\end{paracol}
-\begin{figure}[H]
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-lfr-circ.pdf}
-    \caption{Full diagram for C-LFR-CIRC thermal energy storage charging orientation\label{c-lfr-circ}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-The charging subsection of this diagram is composed of a circulation cycle that has heat inputed through the LFR heat exchanger. This subsection is seen in Figure \ref{c-lfr-circ-sub}.
-
-\end{paracol}
-\begin{figure}[H]
-    \widefigure
-    \includegraphics[width=10 cm]{Definitions/c-lfr-circ-sub.pdf}
-    \caption{Diagram for C-LFR-CIRC subcycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
-\end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-The flow then continues through a circulator which has neglegible pressure rise.
-A heat exchanger then extracts heat from the flow, transfering into the hot TES for later use.
-Excess heat that is not extracted is then dumped into a reservior through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of 673.2 K.
-Three different temperatures; 663.2 K, 683.2 K, and 713.2 K, are compared in Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.\\
+Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
 
@@
 \end{specialtable}
+
+%This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
 
@@
 \end{equation}
+
 the text following an equation need not be a new paragraph. Please punctuate equations as regular text.

### 2021-07-29 simulations/dispatch/NuclearDispatch.py
fixing unit issues with Qs and Es. updating to phoenix weather

@@ -185,8 +185,7 @@ class NuclearDispatch(GeneralDispatch):
             return model.xnsu[t] <= model.Qnu*model.ynsu[t]
         def nontrivial_solar_rule(model,t):
             """ NP trivial power prevents startup """
-            u = self.u_pyomo
-            return model.ynsu[t] <= model.Qin_nuc[t] / (1*u.kW)
+            return model.ynsu[t] <= model.Qin_nuc[t] / model.Qnl
         
         self.model.nuc_inventory_con = pe.Constraint(self.model.T,rule=nuc_inventory_rule)
         self.model.nuc_inv_nonzero_con = pe.Constraint(self.model.T,rule=nuc_inv_nonzero_rule)
@@ -205,19 +204,16 @@ class NuclearDispatch(GeneralDispatch):
         """
         def nuc_production_rule(model,t):
             """ Upper bound on thermal energy produced by NP """
-            u = self.u_pyomo
-            return model.xn[t] + model.xnsu[t] + model.Qnsd*model.ynsd[t]/(1*u.hr) <= model.Qin_nuc[t]
+            return model.xn[t] + model.xnsu[t] + model.Qnsd*model.ynsd[t] <= model.Qin_nuc[t]
         def nuc_generation_rule(model,t):
             """ Thermal energy production by NP only when operating """
             return model.xn[t] <= model.Qin_nuc[t] * model.yn[t]
         def min_generation_rule(model,t):
             """ Lower bound on thermal energy produced by NP """
-            u = self.u_pyomo
-            return model.xn[t] >= model.Qnl/(1*u.hr) * model.yn[t]
+            return model.xn[t] >= model.Qnl * model.yn[t]
         def nuc_gen_persist_rule(model,t):
             """ NP not able to operate if no thermal power (adapted from CSP) """
-            u = self.u_pyomo
-            return model.yn[t] <= model.Qin_nuc[t]/model.Qnl * (1*u.hr)
+            return model.yn[t] <= model.Qin_nuc[t] / model.Qnl 
         
         self.model.nuc_production_con = pe.Constraint(self.model.T,rule=nuc_production_rule)
         self.model.nuc_generation_con = pe.Constraint(self.model.T,rule=nuc_generation_rule)
@@ -286,10 +282,9 @@ class NuclearDispatch(GeneralDispatch):
[…]

### 2021-07-29 simulations/scripts/output_scripts/plot_psweep_nucTES_pricePerformance_wDispatch.py
plotting only PPA and simple revenue

@@ -27,7 +27,7 @@ print("PID = ", pid)
 
 # locating output directory
 output_dir = FileMethods.output_dir
-filename   = 'pricePerfvsDispatch_sizingTESandCycle_irr11pct_simplerevenue.nuctes' 
+filename   = 'pricePerfvsDispatch_TES_6_15__Pref_500_1000_irr11pct.nuctes' 
 NTPath = os.path.join(output_dir, filename)
 
 # pickling
@@ -62,31 +62,30 @@ def print_string_header(header):
     print("=====================================================\n")
 
 # creating figure
-fig = plt.figure(figsize=[18.5,6])
+fig = plt.figure(figsize=[13,6])
 fig.suptitle("IRR: {0:.1f}".format(irr_mean), fontsize=14, fontweight='bold')
-ax1 = fig.add_subplot(131)
-ax2 = fig.add_subplot(132)
-ax3 = fig.add_subplot(133)
+ax1 = fig.add_subplot(121)
+ax2 = fig.add_subplot(122)
+
 
 # adjusting space between 
 plt.subplots_adjust(wspace=0.4)
 
 # names of dispatch scenarios
-dispatch_scenarios  = ['Pyomo - 24hr Horizon', 'Pyomo - 48hr Horizon', 'No Pyomo - SSC Only']  
+dispatch_scenarios  = ['Pyomo - 48hr Horizon', 'No Pyomo - SSC Only']  
 
 # specific performance metrics to plot 
-performance_metrics = [annual_energy_array, ppa_array, revenue]
+performance_metrics = [ppa_array, revenue]
 N              = len(performance_metrics)
-get_max        = [True, False, True] # whether each performance is optimized with max or min
-axes           = [ax1,ax2,ax3] # list of axes
-heat_cmap_list = ['Blues', 'Blues_r', 'Blues'] # colormaps used for each performance metric
-metric_labels  = ['Annual Energy Production \n(TWh)',
-                  'PPA Price \n(cents/kWh)',
+get_max        = [False, True] # whether each performance is optimized with max or min
+axes           = [ax1,ax2] # list of axes
+heat_cmap_list = ['Blues_r', 'Blues'] # colormaps used for each performance metric
+metric_labels  = ['PPA Price \n(cents/kWh)',
                   'Revenue - Simple Calculation \n($B)' ] # labels for each performance metric
 
 # some other arrays
-P_array  = P_ref * p_mult #actual power cycle reference outputs
-lp = 12 #labelpad
[…]

### 2021-07-29 simulations/scripts/output_scripts/generate_psweep_nucTES_pricePerformance_wDispatch.py
working script for generating sweeps, nuc plant operating at full

@@ -23,13 +23,13 @@ print("PID = ", pid)
 # =============================================================================
 
 # setting up arrays to cycle through
-dispatch  = np.array([ True, True, False ])
-tshours   = np.array([ 10, 12, 14, 16, 18])
-p_mult    = np.array([ 1.05, 1.15, 1.25, 1.35, 1.45])
+dispatch  = np.array([ True, False ])
+tshours   = np.array([ 6, 9, 12, 15])
+p_mult    = np.array([ 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000])
 
 # SSC and dispatch horizons for each dispatch element above ^
-sscH = np.array([12, 24, 24])
-pyoH = np.array([24, 48, 48])
+sscH = np.array([24, 24])
+pyoH = np.array([48, 48])
 
 # baseline cycle power output
 P_ref = 465
@@ -81,7 +81,7 @@ for d,dp in enumerate(dispatch): #over dispatch type
             nuctes.dispatch_wrap = nuctes.create_dispatch_wrapper( nuctes.PySAM_dict )
             
             # update SSC dictionary parameters
-            nuctes.SSC_dict['P_ref'] = fm*P_ref
+            nuctes.SSC_dict['P_ref'] = fm
             nuctes.SSC_dict['tshours'] = th
             
             # update target IRR, nominal was 11% for CSP
@@ -155,7 +155,7 @@ Storage['simple_revenue']      = simple_revenue
 
 # locating output directory
 output_dir = FileMethods.output_dir
-filename   = 'pricePerfvsDispatch_sizingTESandCycle_irr11pct_simplerevenue.nuctes' 
+filename   = 'pricePerfvsDispatch_TES_6_15__Pref_500_1000_irr11pct.nuctes' 
 NTPath = os.path.join(output_dir, filename)
 
 # pickling

### 2021-07-29 simulations/dispatch/SolarDispatch.py
adding units to variables and fixing parameter units

@@ -112,12 +112,13 @@ class SolarDispatch(GeneralDispatch):
         # generating GeneralDispatch variables first (PowerCycle, etc.)
         GeneralDispatch.generate_variables(self)
         
+        u = self.u_pyomo
         ### Decision Variables ###
         #------- Variables ---------
-        self.model.s = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.Eu))    #s: TES reserve quantity at period $t$  [kWt$\cdot$h]
-        self.model.ursu = pe.Var(self.model.T, domain=pe.NonNegativeReals)     #u^{rsu}: Receiver start-up energy inventory at period $t$ [kWt$\cdot$h]
-        self.model.xr = pe.Var(self.model.T, domain=pe.NonNegativeReals)       #x^r: Thermal power delivered by the receiver at period $t$ [kWt]
-        self.model.xrsu = pe.Var(self.model.T, domain=pe.NonNegativeReals)     #x^{rsu}: Receiver start-up power consumption at period $t$ [kWt]
+        self.model.s = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.Eu), units=u.kWh)    #s: TES reserve quantity at period $t$  [kWt$\cdot$h]
+        self.model.ursu = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kWh)     #u^{rsu}: Receiver start-up energy inventory at period $t$ [kWt$\cdot$h]
+        self.model.xr = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW)       #x^r: Thermal power delivered by the receiver at period $t$ [kWt]
+        self.model.xrsu = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW)     #x^{rsu}: Receiver start-up power consumption at period $t$ [kWt]
         
         #------- Binary Variables ---------
         self.model.yr = pe.Var(self.model.T, domain=pe.Binary)        #y^r: 1 if receiver is generating ``usable'' thermal power at period $t$; 0 otherwise
@@ -184,7 +185,7 @@ class SolarDispatch(GeneralDispatch):
             return model.xrsu[t] <= model.Qru*model.yrsu[t]
         def nontrivial_solar_rule(model,t):
             """ CSP trivial power prevents startup """
-            return model.yrsu[t] <= model.Qin[t]
[…]

### 2021-07-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Comments and minor alterations to paper

@@
 The salt CSP cycle can be either in charging mode or electrical generation mode. 
+%Here you need to explain what a conventional CSP cycle looks like (briefly).
+I.e.
+CSP charges salt, it can discharge when you want it to.
+Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
 When the CSP cycle is in charging mode, excess heat is transfered from the sCO$_{2}$ Brayton cycle through the SALT HX.
 The heated salt is then stored in the hot storage until grid demand increases.
+%Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX
 
-When electrical generation is occuring, the heat input in this cycle is accomplished through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
+When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
 The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
@@
 
-The values displayed in Table \ref{cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Corporation.
+The values displayed in Table \ref{cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Company.
 
@@
 These cycle models fall into two categories: non-charging and charging.
-The non-charging category decides the configuration of the cycle with a focus on electricity generation.
+The non-charging category is used to determine the configuration of the cycle with a focus on electricity generation.
 This includes the number and location of turbines, recuperators, and heat input to the system by the CSP and LFR.
@@
 The denominator is the total power input into the system from the LFR, $\dot{Q}_{LFRHX}$, and CSP, $\dot{Q}_{CSPHX}$.
+
+%BL: I would include the naming scheme upfront and give a table (C-LFR-ON etc.)
 
@@
 The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency.
-The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K.
+The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400^${circ}C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
+%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint
 
@@
 
+%BL: be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from
+
 \end{paracol}
@@
 The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K.
-The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature.
-To obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K.
+The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt).
+In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K.
+%BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
+Asp you will want to explain the criteria that go into cold storage temp.
+Lower = more delta T = more dispatchability
 
@@
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
+%BL: this is more about having a compromise option of intermediate complexity and efficiency
 
@@
 The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of 663.2 K.
+%BL: this is clearer than the previous one but bullets could still be useful
 
@@
 To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
+%BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output
+%BL: SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage
 
@@
 The amount of energy that could be extracted before the turbine would be small and therefore the heat storage efficiency would be small.
-There is no quantitative study done on this diagram because, due to the efficiency losses, it is non-viable.
+There is no quantitative study done on this case because, due to the efficiency losses, it is non-viable.
 
@@
 
+%BL: explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)
+
 \end{paracol}
@@
 
-The flow continues through a circulator which is assumed to have neglegible pressure rise.
+The flow continues through a circulator which is assumed to have neglegible pressure rise (i.e.
+there is assumed to be negligible pressure drop in this case).
 A heat exchanger, SALT HX, extracts heat from the flow, storing the thermal energy in the hot TES for later use.

### 2021-07-30 simulations/dispatch/GeneralDispatch.py
adding ability to read in Q_thermal from plant outputs
idea is we call SSC once before running dispatch and just extract Receiver Q_in as an input to dispatch

@@ -787,7 +787,7 @@ class GeneralDispatchParamWrap(object):
         if np.isnan(e_pb_suinitremain): # SSC seems to report NaN when startup is completed
             self.ucsu0 = self.Ec
         else:   
-            self.ucsu0 = max(0.0, self.Ec - e_pb_suinitremain ) 
+            self.ucsu0 = max(0.0*u.MWh, self.Ec - e_pb_suinitremain ) 
             if self.ucsu0 > (1.0 - tol)*self.Ec:
                 self.ucsu0 = self.Ec
         

### 2021-07-30 simulations/dispatch/SolarDispatch.py

@@ -489,7 +489,7 @@ class SolarDispatchParamWrap(GeneralDispatchParamWrap):
         return param_dict
 
 
-    def set_time_series_solar_parameters(self, param_dict, updated_dict=None):
+    def set_time_series_solar_parameters(self, param_dict, plant_dict, updated_dict=None):
         """ Method to set fixed costs of the Plant for Dispatch optimization
         
         This method calculates some time series parameters for the Plant operations, startup,
@@ -517,8 +517,7 @@ class SolarDispatchParamWrap(GeneralDispatchParamWrap):
         
         # thermal power and startup params
         self.Drsu  = self.current_Plant['rec_su_delay']*u.hr   # Minimum time to start the CSP plant (hr)
-        self.Qin   = np.array([self.q_rec_design.m]*self.T)*self.q_rec_design.u if self.first_run \
-                                else self.current_Plant['q_dot_rec_inc']
+        self.Qin   = plant_dict['Q_thermal']*u.MW              # value here taken from a previous Plant-SSC run
         
         # instantiating arrays
         n  = len(self.Delta)

### 2021-07-30 simulations/modules/SolarTES.py

@@ -6,7 +6,7 @@ Created on Fri Jul 16 13:49:24 2021
 @author: gabrielsoto
 """
 
-import sys
+import sys, copy
 sys.path.append('..')
 import PySAM.TcsmoltenSalt as TcsmoltenSalt
 from modules.GenericSSCModule import GenericSSCModule
@@ -115,12 +115,112 @@ class SolarTES(NuclearTES):
         # run the setters from the GenericSSCModule parent class
         params = GenericSSCModule.create_dispatch_params(self, current_pyomo_slice)
         
+        # set up Plant outputs dictionary
+        plant_dict = self.Plant.Outputs.export()
+        
         # these are SolarTES-specific setters
         params = DW.set_solar_parameters( params )
-        params = DW.set_time_series_solar_parameters( params )
+        params = DW.set_time_series_solar_parameters( params, plant_dict )
         
         # this sets the initial states for the SolarTES
         params = DW.set_initial_state( params )
         
         return params
 
+
+    def update_Pyomo_after_SSC(self, params, current_pyomo_slice):
+        """ Update Pyomo inputs with SSC outputs from previous segment simulation
+        
+        Note:
+            self.run_loop    == True
+            self.is_dispatch == True 
+                          
+        This method uses the SSC end results from the previous simulation segment
+        and uses them to update the existing Dispatch parameter dictionary that
+        is ultimately sent to Pyomo. Essentially just updates the initial conditions
+        of the Dispatch parameter dictionary. 
+        
+        Args:
+            params (dict): 
+                dictionary of Pyomo dispatch parameters
+            current_pyomo_slice (slice): 
+                range of current pyomo horizon (ints representing hours)
+        Returns:
+            params (dict): 
+                updated dictionary of Pyomo dispatch parameters
+                
+        """
+        
+        updated_SSC_dict = copy.deepcopy(self.SSC_dict)
+        
+        # saving relevant end-of-sim outputs from the last simulation segment
+        updated_SSC_dict['rec_op_mode_initial']              = self.Plant.Outputs.rec_op_mode_final[self.t_ind-1]
+        updated_SSC_dict['rec_startup_time_remain_init']     = self.Plant.Outputs.rec_startup_time_remain_final[self.t_ind-1]
[…]

### 2021-07-30 simulations/modules/GenericSSCModule.py
calling SSC before dispatch calls, also safe exit from bad SSC calls

@@ -262,20 +262,26 @@ class GenericSSCModule(ABC):
         
         # run dispatch optimization for the first time
         if self.is_dispatch:
+            
+            # one pre-run of Plant, used to grab inputs to dispatch in some modules
+            # runs for the Pyomo Horizon, not the SSC Horizon
+            ssc_run_success = self.run_Plant_through_SSC( time_start , self.pyomo_horizon.to('s') )
+            
             # create dispatch parameters for the first time
             disp_params = self.create_dispatch_params( self.slice_pyo_currentH )
             
             # run pyomo optimization
-            self.run_pyomo(disp_params)
+            self.run_pyomo( disp_params )
             
             # update: Pyomo(t) -> Plant(t) 
             self.update_Plant_after_Pyomo()
         
-        # first execution of Plant through SSC
-        self.run_Plant_through_SSC( time_start , time_next )
+        # first real execution of Plant through SSC
+        ssc_run_success = self.run_Plant_through_SSC( time_start , time_next )
         self.log_SSC_arrays()
         
         # setting up iterable time to cycle thorugh in for loop
+        # TODO: this needs to be variable with SSC Horizon
         p_time_next = int(np.round(time_next.to('d').m) )
         p_time_end  = int(np.round(time_end.to('d').m) )
         remaining_sim_time = range(p_time_next, p_time_end) if self.run_loop else range(0)
@@ -314,10 +320,16 @@ class GenericSSCModule(ABC):
                 self.update_Plant_after_Pyomo( )
             
             # run Plant again
-            self.run_Plant_through_SSC( time_start, time_next )
+            ssc_run_success = self.run_Plant_through_SSC( time_start, time_next )
+            if not ssc_run_success:
+                print('\n Plant Simulation ended prematurely.')
+                self.log_SSC_arrays(log_final=True)
+                break
+            
             self.log_SSC_arrays()
         
-        print('\n Plant Simulation successfully completed.')
+        if ssc_run_success:
+            print('\n Plant Simulation successfully completed.')
         
         
     def run_Plant_through_SSC(self, start_hr, end_hr):
@@ -334,15 +346,24 @@ class GenericSSCModule(ABC):
                 starting time for next simulation (hours)
             end_hr (float Quant): 
                 ending time for next simulation (hours)
-            
+        Returns:
+            exec_success (bool): 
+                True if SSC execution is successful
         """
 
         # start and end times for full simulation
[…]

### 2021-07-30 simulations/util/SSCHelperMethods.py

@@ -9,6 +9,7 @@ Created on Fri May  7 10:50:27 2021
 import numpy as np
 import pint
 from pyomo.environ import units
+from util.FileMethods import FileMethods
 
 class SSCHelperMethods(object):
     """
@@ -238,14 +239,14 @@ class SSCHelperMethods(object):
         
         T = T.to('kelvin')
 
-        a = -1.0e-07 * u.kg/u.m**3/u.kelvin**3
-        b =  0.0002  * u.kg/u.m**3/u.kelvin**2
-        c = -0.7875  * u.kg/u.m**3/u.kelvin
-        d =  2299.4  * u.kg/u.m**3
+        a = -1.0e-07     * u.kg/u.m**3/u.kelvin**3
+        b =  0.0002      * u.kg/u.m**3/u.kelvin**2
+        c = -0.7875      * u.kg/u.m**3/u.kelvin
+        d =  2299.4      * u.kg/u.m**3
+        max_rho = 1000.0 *u.kg/u.m**3
         
         rho = (a*T**3 + b*T**2 + c*T + d).to('kg/m^3')
-        
-        # rho = np.max(rho, 1000.0*u.kg/u.m**3)
+        rho = max(rho, max_rho)
         
         return rho 
 
@@ -423,12 +424,12 @@ class SSCHelperMethods(object):
         if nperpath%2 == 1:   
             dp += rho * g0 * Htot  
         
-        # pumpimh parasitic
+        # pumpimg parasitic
         wdot = dp * dm_rec_design / rho / eta_pump   # Pumping parasitic at design point reciever mass flow rate (MWe)
         wdot = wdot.to('MW')
         
         return wdot
-
+    
 
     def get_pc_persist_and_off_logs( param_dict, plant, npts ):
         """ Method to log the amount of time Power Cycle has been ON and OFF
@@ -452,7 +453,9 @@ class SSCHelperMethods(object):
         # cycle state before start of most recent set of simulation calls
         previous_pc_state = plant.SystemControl.pc_op_mode_initial
         # cycle state after most recent set of simulation calls
-        current_pc_state  = plant.Outputs.pc_op_mode_final
+        tmp_final_op_mode = plant.Outputs.pc_op_mode_final
+        current_pc_state  = tmp_final_op_mode if type(tmp_final_op_mode) == float \
+                                else tmp_final_op_mode[npts-1]
         # times when cycle is not generating power
         is_pc_not_on = np.array( plant.Outputs.P_cycle[0:npts-1] ) <= 1.e-3
         

### 2021-07-30 simulations/util/PostProcessing.py
differentiating between Q_thermal and Q_dot_in

@@ -73,6 +73,7 @@ class OutputExtraction(object):
         self.p_cycle      = np.asarray(mod_out.P_cycle) * u.MW
         self.gen          = (np.asarray(mod_out.gen) * u.kW).to('MW')
         self.q_dot_rec_in = np.asarray(mod_out.q_dot_rec_inc) * u.MW
+        self.q_thermal    = np.asarray(mod_out.Q_thermal) * u.MW
         self.q_pb         = np.asarray(mod_out.q_pb) * u.MW
         self.q_dot_pc_su  = np.asarray(mod_out.q_dot_pc_startup) * u.MW
         self.m_dot_pc     = np.asarray(mod_out.m_dot_pc) * u.kg/u.s
@@ -466,7 +467,7 @@ class Plots(object):
         ax.set_yticks([0, 250, 500, 750, 1000])
 
         # plot Power arrays
-        power_array_list = ['p_cycle', 'q_dot_rec_in', 'gen', 'q_dot_pc_su'] # list of array strings
+        power_array_list = ['p_cycle', 'q_thermal', 'gen', 'q_dot_pc_su'] # list of array strings
         power_label_list = ['P_cycle (Electric)',
                             'Q_dot to Salt (Thermal)',
                             'Power generated (Electric)',

### 2021-07-30 simulations/util/SolarPlots.py

@@ -53,6 +53,7 @@ class SolarOutputExtraction(OutputExtraction):
         self.p_cycle      = np.asarray(mod_out.P_cycle) * u.MW
         self.gen          = (np.asarray(mod_out.gen) * u.kW).to('MW')
         self.q_dot_rec_in = np.asarray(mod_out.q_dot_rec_inc) * u.MW
+        self.q_thermal    = np.asarray(mod_out.Q_thermal) * u.MW
         self.q_pb         = np.asarray(mod_out.q_pb) * u.MW
         self.q_dot_pc_su  = np.asarray(mod_out.q_dot_pc_startup) * u.MW
         self.m_dot_pc     = np.asarray(mod_out.m_dot_pc) * u.kg/u.s
@@ -218,6 +219,87 @@ class SolarPlots(Plots):
             # extracting outputs
             SolarOutputExtraction.set_ssc_outputs(self, Outputs)
         
+        
+    def plot_SSC_power_and_energy(self, ax=None, title_label=None, plot_all_time=True, \
+                                  start_hr=0, end_hr=48, hide_x=False, x_legend=1.2, \
+                                  y_legend_L=1.0, y_legend_R=1.0):
+        """ Method to plot power and energy data on single plot
+
+        This method is used specifically to plot power and energy data from SSC simulation
+        results. Built-in options to plot legend off-axis. 
+
+        Inputs:
+            ax (object)         : axis object to plot on
+            plot_all_time(bool) : are we plotting all results or just a portion?
+            title_label(str)    : title name for plot
+            start_hr (int)      : (plot_all_time==False) hour used for starting index 
+            end_hr (int)        : (plot_all_time==False) hour used for ending index
+            hide_x(bool)        : hiding the x-axis from this particular plot
+            x_legend (float)    : (legend_offset==True) x-offset defining left-most side of legend
+            y_legend_L (float)  : (legend_offset==True) y-offset of left y-axis plot
+            y_legend_R (float)  : (legend_offset==True) y-offset of right y-axis plot
+        """
+        #========================#
+        #--- Creating Figure  ---#
+        #========================#
+
+        # if no axis object specified, create a figure and axis from it
+        if ax is None:
+            fig = plt.figure(figsize=[10, 5])
+            ax = fig.gca()   # this is the power plot
+
+        # twin axis to plot energy on opposite y-axis
+        ax2 = ax.twinx()  # this is the energy plot
+        
+        # custom y limits and ticks to be integers for Power
[…]

### 2021-07-30 simulations/dispatch/GeneralDispatch.py
calling the update_Plant_after_Pyomo method now with extra option to update over pyomo horizon rather than ssc horizon

@@ -816,7 +816,7 @@ class GeneralDispatchOutputs(object):
     and SSC calls. 
     """
     
-    def get_dispatch_targets_from_Pyomo(dispatch_model, ssc_horizon, N_full, run_loop=False):
+    def get_dispatch_targets_from_Pyomo(dispatch_model, horizon, N_full, run_loop=False):
         """ Method to set fixed costs of the Plant
         
         This method parses through the solved Pyomo model for Dispatch optimization
@@ -828,7 +828,7 @@ class GeneralDispatchOutputs(object):
         
         Inputs:
             dispatch_model (Pyomo model) : solved Pyomo Dispatch model (ConcreteModel)
-            ssc_horizon (float Quant)    : length of time of SSC horizon (in hours)
+            horizon (float Quant)        : length of time of horizon, whether SSC or Pyomo (in hours)
             N_full (int)                 : length of full simulation time (in hours, no Quant)
             run_loop (bool)              : flag to determine if simulation is segmented
         Outputs:
@@ -839,7 +839,7 @@ class GeneralDispatchOutputs(object):
         
         # range of pyomo and SSC horizon times
         t_pyomo = dm.model.T
-        f_ind   = int( ssc_horizon.to('hr').m ) # index in hours of final horizon (e.g. 24)
+        f_ind   = int( horizon.to('hr').m ) # index in hours of final horizon (e.g. 24)
         t_horizon = range(f_ind)
         
         # if we're not running a loop, define a list of 0s to pad the output so it matches full array size

### 2021-07-30 simulations/dispatch/NuclearDispatch.py

@@ -607,7 +607,7 @@ class NuclearDispatchOutputs(object):
     and SSC calls. 
     """
     
-    def get_dispatch_targets_from_Pyomo(dispatch_model, ssc_horizon, N_full, run_loop=False):
+    def get_dispatch_targets_from_Pyomo(dispatch_model, horizon, N_full, run_loop=False):
         """ Method to set fixed costs of the Plant
         
         This method parses through the solved Pyomo model for Dispatch optimization
@@ -619,7 +619,7 @@ class NuclearDispatchOutputs(object):
         
         Inputs:
             dispatch_model (Pyomo model) : solved Pyomo Dispatch model (ConcreteModel)
-            ssc_horizon (float Quant)    : length of time of SSC horizon (in hours)
+            horizon (float Quant)        : length of time of horizon, whether SSC or Pyomo (in hours)
             N_full (int)                 : length of full simulation time (in hours, no Quant)
             run_loop (bool)              : flag to determine if simulation is segmented
         Outputs:
@@ -630,7 +630,7 @@ class NuclearDispatchOutputs(object):
         
         # range of pyomo and SSC horizon times
         t_pyomo = dm.model.T
-        f_ind   = int( ssc_horizon.to('hr').m ) # index in hours of final horizon (e.g. 24)
+        f_ind   = int( horizon.to('hr').m ) # index in hours of final horizon (e.g. 24)
         t_horizon = range(f_ind)
         
         # if we're not running a loop, define a list of 0s to pad the output so it matches full array size

### 2021-07-30 simulations/modules/GenericSSCModule.py

@@ -253,7 +253,8 @@ class GenericSSCModule(ABC):
         self.t_ind = int(time_next.to('hr').m)
         
         # slice for the first indeces of the SSC Horizon, also initializing current Horizon (updated in loop)
-        self.slice_ssc_firstH   = slice( 0, self.t_ind,1)
+        self.slice_ssc_firstH   = slice( 0, self.t_ind, 1)
+        self.slice_pyo_firstH   = slice( 0, int( self.pyomo_horizon.to('hr').m ),  1)
         self.slice_ssc_currentH = slice( int( time_start.to('hr').m ), self.t_ind, 1)  
         self.slice_pyo_currentH = slice( int( time_start.to('hr').m ), int( self.pyomo_horizon.to('hr').m ), 1) 
         
@@ -265,7 +266,7 @@ class GenericSSCModule(ABC):
             
             # one pre-run of Plant, used to grab inputs to dispatch in some modules
             # runs for the Pyomo Horizon, not the SSC Horizon
-            ssc_run_success = self.run_Plant_through_SSC( time_start , self.pyomo_horizon.to('s') )
+            ssc_run_success = self.run_Plant_through_SSC( time_start , time_start + self.pyomo_horizon )
             
             # create dispatch parameters for the first time
             disp_params = self.create_dispatch_params( self.slice_pyo_currentH )
@@ -274,7 +275,7 @@ class GenericSSCModule(ABC):
             self.run_pyomo( disp_params )
             
             # update: Pyomo(t) -> Plant(t) 
-            self.update_Plant_after_Pyomo()
+            self.update_Plant_after_Pyomo( pre_dispatch_run=False )
         
         # first real execution of Plant through SSC
         ssc_run_success = self.run_Plant_through_SSC( time_start , time_next )
@@ -310,6 +311,14 @@ class GenericSSCModule(ABC):
             # run dispatch optimization
             if self.is_dispatch:
                 
+                # update Plant to gather Pyomo inputs... 
+                # TODO: this nomenclature is a bit confusing
+                self.update_Plant_after_Pyomo( pre_dispatch_run=True )
+            
+                # one pre-run of Plant, used to grab inputs to dispatch in some modules
+                # runs for the Pyomo Horizon, not the SSC Horizon
+                ssc_run_success = self.run_Plant_through_SSC( time_start , time_start + self.pyomo_horizon )
+                
                 # update: SSC(t) -> Pyomo(t+1)
[…]

### 2021-07-30 simulations/modules/NuclearTES.py

@@ -280,29 +280,37 @@ class NuclearTES(GenericSSCModule):
         return params
 
 
-    def update_Plant_after_Pyomo(self):
+    def update_Plant_after_Pyomo(self, pre_dispatch_run=False):
         """ Update SSC Plant inputs with Pyomo optimization outputs from current segment simulation
 
-        ** self.run_loop    == True (can be called outside loop)
-        ** self.is_dispatch == True 
+        Note:
+            self.run_loop    == True (can be called outside loop)
+            self.is_dispatch == True 
         
         This method uses the optimization results from Pyomo and ensures that 
         the next SSC segment uses them throughout the corresponding SSC Horizon.
         SSC normally takes single values for initial conditions (for the first hour
         of the SSC Horizon), but it can also take in an array of values for each
         step in the SSC Horizon. These are called "dispatch_targets". Steps are:
-            (1) extract solutions from Pyomo over the Pyomo Horizon, 
-            (2) keep the solutions for the shorter SSC Horizon and 
-            (3) save these "dispatch target" inputs to the Plant object for the 
-                   next SSC simulation segment. 
+        (1) extract solutions from Pyomo over the Pyomo Horizon, 
+        (2) keep the solutions for the shorter SSC Horizon and 
+        (3) save these "dispatch target" inputs to the Plant object for the 
+        next SSC simulation segment. 
+
+        Args:
+            pre_dispatch_run (bool): 
+                are we updating the Plant for a pre- or post- dispatch run.
+                Recall that we only log post-dispatch Plant runs
+                
         """
         
         # number of times in full simulation 
         N_full     = int((self.SSC_dict['time_stop']*self.u.s).to('hr').m)
         
         # the heavy-lifting happens here -> return a dictionary of dispatch target arrays from Pyomo optimization results
+        horizon = self.pyomo_horizon if pre_dispatch_run else self.ssc_horizon
         dispatch_targets = self.Dispatch_Outputs.get_dispatch_targets_from_Pyomo( \
-                                                self.current_disp_model, self.ssc_horizon, N_full, self.run_loop)
+                                                self.current_disp_model, horizon, N_full, self.run_loop)
         
         ### Set Dispatch Targets ### 
         # setting dispatch targets to True so that SSC can read in Pyomo inputs

### 2021-07-30 simulations/dispatch/SolarDispatch.py
updating solar inputs, new Q_thermal input

@@ -428,7 +428,7 @@ class SolarDispatchParamWrap(GeneralDispatchParamWrap):
         # TODO: old values from LORE files
         C_rec  = self.PySAM_dict['rec_op_cost'] * u.USD / u.MWh #Q_ratio * 0.002  * u.USD/u.kWh        
         C_rsu  = self.PySAM_dict['rec_cold_su'] * u.USD
-        C_rhsp = self.PySAM_dict['rec_hot_su'] * u.USD
+        C_rhsp = self.PySAM_dict['rec_hot_su']  * u.USD
 
         ### Cost Parameters ###
         param_dict['Crec']   = C_rec.to('USD/kWh')  #C^{rec}: Operating cost of heliostat field and receiver [\$/kWt$\cdot$h]
@@ -455,23 +455,33 @@ class SolarDispatchParamWrap(GeneralDispatchParamWrap):
         
         # pumpimg parasitics for receiver
         wdot = SSCHelperMethods.estimate_receiver_pumping_parasitic(u, self.T_htf_avg, self.dm_rec_design, self.SSC_dict)
-        wdot     = wdot.to('MW')  
+        wdot = wdot.to('MW')  
         
-        tower_piping_ht_loss    = self.PySAM_dict['tower_piping_ht_loss']*u.kW   # TODO: Tower piping heat trace full-load parasitic load (kWe) 
+        # various pre-parameters and other inputs
+        N_hel = self.SSC_dict['N_hel']
+        
+        tower_piping_ht_loss    = self.PySAM_dict['tower_piping_ht_loss']*u.kW/u.MW   # (from LORE) Tower piping heat trace full-load parasitic load (kWe/MWt) 
         q_rec_standby_fraction  = self.PySAM_dict['q_rec_standby_frac']        
-        q_rec_shutdown_fraction = self.PySAM_dict['q_rec_shutdown_frac']      
+        q_rec_shutdown_fraction = self.PySAM_dict['q_rec_shutdown_frac']   
+        Drsu                    = self.SSC_dict['rec_su_delay']*u.hr
+        heliostat_SU_energy     = self.SSC_dict['p_start']*u.kWh
+        heliostat_track_energy  = self.SSC_dict['p_track']*u.kW
+        receiver_SU_ratio       = self.SSC_dict['rec_qf_delay'] * u.kWh / u.MW 
+        TES_load_hrs            = self.SSC_dict['tshours']*u.hr
[…]

### 2021-07-30 simulations/modules/SolarTES.py

@@ -115,12 +115,15 @@ class SolarTES(NuclearTES):
         # run the setters from the GenericSSCModule parent class
         params = GenericSSCModule.create_dispatch_params(self, current_pyomo_slice)
         
-        # set up Plant outputs dictionary
-        plant_dict = self.Plant.Outputs.export()
+        # set up copy of SSC dict
+        updated_SSC_dict = copy.deepcopy(self.SSC_dict)
+        
+        # extract time series from previous SSC run
+        updated_SSC_dict['Q_thermal'] = self.Plant.Outputs.Q_thermal[self.slice_pyo_firstH]
         
         # these are SolarTES-specific setters
         params = DW.set_solar_parameters( params )
-        params = DW.set_time_series_solar_parameters( params, plant_dict )
+        params = DW.set_time_series_solar_parameters( params, updated_SSC_dict )
         
         # this sets the initial states for the SolarTES
         params = DW.set_initial_state( params )
@@ -166,7 +169,10 @@ class SolarTES(NuclearTES):
         updated_SSC_dict['is_field_tracking_init']           = self.Plant.Outputs.is_field_tracking_final[self.t_ind-1]
         
         # these are specific to the initial states
-        updated_SSC_dict['wdot0'] = self.Plant.Outputs.P_cycle[self.t_ind-1]
+        updated_SSC_dict['wdot0']     = self.Plant.Outputs.P_cycle[self.t_ind-1]
+        
+        # extract time series from a previous SSC run
+        updated_SSC_dict['Q_thermal'] = self.Plant.Outputs.Q_thermal[self.slice_pyo_firstH]
         
         # TODO: removing w_dot_s_prev references in all of Dispatch for now, might need to revisit later
         # updated_SSC_dict['wdot_s_prev'] = 0 #np.array([pe.value(dm.model.wdot_s_prev[t]) for t in dm.model.T])[-1]
@@ -179,34 +185,42 @@ class SolarTES(NuclearTES):
         # updating the initial state and time series Nuclear params
         params = DW.set_time_indexed_parameters( params, self.df_array, self.ud_array, current_pyomo_slice )
         params = DW.set_initial_state( params, updated_SSC_dict, self.Plant, self.t_ind )
-        params = DW.set_time_series_solar_parameters( params, plant_dict )
+        params = DW.set_time_series_solar_parameters( params, updated_SSC_dict )
         
         return params
 
 
-    def update_Plant_after_Pyomo(self):
[…]

### 2021-08-02 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
spelling

@@
 The diagram for this CSP cycle is seen in Figure \ref{csp}.
+%MW: This description is a bit hard to follow. Figure 1 shows the Salt HX, which is a heat exchanger and not a black box.
 
 \end{paracol}
-\begin{figure}[H] 
+%MW: Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. 
+\begin{figure}[htb] 
     \widefigure
@@
 The salt CSP cycle can be either in charging mode or electrical generation mode. 
-%Here you need to explain what a conventional CSP cycle looks like (briefly).
+%BL: Here you need to explain what a conventional CSP cycle looks like (briefly).
 I.e.
@@
 Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
-When the CSP cycle is in charging mode, excess heat is transfered from the sCO$_{2}$ Brayton cycle through the SALT HX.
+When the CSP cycle is in charging mode, excess heat is transferred from the sCO$_{2}$ Brayton cycle through the SALT HX.
 The heated salt is then stored in the hot storage until grid demand increases.
-%Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX
+%BL: Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched directly rather than thru the SALT HX
 
-When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
+When electrical generation is occurring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
 The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
@@
 
-\begin{specialtable}[H] 
+%MW: Also changing the specialtable position to allow latex to better place tables.
+\begin{specialtable}[htbp] 
     \caption{Constant cycle parameters with definition, variable and set value. \label{cycle-constants}}
@@
 
-Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
+Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
 The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency.
-The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400^${circ}C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
-%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint
+The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K ($400^{circ}C$), which is a requirement of the LFR primary circuit to maximize power output within material limits.
+%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivity' case to determine the penalty of the constraint
 
 The CSP cycle for this two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
-The diagram has the necessary pumps, TES tanks, and salt heat exchangers to be representative of a relizable salt CSP cycle.
+The diagram has the necessary pumps, TES tanks, and salt heat exchangers to be representative of a realizable salt CSP cycle.
 
@@
 The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt).
-In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K.
+In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to 653.2 K.
 %BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
@@
 The LFR is powering one turbine, T1, and recuperating heat through a dedicated high temperature recuperator, HTR1.
-The CSP cycle also contains two seperate turbines, T2, while having a dedicated high temperature recuperator, HTR2.
+The CSP cycle also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2.
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
@@
 %BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output
-%BL: SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage
+%BL: SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you don't want to change it at this late stage
 
@@
 
-Whereas $\dot{Q}_{SALT}$ is the amount of heat transfered through the SALT HX and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR and CSP.
+Whereas $\dot{Q}_{SALT}$ is the amount of heat transferred through the SALT HX and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR and CSP.
 
@@
 The requirement of the turbine and CSP hot TES temperature can be accomplished by splitting the flow before the turbine.
-The flow through the salt heat exchanger in this cycle is therefore seperate from the turbine.
+The flow through the salt heat exchanger in this cycle is therefore separate from the turbine.
 After the salt heat exchanger a valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
@@
 
-The charging subsection of this diagram is composed of a circulation cycle that has heat inputed through the LFR heat exchanger.
+The charging subsection of this diagram is composed of a circulation cycle that has heat inputted through the LFR heat exchanger.
 This subsection is encircled in blue and can be seen in Figure \ref{c-lfr-circ-sub}.
@@
     \includegraphics[width=10 cm]{Definitions/c-lfr-circ-sub.pdf}
-    \caption{Diagram for C-LFR-CIRC subcycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
+    \caption{Diagram for C-LFR-CIRC sub-cycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
 \end{figure}
@@
 
-The flow continues through a circulator which is assumed to have neglegible pressure rise (i.e.
+The flow continues through a circulator which is assumed to have negligible pressure rise (i.e.
 there is assumed to be negligible pressure drop in this case).
 A heat exchanger, SALT HX, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
-Excess heat that is not extracted is then dumped into a reservior through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of 673.2 K.
+Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of 673.2 K.
 Three different temperatures; 663.2 K, 683.2 K, and 713.2 K, are compared in a sensitivity study.
@@
 
-Modeling the C-LFR-ON cycle in EES yeilded the results in Table \ref{tab-c-lfr-on}.
+Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
 
-\begin{specialtable}[H] 
+\begin{specialtable}[htbp] 
     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-on}}
@@
 
-\begin{specialtable}[H] 
+\begin{specialtable}[htbp] 
     \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
@@
 
-\begin{specialtable}[H] 
+\begin{specialtable}[htbp] 
     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.
@@
 
-\begin{specialtable}[H]
+\begin{specialtable}[htbp]
     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-2htr3t-on}}
@@
 
-\begin{specialtable}[H]
+\begin{specialtable}[htbp]
     \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
@@
 
-\begin{specialtable}[H]
+\begin{specialtable}[htbp]
     \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
@@
 
-\begin{specialtable}[H]
-    \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-circ}}
+\begin{specialtable}[htbp]
+    \caption{Calculated system parameters for charging C-LFR-CIRC sub-cycle configuration with constrained Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-circ}}
     \begin{tabular}{lcccc}
@@
 % The MDPI table float is called specialtable
-\begin{specialtable}[H] 
+\begin{specialtable}[htbp] 
 \caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}

### 2021-08-03 simulations/modules/GenericSSCModule.py
new print statements and duplicate_Plant method

@@ -216,7 +216,28 @@ class GenericSSCModule(ABC):
         # import Singleowner-specific data to Singleowner object
         self.SO.assign(Singleowner.wrap(so_dat).export())
 
-
+    @abstractmethod
+    def duplicate_Plant(self, Plant):
+        """ Method to create Plant object as a duplicate of existing Plant
+        
+        This method creates a Plant object from an existing Plant. The new 
+        Plant object will have a copy of the original Plant's subclasses
+        EXCEPT the Output subclass. The two plant's outputs will NOT be linked.
+        
+        Note:
+            Verified in imulations/scripts/sanity_check_scripts
+        
+        Args:
+            Plant (obj): 
+                original PySAM Plant module to be copied
+        Returns:
+            newPlant (obj): 
+                duplicate PySAM Plant module, unlinked from original
+        """
+        
+        return Plant
+        
+        
     def simulate_Plant(self):
         """ Method to run full simulation of Plant
         
@@ -264,9 +285,12 @@ class GenericSSCModule(ABC):
         # run dispatch optimization for the first time
         if self.is_dispatch:
             
+            print("\nRunning with Dispatch Optimization.")
+            
             # one pre-run of Plant, used to grab inputs to dispatch in some modules
             # runs for the Pyomo Horizon, not the SSC Horizon
             ssc_run_success = self.run_Plant_through_SSC( time_start , time_start + self.pyomo_horizon )
+            print("First pre-Pyomo SSC run status : {0}".format("Success" if ssc_run_success else "Failed") )
             
             # create dispatch parameters for the first time
             disp_params = self.create_dispatch_params( self.slice_pyo_currentH )
@@ -279,6 +303,7 @@ class GenericSSCModule(ABC):
         
         # first real execution of Plant through SSC
         ssc_run_success = self.run_Plant_through_SSC( time_start , time_next )
+        print("First SSC run status : {0}".format("Success" if ssc_run_success else "Failed") )
         self.log_SSC_arrays()
         
         # setting up iterable time to cycle thorugh in for loop

### 2021-08-03 simulations/modules/NuclearTES.py

@@ -122,6 +122,34 @@ class NuclearTES(GenericSSCModule):
         
         #set curtailment to be really high
         self.Grid.GridLimits.grid_curtailment = self.gc_array  
+
+
+    def duplicate_Plant(self, Plant):
+        """ Method to create Plant object as a duplicate of existing Plant
+        
+        This method creates a Plant object from an existing Plant. The new 
+        Plant object will have a copy of the original Plant's subclasses
+        EXCEPT the Output subclass. The two plant's outputs will NOT be linked.
+        
+        Note:
+            Verified in imulations/scripts/sanity_check_scripts
+        
+        Args:
+            Plant (obj): 
+                original PySAM Plant module to be copied
+        Returns:
+            newPlant (obj): 
+                duplicate PySAM Plant module, unlinked from original
+                
+        """
+        # retrieve Plant dictionary
+        plant_dict = Plant.export()
+        
+        # create new Plant object from dictionary
+        newPlant = self.PySAM_Module.new()
+        newPlant.assign(plant_dict)
+        
+        return newPlant
         
         
     def run_pyomo(self, params):

### 2021-08-06 simulations/dispatch/NuclearDispatch.py
storing and extracting  Q_thermal from NuclearTES SSC run as prediction for Pyomo optimization

@@ -484,7 +484,7 @@ class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
         return param_dict
     
     
-    def set_time_series_nuclear_parameters(self, param_dict):
+    def set_time_series_nuclear_parameters(self, param_dict, updated_dict=None):
         """ Method to set fixed costs of the Plant for Dispatch optimization
         
         This method calculates some time series parameters for the Plant operations, startup,
@@ -494,6 +494,7 @@ class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
         
         Inputs:
             param_dict (dict) : dictionary of Pyomo dispatch parameters
+            updated_dict (dict) : dictionary with updated SSC initial conditions from previous run  
         Outputs:
             param_dict (dict) : updated dictionary of Pyomo dispatch parameters
         """
@@ -501,9 +502,20 @@ class NuclearDispatchParamWrap(GeneralDispatchParamWrap):
         #MAKE SURE TO CALL THIS METHOD AFTER THE NUCLEAR PARAMETERS 
         u = self.u
         
+        # differentiating between first and updated runs
+        if updated_dict is None:
+            self.current_Plant = copy.deepcopy(self.SSC_dict)
+            self.first_run = True
+        else:
+            self.current_Plant = updated_dict
+            self.first_run = False
+        
         # thermal power and startup params
         self.Dnsu    = self.PySAM_dict['Dnsu']*u.hr   # Minimum time to start the nuclear plant (hr)
-        self.Qin_nuc = np.array([self.q_nuc_design.m]*self.T)*self.q_nuc_design.u #TODO: update at each segment
+        self.Qin_nuc = self.current_Plant['Q_thermal'] * u.MW    # value here taken from a previous Plant-SSC run
+
+        if len(self.Qin_nuc) < len(param_dict['Delta']):
+            self.Qin_nuc = np.hstack( [self.current_Plant['Q_thermal'], self.current_Plant['Q_thermal']] ) * u.MW
         
         # instantiating arrays
         n  = len(self.Delta)

### 2021-08-06 simulations/modules/NuclearTES.py

@@ -239,16 +239,23 @@ class NuclearTES(GenericSSCModule):
                 wrapper object for the class that creates dispatch parameters
                 
         """
-        
         # get the object
         DW = self.dispatch_wrap
         
         # run the setters from the GenericSSCModule parent class
         params = GenericSSCModule.create_dispatch_params(self, Plant )
+
+        # extract array from full run of Plant
+        assert hasattr(Plant.Outputs, "Q_thermal"), "Q_thermal was not found in the outputs of Plant."
+        self.Q_nuc_guess = Plant.Outputs.Q_thermal
+        
+        # set up copy of SSC dict
+        updated_SSC_dict = copy.deepcopy(self.SSC_dict)
+        updated_SSC_dict['Q_thermal'] = self.Q_nuc_guess[self.slice_pyo_firstH]
         
         # these are NuclearTES-specific setters
         params = DW.set_nuclear_parameters( params )
-        params = DW.set_time_series_nuclear_parameters( params )
+        params = DW.set_time_series_nuclear_parameters( params, updated_SSC_dict )
         
         # this sets the initial set for the NuclearTES
         params = DW.set_initial_state( params )
@@ -294,6 +301,9 @@ class NuclearTES(GenericSSCModule):
         
         # these are specific to the initial states
         updated_SSC_dict['wdot0'] = Plant.Outputs.P_cycle[self.t_ind-1]
+
+        # extract time series from a previous SSC run
+        updated_SSC_dict['Q_thermal'] = self.Q_nuc_guess[self.slice_pyo_currentH]
         
         # TODO: removing w_dot_s_prev references in all of Dispatch for now, might need to revisit later
         # updated_SSC_dict['wdot_s_prev'] = 0 #np.array([pe.value(dm.model.wdot_s_prev[t]) for t in dm.model.T])[-1]
@@ -303,7 +313,7 @@ class NuclearTES(GenericSSCModule):
         # updating the initial state and time series Nuclear params
         params = DW.set_time_indexed_parameters( params, self.df_array, self.ud_array, self.slice_pyo_currentH )
         params = DW.set_initial_state( params, updated_SSC_dict, Plant, self.t_ind )
-        params = DW.set_time_series_nuclear_parameters( params )
+        params = DW.set_time_series_nuclear_parameters( params, updated_SSC_dict )
         
         return params
 

### 2021-08-06 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
new updates to methods and materials

--- 2021-07-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Materials and Methods}
@@
 \subsection{Cycle Component Modeling}
-\subsubsection{Counter Flow and Black Box Heat Exchangers}
+%======================================================================================
+Components present in the cycles are modeled using various techniques.
+Turbines and compressors are analyzed using isentropic efficiencies.
+Counter flow heat exchangers use the effectiveness-NTU method while black box heat exchangers use a simple energy balance for state point calculations.
+The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
+The concentrating solar power cycle is modeled with necessary components including hot and cold TES, reciever, pumps and counter flow heat exchangers.
 
-\subsubsection{Turbines}
+\subsubsection{Turbines and Compressors }
+%--------------------------------------------------------------------------------------
 
-\subsubsection{Compressors}
+The modeled cycles have a number of compressors and turbines.
+The turbines and compressors are modeled for each cycle using constant isentropic efficiency values summarized in Table \ref{tab-cycle-constants}.
+Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$.
+The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have a single inlet and outlet.
+Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.
+Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor can be calculated \cite{klein_nellis_2011}.
 
-\subsubsection{Lead-Fast Reactor}
+\subsubsection{Black Box and Counter Flow Heat Exchangers}
+%--------------------------------------------------------------------------------------
+
+Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point.
+These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy.
+The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.
+
+\begin{equation}
+    \label{eq-black}
+    \dot{m}_{in}*h_{in} + \dot{Q}_{in} = \dot{m}_{out}*h_{out} + \dot{Q}_{out},
+\end{equation}
+
+In this equation the energy input to the system is on the left hand side with $\dot{m}_{in}$ multiplied by $h_{in}$ being energy from the mass flow and $\dot{Q}_{in}$ being heat transfer directly to the flow from an outside source.
+The right hand side of the equation is heat leaving the energy balance.
+The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow.
+Black box energy balances are used in three situations, the Reciever, LFR HX, and PC HX.
+These heat exchangers are not exchaustively modeled because the state points on the inlet and outlet are constrained by design parameters.
+
+Counter flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
+The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature.
+A diagram showing a simplified example of a counterflow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
+
+\end{paracol}
+\begin{figure}[H] 
+    \widefigure
+    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
+    \caption{Simple counter flow heat exchanger diagram. \label{counter-flow-hx}}
+\end{figure}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+Additional assumptions of the counter flow heat exchanger model are no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, and no pressure drops accross the heat exchangers.
+Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
+In all of the modeled cases, the approach temperature is set to a value of 10 K.
+The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+
+To analyze the counter flow heat exchanger a side is chosen, usually high, to start the calculations.
+The approach temperature is initially subtracted from the hot stream on the high side to find the missing cold temperature according to Equation \ref{temp_h}.
+
+\begin{equation}
+   \label{temp_h}
+    T_{out,c} = T_{in,h}-\Delta_{T},
+\end{equation}
+
+Where T$_{out,c}$ is the cold stream outlet temperature and T$_{in,h}$ is the hot stream inlet temperature.
+Knowing the two state points allows for the enthalpy to be found using correlations from the fluid property libraries.
+
+[More Desctription on Counterflow HX]
+
+\subsubsection{Lead-Cooled Fast Reactor}
+%--------------------------------------------------------------------------------------
+Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead.
+This lead is used to both cool the core as well as transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}.
+The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX.
+The inlet, outlet and heat transfer rates are defined by our industry partner, Westinghouse Electric Company making the black box simplification viable.
+The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.
+
+\begin{equation}
+    \label{eq-lfr-black-box}
+    \dot{m}_{inlet}*h_{inlet} + \dot{Q}_{LFRHX} = \dot{m}_{outlet}*h_{outlet},
+\end{equation}
+
+Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$.
+The amount of energy transfered into the cycle, $\dot{Q}_{LFRHX}$, is set at 950 MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C.
+The outlet temperature of the LFR is rigid due to high temperature material limits on the LFR lead side.
+Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C.
+Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.
 
 \subsubsection{Concentrating Solar Power Cycle}
+%--------------------------------------------------------------------------------------
 
-The CSP cycles modeled in this paper are composed of the hot and cold thermal energy storage, pumps to move the molten salt, and a black box heat input.
-The diagram for this CSP cycle is seen in Figure \ref{csp}.
+The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-Salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX).
+The diagram for this CSP salt cycle is seen in Figure \ref{csp}.
 
@@
 
-The salt CSP cycle can be either in charging mode or electrical generation mode. 
-%Here you need to explain what a conventional CSP cycle looks like (briefly).
-I.e.
-CSP charges salt, it can discharge when you want it to.
-Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
-When the CSP cycle is in charging mode, excess heat is transfered from the sCO$_{2}$ Brayton cycle through the SALT HX.
-The heated salt is then stored in the hot storage until grid demand increases.
-%Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX
+The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid.
+Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low.
+Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C.
+Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
+The cold TES temperature takes on three different values according to cycle configuration capabilitites: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
+In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}.
+The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle.
+It is assumed that only one hot TES charging option can be active at any given time.
 
+The C2S heat exchanger is active during the 'charging' cycle configurations, when the focus is on heat storage for later use.
+During this process there is no solar salt flow through the receiver.
+Pump 1 is active moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.
+
+'Non-charging' cycle configurations has the receiver charging the hot TES, C2S heat exchanger is not transfering heat, and the LFR is dispatching energy directly into electrical generation.
 When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
 The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
-The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the heliostat field is added.
+The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.
 
 \subsection{Generalization of Cycle Modeling}
+%======================================================================================
 
@@
 The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
-These values are summarized in Table \ref{cycle-constants}.
+These values are summarized in Table \ref{tab-cycle-constants}.
 
 \begin{specialtable}[H] 
-    \caption{Constant cycle parameters with definition, variable and set value. \label{cycle-constants}}
+    \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
     \begin{tabular}{lcc}
@@
     \textit{Heat Into System}\\
-    Lead-Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
+    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
     Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
@@
     Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
-    %Lead-Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
-    Lead-Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
+    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
+    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
     \midrule
@@
 
-The values displayed in Table \ref{cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Company.
+The values displayed in Table \ref{tab-cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Company.
 
@@
 
-\subsection{Non-Charging Cycle Configurations}%===================================
+Modeled cycles are summarized in Table \ref{tab-cycle_sum}.
+
+\begin{specialtable}[H] 
+    \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
+    \begin{tabular}{ll}
+    \toprule
+    \textbf{Cycle Label} & \textbf{Description}\\
+    \midrule
+    \textit{Non-Charging}\\
+    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
+    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
+    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
+    C-2HTR3T-ON & Seperatre CSP and LFR loops each with dedicated HTR and turbine.\\
+    \midrule
+    \textit{Charging}\\
+    C-LFR-PRE & Turbine is prior to the SALT HX.\\
+    C-LFR-POST & Turbine is after the SALT HX.\\
+    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
+    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
+    \bottomrule
+    \end{tabular}
+\end{specialtable}
+
+\subsection{Non-Charging Cycle Configurations} 
+%======================================================================================
+
 Various cycles are modeled to test their advantages and disadvantages.
@@
     \label{eq-eta-cycle}
-    \eta_{heatstorage} = \frac{\dot{W}_{T}-\dot{W}_{MC}-\dot{W}_{RC}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
+    \eta_{cycle} = \frac{\dot{W}_{T}-\dot{W}_{MC}-\dot{W}_{RC}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
 \end{equation}
@@
 The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$.
-The denominator is the total power input into the system from the LFR, $\dot{Q}_{LFRHX}$, and CSP, $\dot{Q}_{CSPHX}$.
+The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.
 
-%BL: I would include the naming scheme upfront and give a table (C-LFR-ON etc.)
+\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON} %--------------------------------------------------------------------------------------
 
-\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON} %--------------------------------------------------------
-
-The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a salt CSP cycle.
+The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a CSP cycle.
 This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON.
 Configuration of components for these two cycles is identical with the exception of heat inputs.
-C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from a CSP.
+C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP.
 These two cycles individually operate when the focus of plant operation is primarily electricity generation.
 
-The LFR cycle for this two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.
+The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.
 
@@
 The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency.
-The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400^${circ}C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
+The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
 %BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint
 
-The CSP cycle for this two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
-The diagram has the necessary pumps, TES tanks, and salt heat exchangers to be representative of a relizable salt CSP cycle.
+The cycle that is using the CSP heat input in the two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
 
@@
 
-\subsubsection{C-1HTR1T-ON} %-----------------------------------------------------
+\subsubsection{C-1HTR1T-ON} 
+%--------------------------------------------------------------------------------------
 
@@
 Combining the two cycles into one would reduce redundancy and complexity.
-Heat addition from the CSP and LFR in parallel orientation is therefore studied in the C-1HTR1T-ON model.
+Heat addition from the CSP HX and LFR HX in parallel orientation is therefore studied in the C-1HTR1T-ON model.
 This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency.
@@
 
-In this cycle, the LFR and CSP have identical inlet temperatures due to splitting the flow prior to their parallel orientation.
+In this cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation.
 Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model.
@@
 
-\subsubsection{C-2HTR3T-ON} %-----------------------------------------------------
+\subsubsection{C-2HTR3T-ON} 
+%--------------------------------------------------------------------------------------
 
@@
 
-\subsection{Thermal Energy Storage Charging Techniques} %=========================
+\subsection{Thermal Energy Storage Charging Techniques} 
+%======================================================================================
 
@@
 %BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output
-%BL: SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage
 
@@
     \label{eq-eta-heatstorage}
-    \eta_{heatstorage} = \frac{\dot{Q}_{SALT}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
+    \eta_{heatstorage} = \frac{\dot{Q}_{C2S}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
 \end{equation}
 
-Whereas $\dot{Q}_{SALT}$ is the amount of heat transfered through the SALT HX and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR and CSP.
+Whereas $\dot{Q}_{S2C}$ is the amount of heat transfered through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
 
-\subsubsection{C-LFR-PRE} %-------------------------------------------------------
+\subsubsection{C-LFR-PRE} 
+%--------------------------------------------------------------------------------------
 
@@
 
-\subsubsection{C-LFR-POST} %------------------------------------------------------
+\subsubsection{C-LFR-POST} 
+%--------------------------------------------------------------------------------------
 
@@
 
-\subsubsection{C-LFR-PAR} %-------------------------------------------------------
+\subsubsection{C-LFR-PAR} 
+%--------------------------------------------------------------------------------------
 
@@
 
-\subsubsection{C-LFR-CIRC} %------------------------------------------------------
+\subsubsection{C-LFR-CIRC} 
+%--------------------------------------------------------------------------------------
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
@@
 \subsection{Non-Charging Cycle Configurations}
+%======================================================================================
 
 \subsubsection{C-LFR-ON and C-CSP-ON}
+%--------------------------------------------------------------------------------------
 
@@
 \begin{specialtable}[H] 
-    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-on}}
+    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
     \begin{tabular}{lccc}
@@
 \subsubsection{C-1HTR1T-ON}
+%--------------------------------------------------------------------------------------
 
@@
 \begin{specialtable}[H] 
-    \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.
+    \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
 Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
@@
 \subsubsection{C-2HTR3T-ON}
+%--------------------------------------------------------------------------------------
 
@@
 \begin{specialtable}[H]
-    \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-2htr3t-on}}
+    \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
     \begin{tabular}{lcccc}
@@
 \subsection{Thermal Energy Storage Charging Techniques}
+%======================================================================================
 
 \subsubsection{C-LFR-PRE}
+%--------------------------------------------------------------------------------------
 
@@
 \subsubsection{C-LFR-POST}
+%--------------------------------------------------------------------------------------
 
 \subsubsection{C-LFR-PAR}
+%--------------------------------------------------------------------------------------
 
@@
 \subsubsection{C-LFR-CIRC}
+%--------------------------------------------------------------------------------------
 
@@
 \begin{specialtable}[H]
-    \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-circ}}
+    \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
     \begin{tabular}{lcccc}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{how to use}
@@
 \end{paracol}
+
+%Completed suggestions from Ben:
+
+%-I would include the naming scheme upfront and give a table (C-LFR-ON etc.)
+
+%-Here you need to explain what a conventional CSP cycle looks like (briefly).
+I.e.
+CSP charges salt, it can discharge when you want it to.
+Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
+
+%-Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX
+
+%-SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage
+
+%Completed suggestions from Mike:

### 2021-08-09 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

@@
 \end{paracol}
-\begin{figure}[H] 
+%MW: Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. 
+\begin{figure}[htb] 
     \widefigure
@@
 
-\begin{specialtable}[H] 
+%MW: Also changing the specialtable position to allow latex to better place tables.
+\begin{specialtable}[htbp] 
     \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
@@
 
-Modeling the C-LFR-ON cycle in EES yeilded the results in Table \ref{tab-c-lfr-on}.
+Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
 
-\begin{specialtable}[H] 
+\begin{specialtable}[htbp] 
     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
@@
 
-\begin{specialtable}[H] 
+\begin{specialtable}[htbp] 
     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
@@
 
-\begin{specialtable}[H]
+\begin{specialtable}[htbp]
     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
@@
 
-\begin{specialtable}[H]
+\begin{specialtable}[htbp]
     \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}

### 2021-08-09 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
comments and edits

@@
 
+% **************************************
+
+%MW: I've fixed spelling in a few places. You can install a spell checker to highlight misspelled words. I use the "Code spell checker" extension.
+
 \subsection{Cycle Component Modeling}
 %======================================================================================
-Components present in the cycles are modeled using various techniques.
+Components present in the cycles are modeled using various techniques \added{and are discussed in more detail below}.
 Turbines and compressors are analyzed using isentropic efficiencies.
-Counter flow heat exchangers use the effectiveness-NTU method while black box heat exchangers use a simple energy balance for state point calculations.
+Counter flow heat exchangers use the effectiveness-NTU method while \added{simplified} ``black box'' heat exchangers use a simple energy balance for state point calculations.
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
-The concentrating solar power cycle is modeled with necessary components including hot and cold TES, reciever, pumps and counter flow heat exchangers.
+The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter flow heat exchangers.
 
@@
 
-The modeled cycles have a number of compressors and turbines.
-The turbines and compressors are modeled for each cycle using constant isentropic efficiency values summarized in Table \ref{tab-cycle-constants}.
+\replaced{Turbines}{The modeled cycles have a number of compressors and turbines.
+The turbines} and compressors are modeled for each cycle using constant isentropic efficiency values \added{which are} summarized in Table \ref{tab-cycle-constants}.
 Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$.
-The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have a single inlet and outlet.
-Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.
-Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor can be calculated \cite{klein_nellis_2011}.
+The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have single inlet and outlet \added{streams}.
+Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.\mw{this is kind of an awkward way to describe what's happening.
+I think most readers are familiar with isentropic efficiencies and this can be omitted.} Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor \replaced{are}{can be} calculated \cite{klein_nellis_2011}.
 
@@
 These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy.
-The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.
+The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.\mw{This is for a single flow stream.
+Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream?
+Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$.}
 
@@
 \end{equation}
+\mw{Use the command ``\textbackslash cdot'' instead of asterisks to denote multiplication}
 
@@
 The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow.
-Black box energy balances are used in three situations, the Reciever, LFR HX, and PC HX.
-These heat exchangers are not exchaustively modeled because the state points on the inlet and outlet are constrained by design parameters.
+Black box energy balances are used in three situations, the Receiver, LFR HX, and PC HX.
+These heat exchangers are not exhaustively modeled because the state points on the inlet and outlet are constrained by design parameters.
 
-Counter flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
+Counter flow \mw{I normally use ``counter-flow''} heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
 The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature.
-A diagram showing a simplified example of a counterflow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
+A diagram showing a simplified example of a counter flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
 
@@
 
-Additional assumptions of the counter flow heat exchanger model are no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, and no pressure drops accross the heat exchangers.
+Additional assumptions of the counter flow heat exchanger model are: no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, \mw{these are equivalent} and no pressure drops across the heat exchangers.
 Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
-In all of the modeled cases, the approach temperature is set to a value of 10 K.
-The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+In all of the modeled cases, the approach temperature is set to a value of $10 K$.\mw{Justify} The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
 
@@
 \end{equation}
+\mw{If mass is conserved, use a single $\dot{m}$}
 
 Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$.
-The amount of energy transfered into the cycle, $\dot{Q}_{LFRHX}$, is set at 950 MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C.
-The outlet temperature of the LFR is rigid due to high temperature material limits on the LFR lead side.
+The amount of energy transferee into the cycle, $\dot{Q}_{LFRHX}$, is set at $950 MW$, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C.
+\mw{Make sure numbers are in math mode}
+The outlet temperature of the LFR is \replaced{specified, accounting for the}{rigid due to} high temperature material limits on the LFR lead side.
 Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C.
+\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right?} 
 Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.
@@
 
-The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-Salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX).
+The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX).
 The diagram for this CSP salt cycle is seen in Figure \ref{csp}.
 
-\end{paracol}
-%MW: Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. 
+\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. }
+
+% \end{paracol}
+
 \begin{figure}[htb]
+
     \widefigure
@@
 \end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
+% \begin{paracol}{2}
+% \linenumbers
+% \switchcolumn
 
@@
 Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
-The cold TES temperature takes on three different values according to cycle configuration capabilitites: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
+The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
 In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}.
@@
 
-The C2S heat exchanger is active during the 'charging' cycle configurations, when the focus is on heat storage for later use.
+The C2S heat exchanger is active \replaced{in}{during} the 'charging' cycle configurations, when the focus is on heat storage for later use.
 During this process there is no solar salt flow through the receiver.
-Pump 1 is active moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.
+\mw{Is this necessarily true?
+Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP?} Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.
 
-'Non-charging' cycle configurations has the receiver charging the hot TES, C2S heat exchanger is not transfering heat, and the LFR is dispatching energy directly into electrical generation.
-When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
+'Non-charging' cycle configurations \replaced{are characterized by operations wherein}{has} the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is \replaced{heat}{dispatching energy} directly to generate electricity.
+When electrical generation is occurring, the heat input in this \mw{``this'' is ambiguous} cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
 The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
@@
 %======================================================================================
+\mw{What do you mean by ``generalized?''}
 
-The cycles presented are generalized in order to draw a more direct comparison.
-The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
+\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations.
+It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.}
+
+\replaced{In order to draw a more direct comparison, the cycles are generalized in terms of}{The cycles presented are generalized in order to draw a more direct comparison.
+The generalized parameters include} isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
 These values are summarized in Table \ref{tab-cycle-constants}.
 
-%MW: Also changing the specialtable position to allow latex to better place tables.
 \begin{specialtable}[htbp] 
+    \mw{Also changing the specialtable position to allow latex to better place tables.}
+
     \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
-    \begin{tabular}{lcc}
+    \begin{tabular}{L{0.5\linewidth}cc}
     \toprule
@@
 The recompression side contains a PreCooler, Low Temperature Recuperator, and two compressors; Main Compressor and ReCompressor.
+\mw{components don't need to be capitalized -- they aren't proper nouns}
 
@@
     \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
-    \begin{tabular}{ll}
+    \begin{tabular}{lL{0.7\linewidth}}
     \toprule
@@
 
-The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$.
+The numerator in Equation \ref{eq-eta-cycle} is the \replaced{alternator}{Alternator} power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$.
 The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.
@@
 
-The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a CSP cycle.
+The two-cycle configuration that is tested has independent sCO$_{2}$ loops \replaced{that share a common}{bridged by a} CSP cycle.
 This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON.
@@
 The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.
+\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.}
 
 \end{paracol}
-\begin{figure}[H] 
+\begin{figure}[!h] 
     \widefigure
@@
 
-Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
+Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
 The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency.
 The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
-%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint
-
+\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
+% 
 The cycle that is using the CSP heat input in the two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.
@@
 \end{paracol}
-\begin{figure}[H] 
+\begin{figure}[!h] 
     \widefigure
@@
 
-%BL: be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from
+\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
+\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
+I think it's a problem with the MDPI template.
+The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.}
+\end{paracol}
 
-\end{paracol}
 \begin{figure}[H] 
@@
 \end{figure}
+
 \begin{paracol}{2}
@@
 Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model.
-The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency.
-The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K.
+The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES \mw{varied cold CSP TES ...
+what?
+temperature?} and maximized cycle efficiency.
+\mw{State what variable(s) are manipulated in order to maximize cycle efficiency} \replaced{Two cold CSP TES temperature values are tested (683.2 K and 713.2 K)}{The two tested values for cold CSP TES} with constrained LFR low temperature\deleted{ are 683.2 K and 713.2 K}.
 The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt).
-In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K.
-%BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
+In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to 653.2 K.
+\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
 Asp you will want to explain the criteria that go into cold storage temp.
-Lower = more delta T = more dispatchability
+Lower = more delta T = more dispatchability}
 
@@
 
-Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency.
+Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}.
 To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired.
@@
 The LFR is powering one turbine, T1, and recuperating heat through a dedicated high temperature recuperator, HTR1.
-The CSP cycle also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2.
-After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
-%BL: this is more about having a compromise option of intermediate complexity and efficiency
+\mw{The LFR doesn't recuperate heat.
+Clarify what you mean here.} The CSP cycle \mw{CSP cycle refers to the salt loop.
+Here we mean something else.} also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2.
+\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
+\bl{this is more about having a compromise option of intermediate complexity and efficiency}
 
@@
 
-Three sensitivity studies are done on the C-2HTR3T-ON model.
-Two with the LFR low temperature constrained and one without this constraint.
-The two constrained studies had varied cold CSP TES temperature with the lowest temperature of 663.2 K and highest temperature of 713.2 K.
+Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint.
+The two constrained studies had varied\mw{present tense} cold CSP TES temperature with the lowest temperature of 663.2 K and highest temperature of 713.2 K.
 The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of 663.2 K.
-%BL: this is clearer than the previous one but bullets could still be useful
+\bl{this is clearer than the previous one but bullets could still be useful}
 
@@
 
-Charging cycle configurations focus on an energy storage operating mode.
-These configurations test the optimal location of LFR heat extraction through the SALT HX.
-To maximize the available heat for extraction, alternator power is set to zero and turbine power is therefore equal to the compressors' demand.
+Charging cycle configurations \replaced{accommodate}{focus on an} energy storage \replaced{modes of operation}{operating mode}.
+These configurations \replaced{examine the}{test the optimal} location of LFR heat extraction \replaced{via}{through} the SALT HX.
+To maximize the available heat for extraction, alternator \added{net} power is set to zero\added{, therefore requiring that the} turbine power is \deleted{therefore} equal to the compressors' demand.
 The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases.
-Comparison of where thermal energy is extracted in the cycle is done by using the same Brayton cycle, C-LFR-ON, and configuring the salt heat exchanger in different locations around the turbine.
-To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
-%BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output
+\replaced{The location of heat extraction}{Comparison of where thermal energy is extracted} in the cycle is \replaced{compared within the C-LFR-ON Brayton cycle by placing}{done by using the same Brayton cycle, C-LFR-ON, and configuring} the salt heat exchanger in different locations around the turbine.
+To quantify the effectiveness of TES charging techniques a heat storage efficiency, \added{we define the metric} $\eta_{heatstorage}$ \deleted{, is defined by} in Equation \ref{eq-eta-heatstorage}.
+\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output}
 
@@
 
-Whereas $\dot{Q}_{S2C}$ is the amount of heat transfered through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
+Whereas $\dot{Q}_{S2C}$ is the amount of heat transferred through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
+\mw{not a full sentence}
 
@@
 This excess thermal energy is stored in the hot CSP TES.
-The diagram outlining this process is C-LFR-PRE in Fig.
+\mw{Careful here.
+Be precise about what ``excess'' means in this context.
+Any fluid above absolute zero technically has excess thermal energy if the reference is zero.
+Depending on this definition, not all excess energy from the turbine is stored in TES.} The diagram outlining this process is C-LFR-PRE in Fig.
 \ref{c-lfr-pre}.
+\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations.}
 
@@
 
-This TES charging cycle extracts heat before the turbine and therefore would have a large negative effect on the amount of work that the turbine could produce.
-The turbine needs to offset the requirements of both compressors and this would require the inlet temperature to be high.
+This TES charging cycle extracts heat before the turbine and therefore would have \mw{tense..
+it ``has''} a large negative effect on the amount of work that the turbine could \mw{tense} produce.
+The turbine needs to offset \mw{the turbine does not have feelings :)} the requirements of both compressors and this would require the inlet temperature to be high.
 The amount of energy that could be extracted before the turbine would be small and therefore the heat storage efficiency would be small.
 There is no quantitative study done on this case because, due to the efficiency losses, it is non-viable.
+\mw{write matter-of-factly, not in a hypothetical tense.}
 
@@
 
-The requirement of the turbine and CSP hot TES temperature can be accomplished by splitting the flow before the turbine.
+The requirements of the turbine and CSP hot TES can be \replaced{satisfied}{accomplished} by splitting the flow before the turbine.
 The flow through the salt heat exchanger in this cycle is therefore separate from the turbine.
-After the salt heat exchanger a valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
+After the salt heat exchanger, a valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
 
@@
 
-Two sensitivity studies with varying cold CSP TES are desired to see the impact on heat storage efficiency.
-The TES temperature study is calculated with a low TES temperature of 663.2 K and a high TES temperature of 713.2 K.
+Two sensitivity studies \mw{this is one study with two parameter values, right?} with varying cold CSP TES \added{temperature} are \replaced{carried out to determine}{desired to see} the impact on heat storage efficiency.
+\replaced{The study considers two temperature values of 663.2 K and 713.2 K.}{The TES temperature study is calculated with a low TES temperature of 663.2 K and a high TES temperature of 713.2 K.} \mw{make sure I didn't change the meaning here}
 
@@
 
-%BL: explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)
+\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed}
 

### 2021-08-09 simulations/util/PostProcessing.py
fixing pricing plots and TES energy limits

@@ -175,7 +175,8 @@ class Plots(object):
     """
 
     def __init__(self, module, fsl='x-small', loc='best', legend_offset=False,
-                 lp=16, lps=12, fs=12, lw=2, x_shrink=0.85, x_legend=12):
+                 lp=16, lps=12, fs=12, lw=2, x_shrink=0.85, x_legend=12,
+                 fE_min=-0.05, fE_max=0.7):
         """ Initializes the Plots module
 
         The instantiation of this class receives a full module object, the module
@@ -193,6 +194,8 @@ class Plots(object):
             fs (int)            : fontsize for labels, titles, etc.
             lw (int)            : linewidth for plotting
             x_shrink (float)    : (legend_offset==True) amount to shrink axis to make room for legend
+            fE_min (float)      : minimum fraction of TES energy for ylim
+            fE_max (float)      : maximum fraction of TES energy for ylim
         """
         
         self.u = u
@@ -204,6 +207,10 @@ class Plots(object):
         self.lw  = lw   # linewidth
         self.fsl = fsl  # fontsize legend
         self.loc = loc  # location of legend
+        
+        # ylims
+        self.fE_min = fE_min
+        self.fE_max = fE_max
 
         # offsetting legend
         self.legend_offset = legend_offset # boolean - are we plotting legends off-axis?
@@ -481,7 +488,7 @@ class Plots(object):
                                     start_hr=start_hr, end_hr=end_hr, hide_x=hide_x)
 
         # custom y limits and ticks to be integers for Energy
-        ax2.set_ylim(-0.05*self.e_tes_design.m, 0.7*self.e_tes_design.m)
+        ax2.set_ylim(self.fE_min*self.e_tes_design.m, self.fE_max*self.e_tes_design.m)
 
         # plot Energy array(s)
         energy_array_list = ['e_ch_tes']
@@ -616,8 +623,11 @@ class Plots(object):
         ax2 = ax.twinx()  # this is the pricing plot
 
         # custom y limits and ticks to be integers
-        ax2.set_ylim(0, 2.5)
-        ax2.set_yticks(np.arange(0, 2.5, 0.5))
+        price = self.price[ start_hr:end_hr  ]
+        minP = 1.05*price.min() if price.min() < 0 else 0
+        maxP = 1.05*price.max()
+        ax2.set_ylim(minP, maxP)
+        ax2.set_yticks(np.arange(minP, maxP, 0.5))
         
         # plot price array(s)
         price_array_list = ['price']

### 2021-08-30 simulations/scripts/sanity_check_scripts/test_NuclearTES_PySSC_defocus.py
new plotting capabilities for this test script, distinguishing failure modes

@@ -30,7 +30,7 @@ print("PID = ", pid)
 # p_cycle_2     = np.array([ 700, 650, 600, 550, 500,      400, 350, 300, 250, 200, 150 ]) # Pref= 450, tshours=2
 # p_cycle_4     = np.array([ 700, 650, 600, 550, 500,                300, 250, 200, 150 ]) # Pref= [350,450], tshours=4
 # p_cycle_6     = np.array([ 700, 650, 600, 550, 500,      400,      300, 250, 200, 150 ]) # Pref= {350,450}, tshours=6
-p_cycle_8     = np.array([ 700, 650, 600, 550, 500, 450,           350, 300, 250,      150 ]) # Pref= {250,400,450}, tshours=8
+p_cycle_8     = np.array([ 700, 650, 600, 550, 500,           350, 300, 250,      150 ]) # Pref= {250,400,450}, tshours=8
 # p_cycle_10    = np.array([ 700, 650, 600, 550, 500,      400, 350, 300, 250, 200, 150 ]) # Pref= 450, tshours=10
 # p_cycle_12    = np.array([ 700, 650, 600, 550, 500,           350, 300, 250,      150 ]) # Pref= {200,400,450}, tshours=12
 # p_cycle_14    = np.array([ 700, 650, 600, 550, 500,      400, 350, 300, 250, 200, 150 ]) # Pref= 450, tshours=14
@@ -48,6 +48,7 @@ empty = np.zeros([  len(iterator1) , year_in_hours ])
 time_array     = empty.copy()
 defocus_array  = empty.copy()
 gen_array      = empty.copy()
+eta_array      = empty.copy()
 qdot_nuc_array = empty.copy()
 op_mode_array  = empty.copy()
 sim_success    = empty.copy()
@@ -82,6 +83,7 @@ for i, pc in enumerate(iterator1): #over P_cycle rating
         # log outputs
         time_array[i,:]      = pw.get_array('time_hr') / 24
         gen_array[i,:]       = pw.get_array('gen') / 1e3
+        eta_array[i,:]       = pw.get_array('eta')
         qdot_nuc_array[i,:]  = pw.get_array('q_dot_rec_inc')
         defocus_array[i,:]   = pw.get_array('defocus')
         op_mode_array[i,:]   = pw.get_array('op_mode_1')
@@ -117,3 +119,43 @@ ax.set_xlabel("Time (hr)", fontweight="bold")
[…]

### 2021-08-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

--- 2021-08-09 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 
+Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
+Higher efficiencies, in some simple recompression cycles reaching 50\% efficiency, allows for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}.
+Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.
+Due to the benefits of sCO$_2$ Brayton cycles the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
+Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each.
+Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
+
+A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
+Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2012, turchi_2013, ho_2015, wang_2018}.
+Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases.
+With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch.
+A LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 595 $^{\circ}$C.
+LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}.
+Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} .
+In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.
+
+Implementation of a combined solar and nuclear plant, modeled in a 2020 study from the School of Energy and Power Engineering in Jilin, China, shows a single recompression cycle layout with and emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility with no demonstration of varied cycle arrangements \cite{wang_2020}.
+
+\hl{This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
+Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.}
+
+%Korea Atomic Energy Research Institute \cite{cha_2016}  
+%interest in brayton \cite{doe_2012}
+%Efficiency 50\% \cite{turchi_2013} \cite{wright_2009}
+%Thermal storage \cite{paul_2010} \cite{sioshansi_2010}
+%sCO2 Brayton nuclear \cite{dostal_2005} \cite{dostal_2004} \cite{luo_2020}
+%sCO2 Brayton solar \cite{turchi_2012} \cite{turchi_2013} \cite{ho_2015} \cite{wang_2018}
+%Cycle Configs \cite{turchi_2012} \cite{wang_2018}
+%Similar Works \cite{wang_2020}
+%Experimental Plants \cite{cha_2016} \cite{wright_2011}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+% **************************************
+
+%MW: I've fixed spelling in a few places. You can install a spell checker to highlight misspelled words. I use the "Code spell checker" extension.
+
 \subsection{Cycle Component Modeling}
 %======================================================================================
-Components present in the cycles are modeled using various techniques.
+Components present in the cycles are modeled using various techniques and are discussed in more detail below.
 Turbines and compressors are analyzed using isentropic efficiencies.
-Counter flow heat exchangers use the effectiveness-NTU method while black box heat exchangers use a simple energy balance for state point calculations.
+Counter-flow heat exchangers use the effectiveness-NTU method while simplified ``black box'' heat exchangers use a simple energy balance for state point calculations.
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
-The concentrating solar power cycle is modeled with necessary components including hot and cold TES, reciever, pumps and counter flow heat exchangers.
+The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
 
@@
 
-The modeled cycles have a number of compressors and turbines.
-The turbines and compressors are modeled for each cycle using constant isentropic efficiency values summarized in Table \ref{tab-cycle-constants}.
+Turbines and compressors are modeled for each cycle using constant isentropic efficiency values which are summarized in Table \ref{tab-cycle-constants}.
 Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$.
-The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have a single inlet and outlet.
-Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.
-Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor can be calculated \cite{klein_nellis_2011}.
+The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have single inlet and outlet streams.
+Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor are calculated \cite{klein_nellis_2011}.
 
-\subsubsection{Black Box and Counter Flow Heat Exchangers}
+%Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.\mw{this is kind of an awkward way to describe what's happening.
+I think most readers are familiar with isentropic efficiencies and this can be omitted.}
+
+\subsubsection{Black Box and Counter-Flow Heat Exchangers}
 %--------------------------------------------------------------------------------------
@@
 
+%\mw{This is for a single flow stream.
+Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream?
+Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$.
+-BW}
+
 \begin{equation}
     \label{eq-black}
-    \dot{m}_{in}*h_{in} + \dot{Q}_{in} = \dot{m}_{out}*h_{out} + \dot{Q}_{out},
+    \dot{m} \cdot h_{in} + \dot{Q}_{HX} = \dot{m} \cdot h_{out} ,
 \end{equation}
 
-In this equation the energy input to the system is on the left hand side with $\dot{m}_{in}$ multiplied by $h_{in}$ being energy from the mass flow and $\dot{Q}_{in}$ being heat transfer directly to the flow from an outside source.
-The right hand side of the equation is heat leaving the energy balance.
-The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow.
-Black box energy balances are used in three situations, the Reciever, LFR HX, and PC HX.
-These heat exchangers are not exchaustively modeled because the state points on the inlet and outlet are constrained by design parameters.
+In this equation the energy input to the system is on the left hand side with $\dot{m}$ multiplied by $h_{in}$ being energy from the mass flow while $\dot{Q}_{HX}$ is heat transfer directly into, positive, or out of, negative, the flow from an outside source.
+The right hand side of the equation is heat leaving the black box heat exchanger with $\dot{m}$ and enthalpy of $h_{out}$.
+Black box energy balances are used in three situations, the receiver, LFR heat exchanger, and PC heat exchanger.
+These heat exchangers are not exhaustively modeled because the state points on the inlet and outlet are defined by design parameters.
 
-Counter flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
+Counter-flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
 The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature.
-A diagram showing a simplified example of a counterflow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
+A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
 
@@
     \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
-    \caption{Simple counter flow heat exchanger diagram. \label{counter-flow-hx}}
+    \caption{Simple counter-flow heat exchanger diagram. \label{counter-flow-hx}}
 \end{figure}
@@
 
-Additional assumptions of the counter flow heat exchanger model are no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, and no pressure drops accross the heat exchangers.
-Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
-In all of the modeled cases, the approach temperature is set to a value of 10 K.
-The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+Additional assumptions of the counter-flow heat exchanger model are: no heat loss to the surroundings, no pressure drops across the heat exchangers, and no fouling resistances.
+In Figure \ref{counter-flow-hx} the subscript 'out' denotes where the streams are leaving, 'in' denotes the entering streams, 'c' and 'h' signify cold and hot streams respectively, $\dot{Q}_{HX}$ is the total heat transfer from the hot to cold stream, and $\dot{Q}_{surr}$ is the heat transfer to the surroundings.
 
-To analyze the counter flow heat exchanger a side is chosen, usually high, to start the calculations.
-The approach temperature is initially subtracted from the hot stream on the high side to find the missing cold temperature according to Equation \ref{temp_h}.
+Counter-flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
+\hl{In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers} \cite{seidel_2010_model_development}.
+%\mw{Justify -BW} 
+The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+
+To analyze the counter-flow heat exchanger a side is chosen, usually the high side, to start the calculations.
+The approach temperature is initially subtracted from the hot stream on the high temperature side to find the missing cold temperature according to Equation \ref{temp_h}.
 
@@
 Where T$_{out,c}$ is the cold stream outlet temperature and T$_{in,h}$ is the hot stream inlet temperature.
-Knowing the two state points allows for the enthalpy to be found using correlations from the fluid property libraries.
+Knowing the two state points allows for the enthalpy out to be found using correlations from the fluid property libraries.
+This enthalpy then allows for the heat transfer of the heat exchanger to be found with Equation \ref{heattrans_h}.
 
-[More Desctription on Counterflow HX]
+\begin{equation}
+    \label{heattrans_h}
+     \dot{Q}_{HX} = \dot{m}_{c}(h_{out,c}-h_{in,c}),
+ \end{equation}
+
+ Where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and $h_{in,c}$ is the inlet of the cold side.
+ The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is done with Equation \ref{enthalpy_h}.
+
+ \begin{equation}
+    \label{enthalpy_h}
+     h_{out,h} = h_{in,h} - \frac{\dot{Q}_{HX}}{\dot{m}_{h}},
+ \end{equation}
+
+Knowing the hot stream enthalpy out allows for all states to be set on the outlets and inlets of the counter-flow heat exchanger.
+The temperature difference of the low side is then checked to ensure that it is larger than the approach temperature, defined at $10^\circ$C.
+If the temperature difference on the low side is smaller than the approach temperature, the same computations are carried with the low side as the starting point.
+
+Knowing the state points on all inlets and outlets of the counter-flow heat exchanger allows for the heat exchanger performance metrics to be calculated.
+Performance metrics include effectiveness, capacitance ratio, UA, and NTU for heat exchangers.
+Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature.
+Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_max$ is found with the maximum enthalpy.
+Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet.
+Using the maximum enthalpy, $h_{max}$, the maximum heat transfer rate is calculated using Equation \ref{heattrans_max}.
+
+\begin{equation}
+    \label{heattrans_max}
+    \dot{Q}_{max} = \dot{m}_{c}(h_{max}-h_{in,c}),
+\end{equation}
+
+Calculating the maximum heat transfer rate allows for effectiveness to be calculated using the ratio in Equation \ref{effective}.
+
+\begin{equation}
+    \label{effective}
+    \varepsilon = \frac{\dot{Q}_{HX}}{\dot{Q}_{max}},
+\end{equation}
+
+All of the prior equations are carried out in a built in function within EES.
+EES is an iterative solver, therefore as long as there is a feasible solution, the functions can take any of the four state points around the heat exchanger and converge on a solution.
+
+After the effectiveness is solved for, capacitance ratio is necessary.
+The capacitance ratio is defined as the average minimum capacitance rate, $\dot{C}_{min}$, over the average maximum capacitance rate, $\dot{C}_{max}$.
+Average capacitance rates for the hot and cold streams are found by multiplying the addition of the specific heat at the inlet and outlet of the stream by the mass flow and dividing by two as seen in Equation \ref{avg_cap}.
+
+\begin{equation}
+    \label{avg_cap}
+    \dot{C}_{avg} = \frac{\dot{m}(c_{in}+c_{out})}{2},
+\end{equation}
+
+Where $C_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively.
+Specific heat is found using library correlations.
+Once both average capacitances are calculated for the hot and cold streams, the one will have a larger value, $\dot{C}_{max}$, and one will have a smaller value,  $\dot{C}_{min}$.
+These maximum and minimum values are then used to find the capacitance ratio, $CR$, in Equation \ref{cap_ratio}.
+
+\begin{equation}
+    \label{cap_ratio}
+    CR = \frac{\dot{C}_{min}}{\dot{C}_{max}},
+\end{equation}
+
+\hl{Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$} \cite{klein_nellis_2011,nellis_klein_2008}.
 
@@
     \label{eq-lfr-black-box}
-    \dot{m}_{inlet}*h_{inlet} + \dot{Q}_{LFRHX} = \dot{m}_{outlet}*h_{outlet},
+    \dot{m} \cdot h_{inlet} + \dot{Q}_{LFRHX} = \dot{m} \cdot h_{outlet},
 \end{equation}
 
-Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$.
-The amount of energy transfered into the cycle, $\dot{Q}_{LFRHX}$, is set at 950 MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C.
-The outlet temperature of the LFR is rigid due to high temperature material limits on the LFR lead side.
-Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C.
+%\mw{If mass is conserved, use a single $\dot{m}$ - BW}
+
+Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$.
+The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C.
+%\mw{Make sure numbers are in math mode -BW}
+The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side.
+Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by our industry partner.
+%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
 Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.
@@
 
-The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-Salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX).
+The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-salt counter-flow heat exchanger (C2S), and CSP counter-flow heat exchanger (CSP HX).
 The diagram for this CSP salt cycle is seen in Figure \ref{csp}.
 
-\end{paracol}
-%MW: Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. 
-\begin{figure}[htb] 
+%\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}
+
+% \end{paracol}
+
+\begin{figure}[H] 
+    %[htb]
     \widefigure
@@
 Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
-The cold TES temperature takes on three different values according to cycle configuration capabilitites: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
+The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
 In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}.
 The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle.
-It is assumed that only one hot TES charging option can be active at any given time.
+While the hot TES is charging the receiver and LFR are storing heat for later use when grid demand increases.
+The hot TES storage is not dispensing salt for use in the CSP cycle while charging.
 
-The C2S heat exchanger is active during the 'charging' cycle configurations, when the focus is on heat storage for later use.
-During this process there is no solar salt flow through the receiver.
-Pump 1 is active moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.
+\hl{The C2S heat exchanger is active in the 'charging' cycle configurations, when the focus is on heat storage for later use.
+Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle.
+Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver then being stored in the hot TES.}
+%\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }
 
-'Non-charging' cycle configurations has the receiver charging the hot TES, C2S heat exchanger is not transfering heat, and the LFR is dispatching energy directly into electrical generation.
-When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field.
+'Non-charging' cycle configurations are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
+When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
 The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
@@
 
-\subsection{Generalization of Cycle Modeling}
+\subsection{Standardization of Cycle Modeling}
 %======================================================================================
+%\mw{What do you mean by ``generalized?''-BW}
 
-The cycles presented are generalized in order to draw a more direct comparison.
-The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
+In order to draw a more direct comparison, the cycles are standardized in terms of isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants.
 These values are summarized in Table \ref{tab-cycle-constants}.
 
-%MW: Also changing the specialtable position to allow latex to better place tables.
-\begin{specialtable}[htbp] 
-    \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
-    \begin{tabular}{lcc}
+\begin{specialtable}[H] 
+    %[htbp]
+    %\mw{Also changing the specialtable position to allow latex to better place tables.-BW}
+    \caption{Standardized constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
+    \begin{tabular}{L{0.5\linewidth}cc}
     \toprule
@@
     \textit{Approach Temperatures}\\
-    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
-    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
-    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
+    Low Temperature Recuperator & $\delta_{LTR}$		& 10 ($^{\circ}$C)\\
+    High Temperature Recuperator & $\delta_{HTR}$		& 10 ($^{\circ}$C)\\
+    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 ($^{\circ}$C)\\
     \midrule
@@
     Pressure Ratio & $PR$ & 3.27 (-)\\
-    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
+    High Side Pressure & $P_{2A}$ & 28.8 (MPa)\\
     \midrule
     \textit{Heat Into System}\\
-    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
-    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
+    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 950 (MW)\\
+    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 750 (MW)\\
     \midrule
     \textit{Temperature}\\
-    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
+    Main Compressor Inlet & $T_{1A}$ & 40 ($^{\circ}$C)\\
     %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
-    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
+    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 595 ($^{\circ}$C)\\
     \midrule
     \textit{Pumps}\\
-    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
-    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
+    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726 (MPa)\\
+    Pump Low Side Pressure & $P_{S5-B}$ & 3 (MPa)\\ 
     \bottomrule
@@
 In addition to generalized parameters, all cycles have identical recompression sides.
-The recompression side contains a PreCooler, Low Temperature Recuperator, and two compressors; Main Compressor and ReCompressor.
+The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor.
+\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations.
+It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.}
+%\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
 
@@
     C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
-    C-2HTR3T-ON & Seperatre CSP and LFR loops each with dedicated HTR and turbine.\\
+    C-2HTR3T-ON & Separate CSP and LFR loops each with dedicated HTR and turbine.\\
     \midrule
@@
 
-The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$.
+The numerator in Equation \ref{eq-eta-cycle} is the alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$.
 The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.
@@
 
-The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a CSP cycle.
+The two-cycle configuration that is tested has independent sCO$_{2}$ loops that share a common CSP salt cycle.
 This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON.
@@
 The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}. 
+%\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.}
 
@@
 \begin{figure}[H] 
+    %[!h] 
     \widefigure
@@
 
-Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
-The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency.
-The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
-%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint
+Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON.
+The constrained study is calculated by setting the LFR inlet temperature to the design value of $400^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits.
+In addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency.
+The unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency.
+In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post.
+%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
 
@@
 \begin{figure}[H] 
+    %[!h]
     \widefigure
@@
 Instead, a sensitivity study is done on the temperature of the cold TES.
-Two temperatures are tested, 663.2 K and 713.2 K, to observe the impact of cold TES temperature on cycle efficiency.
+Two temperatures are tested, $390^{\circ}$C and $440^{\circ}$C, to observe the impact of cold TES temperature on cycle efficiency.
 
@@
 
-%BL: be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from
+%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
+%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
+I think it's a problem with the MDPI template.
+The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
+\end{paracol}
 
-\end{paracol}
 \begin{figure}[H] 
@@
 
-In this cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation.
-Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model.
-The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency.
-The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K.
-The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt).
-In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K.
-%BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
+The C2S is located around the turbine and LFR at state points 5 to 6 depending on the charging cycle configuration: pre, parallel, post or circulator.
+In the C-1HTR1T-ON cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation.
+Therefore, three sensitivity studies are done on the model.
+The initial two studies have the low LFR temperature constrained to the value of $400^{\circ}$C with varied cold CSP TES temperature and maximized cycle efficiency.
+To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, was parametrically studied.
+%\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
+Two cold TES temperatures are tested with constrained LFR low temperature of $400^{\circ}$C: 
+\begin{itemize}
+    \item	$410^{\circ}$C: Lowest cold TES temperature possible due to the sCO$_2$ cold inlet constrained from the LFR to $400^{\circ}$C and the addition of $10^{\circ}$C approach temperature;
+    \item	$440^{\circ}$C: Upper bound temperature on cold TES storage;
+\end{itemize}
+
+Additionally a third test is conducted with the desired cold TES temperature of $390^{\circ}$C and the LFR low temperature unconstrained:
+
+\begin{itemize}
+    \item	$390^{\circ}$C: Unconstrained LFR cold inlet temperature allows for the desired cold TES to be achieved;
+\end{itemize}
+
+In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C.
+The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
+%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
 Asp you will want to explain the criteria that go into cold storage temp.
-Lower = more delta T = more dispatchability
+Lower = more delta T = more dispatchability -BW}
 
@@
 
-Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency.
+Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}.
 To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired.
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
-The LFR is powering one turbine, T1, and recuperating heat through a dedicated high temperature recuperator, HTR1.
-The CSP cycle also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2.
+The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR1.
+%\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
+The cycle with heat addition from the CSP also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. 
+\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} 
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
-%BL: this is more about having a compromise option of intermediate complexity and efficiency
+\bl{this is more about having a compromise option of intermediate complexity and efficiency}
 
@@
 
-Three sensitivity studies are done on the C-2HTR3T-ON model.
-Two with the LFR low temperature constrained and one without this constraint.
-The two constrained studies had varied cold CSP TES temperature with the lowest temperature of 663.2 K and highest temperature of 713.2 K.
-The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of 663.2 K.
-%BL: this is clearer than the previous one but bullets could still be useful
+The C2S heat exchanger is located around the turbine and LFR at 7A to 8A depending on the charging configuration: pre, post, parallel or circulator.
+Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint.
+The two constrained studies have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C.
+The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.
+\bl{this is clearer than the previous one but bullets could still be useful}
 
@@
 
-Charging cycle configurations focus on an energy storage operating mode.
-These configurations test the optimal location of LFR heat extraction through the SALT HX.
-To maximize the available heat for extraction, alternator power is set to zero and turbine power is therefore equal to the compressors' demand.
+Charging cycle configurations accommodate energy storage modes of operation.
+These configurations examine the location of LFR heat extraction via the SALT HX.
+To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring that the turbine power is equal to the compressors' demand.
+Despite the components being non-ideal and consuming power, the recompression cycle continues to operate, ensuring that there is mass flow to transfer heat from the Brayton cycle to C2S.
 The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases.
-Comparison of where thermal energy is extracted in the cycle is done by using the same Brayton cycle, C-LFR-ON, and configuring the salt heat exchanger in different locations around the turbine.
-To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
-%BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output
+The location of heat extraction in the cycle is compared within the C-LFR-ON Brayton cycle by placing the salt heat exchanger in different locations around the turbine.
+To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
+%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
 
@@
 
-Whereas $\dot{Q}_{S2C}$ is the amount of heat transfered through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
+In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
+%\mw{not a full sentence -BW}
 
@@
 \ref{c-lfr-pre}.
+
+\mw{Careful here.
+Be precise about what ``excess'' means in this context.
+Any fluid above absolute zero technically has excess thermal energy if the reference is zero.
+Depending on this definition, not all excess energy from the turbine is stored in TES.}
+\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations.}
 
@@
 Problems arise with this salt charging configuration.
-The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of 833.2 K.
+The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $595^{\circ}$C.
 To raise the temperature, some of the high temperature flow before the turbine is redirected through a valve and combined after the turbine.
@@
 
-This TES charging cycle extracts heat before the turbine and therefore would have a large negative effect on the amount of work that the turbine could produce.
-The turbine needs to offset the requirements of both compressors and this would require the inlet temperature to be high.
-The amount of energy that could be extracted before the turbine would be small and therefore the heat storage efficiency would be small.
+This TES charging cycle extracts heat before the turbine and therefore has a large negative effect on the amount of work that the turbine is producing.
+The turbine power offsets the requirements of both compressors, requiring the turbine inlet temperature to be high.
+The amount of energy that is extracted before the turbine is small and therefore the heat storage efficiency is fractional compared to other charging techniques.
 There is no quantitative study done on this case because, due to the efficiency losses, it is non-viable.
+
+%\mw{write matter-of-factly, not in a hypothetical tense.-BW}
 
@@
 
-The requirement of the turbine and CSP hot TES temperature can be accomplished by splitting the flow before the turbine.
+The requirements of the turbine and CSP hot TES can be satisfied by splitting the flow before the turbine.
 The flow through the salt heat exchanger in this cycle is therefore separate from the turbine.
-After the salt heat exchanger a valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
+After the salt heat exchanger, a valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure \ref{c-lfr-par}.
 
@@
 
-Two sensitivity studies with varying cold CSP TES are desired to see the impact on heat storage efficiency.
-The TES temperature study is calculated with a low TES temperature of 663.2 K and a high TES temperature of 713.2 K.
+Two sensitivity studies \mw{this is one study with two parameter values, right?} with varying cold CSP TES temperature are carried out to determine the impact on heat storage efficiency.
+The study considers two temperature values of $390^{\circ}$C and $440^{\circ}$C.
 
@@
 The charging subsection of this diagram is composed of a circulation cycle that has heat inputted through the LFR heat exchanger.
+A separated circulation cycle has a loop which avoids the losses associated with compressor and turbine, therefore achieving higher heat storage efficiency than possible with full cycle operation.
 This subsection is encircled in blue and can be seen in Figure \ref{c-lfr-circ-sub}.
 
-%BL: explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)
+%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
 
@@
 A heat exchanger, SALT HX, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
-Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of 673.2 K.
-Three different temperatures; 663.2 K, 683.2 K, and 713.2 K, are compared in a sensitivity study.
+Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of $400^{\circ}$C.
+Three different cold TES temperatures; $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C, are compared in a sensitivity study.
 
@@
 
+\subsubsection{Large Tables}
+\begin{specialtable}[H] 
+    %[htbp]
+    \caption{Calculated system parameters for non-charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-noncharg}}
+    \begin{tabular}{lccccccccccc}
+    \toprule
+     &  & \textbf{C-LFR-ON} & & \textbf{C-CSP-ON} &  &	\textbf{C-1HTR1T-ON} &	&	&	\textbf{C-2HTR3T-ON}	&	& \\
+    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C} & \textit{N/A} & \textit{N/A} &	\textit{U}	&	\textit{C}	&	\textit{C}	&	\textit{U}	&	\textit{C}	&	\textit{C}
+    \\
+    \midrule
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	395.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	395.2	&	400	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	&	339.1	&	340.6	&	763.9	&	752.3	&	752.6	&	783.7	&	753.7	&	754	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	&	418.5	&	420.2	&	937.4	&	949.2	&	949.3	&	917.6	&	947.6	&	947.9	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	&	95.73	&	96.13	&	214.5	&	194.8	&	194.8	&	209.9	&	216.8	&	216.9	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	&	97.22	&	97.71	&	217.4	&	285.7	&	285.7	&	213.5	&	140.8	&	140.8	\\
+    T1 Power (MW)	&	$\dot{W}_{T1}$	&	678.9	&	626.4	&	532.1	&	534.5	&	1196	&	1233	&	1233	&	679.3	&	626.3	&	626.3	\\
+    T2 Power (MW)	&	$\dot{W}_{T2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	527.8	&	485	&	485.4	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	&	0.6996	&	0.6994	&	0.7	&	0.6333	&	0.6333	&	0.6993	&	0.7846	&	0.7846	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	5.48E-01	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	&	45.4	&	45.53	&	102	&	91.63	&	91.64	&	134.4	&	41.56	&	41.57	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	&	0.9858	&	0.9854	&	0.9867	&	0.9066	&	0.9066	&	0.9853	&	0.847	&	0.847	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	&	548.3	&	551.4	&	549.2	&	614.9	&	615.1	&	1204	&	667.1	&	667.3	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	&	0.9201	&	0.9202	&	0.92	&	0.9485	&	0.9485	&	0.9414	&	0.8741	&	0.8741	\\
+    HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.29	&	42.71	&	34.58	&	34.72	&	78.22	&	82.3	&	82.34	&	48.32	&	42.69	&	42.69	\\
+    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8657	&	0.9627	&	0.8593	&	0.8594	&	0.8595	&	0.8754	&	0.8755	&	0.8661	&	0.8142	&	0.8142	\\
+    HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	998.1	&	1161	&	665.4	&	667.7	&	679.2	&	742.6	&	743	&	545.7	&	636.8	&	636.6	\\
+    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
+    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	34.29	&	31.61	&	31.63	\\
+    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.8594	&	0.8074	&	0.8074	\\
+    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	298.1	&	363.4	&	363.8	\\
+    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.9436	&	0.9561	&	0.9561	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	75.19	&	70.88	&	44.92	&	23.13	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	N/A	&	N/A	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	N/A	&	N/A	&	757.6	&	760.8	&	751.3	&	751.5	&	751.9	&	751.3	&	751.3	&	751.9	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	N/A	&	N/A	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\begin{specialtable}[H] 
+    %[htbp]
+    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
+    \begin{tabular}{lccccccc}
+    \toprule
+     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
+    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
+    \midrule
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	119	&	N/A	&	N/A	&	N/A	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
+    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
+    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
+    CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	N/A	&	35	&	26.27	&	N/A	&	N/A	&	N/A	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
 \subsubsection{C-LFR-ON and C-CSP-ON}
@@
 
-\begin{specialtable}[htbp] 
+\begin{specialtable}[H] 
+    %[htbp]
     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
@@
     \midrule
-    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	&	Data	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	\\
-    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
-    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
-    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
-    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
-    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
-    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
-    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
-    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
-    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
     \bottomrule
@@
 
-\begin{specialtable}[htbp] 
+\begin{specialtable}[H] 
+    %[htbp] 
     \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
@@
     \midrule
-    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	\\
-    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
-    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
-    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
-    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
-    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
-    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
-    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
-    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
-    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
-    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	\\
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
+    LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
     \bottomrule
@@
 
-\begin{specialtable}[htbp] 
+\begin{specialtable}[H] 
+    %[htbp] 
     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
@@
     \midrule	
-    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	&	Data	\\
-    LFR Inlet Temperature (K)	&	$T_{4C}$	&	Data	&	Data	&	Data	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	&	Data	\\
-    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	&	Data	\\
-    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	&	Data	\\
-    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	&	Data	\\
-    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	&	Data	\\
-    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	&	Data	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	&	Data	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	Data	&	Data	&	Data	\\
-    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	&	Data	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	&	Data	\\
-    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	&	Data	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	&	Data	\\
-    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	&	Data	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	&	Data	\\
-    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	&	Data	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	&	Data	\\
-    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
     \bottomrule
@@
 
-\begin{specialtable}[htbp]
+\begin{specialtable}[H]
+    %[htbp]
     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
@@
     \midrule	
-    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	&	Data	\\
-    LFR Inlet Temperature (K)	&	$T_{5A}$	&	Data	&	Data	&	Data	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	&	Data	\\
-    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	&	Data	\\
-    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	&	Data	\\
-    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	&	Data	\\
-    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	&	Data	\\
-    T1 Power (W)	&	$\dot{W}_{T1}$	&	Data	&	Data	&	Data	\\
-    T2 Power (W)	&	$\dot{W}_{T2}$	&	Data	&	Data	&	Data	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	&	Data	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	Data	&	Data	&	Data	\\
-    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	&	Data	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	&	Data	\\
-    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	&	Data	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	&	Data	\\
-    HTR1 UA Value (W/K)	&	$UA_{HTR1}$	&	Data	&	Data	&	Data	\\
-    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	Data	&	Data	&	Data	\\
-    HTR1 Heat Transfer Rate (W)	&	$\dot{Q}_{HTR1}$	&	Data	&	Data	&	Data	\\
-    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	Data	&	Data	&	Data	\\
-    HTR2 UA Value (W/K)	&	$UA_{HTR2}$	&	Data	&	Data	&	Data	\\
-    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	Data	&	Data	&	Data	\\
-    HTR2 Heat Transfer Rate (W)	&	$\dot{Q}_{HTR2}$	&	Data	&	Data	&	Data	\\
-    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	Data	&	Data	&	Data	\\
-    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
+    T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
+    T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
+    HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
+    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
+    HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
+    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
+    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
+    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
+    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
+    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
     \bottomrule
@@
 
-\begin{specialtable}[htbp]
+\begin{specialtable}[H]
+    %[htbp]
     \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
@@
     \midrule	
-    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	\\
-    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	Data	\\
-    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	\\
-    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	\\
-    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	\\
-    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	\\
-    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	\\
-    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	Data	\\
-    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	\\
-    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	\\
-    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	\\
-    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	\\
-    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	\\
-    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	\\
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
     \bottomrule
@@
 
-\begin{specialtable}[htbp]
+\begin{specialtable}[H]
+    %[htbp]
     \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
@@
     \midrule	
-    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	\\
-    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	&	Data	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	Data	&	Data	\\
-    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
-    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
-    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
-    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
-    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
-    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	Data	&	Data	\\
-    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
-    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
-    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
-    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
-    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	\\
-    CSPHX Approach Temperature (K)	&	$\delta_{CSPHX}$	&	Data	&	Data	\\
-
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
+    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
+    CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
     \bottomrule
@@
 
-\begin{specialtable}[htbp]
+\begin{specialtable}[H]
+    %[htbp]
     \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
@@
     \midrule	
-    Cold TES Temperature (K)	&	$T_{CS}$	&	Data	&	Data	&	Data	\\
-    LFR Inlet Temperature (K)	&	$T_{1C}$	&	Data	&	Data	&	Data	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	Data	&	Data	&	Data	\\
-    Chiller Heat Transfer (W)	&	$\dot{Q}_{chill}$	&	Data	&	Data	&	Data	\\
-    CSPHX UA Value (W/K)	&	$UA_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Heat Transfer Rate (W)	&	$\dot{Q}_{CSPHX}$	&	Data	&	Data	&	Data	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	Data	&	Data	&	Data	\\
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
+    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
     \bottomrule
@@
 
+\end{paracol}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{how to use}
+%\section{how to use}
 
-\subsection{Subsection}
-Citing a journal paper \cite{wagner2017optimization} . Now citing a book reference \cite{blair2005sam} or other reference types \cite{hirsch2011standardization}. \cite{nellis_klein_2008}
-\subsubsection{Subsubsection}
+%\subsection{Subsection}
+%Citing a journal paper \cite{wagner2017optimization} . Now citing a book reference \cite{blair2005sam} or other reference types \cite{hirsch2011standardization}. \cite{nellis_klein_2008}
+%\subsubsection{Subsubsection}
 
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
+%Bulleted lists look like this:
+%\begin{itemize}
+%\item	First bullet;
+%\item	Second bullet;
+%\item	Third bullet.
+%\end{itemize}
 
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
+%Numbered lists can be added as follows:
+%\begin{enumerate}
+%\item	First item; 
+%\item	Second item;
+%\item	Third item.
+%\end{enumerate}
 
-The text continues here.
+%The text continues here.
 
-\subsection{Figures, Tables and Schemes}
+%\subsection{Figures, Tables and Schemes}
 
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
+%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
+%\begin{figure}[H]
+%\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
+%\caption{This is a figure.
 Schemes follow the same formatting.
@@
 A caption on a single line should be centered.\label{fig1}}
-\end{figure}
+%\end{figure}
 
 % The MDPI table float is called specialtable
-\begin{specialtable}[htbp] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
+%\begin{specialtable}[htbp] 
+%\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
 %%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabular}
-\end{specialtable}
+%\begin{tabular}{ccc}
+%\toprule
+%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+%\midrule
+%Entry 1		& Data			& Data\\
+%Entry 2		& Data			& Data\\
+%\bottomrule
+%\end{tabular}
+%\end{specialtable}
 
@@
 
-Text.
+%\subsection{Formatting of Mathematical Components}
 
-Text.
+%This is the example 1 of equation:
+%\begin{equation}
+%a = 1,
+%\end{equation}
 
-\subsection{Formatting of Mathematical Components}
-
-This is the example 1 of equation:
-\begin{equation}
-a = 1,
-\end{equation}
-
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
+%the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
 %% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
@@
 
-This is the example 2 of equation:
-\end{paracol}
-\nointerlineskip
-\begin{eqnarray}
-a &=& b + c + d + e + f + g + h + i + j + k + l\nonumber \\
- &+& m + n + o + p + q + r + s + t + u + v + w + x + y + z %\nonumber
-\end{eqnarray}
+%This is the example 2 of equation:
+%\end{paracol}
+%\nointerlineskip
+%\begin{eqnarray}
+%a &=& b + c + d + e + f + g + h + i + j + k + l\nonumber \\
+% &+& m + n + o + p + q + r + s + t + u + v + w + x + y + z %\nonumber
+%\end{eqnarray}
 
@@
 
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%\begin{paracol}{2}
+%\linenumbers
+%\switchcolumn
+%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
 %% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+%\begin{Theorem}
+%Example text of a theorem.
+%\end{Theorem}
 
-The text continues here. Proofs must be formatted as follows:
+%The text continues here. Proofs must be formatted as follows:
 
 %% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+%\begin{proof}[Proof of Theorem 1]
+%Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
+%\end{proof}
+%The text continues here.
 
-\end{paracol}
+%\end{paracol}
 

### 2021-08-30 simulations/modules/GenericSSCModule.py
new method to generate hash and store dispatch targets
also moving initialize_arrays to NuclearTES (idea is to overload for each specific module) and adding capability to log_SSC_arrays to write dispatch targets to file with same name as the unique hash

@@ -18,6 +18,7 @@ from dispatch.GeneralDispatch import GeneralDispatch as GD
 from dispatch.GeneralDispatch import GeneralDispatchParamWrap as GDP
 from dispatch.GeneralDispatch import GeneralDispatchOutputs as GDO
 from tqdm import tqdm
+import pickle as pickle
 import numpy as np
 import copy
 from abc import ABC, abstractmethod
@@ -40,7 +41,8 @@ class GenericSSCModule(ABC):
     
     @abstractmethod
     def __init__(self, plant_name="abstract", json_name="abstract", 
-                       is_dispatch=False, dispatch_time_step=1):
+                       is_dispatch=False, dispatch_time_step=1,
+                       log_dispatch_targets=False):
         """ Initializes the GenericSSCModules
         
         Args:
@@ -52,6 +54,8 @@ class GenericSSCModule(ABC):
                 boolean, if True runs Pyomo dispatch optimization
             dispatch_time_step (int): 
                 time step for dispatch (hours)
+            log_dispatch_targets (bool): 
+                boolean, if True logs dispatch targets calculated by Pyomo at each segment
             
         """
         
@@ -81,6 +85,9 @@ class GenericSSCModule(ABC):
         
         # save flag for dispatch 
         self.is_dispatch = is_dispatch
+
+        # save flag for logging dispatch targets 
+        self.log_dispatch_targets = log_dispatch_targets
         
         # initialize dispatch-specific parameters and loggers
         if self.is_dispatch:
@@ -95,7 +102,12 @@ class GenericSSCModule(ABC):
             
             # initialize dispatch wrap class
             self.dispatch_wrap = self.create_dispatch_wrapper( self.PySAM_dict )
-
+            
+            if self.log_dispatch_targets:
+                hash_exists, hash_filepath = self.generate_hash()
+                self.hash_exists   = hash_exists
+                self.hash_filepath = hash_filepath
+            
 
     def run_sim(self, run_loop=False, export=False, filename='temp.csv'):
         """ Method to run single simulation for Generic System
@@ -156,6 +168,51 @@ class GenericSSCModule(ABC):
         # saving location of solar resource file for SSC input
         parent_dir = FileMethods.parent_dir
         self.solar_resource_file = os.path.join(parent_dir, input_dict['solar_resource_rel_parent']) #os.path.join
+
+    @abstractmethod
+    def generate_hash(self):
+        """ Method to create unique hash for given JSON inputs
+        
[…]

### 2021-08-30 simulations/modules/NuclearTES.py

@@ -14,9 +14,10 @@ from dispatch.NuclearDispatch import NuclearDispatch as ND
 from dispatch.NuclearDispatch import NuclearDispatchParamWrap as NDP
 from dispatch.NuclearDispatch import NuclearDispatchOutputs as NDO
 from pyomo.opt import SolverStatus, TerminationCondition
+import numpy as np
 import PySAM.PySSC as pssc
 from util.FileMethods import FileMethods
-import copy
+import os, copy, hashlib
 
 class NuclearTES(GenericSSCModule): 
     """
@@ -25,7 +26,8 @@ class NuclearTES(GenericSSCModule):
     
     """
     
-    def __init__(self, plant_name="nuclear_tes", json_name="model1", is_dispatch=False):
+    def __init__(self, plant_name="nuclear_tes", json_name="model1", is_dispatch=False,
+                 log_dispatch_targets=False):
         """ Initializes the NuclearTES module
         
         Args:
@@ -35,11 +37,13 @@ class NuclearTES(GenericSSCModule):
                 name of JSON script with input data for module
             is_dispatch (bool): 
                 boolean, if True runs Pyomo dispatch optimization
+            log_dispatch_targets (bool): 
+                boolean, if True logs dispatch targets calculated by Pyomo at each segment
                 
         """
         
         # initialize Generic module, csv data arrays should be saved here
-        GenericSSCModule.__init__( self, plant_name, json_name, is_dispatch )
+        GenericSSCModule.__init__( self, plant_name, json_name, is_dispatch, log_dispatch_targets=log_dispatch_targets )
         
         # define specific PySAM module to be called later
         self.PySAM_Module = NuclearTes
@@ -79,6 +83,52 @@ class NuclearTES(GenericSSCModule):
         self.fm_array = FileMethods.read_csv_through_pandas(samsim_dir + input_dict['flux_file'])
         
         
+    def generate_hash(self):
+        """ Method to create unique hash for given JSON inputs
+        
+        This method creates a unique, permanent hash for a given JSON script.
+        That is, it gathers all of the JSON inputs (including SSC and PySAM inputs)
+        from the designated script and converts both their keynames and values
+        to strings. It collects all of these into a single string variable and
+        then creates a new hexadecimal string or "hash" for that giant string. 
+        This serves as a unique identifier or "fingerprint" for all the values 
+        in the JSON script. This is then used later on as the file name containing
+        outputs from this particular run. Any small changes to the JSON script 
[…]

### 2021-09-01 simulations/modules/GenericSSCModule.py
more comments and moving hash generation to run_im rather than __init__

@@ -103,11 +103,6 @@ class GenericSSCModule(ABC):
             # initialize dispatch wrap class
             self.dispatch_wrap = self.create_dispatch_wrapper( self.PySAM_dict )
             
-            if self.log_dispatch_targets:
-                hash_exists, hash_filepath = self.generate_hash()
-                self.hash_exists   = hash_exists
-                self.hash_filepath = hash_filepath
-            
 
     def run_sim(self, run_loop=False, export=False, filename='temp.csv'):
         """ Method to run single simulation for Generic System
@@ -193,23 +188,32 @@ class GenericSSCModule(ABC):
                 absolute filepath to the hash file in outputs directory
         """
         
+        # static start of the filename
         filename = "generic__"
+        
+        # initializing empty string
         extstr = ''
         
+        # adding SSC dictionary names and values to the existing string
         sscdict = self.SSC_dict
         for s in sscdict.keys():
             extstr += "{0}: {1} ".format( s, str(sscdict[s]) )
         
+        # adding PySAM dictionary names and values to the existing string
         pysamdict = self.PySAM_dict
         for p in pysamdict.keys():
             extstr += "{0}: {1} ".format( p, str(pysamdict[p]) )
         
+        # creating a unique hash from giant string of values using md5 algorithm
         json_hash = hashlib.md5( extstr.encode('utf-8') ).hexdigest()
         
+        # adding the unique hexadecimal hash to the starting filename string
         filename += json_hash
         
+        # creating full path to output hash file
         filepath = os.path.join( FileMethods.output_dir , filename + '.dispatchTargets')
         
+        # checking if this current hash exists already
         hash_exists = os.path.exists(filepath)
         
         return hash_exists, filepath
@@ -427,6 +431,22 @@ class GenericSSCModule(ABC):
         
         # run dispatch optimization for the first time
         if self.is_dispatch:
+            
+            # option, if we're running dispatch, to log all dispatch targets from each segment
+            if self.log_dispatch_targets:
+                
+                # generate unique hash from all JSON inputs
+                hash_exists, hash_filepath = self.generate_hash()
+                
+                # save results of hash, including a unique filename for given inputs
+                self.hash_exists   = hash_exists
+                self.hash_filepath = hash_filepath # dispatch targets will be saved here
+                
+                # printing out locations
+                if self.hash_exists:
+                    print("\nDispatch Targets already exists in {0}. \nWill skip logging.\n".format(self.hash_filepath)) 
[…]

### 2021-09-01 simulations/modules/NuclearTES.py

@@ -106,24 +106,32 @@ class NuclearTES(GenericSSCModule):
                 absolute filepath to the hash file in outputs directory
         """
         
-    
+        # static start of the filename
         filename = "NuclearTES__"
+        
+        # initializing empty string
         extstr = ''
         
+        # adding SSC dictionary names and values to the existing string
         sscdict = self.SSC_dict
         for s in sscdict.keys():
             extstr += "{0}: {1} ".format( s, str(sscdict[s]) )
         
+        # adding PySAM dictionary names and values to the existing string
         pysamdict = self.PySAM_dict
         for p in pysamdict.keys():
             extstr += "{0}: {1} ".format( p, str(pysamdict[p]) )
         
+        # creating a unique hash from giant string of values using md5 algorithm
         json_hash = hashlib.md5( extstr.encode('utf-8') ).hexdigest()
         
+        # adding the unique hexadecimal hash to the starting filename string
         filename += json_hash
         
+        # creating full path to output hash file
         filepath = os.path.join( FileMethods.output_dir , filename + '.dispatchTargets')
         
+        # checking if this current hash exists already
         hash_exists = os.path.exists(filepath)
         
         return hash_exists, filepath

### 2021-09-01 simulations/modules/GenericSSCModule.py
option to overwrite dispatch targets file if already exists

@@ -104,7 +104,7 @@ class GenericSSCModule(ABC):
             self.dispatch_wrap = self.create_dispatch_wrapper( self.PySAM_dict )
             
 
-    def run_sim(self, run_loop=False, export=False, filename='temp.csv'):
+    def run_sim(self, run_loop=False, export=False, filename='temp.csv', overwrite_dispatch_targets=False):
         """ Method to run single simulation for Generic System
         
         This method handles the creating and execution of Plant, Grid, and Financial objects to
@@ -118,10 +118,13 @@ class GenericSSCModule(ABC):
                 if true, exports results to an Excel sheet
             filename (str): 
                 name for Excel sheet saved to the /outputs directory
+            overwrite_dispatch_targets (bool): 
+                if true, overwrites the current stored dispatch target file
             
         """
         
         self.run_loop = run_loop
+        self.overwrite_dispatch_targets = overwrite_dispatch_targets
         
         #--- create Plant object and execute it
         self.create_Plant( )
@@ -441,10 +444,16 @@ class GenericSSCModule(ABC):
                 # save results of hash, including a unique filename for given inputs
                 self.hash_exists   = hash_exists
                 self.hash_filepath = hash_filepath # dispatch targets will be saved here
-                
+            
                 # printing out locations
                 if self.hash_exists:
-                    print("\nDispatch Targets already exists in {0}. \nWill skip logging.\n".format(self.hash_filepath)) 
+                    # overwrite file if requested
+                    if self.overwrite_dispatch_targets:
+                        self.hash_exists = False
+                        print("\nOverwriting current Dispatch Targets at {0}.".format(self.hash_filepath)) 
+                    # file exists, do nothing
+                    else:
+                        print("\nDispatch Targets already exists in {0}. \nWill skip logging.\n".format(self.hash_filepath)) 
                 else:
                     print("\nDispatch Targets do not exist for this configuration. \n Will write to {0}.\n".format(self.hash_filepath))
             

### 2021-09-01 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Intro additions and large tables

@@
 Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
-Higher efficiencies, in some simple recompression cycles reaching 50\% efficiency, allows for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}.
+High efficiencies, in some simple recompression cycles reaching 50\% efficiency, allow for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}.
 Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.
-Due to the benefits of sCO$_2$ Brayton cycles the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
+Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
+Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}.
 Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each.
@@
 
-Implementation of a combined solar and nuclear plant, modeled in a 2020 study from the School of Energy and Power Engineering in Jilin, China, shows a single recompression cycle layout with and emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility with no demonstration of varied cycle arrangements \cite{wang_2020}.
+Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows.
+Monnerie et al.
+(2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.
+Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}.
+Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper.
+Implementation of a combined solar and nuclear plant, modeled in the Wang et al.
+(2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
+This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative.
+Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a suplementary CSP TES charging technique.
 
@@
 
-Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point.
+Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point and are modeled as a perfect heat transfer into or out of the cycle.
 These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy.
@@
  Where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and $h_{in,c}$ is the inlet of the cold side.
- The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is done with Equation \ref{enthalpy_h}.
+ The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is accomplished with Equation \ref{enthalpy_h}.
 
@@
 Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature.
-Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_max$ is found with the maximum enthalpy.
+Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_{max}$ is found with the maximum enthalpy.
 Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet.

### 2021-09-02 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
BL comments

@@
 Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
-High efficiencies, in some simple recompression cycles reaching 50\% efficiency, allow for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}.
+High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allowing them to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
+\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument}
 Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.
@@
 
+\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton? In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common}
 A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
@@
 With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch.
-A LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 595 $^{\circ}$C.
+An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C.
 LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}.
-Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} .
+Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} \bl{If you are reading this reference https://www.osti.gov/servlets/purl/1108068 I think the loop is in Sandia National Lab and the conference where the paper was published was in Boulder}.
 In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.
 
+\bl{I would bullet out the next three citations}
 Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows.
@@
 Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a suplementary CSP TES charging technique.
+\bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences).
+You could start by saying that it is prior work on the LFR-CSP-sCO2 concept.
+Then describe its cycle configuration with the high temperature salt.
+Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed.
+The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang}
 
@@
 Turbines and compressors are analyzed using isentropic efficiencies.
-Counter-flow heat exchangers use the effectiveness-NTU method while simplified ``black box'' heat exchangers use a simple energy balance for state point calculations.
+Counter-flow heat exchangers are modelled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available.
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
 The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
+\bl{does above make this clearer?}
 
@@
 Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead.
-This lead is used to both cool the core as well as transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}.
+This lead is used to cool the core and transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}.
 The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX.
-The inlet, outlet and heat transfer rates are defined by our industry partner, Westinghouse Electric Company making the black box simplification viable.
+The inlet, outlet and heat transfer rates were provided by Westinghouse, making the black box simplification viable.
 The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.
@@
 The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side.
-Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by our industry partner.
+Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by Westinghouse.
 %\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
@@
 
-\hl{The C2S heat exchanger is active in the 'charging' cycle configurations, when the focus is on heat storage for later use.
+\hl{The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use.
 Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle.
@@
 
-'Non-charging' cycle configurations are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
+'Non-charging' cycle operating modes are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
 When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
@@
 The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.
+
+\bl{I don think the above covers the case where the salt discharges.
+It might be worth eliciting how the operating modes change as power demand increases.
+From highest to lowest demand.
+In all modes CSP will charge the salt is sun is available: (1) LFR and S2C both dispatch, maximum power (2) As power demand decreases, S2C ramps down until no power dispatched through salt (i.e.
+salt is charged) (3) LFR dispatches, no dispatch from S2C (4) LFR ramps down and gradually transfers greater and greater fraction of power to salt using C2S.
+(5) No electricity dispatched, all LFR heat passes through C2S
+}
 
@@
 In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post.
-%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
+%%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
 
@@
 
-%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
+%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
 %\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
@@
 The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
-%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
+%%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
 Asp you will want to explain the criteria that go into cold storage temp.
@@
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
-\bl{this is more about having a compromise option of intermediate complexity and efficiency}
+%\bl{this is more about having a compromise option of intermediate complexity and efficiency}
 
@@
 The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.
-\bl{this is clearer than the previous one but bullets could still be useful}
+%\bl{this is clearer than the previous one but bullets could still be useful}
 
@@
 To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
-%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
+%%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
 
@@
 
-%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
+%%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
 

### 2021-09-08 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Additional changes according to comments, need tables formatted

@@
 High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allowing them to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
-\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument}
+\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
 Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.
@@
 
-\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton? In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common}
+\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton?
+In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common -BW I would say sCO2 Brayton, Brayton uses gaseous fluid with a compressor, turbine, and heat addition.
+I dont think that distiguishing between supercritical fluid vs gasuous is detrimental?
+Correct me if I'm wrong}
 A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
@@
 LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}.
-Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} \bl{If you are reading this reference https://www.osti.gov/servlets/purl/1108068 I think the loop is in Sandia National Lab and the conference where the paper was published was in Boulder}.
+Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Arvada, Colorado, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}.
 In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.
 
-\bl{I would bullet out the next three citations}
-Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows.
-Monnerie et al.
+\bl{I would bullet out the next three citations-BW}
+Various studies on complimentary solar-nuclear systems have been accomplished with several reviewed as follows:
+
+\begin{itemize}
+    \item	Monnerie et al.
+(2011): In search of an alternative to the typical fossil fuel-based process, reports on synthesizing hydrogen with complimentary solar-nuclear technologies being utilized as consistent heat sources for chemical decomposition of sulphuric acid to aid in simple, low-temperature electrolysis \cite{monnerie_2011}.
+    \item   Curtis J.D.
+(2015): Massachusetts Institute of Technology thesis reports cycle configuration, performance, and development of complimentary solar-nuclear systems with a focus on shale oil extraction and production from kerogen deposits \cite{curtis_2015}.
+    \item   Wang et al.
+(2020): Implements a combined solar and nuclear plant discussing a sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
+\end{itemize}
+
+The economic and physical feasibility of producing shale oil and hydrogen with complimentary solar-nuclear cycles, as discussed in the Curtis J.D.
+(2015) thesis and Monnerie et al.
+(2011) article, is not within the scope of sCO$_2$ Brayton recompression cycle electrical generation and storage presented in this paper.
+
+The single cycle configuration in Wang et al.
+(2020) has a higher-temperature operating salt, 67\%KCl-33\%MgCl$_2$, as the heat transfer fluid in the CSP which is capable of temperatures in the range of 450 - 1400 $^{\circ}$C.
+The lower operating point of the studied solar salt in this paper, 60\%NaNO$_3$-40\%KNO$_3$ with a temperature range of 250 - 585 $^{\circ}$C, is employed because the technology is more established when compared to KCl-MgCl$_2$ \cite{turchi_2018}.
+The higher temperature salt requires preheating which is achieved prior to the CSP heat addition by a small modular lead-cooled fast reactor.
+The small modular LFR operates at a low temperature and a fixed location when compared to the higher temperature lead and variable location that the Westinghouse LFR studied in this paper is capable of.
+Due to the similar operating temperatures of the CSP and LFR, multiple cycle configurations are studied that are not possible with the similar components in Wang et al.
+(2020).
+Specifically studied in this paper are the effects on cycle and heat storage efficiency of different cycle configurations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique.
+This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
+Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied with the results discussed.
+
+%Monnerie et al.
 (2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.
@@
 Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper.
-Implementation of a combined solar and nuclear plant, modeled in the Wang et al.
+
+%Implementation of a combined solar and nuclear plant, modeled in the Wang et al.
 (2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
 This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative.
-Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a suplementary CSP TES charging technique.
+Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique.
+%This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
+Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.
 \bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences).
@@
 Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed.
-The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang}
-
-\hl{This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
-Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.}
+The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang - BW}
 
@@
 The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
-\bl{does above make this clearer?}
+\bl{does above make this clearer? -BW}
 
@@
 Counter-flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
-\hl{In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers} \cite{seidel_2010_model_development}.
-%\mw{Justify -BW} 
-The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers \cite{seidel_2010_model_development}.
+The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO$_3$ 40\% KNO$_3$) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
 
@@
 
-\hl{Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$} \cite{klein_nellis_2011,nellis_klein_2008}.
+Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$ \cite{klein_nellis_2011,nellis_klein_2008}.
 
@@
 
-The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid.
+The CSP salt cycle uses 60\% sodium nitrate, NaNO$_3$, and 40\% potassium nitrate, KNO$_3$, 'solar salt' as the heat transfer fluid.
 Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low.
-Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C.
+Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C.
 Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
@@
 
-\hl{The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use.
+The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use.
 Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle.
-Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver then being stored in the hot TES.}
+Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver to be stored in the hot TES.
 %\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }
@@
 When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
-The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
-The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.
-
-\bl{I don think the above covers the case where the salt discharges.
+The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle through CSP HX to be converted into electricity.
+The cooled salt is stored in cold storage and moved through Pump 2 where the heat from the receiver is again transferred into the CSP cycle.
+
+When grid demand for electrical power increases, a series operating modes are activated.
+During the highest demand times, cycle operation focuses on maximum electrical generation.
+This is achieved through the C2S being turned off for direct electrical production from the LFR and the hot TES is discharging heat through the CSP HX for electrical production in the sCO$_2$ Brayton cycle.
+As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.
+During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S.
+This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.
+
+\bl{I dont think the above covers the case where the salt discharges.
 It might be worth eliciting how the operating modes change as power demand increases.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Results and Discussion}
 
@@
 
-\subsubsection{Large Tables}
 \begin{specialtable}[H] 
@@
 
+\subsection{Thermal Energy Storage Charging Techniques}
+
 \begin{specialtable}[H] 
@@
 
-\subsubsection{C-LFR-ON and C-CSP-ON}
+\subsection{Small Tables}
 %--------------------------------------------------------------------------------------
@@
 
-\subsubsection{C-1HTR1T-ON}
 %--------------------------------------------------------------------------------------
@@
 
-\subsubsection{C-2HTR3T-ON}
 %--------------------------------------------------------------------------------------
@@
 
-\subsection{Thermal Energy Storage Charging Techniques}
 %======================================================================================
 
-\subsubsection{C-LFR-PRE}
 %--------------------------------------------------------------------------------------
@@
 
-\subsubsection{C-LFR-POST}
-%--------------------------------------------------------------------------------------
-
-\subsubsection{C-LFR-PAR}
+%--------------------------------------------------------------------------------------
+
 %--------------------------------------------------------------------------------------
@@
 
-\subsubsection{C-LFR-CIRC}
 %--------------------------------------------------------------------------------------

### 2021-09-10 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
changing sources, demonstration

@@
 \bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
-Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.
+Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2013}.
 Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
@@
 A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
-Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2012, turchi_2013, ho_2015, wang_2018}.
+Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}.
 Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases.
@@
 The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang - BW}
-
-%Korea Atomic Energy Research Institute \cite{cha_2016}  
-%interest in brayton \cite{doe_2012}
-%Efficiency 50\% \cite{turchi_2013} \cite{wright_2009}
-%Thermal storage \cite{paul_2010} \cite{sioshansi_2010}
-%sCO2 Brayton nuclear \cite{dostal_2005} \cite{dostal_2004} \cite{luo_2020}
-%sCO2 Brayton solar \cite{turchi_2012} \cite{turchi_2013} \cite{ho_2015} \cite{wang_2018}
-%Cycle Configs \cite{turchi_2012} \cite{wang_2018}
-%Similar Works \cite{wang_2020}
-%Experimental Plants \cite{cha_2016} \cite{wright_2011}
 

### 2021-09-14 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
added results and discussion for charging configurations

@@
 Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
-High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allowing them to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
+High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
 \bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
-Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2013}.
+Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
 Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
@@
 
-\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton?
-In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common -BW I would say sCO2 Brayton, Brayton uses gaseous fluid with a compressor, turbine, and heat addition.
-I dont think that distiguishing between supercritical fluid vs gasuous is detrimental?
-Correct me if I'm wrong}
+\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton? In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common -BW}
 A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
@@
 An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C.
-LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}.
+Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}.
 Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Arvada, Colorado, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}.
@@
 The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
-\bl{does above make this clearer? -BW}
 
@@
 
-All of the prior equations are carried out in a built in function within EES.
+All of the prior equations are carried out in a built-in function within EES.
 EES is an iterative solver, therefore as long as there is a feasible solution, the functions can take any of the four state points around the heat exchanger and converge on a solution.
@@
 The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX.
-The inlet, outlet and heat transfer rates were provided by Westinghouse, making the black box simplification viable.
+The inlet, outlet and heat transfer rates are provided by our industry partner, Westinghouse, making the black box simplification viable.
 The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.
@@
 The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side.
-Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by Westinghouse.
+LFR sCO$_2$ inlet low temperature has a lower bound of $340^{\circ}$C and an optimal value of $400^{\circ}$C, as provided by Westinghouse.
 %\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
-Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.
+Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.
 
@@
 Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C.
-Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
+Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 560$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
 The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
@@
 The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle.
-While the hot TES is charging the receiver and LFR are storing heat for later use when grid demand increases.
+While the hot TES is charging, the receiver and LFR are storing heat for later use when grid demand increases.
 The hot TES storage is not dispensing salt for use in the CSP cycle while charging.
@@
 Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle.
-Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver to be stored in the hot TES.
+Additionally, while the focus is on heat storage, and the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot TES.
 %\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }
 
-'Non-charging' cycle operating modes are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
+'Non-charging' cycle operating modes are characterized by operations wherein the CSP salt cycle is discharging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
 When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
-The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle through CSP HX to be converted into electricity.
+The hot TES solar salt is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle through CSP HX to be converted into electricity.
 The cooled salt is stored in cold storage and moved through Pump 2 where the heat from the receiver is again transferred into the CSP cycle.
 
-When grid demand for electrical power increases, a series operating modes are activated.
+When grid demand for electrical power increases, a series of operating modes are activated.
 During the highest demand times, cycle operation focuses on maximum electrical generation.
@@
 salt is charged) (3) LFR dispatches, no dispatch from S2C (4) LFR ramps down and gradually transfers greater and greater fraction of power to salt using C2S.
-(5) No electricity dispatched, all LFR heat passes through C2S
+(5) No electricity dispatched, all LFR heat passes through C2S -BW
 }
@@
     Turbine & $\eta_{T}$		& 0.90 (-)\\
-    Pump & $\eta_{P}$      & 0.90 (-)\\
+    Pumps 1-3 & $\eta_{P}$      & 0.90 (-)\\
     \midrule
@@
 
-In addition to generalized parameters, all cycles have identical recompression sides.
+In addition to standardized parameters, all cycles have identical recompression sides.
 The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor.
@@
     C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
-    C-2HTR3T-ON & Separate CSP and LFR loops each with dedicated HTR and turbine.\\
+    C-2HTR3T-ON & CSP and LFR loops each with dedicated HTR and turbine.\\
     \midrule
@@
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
-The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR1.
+The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, \hl{HTR1}.
 %\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
@@
     \widefigure
-    \includegraphics[width=10 cm]{Definitions/c-lfr-circ-sub.pdf}
+    \includegraphics[width=8 cm]{Definitions/c-lfr-circ-sub.pdf}
     \caption{Diagram for C-LFR-CIRC sub-cycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
@@
 
+For all cycle configurations presented, with constrained or unconstrained LFR low temperature inlet and varied cold TES temperature, cycle and heat storage efficiencies were maximized using parametric studies on flow splitter fractions.
+These results were obtained using standardized values found in Table \ref{tab-cycle_sum} for a more direct comparison between cycles.
+Presentation and discussion of the results is fulfilled in the following section.
+
 \subsection{Non-Charging Cycle Configurations}
@@
 
+The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.
+
+\end{paracol}
 \begin{specialtable}[H] 
@@
     \caption{Calculated system parameters for non-charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-noncharg}}
+    \resizebox{\columnwidth}{!}{
     \begin{tabular}{lccccccccccc}
@@
     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	395.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	395.2	&	400	&	400	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
@@
     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	&	0.6996	&	0.6994	&	0.7	&	0.6333	&	0.6333	&	0.6993	&	0.7846	&	0.7846	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	5.48E-01	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\
     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	&	45.4	&	45.53	&	102	&	91.63	&	91.64	&	134.4	&	41.56	&	41.57	\\
@@
     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	&	0.9201	&	0.9202	&	0.92	&	0.9485	&	0.9485	&	0.9414	&	0.8741	&	0.8741	\\
-    HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.29	&	42.71	&	34.58	&	34.72	&	78.22	&	82.3	&	82.34	&	48.32	&	42.69	&	42.69	\\
-    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8657	&	0.9627	&	0.8593	&	0.8594	&	0.8595	&	0.8754	&	0.8755	&	0.8661	&	0.8142	&	0.8142	\\
-    HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	998.1	&	1161	&	665.4	&	667.7	&	679.2	&	742.6	&	743	&	545.7	&	636.8	&	636.6	\\
-    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	&	34.58	&	34.72	&	78.22	&	82.3	&	82.34	&	48.32	&	42.69	&	42.69	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.8143	&	0.8593	&	0.8594	&	0.8595	&	0.8754	&	0.8755	&	0.8661	&	0.8142	&	0.8142	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	&	665.4	&	667.7	&	679.2	&	742.6	&	743	&	545.7	&	636.8	&	636.6	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
     HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	34.29	&	31.61	&	31.63	\\
@@
     HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.9436	&	0.9561	&	0.9561	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	75.19	&	70.88	&	44.92	&	23.13	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	N/A	&	N/A	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
@@
     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	N/A	&	N/A	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\
+
     \bottomrule
-    \end{tabular}\\
+    \end{tabular}
+    }
 \end{specialtable}
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency.
+Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
+
+\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON}
+
+The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually.
+C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%.
+The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
+According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger.
+Additionally, Westinghouse concluded that a lower sCO$_2$, down to 340$^{\circ}$C, is desirable for LFR heat generation efficiency.
+The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, reducing LFR heat generation efficiency and demanding a larger, more idealized, LFR heat exchanger.
+\hl{would I need more information on the LFR from westinghouse (ie report) to make these statements?
+additionally a conclusion to these statements needs more supporting detail, should I go with the higher efficiency or the cycle that I know works with design values?}
+
+C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature during non-charging configuration because the two cycles are not tethered.
+Two individual studies were conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
+A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate between the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
+Cold TES temperature was found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%.
+The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
+
+\subsubsection{C-1HTR1T-ON}
+The single cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions.
+Identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C.
+A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency.
+Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C had no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
+Increasing the solar salt mass flow rate requires more storage for the same heat input and larger pumps increasing the cost of the system.
+Therefore, a lower cold TES temperature is desirable.
+Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to 390$^{\circ}$C.
+Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, 390$^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases.
+The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components.
+The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher LFR efficiency.
+
+\subsubsection{C-2HTR3T-ON}
+C-2HTR3T-ON has dedicated recuperators and turbines for the LFR and CSP, allowing for independent inlet temperatures.
+Three studies were conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions.
+The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences.
+Similarly to the studies done on C-1HTR1T-ON, the cold TES temperature had an effect on mass flow rate of solar salt with the 440$^{\circ}$C case having a larger value and therefore higher component cost.
+The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, a 1.76\% increase over the constrained cases.
+Additionally, the sCO$_2$ LFR inlet temperature increased by a value of 15.2$^{\circ}$C to 415.2$^{\circ}$C, having a negative effect on LFR efficiency and heat exchanger parameters.
+
+\hl{again how do I justify the heat exchanger and LFR efficiency gains? I do not have any sources other than what westinghouse has supplied over email and in general meetings}
 
@@
 
+When the focus of the cycles is thermal storage for later use, the LFR charges the hot TES through the C2S heat exchanger.
+Studies done on the charging techniques, C-LFR-PRE, C-LFR-PAR, and C-LFR-CIRC, have constrained sCO$_2$ LFR inlet temperatures to 400$^{\circ}$C with set values of cold TES temperature of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C.
+The results are presented in Table \ref{tab-charg}.
+
+\end{paracol}
 \begin{specialtable}[H] 
@@
     \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
+    \resizebox{\columnwidth}{!}{
     \begin{tabular}{lccccccc}
@@
     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	119	&	N/A	&	N/A	&	N/A	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
     RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
@@
     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
@@
     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
@@
     \bottomrule
-    \end{tabular}\\
+    \end{tabular}
+    }
 \end{specialtable}
-
-\subsection{Small Tables}
-%--------------------------------------------------------------------------------------
-
-Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
-
-\begin{specialtable}[H] 
-    %[htbp]
-    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
-    \begin{tabular}{lccc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
-    \midrule
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
-
-\textbf{Discussion of Results}
-
-The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
-
-\begin{specialtable}[H] 
-    %[htbp] 
-    \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
-    \begin{tabular}{lccc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} &  &\\
-    \midrule
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
-    LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
-
-\textbf{Discussion of Results}
-
-%--------------------------------------------------------------------------------------
-
-These values are displayed in Table \ref{tab-c-1htr1t-on}.
-
-\begin{specialtable}[H] 
-    %[htbp] 
-    \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+\subsubsection{C-LFR-PRE}
+
+\subsubsection{C-LFR-PAR}
+
+\subsubsection{C-LFR-CIRC}
+
+% \subsection{Small Tables}
+% %--------------------------------------------------------------------------------------
+
+% Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
+
+% \begin{specialtable}[H] 
+%     %[htbp]
+%     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
+%     \begin{tabular}{lccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
+%     \midrule
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
+
+% \begin{specialtable}[H] 
+%     %[htbp] 
+%     \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
+%     \begin{tabular}{lccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} &  &\\
+%     \midrule
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
+%     LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %--------------------------------------------------------------------------------------
+
+% These values are displayed in Table \ref{tab-c-1htr1t-on}.
+
+% \begin{specialtable}[H] 
+%     %[htbp] 
+%     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
 Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
-    \begin{tabular}{lcccc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
-    & & \textit{U} & \textit{C} & \textit{C}\\
-    \midrule	
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
-
-\textbf{Discussion of Results}
-
-%--------------------------------------------------------------------------------------
-
-The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
-
-\begin{specialtable}[H]
-    %[htbp]
-    \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
-    \begin{tabular}{lcccc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
-    & & \textit{U} & \textit{C} & \textit{C}\\
-    \midrule	
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
-    T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
-    T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
-    HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
-    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
-    HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
-    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
-    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
-    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
-    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
-    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
-
-\textbf{Discussion of Results}
-
-%======================================================================================
-
-%--------------------------------------------------------------------------------------
-
-The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
-
-\begin{specialtable}[H]
-    %[htbp]
-    \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
-    \begin{tabular}{lcc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
-    & & \textit{C}\\
-    \midrule	
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
-    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
-
-\textbf{Discussion of Results}
-
-%--------------------------------------------------------------------------------------
-
-%--------------------------------------------------------------------------------------
-
-The results from this study are displayed in Table \ref{tab-c-lfr-par}.
-
-\begin{specialtable}[H]
-    %[htbp]
-    \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
-    \begin{tabular}{lccc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
-    & & \textit{C} & \textit{C}\\
-    \midrule	
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
-    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
-    CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
-
-Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
+%     \begin{tabular}{lcccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
+%     & & \textit{U} & \textit{C} & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
+%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %--------------------------------------------------------------------------------------
+
+% The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
+%     \begin{tabular}{lcccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
+%     & & \textit{U} & \textit{C} & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
+%     T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
+%     T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
+%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
+%     HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
+%     HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
+%     HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
+%     HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
+%     HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
+%     HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
+%     HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
+%     HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %======================================================================================
+
+% %--------------------------------------------------------------------------------------
+
+% The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
+%     \begin{tabular}{lcc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
+%     & & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
+%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
+%     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %--------------------------------------------------------------------------------------
+
+% %--------------------------------------------------------------------------------------
+
+% The results from this study are displayed in Table \ref{tab-c-lfr-par}.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
+%     \begin{tabular}{lccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
+%     & & \textit{C} & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
+%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
+%     SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
+%     CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
 The CSP salt mass flow rate and approach temperature of the SALT HX would adjust according to the temperature difference in the TES and keep the efficiency constant.
 
-%--------------------------------------------------------------------------------------
-
-Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
-
-\begin{specialtable}[H]
-    %[htbp]
-    \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
-    \begin{tabular}{lcccc}
-    \toprule
-    \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
-    \midrule	
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
-    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
-    \bottomrule
-    \end{tabular}\\
-\end{specialtable}
+% %--------------------------------------------------------------------------------------
+
+% Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
+%     \begin{tabular}{lcccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
+%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
+%     Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+% \section{Discussion}
+
+% Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
 The findings and their implications should be discussed in the broadest context possible.

### 2021-09-15 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
comment on LFR power density/temperature constraint

@@
 %\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
+\bl{In an LFR, the outlet temperature is limited by materials considerations.
+The flow velocity is limited by erosion of the fuel (if the lead gets too fast, it erodes the fuel).
+We want the core to be compact.
+Therefore the mass flow is limited.
+This means that a lower inlet temperature gives a higher power (subject to constraints on fuel temperautre, which is also a function of power density).
+There is a limit of about 340C, below which the lead might freeze (which is operationally unacceptable), but until that value, lower inlet = higher core power.
+However, from thermodynamics, higher inlet = higher efficiency.
+There is a trade-off between driving the core harder and getting better cycle performance.
+The trade-off gives 400C as a temperature that doesnt overly compromise core power while still providing reasonable efficiency.
+Raising this temperature higher would drop the core power below the 950 MW}
 Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.

### 2021-09-15 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Some additional edits

--- 2021-09-14 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
-Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency.
+Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
 Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
@@
 According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger.
-Additionally, Westinghouse concluded that a lower sCO$_2$, down to 340$^{\circ}$C, is desirable for LFR heat generation efficiency.
+Additionally, Westinghouse concluded that a lower sCO$_2$ LFR inlet temperature, down to 340$^{\circ}$C, is desirable for LFR heat generation efficiency.
 The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, reducing LFR heat generation efficiency and demanding a larger, more idealized, LFR heat exchanger.
@@
 
-C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature during non-charging configuration because the two cycles are not tethered.
+C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration.
 Two individual studies were conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
-A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate between the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
+A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
 Cold TES temperature was found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%.
@@
 The single cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions.
-Identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C.
+Due to the 10$^{\circ}$C approach temperature, the identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C.
 A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency.
 Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C had no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
-Increasing the solar salt mass flow rate requires more storage for the same heat input and larger pumps increasing the cost of the system.
+Increasing the solar salt mass flow rate requires more storage for the same CSP heat input, a reduction in dispatchability, and larger pumps, increasing the cost of the system.
 Therefore, a lower cold TES temperature is desirable.
@@
 The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences.
-Similarly to the studies done on C-1HTR1T-ON, the cold TES temperature had an effect on mass flow rate of solar salt with the 440$^{\circ}$C case having a larger value and therefore higher component cost.
-The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, a 1.76\% increase over the constrained cases.
-Additionally, the sCO$_2$ LFR inlet temperature increased by a value of 15.2$^{\circ}$C to 415.2$^{\circ}$C, having a negative effect on LFR efficiency and heat exchanger parameters.
-
-\hl{again how do I justify the heat exchanger and LFR efficiency gains? I do not have any sources other than what westinghouse has supplied over email and in general meetings}
+Similarly to the studies done on C-1HTR1T-ON, the 440$^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost.
+The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases.
+Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing LFR efficiency and heat exchanger parameters to be less than ideal.
+
+\hl{should I include in table 3 important mass flow rates like solar salt mass flow and total mass flow in sCO2?}
 
@@
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 

### 2021-09-17 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
added TES charging techniques

@@
     \textit{Charging}\\
-    C-LFR-PRE & Turbine is prior to the SALT HX.\\
-    C-LFR-POST & Turbine is after the SALT HX.\\
-    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
-    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
+    C-LFR-PRE & Turbine is prior to the C2S.\\
+    C-LFR-POST & Turbine is after the C2S.\\
+    C-LFR-PAR & Turbine is parallel to the C2S.\\
+    C-LFR-CIRC & Circulator bridges the LFR and C2S.\\
     \bottomrule
@@
 Charging cycle configurations accommodate energy storage modes of operation.
-These configurations examine the location of LFR heat extraction via the SALT HX.
-To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring that the turbine power is equal to the compressors' demand.
+These configurations examine the location of LFR heat extraction via C2S.
+To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring the turbine power to balance with the compressors' demand.
 Despite the components being non-ideal and consuming power, the recompression cycle continues to operate, ensuring that there is mass flow to transfer heat from the Brayton cycle to C2S.
 The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases.
-The location of heat extraction in the cycle is compared within the C-LFR-ON Brayton cycle by placing the salt heat exchanger in different locations around the turbine.
+Comparison of the heat extraction point in the cycle, C2S, is accomplished by implementing C2S in different locations around the turbine in the C-LFR-ON non-charging cycle configuration; C-LFR-PRE has the turbine prior to C2S, C-LFR-POST has the turbine after C2S, C-LFR-PAR has the turbine in parallel to C2S, and C-LFR-CIRC uses a circulating loop instead of in-flow implementation.
+C-LFR-ON is the configuration used for these studies because during charging operation, flow through the CSP HX is deactivated, effectively making all non-charging cycles take the identical form of C-LFR-ON.
 To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
@@
 there is assumed to be negligible pressure drop in this case).
-A heat exchanger, SALT HX, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
+A heat exchanger, C2S, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
 Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of $400^{\circ}$C.
@@
     \midrule
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
-    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	&	339.1	&	340.6	&	763.9	&	752.3	&	752.6	&	783.7	&	753.7	&	754	\\
@@
     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	N/A	&	N/A	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\
-
     \bottomrule
@@
 The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
-According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger.
-Additionally, Westinghouse concluded that a lower sCO$_2$ LFR inlet temperature, down to 340$^{\circ}$C, is desirable for LFR heat generation efficiency.
-The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, reducing LFR heat generation efficiency and demanding a larger, more idealized, LFR heat exchanger.
+According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger, but does increase the LFR efficiency.
+Additionally, Westinghouse concluded that a lower sCO$_2$ LFR inlet temperature, down to 340$^{\circ}$C, is desirable for higher core power.
+The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
 \hl{would I need more information on the LFR from westinghouse (ie report) to make these statements?
@@
 The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components.
-The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher LFR efficiency.
+The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher core power.
 
@@
 The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases.
-Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing LFR efficiency and heat exchanger parameters to be less than ideal.
+Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR efficiency.
 
@@
     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
-    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
+    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
@@
     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
-    CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	N/A	&	35	&	26.27	&	N/A	&	N/A	&	N/A	\\
+    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
+    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
+    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
+    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
+    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
     \bottomrule
@@
 \subsubsection{C-LFR-PRE}
+The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
+The hot TES is at a temperature of 560$^{\circ}C$, with a 10$^{\circ}C$ approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}C$.
+In cases where the turbine outlet temperature is less than 570$^{\circ}C$, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
+For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}C$.
+With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
+As the temperature of the hot TES is raised above a value of 540$^{\circ}$, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
+The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$ to allow for operation of this cycle.
+With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
+This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.
 
@@
 
+To test the effects of splitting flow prior to the turbine, a parallel configuration C-LFR-PAR is studied.
+To reduce the pressure from 28.8 MPa to 8.8 MPa, an isenthalpic valve is required after heat is extracted through C2S.
+
 \subsubsection{C-LFR-CIRC}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+
+% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+
+\end{paracol}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-\end{paracol}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\section{how to use}
@@
 %\end{paracol}
-
-%Completed suggestions from Ben:
-
-%-I would include the naming scheme upfront and give a table (C-LFR-ON etc.)
-
-%-Here you need to explain what a conventional CSP cycle looks like (briefly).
-I.e.
-CSP charges salt, it can discharge when you want it to.
-Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
-
-%-Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX
-
-%-SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage
-
-%Completed suggestions from Mike:

### 2021-09-17 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
finished the Results and Discussion section

@@
 Specifically studied in this paper are the effects on cycle and heat storage efficiency of different cycle configurations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique.
-This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
+This paper provides an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
 Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied with the results discussed.
@@
 Specific heat is found using library correlations.
-Once both average capacitances are calculated for the hot and cold streams, the one will have a larger value, $\dot{C}_{max}$, and one will have a smaller value,  $\dot{C}_{min}$.
-These maximum and minimum values are then used to find the capacitance ratio, $CR$, in Equation \ref{cap_ratio}.
+Once both average capacitances are calculated for the hot and cold streams, one has a larger value, $\dot{C}_{max}$, and one has a smaller value,  $\dot{C}_{min}$.
+These maximum and minimum values are used to find the capacitance ratio, $CR$, in Equation \ref{cap_ratio}.
 
@@
 The initial two studies have the low LFR temperature constrained to the value of $400^{\circ}$C with varied cold CSP TES temperature and maximized cycle efficiency.
-To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, was parametrically studied.
+To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, is parametrically studied.
 %\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
@@
 
-For all cycle configurations presented, with constrained or unconstrained LFR low temperature inlet and varied cold TES temperature, cycle and heat storage efficiencies were maximized using parametric studies on flow splitter fractions.
-These results were obtained using standardized values found in Table \ref{tab-cycle_sum} for a more direct comparison between cycles.
+For all cycle configurations presented, with constrained or unconstrained LFR low temperature inlet and varied cold TES temperature, cycle and heat storage efficiencies are maximized using parametric studies on flow splitter fractions.
+These results are obtained using standardized values found in Table \ref{tab-cycle_sum} for a more direct comparison between cycles.
 Presentation and discussion of the results is fulfilled in the following section.
@@
 C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration.
-Two individual studies were conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
-A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
-Cold TES temperature was found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%.
+Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
+A cold TES temperature of 410$^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
+Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%.
 The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
@@
 A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency.
-Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C had no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
+Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C has no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
 Increasing the solar salt mass flow rate requires more storage for the same CSP heat input, a reduction in dispatchability, and larger pumps, increasing the cost of the system.
@@
 C-2HTR3T-ON has dedicated recuperators and turbines for the LFR and CSP, allowing for independent inlet temperatures.
-Three studies were conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions.
+Three studies are conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions.
 The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences.
@@
 The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
-The hot TES is at a temperature of 560$^{\circ}C$, with a 10$^{\circ}C$ approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}C$.
-In cases where the turbine outlet temperature is less than 570$^{\circ}C$, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
-For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}C$.
+The hot TES is at a temperature of 560$^{\circ}$C, with a 10$^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}$C.
+In cases where the turbine outlet temperature is less than 570$^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
+For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}$C.
 With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
-As the temperature of the hot TES is raised above a value of 540$^{\circ}$, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
-The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$ to allow for operation of this cycle.
+As the temperature of the hot TES is raised above a value of 540$^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
+The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$C to allow for operation of this cycle.
 With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
@@
 To test the effects of splitting flow prior to the turbine, a parallel configuration C-LFR-PAR is studied.
-To reduce the pressure from 28.8 MPa to 8.8 MPa, an isenthalpic valve is required after heat is extracted through C2S.
+To reduce the pressure from 28.8 MPa to 8.8 MPa, an isenthalpic valve is required after heat is extracted for storage through C2S.
+With this configuration two different values for cold TES are studied, one with a cold TES storage of 390$^{\circ}$C the other with a temperature of 440$^{\circ}$C.
+A noteworthy difference for this cycle is the C2S approach temperature is not set to 10$^{\circ}$C.
+Defining the approach temperature as 10$^{\circ}$C causes the energy balance governing combiner 2 to be over constrained.
+Therefore this value is free and calculated to be 35$^{\circ}$C for the 390$^{\circ}$C case and 26.27$^{\circ}$C for the 440$^{\circ}$C case.
+Both of these different temperature cold TES studies do not change the cycle parameters because, as seen in C-1HTR1T-ON and C-2HTR3T-ON, the solar salt mass flow rate adjusts to accommodate for the temperature difference.
+The higher cold TES temperature of 440$^{\circ}$C causes the mass flow rate in the CSP to increase by approximately 650 kg/s.
+Increasing the mass flow rate has a higher demand on system components but in this situation it allows for the salt to be charged at a higher rate, increasing the storage capabilities.
+Both cycles have a heat storage efficiency of 45.30\%.
+\hl{Should I include solar salt mass flow also in table 4?}
 
 \subsubsection{C-LFR-CIRC}
+
+C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from losses associated with turbines, compressors, and heat exchangers.
+This is due to the fact that a separate recirculation cycle is modeled taking heat directly from the LFR, passing it through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, 400$^{\circ}$C.
+This is the most adoptable TES charging technique a wide range of possible TES charging temperatures with almost all of the heat from the LFR being transferred into the hot TES depending on the temperature.
+Multiple temperatures for the cold TES are studied; 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
+Of these three temperatures, the highest efficiency is a cold TES temperature of 390$^{\circ}$ with a heat storage efficiency of 99.92\%.
+The heat storage efficiency reduces as the temperature of the cold TES is increased, the 410$^{\circ}$C case has an efficiency of 89.66\% while the 440$^{\circ}$C case has an efficiency of 74.29\%.
+This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore the more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
+A drawback of this TES charging technique is the additional components needed for the circulation loop, with an additional chiller and circulator component, adding cost.
 

### 2021-09-21 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
BL commits on results & discussion

@@
 %\bl{this is more about having a compromise option of intermediate complexity and efficiency}
+\bl{also why this isnt really an addition turbine, it is using the turbines that power the compressors}
 
@@
 The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
-According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger, but does increase the LFR efficiency.
-Additionally, Westinghouse concluded that a lower sCO$_2$ LFR inlet temperature, down to 340$^{\circ}$C, is desirable for higher core power.
-The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
-\hl{would I need more information on the LFR from westinghouse (ie report) to make these statements?
-additionally a conclusion to these statements needs more supporting detail, should I go with the higher efficiency or the cycle that I know works with design values?}
+Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficency perspective, but reduces the LFR thermal power.
+This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power.
+In principle, dropping the LFR inlet temperature further, to as low as 340^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
+When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
+\bl{text revised}
 
 C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration.
-Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
+\bl{Provided that the charging configuration is suitably configured} Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
 A cold TES temperature of 410$^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
@@
 The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
+\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination}
 
@@
 Due to the 10$^{\circ}$C approach temperature, the identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C.
-A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency.
+A supplementary 440$^{\circ}$C cold TES study is run to test the effects that higher temperature storage has on cycle efficiency.
 Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C has no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
@@
 
-C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from losses associated with turbines, compressors, and heat exchangers.
+C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from significant losses associated with turbines, compressors, and heat exchangers.
 This is due to the fact that a separate recirculation cycle is modeled taking heat directly from the LFR, passing it through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, 400$^{\circ}$C.
@@
 Multiple temperatures for the cold TES are studied; 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
-Of these three temperatures, the highest efficiency is a cold TES temperature of 390$^{\circ}$ with a heat storage efficiency of 99.92\%.
-The heat storage efficiency reduces as the temperature of the cold TES is increased, the 410$^{\circ}$C case has an efficiency of 89.66\% while the 440$^{\circ}$C case has an efficiency of 74.29\%.
+Of these three temperatures, the highest efficiency is a cold TES temperature of 390$^{\circ}$ with a heat storage efficiency of 100\%.
+The heat storage efficiency reduces as the temperature of the cold TES is increased, the 410$^{\circ}$C case has an efficiency of 90\% while the 440$^{\circ}$C case has an efficiency of 74\%.
 This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore the more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
 A drawback of this TES charging technique is the additional components needed for the circulation loop, with an additional chiller and circulator component, adding cost.
+\bl{need to comment on how this interacts with the choice of cycle configuration.
+If the LFR temperature is 400C and cold TES is 390C then CSP inlet must be 380C and this requires 2HTR3T or separate cycles.
+If 1HTR1T is used, then 410C+ is needed which implies an efficiency penalty}
 

### 2021-09-24 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

--- 2021-09-17 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
-High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
-\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
-Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
+High efficiencies, in some simple recompression cycles reaching 50\% efficiency, allow for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}.
+Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.
 Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
@@
 
-\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton? In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common -BW}
 A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
-Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}.
+Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2012, turchi_2013, ho_2015, wang_2018}.
 Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases.
 With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch.
-An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C.
-Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}.
-Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Arvada, Colorado, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}.
+A LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 595 $^{\circ}$C.
+LFR powered sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{dostal_2005, dostal_2004, luo_2020}.
+Physical testing of simple sCO$_2$ Brayton cycles is researched at the Boulder, Colorado with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011} .
 In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.
 
-\bl{I would bullet out the next three citations-BW}
-Various studies on complimentary solar-nuclear systems have been accomplished with several reviewed as follows:
-
-\begin{itemize}
-    \item	Monnerie et al.
-(2011): In search of an alternative to the typical fossil fuel-based process, reports on synthesizing hydrogen with complimentary solar-nuclear technologies being utilized as consistent heat sources for chemical decomposition of sulphuric acid to aid in simple, low-temperature electrolysis \cite{monnerie_2011}.
-    \item   Curtis J.D.
-(2015): Massachusetts Institute of Technology thesis reports cycle configuration, performance, and development of complimentary solar-nuclear systems with a focus on shale oil extraction and production from kerogen deposits \cite{curtis_2015}.
-    \item   Wang et al.
-(2020): Implements a combined solar and nuclear plant discussing a sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
-\end{itemize}
-
-The economic and physical feasibility of producing shale oil and hydrogen with complimentary solar-nuclear cycles, as discussed in the Curtis J.D.
-(2015) thesis and Monnerie et al.
-(2011) article, is not within the scope of sCO$_2$ Brayton recompression cycle electrical generation and storage presented in this paper.
-
-The single cycle configuration in Wang et al.
-(2020) has a higher-temperature operating salt, 67\%KCl-33\%MgCl$_2$, as the heat transfer fluid in the CSP which is capable of temperatures in the range of 450 - 1400 $^{\circ}$C.
-The lower operating point of the studied solar salt in this paper, 60\%NaNO$_3$-40\%KNO$_3$ with a temperature range of 250 - 585 $^{\circ}$C, is employed because the technology is more established when compared to KCl-MgCl$_2$ \cite{turchi_2018}.
-The higher temperature salt requires preheating which is achieved prior to the CSP heat addition by a small modular lead-cooled fast reactor.
-The small modular LFR operates at a low temperature and a fixed location when compared to the higher temperature lead and variable location that the Westinghouse LFR studied in this paper is capable of.
-Due to the similar operating temperatures of the CSP and LFR, multiple cycle configurations are studied that are not possible with the similar components in Wang et al.
-(2020).
-Specifically studied in this paper are the effects on cycle and heat storage efficiency of different cycle configurations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique.
-This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
-Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied with the results discussed.
-
-%Monnerie et al.
-(2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.
-Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}.
+Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows.
+Monnerie et al., at the German Aerospace Centre - DLR, in search of an alternative to the typical fossil fuel-based process, report on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.
+Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology, Department of Nuclear and Science and Engineering, where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}.
 Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper.
-
-%Implementation of a combined solar and nuclear plant, modeled in the Wang et al.
-(2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
-This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative.
-Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique.
-%This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
-Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.
-\bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences).
-You could start by saying that it is prior work on the LFR-CSP-sCO2 concept.
-Then describe its cycle configuration with the high temperature salt.
-Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed.
-The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang - BW}
+Implementation of a combined solar and nuclear plant, modeled in the Wang et al.
+2020 study from the School of Energy and Power Engineering in Jilin, China, shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
+A single cycle configuration with no comparison of the effects on efficiency of varied heat addition or storage extraction locations is studied in the 2020 article, which is a main focus of the presented sCO$_2$ Brayton models in this paper.
+
+%similar works \cite{chen_2016}
+
+\hl{This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
+Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.}
+
+%Korea Atomic Energy Research Institute \cite{cha_2016}  
+%interest in brayton \cite{doe_2012}
+%Efficiency 50\% \cite{turchi_2013} \cite{wright_2009}
+%Thermal storage \cite{paul_2010} \cite{sioshansi_2010}
+%sCO2 Brayton nuclear \cite{dostal_2005} \cite{dostal_2004} \cite{luo_2020}
+%sCO2 Brayton solar \cite{turchi_2012} \cite{turchi_2013} \cite{ho_2015} \cite{wang_2018}
+%Cycle Configs \cite{turchi_2012} \cite{wang_2018}
+%Similar Works \cite{wang_2020}
+%Experimental Plants \cite{cha_2016} \cite{wright_2011}
 
@@
 Turbines and compressors are analyzed using isentropic efficiencies.
-Counter-flow heat exchangers are modelled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available.
+Counter-flow heat exchangers use the effectiveness-NTU method while simplified ``black box'' heat exchangers use a simple energy balance for state point calculations.
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
@@
 
-Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point and are modeled as a perfect heat transfer into or out of the cycle.
+Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point.
 These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy.
@@
 Counter-flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
-In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers \cite{seidel_2010_model_development}.
-The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO$_3$ 40\% KNO$_3$) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+\hl{In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers} \cite{seidel_2010_model_development}.
+%\mw{Justify -BW} 
+The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
 
@@
  Where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and $h_{in,c}$ is the inlet of the cold side.
- The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is accomplished with Equation \ref{enthalpy_h}.
+ The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is done with Equation \ref{enthalpy_h}.
 
@@
 Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature.
-Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_{max}$ is found with the maximum enthalpy.
+Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_max$ is found with the maximum enthalpy.
 Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet.
@@
 
-All of the prior equations are carried out in a built-in function within EES.
+All of the prior equations are carried out in a built in function within EES.
 EES is an iterative solver, therefore as long as there is a feasible solution, the functions can take any of the four state points around the heat exchanger and converge on a solution.
@@
 
-Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$ \cite{klein_nellis_2011,nellis_klein_2008}.
+\hl{Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$} \cite{klein_nellis_2011,nellis_klein_2008}.
 
@@
 Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead.
-This lead is used to cool the core and transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}.
+This lead is used to both cool the core as well as transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}.
 The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX.
-The inlet, outlet and heat transfer rates are provided by our industry partner, Westinghouse, making the black box simplification viable.
+The inlet, outlet and heat transfer rates are defined by our industry partner, Westinghouse Electric Company making the black box simplification viable.
 The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.
@@
 The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side.
-LFR sCO$_2$ inlet low temperature has a lower bound of $340^{\circ}$C and an optimal value of $400^{\circ}$C, as provided by Westinghouse.
+Low sCO$_2$ LFR inlet temperature has a lower limit of $340^{\circ}$C and an optimal value of $400^{\circ}$C as provided by our industry partner.
 %\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
-\bl{In an LFR, the outlet temperature is limited by materials considerations.
-The flow velocity is limited by erosion of the fuel (if the lead gets too fast, it erodes the fuel).
-We want the core to be compact.
-Therefore the mass flow is limited.
-This means that a lower inlet temperature gives a higher power (subject to constraints on fuel temperautre, which is also a function of power density).
-There is a limit of about 340C, below which the lead might freeze (which is operationally unacceptable), but until that value, lower inlet = higher core power.
-However, from thermodynamics, higher inlet = higher efficiency.
-There is a trade-off between driving the core harder and getting better cycle performance.
-The trade-off gives 400C as a temperature that doesnt overly compromise core power while still providing reasonable efficiency.
-Raising this temperature higher would drop the core power below the 950 MW}
-Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.
+Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.
 
@@
 
-The CSP salt cycle uses 60\% sodium nitrate, NaNO$_3$, and 40\% potassium nitrate, KNO$_3$, 'solar salt' as the heat transfer fluid.
+The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid.
 Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low.
-Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C.
-Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 560$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
+Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C.
+Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
 The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
@@
 The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle.
-While the hot TES is charging, the receiver and LFR are storing heat for later use when grid demand increases.
+While the hot TES is charging the receiver and LFR are storing heat for later use when grid demand increases.
 The hot TES storage is not dispensing salt for use in the CSP cycle while charging.
 
-The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use.
+\hl{The C2S heat exchanger is active in the 'charging' cycle configurations, when the focus is on heat storage for later use.
 Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle.
-Additionally, while the focus is on heat storage, and the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot TES.
+Additionally, while the focus is on heat storage and the receiver is producing heat, pump 2 is active transporting solar salt through the receiver then being stored in the hot TES.}
 %\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }
 
-'Non-charging' cycle operating modes are characterized by operations wherein the CSP salt cycle is discharging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
+'Non-charging' cycle configurations are characterized by operations wherein the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
 When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
-The hot TES solar salt is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle through CSP HX to be converted into electricity.
-The cooled salt is stored in cold storage and moved through Pump 2 where the heat from the receiver is again transferred into the CSP cycle.
-
-When grid demand for electrical power increases, a series of operating modes are activated.
-During the highest demand times, cycle operation focuses on maximum electrical generation.
-This is achieved through the C2S being turned off for direct electrical production from the LFR and the hot TES is discharging heat through the CSP HX for electrical production in the sCO$_2$ Brayton cycle.
-As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.
-During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S.
-This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.
-
-\bl{I dont think the above covers the case where the salt discharges.
-It might be worth eliciting how the operating modes change as power demand increases.
-From highest to lowest demand.
-In all modes CSP will charge the salt is sun is available: (1) LFR and S2C both dispatch, maximum power (2) As power demand decreases, S2C ramps down until no power dispatched through salt (i.e.
-salt is charged) (3) LFR dispatches, no dispatch from S2C (4) LFR ramps down and gradually transfers greater and greater fraction of power to salt using C2S.
-(5) No electricity dispatched, all LFR heat passes through C2S -BW
-}
+The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity.
+The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.
 
@@
     Turbine & $\eta_{T}$		& 0.90 (-)\\
-    Pumps 1-3 & $\eta_{P}$      & 0.90 (-)\\
+    Pump & $\eta_{P}$      & 0.90 (-)\\
     \midrule
@@
 
-In addition to standardized parameters, all cycles have identical recompression sides.
+In addition to generalized parameters, all cycles have identical recompression sides.
 The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor.
@@
     C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
-    C-2HTR3T-ON & CSP and LFR loops each with dedicated HTR and turbine.\\
+    C-2HTR3T-ON & Separate CSP and LFR loops each with dedicated HTR and turbine.\\
     \midrule
     \textit{Charging}\\
-    C-LFR-PRE & Turbine is prior to the C2S.\\
-    C-LFR-POST & Turbine is after the C2S.\\
-    C-LFR-PAR & Turbine is parallel to the C2S.\\
-    C-LFR-CIRC & Circulator bridges the LFR and C2S.\\
+    C-LFR-PRE & Turbine is prior to the SALT HX.\\
+    C-LFR-POST & Turbine is after the SALT HX.\\
+    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
+    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
     \bottomrule
@@
 In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post.
-%%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
+%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
 
@@
 
-%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
+%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
 %\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
@@
 The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
-%%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
+%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
 Asp you will want to explain the criteria that go into cold storage temp.
@@
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
-The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, \hl{HTR1}.
+The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR1.
 %\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
@@
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
-%\bl{this is more about having a compromise option of intermediate complexity and efficiency}
+\bl{this is more about having a compromise option of intermediate complexity and efficiency}
 
@@
 The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.
-%\bl{this is clearer than the previous one but bullets could still be useful}
+\bl{this is clearer than the previous one but bullets could still be useful}
 
@@
 Charging cycle configurations accommodate energy storage modes of operation.
-These configurations examine the location of LFR heat extraction via C2S.
-To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring the turbine power to balance with the compressors' demand.
+These configurations examine the location of LFR heat extraction via the SALT HX.
+To maximize the available heat for extraction, alternator net power is set to zero, therefore requiring that the turbine power is equal to the compressors' demand.
 Despite the components being non-ideal and consuming power, the recompression cycle continues to operate, ensuring that there is mass flow to transfer heat from the Brayton cycle to C2S.
 The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases.
-Comparison of the heat extraction point in the cycle, C2S, is accomplished by implementing C2S in different locations around the turbine in the C-LFR-ON non-charging cycle configuration; C-LFR-PRE has the turbine prior to C2S, C-LFR-POST has the turbine after C2S, C-LFR-PAR has the turbine in parallel to C2S, and C-LFR-CIRC uses a circulating loop instead of in-flow implementation.
-C-LFR-ON is the configuration used for these studies because during charging operation, flow through the CSP HX is deactivated, effectively making all non-charging cycles take the identical form of C-LFR-ON.
+The location of heat extraction in the cycle is compared within the C-LFR-ON Brayton cycle by placing the salt heat exchanger in different locations around the turbine.
 To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
-%%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
+%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
 
@@
 
-%%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
+%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
 
@@
     \widefigure
-    \includegraphics[width=8 cm]{Definitions/c-lfr-circ-sub.pdf}
+    \includegraphics[width=10 cm]{Definitions/c-lfr-circ-sub.pdf}
     \caption{Diagram for C-LFR-CIRC sub-cycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
@@
 there is assumed to be negligible pressure drop in this case).
-A heat exchanger, C2S, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
+A heat exchanger, SALT HX, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
 Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of $400^{\circ}$C.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and Discussion}
-
-For all cycle configurations presented, with constrained or unconstrained LFR low temperature inlet and varied cold TES temperature, cycle and heat storage efficiencies were maximized using parametric studies on flow splitter fractions.
-These results were obtained using standardized values found in Table \ref{tab-cycle_sum} for a more direct comparison between cycles.
-Presentation and discussion of the results is fulfilled in the following section.
+\section{Results}
 
@@
 
-The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.
-
-\end{paracol}
+\subsubsection{Large Tables}
 \begin{specialtable}[H] 
@@
     \caption{Calculated system parameters for non-charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-noncharg}}
-    \resizebox{\columnwidth}{!}{
     \begin{tabular}{lccccccccccc}
@@
     \midrule
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	395.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	395.2	&	400	&	400	\\
     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	&	339.1	&	340.6	&	763.9	&	752.3	&	752.6	&	783.7	&	753.7	&	754	\\
@@
     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	&	0.6996	&	0.6994	&	0.7	&	0.6333	&	0.6333	&	0.6993	&	0.7846	&	0.7846	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	5.48E-01	\\
     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	&	45.4	&	45.53	&	102	&	91.63	&	91.64	&	134.4	&	41.56	&	41.57	\\
@@
     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	&	0.9201	&	0.9202	&	0.92	&	0.9485	&	0.9485	&	0.9414	&	0.8741	&	0.8741	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	&	34.58	&	34.72	&	78.22	&	82.3	&	82.34	&	48.32	&	42.69	&	42.69	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.8143	&	0.8593	&	0.8594	&	0.8595	&	0.8754	&	0.8755	&	0.8661	&	0.8142	&	0.8142	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	&	665.4	&	667.7	&	679.2	&	742.6	&	743	&	545.7	&	636.8	&	636.6	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
+    HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.29	&	42.71	&	34.58	&	34.72	&	78.22	&	82.3	&	82.34	&	48.32	&	42.69	&	42.69	\\
+    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8657	&	0.9627	&	0.8593	&	0.8594	&	0.8595	&	0.8754	&	0.8755	&	0.8661	&	0.8142	&	0.8142	\\
+    HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	998.1	&	1161	&	665.4	&	667.7	&	679.2	&	742.6	&	743	&	545.7	&	636.8	&	636.6	\\
+    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
     HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	34.29	&	31.61	&	31.63	\\
@@
     HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.9436	&	0.9561	&	0.9561	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	75.19	&	70.88	&	44.92	&	23.13	\\
     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	N/A	&	N/A	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
@@
     \bottomrule
-    \end{tabular}
-    }
+    \end{tabular}\\
 \end{specialtable}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
-Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
-Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
-Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
-
-\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON}
-
-The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually.
-C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%.
-The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
-According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger, but does increase the LFR efficiency.
-Additionally, Westinghouse concluded that a lower sCO$_2$ LFR inlet temperature, down to 340$^{\circ}$C, is desirable for higher core power.
-The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
-\hl{would I need more information on the LFR from westinghouse (ie report) to make these statements?
-additionally a conclusion to these statements needs more supporting detail, should I go with the higher efficiency or the cycle that I know works with design values?}
-
-C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration.
-Two individual studies were conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
-A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
-Cold TES temperature was found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%.
-The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
-
-\subsubsection{C-1HTR1T-ON}
-The single cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions.
-Due to the 10$^{\circ}$C approach temperature, the identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C.
-A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency.
-Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C had no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
-Increasing the solar salt mass flow rate requires more storage for the same CSP heat input, a reduction in dispatchability, and larger pumps, increasing the cost of the system.
-Therefore, a lower cold TES temperature is desirable.
-Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to 390$^{\circ}$C.
-Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, 390$^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases.
-The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components.
-The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher core power.
-
-\subsubsection{C-2HTR3T-ON}
-C-2HTR3T-ON has dedicated recuperators and turbines for the LFR and CSP, allowing for independent inlet temperatures.
-Three studies were conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions.
-The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences.
-Similarly to the studies done on C-1HTR1T-ON, the 440$^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost.
-The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases.
-Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR efficiency.
-
-\hl{should I include in table 3 important mass flow rates like solar salt mass flow and total mass flow in sCO2?}
-
-\subsection{Thermal Energy Storage Charging Techniques}
-
-When the focus of the cycles is thermal storage for later use, the LFR charges the hot TES through the C2S heat exchanger.
-Studies done on the charging techniques, C-LFR-PRE, C-LFR-PAR, and C-LFR-CIRC, have constrained sCO$_2$ LFR inlet temperatures to 400$^{\circ}$C with set values of cold TES temperature of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C.
-The results are presented in Table \ref{tab-charg}.
-
-\end{paracol}
+
 \begin{specialtable}[H] 
@@
     \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
-    \resizebox{\columnwidth}{!}{
     \begin{tabular}{lccccccc}
@@
     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	119	&	N/A	&	N/A	&	N/A	\\
     RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
@@
     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
-    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
+    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
@@
     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
-    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
-    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
-    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
-    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
-    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
+    CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	N/A	&	35	&	26.27	&	N/A	&	N/A	&	N/A	\\
     \bottomrule
-    \end{tabular}
-    }
+    \end{tabular}\\
 \end{specialtable}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
+
+\subsubsection{C-LFR-ON and C-CSP-ON}
+%--------------------------------------------------------------------------------------
+
+Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
+
+\begin{specialtable}[H] 
+    %[htbp]
+    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
+    \begin{tabular}{lccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
+    \midrule
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
+The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
+
+\begin{specialtable}[H] 
+    %[htbp] 
+    \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
+    \begin{tabular}{lccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} &  &\\
+    \midrule
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
+    LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
+\subsubsection{C-1HTR1T-ON}
+%--------------------------------------------------------------------------------------
+
+These values are displayed in Table \ref{tab-c-1htr1t-on}.
+
+\begin{specialtable}[H] 
+    %[htbp] 
+    \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
+Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
+    & & \textit{U} & \textit{C} & \textit{C}\\
+    \midrule	
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
+\subsubsection{C-2HTR3T-ON}
+%--------------------------------------------------------------------------------------
+
+The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
+
+\begin{specialtable}[H]
+    %[htbp]
+    \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
+    & & \textit{U} & \textit{C} & \textit{C}\\
+    \midrule	
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
+    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
+    T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
+    T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
+    HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
+    HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
+    HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
+    HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
+    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
+    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
+    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
+    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
+\subsection{Thermal Energy Storage Charging Techniques}
+%======================================================================================
 
 \subsubsection{C-LFR-PRE}
-The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
-The hot TES is at a temperature of 560$^{\circ}C$, with a 10$^{\circ}C$ approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}C$.
-In cases where the turbine outlet temperature is less than 570$^{\circ}C$, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
-For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}C$.
-With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
-As the temperature of the hot TES is raised above a value of 540$^{\circ}$, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
-The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$ to allow for operation of this cycle.
-With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
-This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.
+%--------------------------------------------------------------------------------------
+
+The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
+
+\begin{specialtable}[H]
+    %[htbp]
+    \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
+    \begin{tabular}{lcc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
+    & & \textit{C}\\
+    \midrule	
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+\textbf{Discussion of Results}
+
+\subsubsection{C-LFR-POST}
+%--------------------------------------------------------------------------------------
 
 \subsubsection{C-LFR-PAR}
-
-To test the effects of splitting flow prior to the turbine, a parallel configuration C-LFR-PAR is studied.
-To reduce the pressure from 28.8 MPa to 8.8 MPa, an isenthalpic valve is required after heat is extracted through C2S.
+%--------------------------------------------------------------------------------------
+
+The results from this study are displayed in Table \ref{tab-c-lfr-par}.
+
+\begin{specialtable}[H]
+    %[htbp]
+    \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
+    \begin{tabular}{lccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
+    & & \textit{C} & \textit{C}\\
+    \midrule	
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
+    SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
+    CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
+The CSP salt mass flow rate and approach temperature of the SALT HX would adjust according to the temperature difference in the TES and keep the efficiency constant.
 
 \subsubsection{C-LFR-CIRC}
+%--------------------------------------------------------------------------------------
+
+Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
+
+\begin{specialtable}[H]
+    %[htbp]
+    \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
+    \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
+    \midrule	
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
+    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
+    \bottomrule
+    \end{tabular}\\
+\end{specialtable}
+
+%This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+
+Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
 
@@
 
-% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 
 \end{paracol}
-
-% \subsection{Small Tables}
-% %--------------------------------------------------------------------------------------
-
-% Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
-
-% \begin{specialtable}[H] 
-%     %[htbp]
-%     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
-%     \begin{tabular}{lccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
-%     \midrule
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
-
-% \begin{specialtable}[H] 
-%     %[htbp] 
-%     \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
-%     \begin{tabular}{lccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} &  &\\
-%     \midrule
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
-%     LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %--------------------------------------------------------------------------------------
-
-% These values are displayed in Table \ref{tab-c-1htr1t-on}.
-
-% \begin{specialtable}[H] 
-%     %[htbp] 
-%     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
-Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
-%     \begin{tabular}{lcccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
-%     & & \textit{U} & \textit{C} & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
-%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %--------------------------------------------------------------------------------------
-
-% The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
-%     \begin{tabular}{lcccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
-%     & & \textit{U} & \textit{C} & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
-%     T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
-%     T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
-%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
-%     HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
-%     HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
-%     HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
-%     HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
-%     HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
-%     HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
-%     HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
-%     HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %======================================================================================
-
-% %--------------------------------------------------------------------------------------
-
-% The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
-%     \begin{tabular}{lcc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
-%     & & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
-%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
-%     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %--------------------------------------------------------------------------------------
-
-% %--------------------------------------------------------------------------------------
-
-% The results from this study are displayed in Table \ref{tab-c-lfr-par}.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
-%     \begin{tabular}{lccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
-%     & & \textit{C} & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
-%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
-%     SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
-%     CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
-The CSP salt mass flow rate and approach temperature of the SALT HX would adjust according to the temperature difference in the TES and keep the efficiency constant.
-
-% %--------------------------------------------------------------------------------------
-
-% Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
-%     \begin{tabular}{lcccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
-%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
-%     Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-%This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Discussion}
-
-% Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
 
@@
 %\end{paracol}
+
+%Completed suggestions from Ben:
+
+%-I would include the naming scheme upfront and give a table (C-LFR-ON etc.)
+
+%-Here you need to explain what a conventional CSP cycle looks like (briefly).
+I.e.
+CSP charges salt, it can discharge when you want it to.
+Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
+
+%-Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX
+
+%-SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage
+
+%Completed suggestions from Mike:

### 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
formatting changes

--- 2021-09-21 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 %%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
-%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
-I think it's a problem with the MDPI template.
-The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
-\end{paracol}
-
-\begin{figure}[H] 
-    \widefigure
-    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
-    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
-\end{figure}
-
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
 
@@
 
+%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
+I think it's a problem with the MDPI template.
+The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
+\end{paracol}
+
+\begin{figure}[H] 
+    \widefigure
+    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
+    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
+\end{figure}
+
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
 \subsubsection{C-2HTR3T-ON} 
@@
 
+The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
+Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
+\clearpage 
+\mw{Check that the column breakdown and grouping is correct in what I've changed.}
 \end{paracol}
@@
     %[htbp]
+
     \caption{Calculated system parameters for non-charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-noncharg}}
     \resizebox{\columnwidth}{!}{
-    \begin{tabular}{lccccccccccc}
+    \begin{tabular}{lc|cc|cc|ccc|ccc}
     \toprule
-     &  & \textbf{C-LFR-ON} & & \textbf{C-CSP-ON} &  &	\textbf{C-1HTR1T-ON} &	&	&	\textbf{C-2HTR3T-ON}	&	& \\
+     &  & \multicolumn{2}{c}{\textbf{C-LFR-ON}} & \multicolumn{2}{|c}{\textbf{C-CSP-ON}}  &	\multicolumn{3}{|c}{\textbf{C-1HTR1T-ON}}	&	\multicolumn{3}{|c}{\textbf{C-2HTR3T-ON}} \\
     \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C} & \textit{N/A} & \textit{N/A} &	\textit{U}	&	\textit{C}	&	\textit{C}	&	\textit{U}	&	\textit{C}	&	\textit{C}
@@
     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	$\cdot$	&	$\cdot$	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	$\cdot$	&	$\cdot$	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	&	339.1	&	340.6	&	763.9	&	752.3	&	752.6	&	783.7	&	753.7	&	754	\\
@@
     T1 Power (MW)	&	$\dot{W}_{T1}$	&	678.9	&	626.4	&	532.1	&	534.5	&	1196	&	1233	&	1233	&	679.3	&	626.3	&	626.3	\\
-    T2 Power (MW)	&	$\dot{W}_{T2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	527.8	&	485	&	485.4	\\
+    T2 Power (MW)	&	$\dot{W}_{T2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	527.8	&	485	&	485.4	\\
     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	&	0.6996	&	0.6994	&	0.7	&	0.6333	&	0.6333	&	0.6993	&	0.7846	&	0.7846	\\
-    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\
+    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\
     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	&	45.4	&	45.53	&	102	&	91.63	&	91.64	&	134.4	&	41.56	&	41.57	\\
@@
     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
-    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	34.29	&	31.61	&	31.63	\\
-    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.8594	&	0.8074	&	0.8074	\\
-    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	298.1	&	363.4	&	363.8	\\
-    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.9436	&	0.9561	&	0.9561	\\
-    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
-    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	N/A	&	N/A	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
-    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	N/A	&	N/A	&	757.6	&	760.8	&	751.3	&	751.5	&	751.9	&	751.3	&	751.3	&	751.9	\\
-    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	N/A	&	N/A	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\
+    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	34.29	&	31.61	&	31.63	\\
+    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.8594	&	0.8074	&	0.8074	\\
+    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	298.1	&	363.4	&	363.8	\\
+    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.9436	&	0.9561	&	0.9561	\\
+    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
+    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
+    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	757.6	&	760.8	&	751.3	&	751.5	&	751.9	&	751.3	&	751.3	&	751.9	\\
+    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\
     \bottomrule
@@
 
-The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
-Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
-Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
-Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
-
 \subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON}
@@
 This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power.
-In principle, dropping the LFR inlet temperature further, to as low as 340^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
+In principle, dropping the LFR inlet temperature further, to as low as 340$^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
 When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
@@
 
-\end{paracol}
-\begin{specialtable}[H] 
-    %[htbp]
-    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
-    \resizebox{\columnwidth}{!}{
-    \begin{tabular}{lccccccc}
-    \toprule
-     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
-    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
-    \midrule
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
-    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
-    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
-    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
-    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
-    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
-    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
-    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
-    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
-    \bottomrule
-    \end{tabular}
-    }
-\end{specialtable}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
 \subsubsection{C-LFR-PRE}
@@
 This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.
+
+% \end{paracol}
+
+\begin{specialtable}[H]  
+    %[htbp]
+    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
+    \resizebox{\columnwidth}{!}{
+    \begin{tabular}{lc|c|cc|ccc}
+    \toprule
+     &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
+    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
+    \midrule
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
+    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
+    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
+    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
+    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
+    \bottomrule
+    \end{tabular}
+    }
+\end{specialtable}
+% \begin{paracol}{2}
+% \linenumbers
+% \switchcolumn
 

### 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Draft of paper, finishing conclusion and further edits

--- 2021-09-21 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 
-%\mw{If mass is conserved, use a single $\dot{m}$ - BW}
+\mw{If mass is conserved, use a single $\dot{m}$ - BW}
 
@@
 The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C.
-%\mw{Make sure numbers are in math mode -BW}
-The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side.
-LFR sCO$_2$ inlet low temperature has a lower bound of $340^{\circ}$C and an optimal value of $400^{\circ}$C, as provided by Westinghouse.
-%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
+The outlet temperature of the LFR is specified because of high temperature material limits on the LFR lead side.
+The low temperature side is allowed to vary over a range of values with some considerations.
+The lead flow velocity is limited by the erosion of the fuel, the slower the lead flow velocity reduces fuel erosion and therefore leads to a more desirable compact design.
+Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.
+LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
+When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in LFR efficiency but a reduction in LFR power below $950$ MW.
+There is a compromise between high LFR efficiency and LFR power, therefore a temperature of $400^{\circ}$C for the sCO$_2$ inlet temperature is the optimal value provided by Westinghouse.
+
+\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
 \bl{In an LFR, the outlet temperature is limited by materials considerations.
@@
 The trade-off gives 400C as a temperature that doesnt overly compromise core power while still providing reasonable efficiency.
-Raising this temperature higher would drop the core power below the 950 MW}
-Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.
+Raising this temperature higher would drop the core power below the 950 MW -BW}
 
@@
 \mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations.
-It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.}
+It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.-BW}
 %\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
@@
 Two temperatures are tested, $390^{\circ}$C and $440^{\circ}$C, to observe the impact of cold TES temperature on cycle efficiency.
+Efficiencies need to be combined to draw a comparison of the two-cycle configurations to the single cycle configurations; C-1HTR1T-ON and C-2HTR3T-ON.
+Equation \ref{eq-eta-2cycle} is used to calculate this combined two-cycle efficiency.
+
+ \begin{equation}
+    \label{eq-eta-2cycle}
+    \eta_{combined} = \frac{\dot{W}_{A,C\text{-}LFR\text{-}ON}+\dot{W}_{A,C\text{-}CSP\text{-}ON}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
+\end{equation}
+
+Equation \ref{eq-eta-2cycle} is the ratio of total alternator power of C-LFR-ON, $\dot{W}_{A,C\text{-}LFR\text{-}ON}$, and C-CSP-ON, $\dot{W}_{A,C\text{-}CSP\text{-}ON}$, to the total heat input into the cycles from the LFR and CSP heat exchangers, $\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}$.
 
@@
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
-The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, \hl{HTR1}.
+The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR.
 %\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
@@
 To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
-%%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
+\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
 
@@
 In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
-%\mw{not a full sentence -BW}
+\mw{not a full sentence -BW}
 
@@
 
-Flow leaving the turbine contains excess thermal energy that is not transformed into electrical energy.
-This excess thermal energy is stored in the hot CSP TES.
+The high temperature sCO$_2$ leaving the LFR HX flows through the LFR turbine converting thermal energy to usable work.
+The outlet temperature of the LFR turbine is at a temperature suitable to charge the hot TES, therefore the flow is passed through C2S exchanging heat to the cold solar salt.
 The diagram outlining this process is C-LFR-PRE in Fig.
 \ref{c-lfr-pre}.
-
 \mw{Careful here.
@@
 Any fluid above absolute zero technically has excess thermal energy if the reference is zero.
-Depending on this definition, not all excess energy from the turbine is stored in TES.}
-\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations.}
+Depending on this definition, not all excess energy from the turbine is stored in TES.
+-BW}
+\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations. -BW}
 
@@
 
-Problems arise with this salt charging configuration.
-The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $595^{\circ}$C.
+A problem arises with this salt charging configuration.
+The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $560^{\circ}$C when the turbine power is balanced with the compressor demand.
 To raise the temperature, some of the high temperature flow before the turbine is redirected through a valve and combined after the turbine.
-Combining different temperature flows and reducing the flow through the turbine has a large impact on heat storage efficiency.
+Limiting the flow through the turbine reduces the turbine power and compressor power because of the balancing requirement.
+Due to the reduction in available compressor power, the LFR RC is effectively bypassed, and a large portion of usable heat is expelled in the LFR PC before the LFR MC.
+The thermal storage efficiency reduces as a result of the large amount of heat rejected in the LFR PC.
 
@@
 
-Two sensitivity studies \mw{this is one study with two parameter values, right?} with varying cold CSP TES temperature are carried out to determine the impact on heat storage efficiency.
+A sensitivity study \mw{this is one study with two parameter values, right?
+-BW} with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency.
 The study considers two temperature values of $390^{\circ}$C and $440^{\circ}$C.
@@
 The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
-Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficency perspective, but reduces the LFR thermal power.
+Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficiency perspective, but reduces the LFR thermal power.
 This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power.
-In principle, dropping the LFR inlet temperature further, to as low as 340^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
+In principle, dropping the LFR inlet temperature further, to as low as 340$^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
 When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
-\bl{text revised}
-
-C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration.
-\bl{Provided that the charging configuration is suitably configured} Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
+
+C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because C2S is turned off and therefore the two cycles are not tethered during non-charging configuration.
+Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
 A cold TES temperature of 410$^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
@@
 The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
-\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination}
+
+Combining the two-cycle efficiencies using Equation \ref{eq-eta-2cycle} gives a more direct comparison to the single cycle configurations; C-1HTR1T and C-2HTR3T.
+Two combined efficiencies are calculated for the two-cycle configuration combination.
+The first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low temperature and C-CSP-ON 440$^{\circ}$C cold TES cases.
+This combined efficiency yields a value of 46.05\%.
+The second combined configuration has a lower efficiency with favorable LFR characteristics and solar salt mass flow rate.
+This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON 390$^{\circ}$C cold TES cases with a combined efficiency of 45.05\%.
+\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination-BW}
 
@@
 Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR efficiency.
-
-\hl{should I include in table 3 important mass flow rates like solar salt mass flow and total mass flow in sCO2?}
 
@@
 Both cycles have a heat storage efficiency of 45.30\%.
-\hl{Should I include solar salt mass flow also in table 4?}
 
@@
 C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from significant losses associated with turbines, compressors, and heat exchangers.
-This is due to the fact that a separate recirculation cycle is modeled taking heat directly from the LFR, passing it through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, 400$^{\circ}$C.
-This is the most adoptable TES charging technique a wide range of possible TES charging temperatures with almost all of the heat from the LFR being transferred into the hot TES depending on the temperature.
+The separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high temperature mass flow through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally 400$^{\circ}$C.
+This is the most adoptable TES charging technique with a wide range of possible TES charging temperatures while transferring a majority of the heat from the LFR into the hot TES.
 Multiple temperatures for the cold TES are studied; 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
 Of these three temperatures, the highest efficiency is a cold TES temperature of 390$^{\circ}$ with a heat storage efficiency of 100\%.
-The heat storage efficiency reduces as the temperature of the cold TES is increased, the 410$^{\circ}$C case has an efficiency of 90\% while the 440$^{\circ}$C case has an efficiency of 74\%.
-This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore the more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
+The heat storage efficiency reduces as the temperature of the cold TES is increased; the 410$^{\circ}$C case has an efficiency of 90\% while the 440$^{\circ}$C case has an efficiency of 74\%.
+This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
+The non-charging cycle configuration that this charging cycle is implemented in requires further consideration.
+For C-LFR-CIRC, the highest efficiencies are achieved when the cold TES temperature is 10$^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger.
+If the desired temperature of cold TES is 390$^{\circ}$C, the non-charging cycle configurations with sCO$_2$ LFR inlet temperatures of 400$^{\circ}$C are required for highest efficiency.
 A drawback of this TES charging technique is the additional components needed for the circulation loop, with an additional chiller and circulator component, adding cost.
@@
 If the LFR temperature is 400C and cold TES is 390C then CSP inlet must be 380C and this requires 2HTR3T or separate cycles.
-If 1HTR1T is used, then 410C+ is needed which implies an efficiency penalty}
+If 1HTR1T is used, then 410C+ is needed which implies an efficiency penalty -BW}
 
@@
 
+This paper analyzed contending sCO$_2$ Brayton cycle configurations for complimentary CSP and LFR cycles with non-charging cycle configurations focusing on electrical generation.
+An additional operating mode, hot TES charging, is considered where the CSP hot TES is charged when grid demand is low.
+This operating mode positions the heat extraction point at different locations around the turbine in a sCO$_2$ Brayton recompression cycle.
+The performance parameters that are used for comparison of the cycles are cycle efficiency when the cycle is producing electricity and heat storage efficiency when the focus is on energy storage for later use in the charging mode.
+These efficiencies are maximized using flow splitter values at different values of cold TES temperature and constrained or unconstrained sCO$_2$ inlet LFR temperature.
+The conclusions drawn in this paper are as follows:
+
+\begin{itemize}
+    \item	x
+    \item	x
+    \item   x
+\end{itemize}
+
+The cycle configurations with the listed conclusions can be used as reference for future cycle design and proof of concept considerations.
+Further studies and cycle analysis must be done before these cycles are used for implementation into a physical plant.
+
 % This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
@@
 \end{paracol}
-
-% \subsection{Small Tables}
-% %--------------------------------------------------------------------------------------
-
-% Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
-
-% \begin{specialtable}[H] 
-%     %[htbp]
-%     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
-%     \begin{tabular}{lccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
-%     \midrule
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
-
-% \begin{specialtable}[H] 
-%     %[htbp] 
-%     \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
-%     \begin{tabular}{lccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} &  &\\
-%     \midrule
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
-%     LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %--------------------------------------------------------------------------------------
-
-% These values are displayed in Table \ref{tab-c-1htr1t-on}.
-
-% \begin{specialtable}[H] 
-%     %[htbp] 
-%     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
-Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
-%     \begin{tabular}{lcccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
-%     & & \textit{U} & \textit{C} & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
-%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %--------------------------------------------------------------------------------------
-
-% The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
-%     \begin{tabular}{lcccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
-%     & & \textit{U} & \textit{C} & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
-%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
-%     T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
-%     T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
-%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
-%     HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
-%     HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
-%     HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
-%     HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
-%     HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
-%     HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
-%     HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
-%     HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %======================================================================================
-
-% %--------------------------------------------------------------------------------------
-
-% The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
-%     \begin{tabular}{lcc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
-%     & & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
-%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
-%     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% \textbf{Discussion of Results}
-
-% %--------------------------------------------------------------------------------------
-
-% %--------------------------------------------------------------------------------------
-
-% The results from this study are displayed in Table \ref{tab-c-lfr-par}.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
-%     \begin{tabular}{lccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
-%     & & \textit{C} & \textit{C}\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
-%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
-%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
-%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
-%     MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
-%     RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
-%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
-%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
-%     SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
-%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
-%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
-%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
-%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
-%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
-%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
-%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
-%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
-%     CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-% Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
-The CSP salt mass flow rate and approach temperature of the SALT HX would adjust according to the temperature difference in the TES and keep the efficiency constant.
-
-% %--------------------------------------------------------------------------------------
-
-% Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
-
-% \begin{specialtable}[H]
-%     %[htbp]
-%     \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
-%     \begin{tabular}{lcccc}
-%     \toprule
-%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
-%     \midrule	
-%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
-%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
-%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
-%     Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
-%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
-%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
-%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
-%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
-%     \bottomrule
-%     \end{tabular}\\
-% \end{specialtable}
-
-%This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Discussion}
-
-% Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
 

### 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
conclusion and edits

@@
 
-The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.
+\hl{The values for the three non-charging cycle models with a focus on producing positive alternator power (provide electrical power to the grid), 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON,} are displayed in Table \ref{tab-noncharg}.
 

### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Finished conclusion, finalized comments, updated abstract

--- 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 \bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
-Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
+Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
 Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
@@
 
-%Monnerie et al.
-(2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.
-Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}.
-Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper.
-
-%Implementation of a combined solar and nuclear plant, modeled in the Wang et al.
-(2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.
-This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative.
-Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique.
-%This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle.
-Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.
 \bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences).
@@
 % **************************************
-
-%MW: I've fixed spelling in a few places. You can install a spell checker to highlight misspelled words. I use the "Code spell checker" extension.
 
@@
 
-%Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.\mw{this is kind of an awkward way to describe what's happening.
-I think most readers are familiar with isentropic efficiencies and this can be omitted.}
+\mw{this is kind of an awkward way to describe what's happening. I think most readers are familiar with isentropic efficiencies and this can be omitted.-BW}
 
@@
 
-%\mw{This is for a single flow stream.
+\mw{This is for a single flow stream.
 Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream?
@@
     \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
-    \caption{Simple counter-flow heat exchanger diagram. \label{counter-flow-hx}}
+    \caption{Simplified counter-flow heat exchanger diagram. \label{counter-flow-hx}}
 \end{figure}
@@
 
-%\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}
+\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}
 
@@
 Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C.
-Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 560$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
-The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
+Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to $720^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at $560^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
+The cold TES temperature takes on three different values according to cycle configuration capabilities: $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C.
 In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}.
@@
 Additionally, while the focus is on heat storage, and the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot TES.
-%\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }
+\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP?-BW}
 
@@
 %======================================================================================
-%\mw{What do you mean by ``generalized?''-BW}
+\mw{What do you mean by ``generalized?''-BW}
 
@@
     %[htbp]
-    %\mw{Also changing the specialtable position to allow latex to better place tables.-BW}
     \caption{Standardized constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
@@
     Main Compressor Inlet & $T_{1A}$ & 40 ($^{\circ}$C)\\
-    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
     Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 595 ($^{\circ}$C)\\
@@
 It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.-BW}
-%\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
-
-Modeled cycles are summarized in Table \ref{tab-cycle_sum}.
+\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
+The modeled cycles are summarized in Table \ref{tab-cycle_sum}.
 
@@
 The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}. 
-%\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.}
+\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.-BW}
 
@@
 In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post.
-%%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
+\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint-BW}
 
@@
 One drawback of having a two-cycle design, as seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components.
-Combining the two cycles into one would reduce redundancy and complexity.
+Combining the two cycles into one would reduce redundancy, complexity, and cost.
 Heat addition from the CSP HX and LFR HX in parallel orientation is therefore studied in the C-1HTR1T-ON model.
@@
 
-%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
-%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
+\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from-BW}
+\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
 I think it's a problem with the MDPI template.
@@
 To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, is parametrically studied.
-%\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
+\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
 Two cold TES temperatures are tested with constrained LFR low temperature of $400^{\circ}$C: 
@@
 In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C.
-The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
-%%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
+The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX, increasing dispatchability.
+\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
 Asp you will want to explain the criteria that go into cold storage temp.
@@
 
-Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}.
-To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired.
+The identical inlet temperatures due to the parallel configuration makes the C-1HTR1T-ON cycle configuration restricted.
+Another single cycle configuration is desired to allow dissimilar inlet temperatures for the CSP HX and LFR HX while additionally testing the effect that mixing flows downstream from the HTR has on cycle efficiency.
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
 The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR.
-%\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
-The cycle with heat addition from the CSP also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. 
-\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} 
+The cycle with heat addition from the CSP also contains two separate turbines, diagrammatically shown as one turbine T2, while having a dedicated high temperature recuperator, HTR2.
+The two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine.
+Additionally, the power produced by the two turbines is proportional to mass flow rate, each receives a fraction of the mass flow rate therefore producing the same fraction of power.
+Summing these power fractions together yields the total power of a singular turbine in the same position.
+\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.-BW} 
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
-%\bl{this is more about having a compromise option of intermediate complexity and efficiency}
-\bl{also why this isnt really an addition turbine, it is using the turbines that power the compressors}
+\bl{this is more about having a compromise option of intermediate complexity and efficiency}
+\bl{also why this isnt really an addition turbine, it is using the turbines that power the compressors -BW}
 
@@
 Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint.
-The two constrained studies have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C.
+The two constrained studies, with an LFR temperature of $400^{\circ}$, have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C.
 The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.
-%\bl{this is clearer than the previous one but bullets could still be useful}
 
@@
 In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
-\mw{not a full sentence -BW}
 
@@
 
-%\mw{write matter-of-factly, not in a hypothetical tense.-BW}
-
 \subsubsection{C-LFR-PAR} 
@@
 
-%%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
+\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
 
@@
 
-The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.
+The three non-charging cycle models have a focus on producing the highest positive alternator power to heat input, or cycle efficiency.
+The two-cycle configuration, composed of C-LFR-ON and C-CSP-ON, has independent recompression cycles with dedicated compressors, turbine, recuperators, and precooler for the LFR and CSP.
+C-1HTR1T-ON, with the heat additions in parallel, and C-2HTR3T, with dedicated HTR for both heat additions, are cycles which incorporate the CSP and LFR in the same cycle.
+The results from studies done on these cycles are displayed in Table \ref{tab-noncharg}.
 
@@
 The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
-Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
-Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to $400^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Values listed in the Cold TES Temperature row are set to values of $390^{\circ}$C, $410^{\circ}$C, or $440^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
 Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
@@
 The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
-Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficiency perspective, but reduces the LFR thermal power.
+Increasing the LFR sCO$_2$ inlet temperature above the design value of $400^{\circ}$C is favorable from a cycle efficiency perspective, but reduces the LFR thermal power.
 This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power.
-In principle, dropping the LFR inlet temperature further, to as low as 340$^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
-When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
+In principle, dropping the LFR inlet temperature further, to as low as $340^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed.
+When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by $15.1^{\circ}$C to a value of $415.1^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
 
 C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because C2S is turned off and therefore the two cycles are not tethered during non-charging configuration.
-Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
-A cold TES temperature of 410$^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
-Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%.
-The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
+Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of $390^{\circ}$C and another with a higher value of $440^{\circ}$C.
+A cold TES temperature of $410^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the $390^{\circ}$C and $440^{\circ}$C calculated values.
+Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the $440^{\circ}$C case gaining 0.35\%.
+The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of $390^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
 
@@
 Two combined efficiencies are calculated for the two-cycle configuration combination.
-The first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low temperature and C-CSP-ON 440$^{\circ}$C cold TES cases.
+The first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low temperature and C-CSP-ON $440^{\circ}$C cold TES cases.
 This combined efficiency yields a value of 46.05\%.
 The second combined configuration has a lower efficiency with favorable LFR characteristics and solar salt mass flow rate.
-This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON 390$^{\circ}$C cold TES cases with a combined efficiency of 45.05\%.
+This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON $390^{\circ}$C cold TES cases with a combined efficiency of 45.05\%.
 \bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination-BW}
@@
 The single cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions.
-Due to the 10$^{\circ}$C approach temperature, the identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C.
-A supplementary 440$^{\circ}$C cold TES study is run to test the effects that higher temperature storage has on cycle efficiency.
-Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C has no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
+Due to the $10^{\circ}$C approach temperature, the identical inlet conditions lead to a lower bound of $410^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to $400^{\circ}$C.
+A supplementary $440^{\circ}$C cold TES study is run to test the effects that higher temperature storage has on cycle efficiency.
+Raising the temperature of the cold TES from $410^{\circ}$C to $440^{\circ}$C has no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side.
 Increasing the solar salt mass flow rate requires more storage for the same CSP heat input, a reduction in dispatchability, and larger pumps, increasing the cost of the system.
 Therefore, a lower cold TES temperature is desirable.
-Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to 390$^{\circ}$C.
-Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, 390$^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases.
+Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to $390^{\circ}$C.
+Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, $390^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases.
 The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components.
-The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher core power.
+The sCO$_2$ LFR inlet temperature for the $390^{\circ}$C cold TES study is $380^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher core power.
 
@@
 Three studies are conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions.
-The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences.
-Similarly to the studies done on C-1HTR1T-ON, the 440$^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost.
-The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases.
-Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR efficiency.
+The constrained studies have cold TES temperatures of $390^{\circ}$C and $440^{\circ}$, both of which have negligible efficiency differences.
+Similarly to the studies done on C-1HTR1T-ON, the $440^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost.
+The $390^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases.
+Additionally, the sCO$_2$ LFR inlet temperature is $415.2^{\circ}$C, $15.2^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR efficiency.
 
@@
 When the focus of the cycles is thermal storage for later use, the LFR charges the hot TES through the C2S heat exchanger.
-Studies done on the charging techniques, C-LFR-PRE, C-LFR-PAR, and C-LFR-CIRC, have constrained sCO$_2$ LFR inlet temperatures to 400$^{\circ}$C with set values of cold TES temperature of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C.
+Studies done on the charging techniques have constrained sCO$_2$ LFR inlet temperatures to $400^{\circ}$C with set values of cold TES temperature of $390^{\circ}$C, $410^{\circ}$C, or $440^{\circ}$C.
+The two charging techniques which run the full recompression cycle are C-LFR-PRE, with the turbine before the heat extraction, and C-LFR-PAR, with heat extraction in parallel to the turbine.
+The third charging technique, C-LFR-CIRC, has a dedicated circulation loop and additional chiller and circulator pump to avoid losses associated with the compressors and turbines.
 The results are presented in Table \ref{tab-charg}.
@@
 The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
-The hot TES is at a temperature of 560$^{\circ}$C, with a 10$^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}$C.
-In cases where the turbine outlet temperature is less than 570$^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
-For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}$C.
+The hot TES is at a temperature of $560^{\circ}$C, with a $10^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least $570^{\circ}$C.
+In cases where the turbine outlet temperature is less than $570^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
+For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of $595^{\circ}$C.
 With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
-As the temperature of the hot TES is raised above a value of 540$^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
-The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$C to allow for operation of this cycle.
+As the temperature of the hot TES is raised above a value of $540^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
+The temperature in the hot TES is therefore set to a lower value of $540^{\circ}$C to allow for operation of this cycle.
 With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
@@
 To reduce the pressure from 28.8 MPa to 8.8 MPa, an isenthalpic valve is required after heat is extracted for storage through C2S.
-With this configuration two different values for cold TES are studied, one with a cold TES storage of 390$^{\circ}$C the other with a temperature of 440$^{\circ}$C.
-A noteworthy difference for this cycle is the C2S approach temperature is not set to 10$^{\circ}$C.
-Defining the approach temperature as 10$^{\circ}$C causes the energy balance governing combiner 2 to be over constrained.
-Therefore this value is free and calculated to be 35$^{\circ}$C for the 390$^{\circ}$C case and 26.27$^{\circ}$C for the 440$^{\circ}$C case.
+With this configuration two different values for cold TES are studied, one with a cold TES storage of $390^{\circ}$C the other with a temperature of $440^{\circ}$C.
+A noteworthy difference for this cycle is the C2S approach temperature is not set to $10^{\circ}$C.
+Defining the approach temperature as $10^{\circ}$C causes the energy balance governing combiner 2 to be over constrained.
+Therefore this value is free and calculated to be $35^{\circ}$C for the $390^{\circ}$C case and $26.27^{\circ}$C for the $440^{\circ}$C case.
 Both of these different temperature cold TES studies do not change the cycle parameters because, as seen in C-1HTR1T-ON and C-2HTR3T-ON, the solar salt mass flow rate adjusts to accommodate for the temperature difference.
-The higher cold TES temperature of 440$^{\circ}$C causes the mass flow rate in the CSP to increase by approximately 650 kg/s.
+The higher cold TES temperature of $440^{\circ}$C causes the mass flow rate in the CSP to increase by approximately 650 kg/s.
 Increasing the mass flow rate has a higher demand on system components but in this situation it allows for the salt to be charged at a higher rate, increasing the storage capabilities.
@@
 C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from significant losses associated with turbines, compressors, and heat exchangers.
-The separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high temperature mass flow through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally 400$^{\circ}$C.
+The separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high temperature mass flow through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally $400^{\circ}$C.
 This is the most adoptable TES charging technique with a wide range of possible TES charging temperatures while transferring a majority of the heat from the LFR into the hot TES.
-Multiple temperatures for the cold TES are studied; 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
-Of these three temperatures, the highest efficiency is a cold TES temperature of 390$^{\circ}$ with a heat storage efficiency of 100\%.
-The heat storage efficiency reduces as the temperature of the cold TES is increased; the 410$^{\circ}$C case has an efficiency of 90\% while the 440$^{\circ}$C case has an efficiency of 74\%.
+Multiple temperatures for the cold TES are studied; $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C.
+Of these three temperatures, the highest efficiency is a cold TES temperature of $390^{\circ}$ with a heat storage efficiency of 100\%.
+The heat storage efficiency reduces as the temperature of the cold TES is increased; the $410^{\circ}$C case has an efficiency of 90\% while the $440^{\circ}$C case has an efficiency of 74\%.
 This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
 The non-charging cycle configuration that this charging cycle is implemented in requires further consideration.
-For C-LFR-CIRC, the highest efficiencies are achieved when the cold TES temperature is 10$^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger.
-If the desired temperature of cold TES is 390$^{\circ}$C, the non-charging cycle configurations with sCO$_2$ LFR inlet temperatures of 400$^{\circ}$C are required for highest efficiency.
+For C-LFR-CIRC, the highest efficiencies are achieved when the cold TES temperature is $10^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger.
+If the desired temperature of cold TES is $390^{\circ}$C, the non-charging cycle configurations with sCO$_2$ LFR inlet temperatures of $400^{\circ}$C are required for highest efficiency.
 A drawback of this TES charging technique is the additional components needed for the circulation loop, with an additional chiller and circulator component, adding cost.
@@
 
+\textit{Non-charging configurations:}
 \begin{itemize}
-    \item	x
-    \item	x
-    \item   x
+    \item	Two-cycle configuration C-LFR-ON and C-CSP-ON: Offers the highest cycle efficiency because of the freedom of the two cycles to operate independently when generating electrical power.
+The cycles individually are simple recompression but lead to redundancy in cycle components increasing cost and complexity.
+    \item	C-1HTR1T-ON: Single cycle configuration that is the least complex, therefore cost efficient and compact, with heat additions from the CSP and LFR in parallel.
+This cycle has the lowest cycle efficiencies with constrained inlet temperatures to the LFR and CSP, limiting versatility.
+    \item   C-2HTR3T-ON: Single cycle configuration that has dedicated turbines and HTRs for the LFR and CSP.
+This cycle makes a compromise between complexity with reduced cycle component redundancy, flexibility for dissimilar inlet temperatures on the CSP and LFR inlet, and median efficiency.
+\end{itemize}
+
+\textit{Thermal energy storage charging techniques:}
+\begin{itemize}
+    \item	C-LFR-PRE: Charging technique with the turbine prior to C2S heat exchanger with a valve that bypasses the turbine, demands a high outlet temperature for the LFR to be effective.
+Due to LFR outlet temperature limitations, this configuration has the lowest heat storage efficiency.
+    \item	C-LFR-PAR: Charging technique that splits the flow directly after the LFR with the turbine and C2S heat exchanger in parallel.
+The heat storage efficiency is median of the tested charging techniques with a lower cold TES temperature having no effect other than increasing the solar salt mass flow rate increasing CSP component sizes.
+    \item   C-LFR-CIRC: Flexible technique with a heat storage efficiency being highly dependent on cold TES temperature and LFR inlet temperature.
+Able to achieve heat storage efficiency to near 100\% by eliminating losses associated with the turbines and compressors.
+The additional chiller and circulator components in the dedicated circulation loop increase complexity and cost.
 \end{itemize}
@@
 Further studies and cycle analysis must be done before these cycles are used for implementation into a physical plant.
-
-% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 

### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
edits to summary and conclusion

@@
 High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
-\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
 Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
@@
 Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
-
-\bl{not a big issue but do we want to describe as sCO2 or sCO2 Brayton? In project nomenclature to date I have used sCO2 with the logic that sCO2 'isnt really a Brayton cycle' but both are common -BW}
 A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
@@
 
-\bl{I would bullet out the next three citations-BW}
 Various studies on complimentary solar-nuclear systems have been accomplished with several reviewed as follows:
@@
 
-\bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences).
-You could start by saying that it is prior work on the LFR-CSP-sCO2 concept.
-Then describe its cycle configuration with the high temperature salt.
-Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed.
-The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang - BW}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW}
-\bl{In an LFR, the outlet temperature is limited by materials considerations.
-The flow velocity is limited by erosion of the fuel (if the lead gets too fast, it erodes the fuel).
-We want the core to be compact.
-Therefore the mass flow is limited.
-This means that a lower inlet temperature gives a higher power (subject to constraints on fuel temperautre, which is also a function of power density).
-There is a limit of about 340C, below which the lead might freeze (which is operationally unacceptable), but until that value, lower inlet = higher core power.
-However, from thermodynamics, higher inlet = higher efficiency.
-There is a trade-off between driving the core harder and getting better cycle performance.
-The trade-off gives 400C as a temperature that doesnt overly compromise core power while still providing reasonable efficiency.
-Raising this temperature higher would drop the core power below the 950 MW -BW}
 
@@
 This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.
-
-\bl{I dont think the above covers the case where the salt discharges.
-It might be worth eliciting how the operating modes change as power demand increases.
-From highest to lowest demand.
-In all modes CSP will charge the salt is sun is available: (1) LFR and S2C both dispatch, maximum power (2) As power demand decreases, S2C ramps down until no power dispatched through salt (i.e.
-salt is charged) (3) LFR dispatches, no dispatch from S2C (4) LFR ramps down and gradually transfers greater and greater fraction of power to salt using C2S.
-(5) No electricity dispatched, all LFR heat passes through C2S -BW
-}
 
@@
 In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post.
-\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint-BW}
 
@@
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
-\bl{this is more about having a compromise option of intermediate complexity and efficiency}
-\bl{also why this isnt really an addition turbine, it is using the turbines that power the compressors -BW}
+
+In practice, sCO$_2$ cycles typically have 3 turbines, with 2 of these driving the compressor and recompressor.
+Therefore, this configuration will not in general require additional turbines compared to the C-1HTR1T-ON configuration.
+Furthermore, it is anticipated that the cost of the high temperature recuperator is likely most related to its volume, and hence having two smaller high temperature recuperators is unlikely to cost significantly more than one large one.
 
@@
 This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON $390^{\circ}$C cold TES cases with a combined efficiency of 45.05\%.
-\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination-BW}
 
@@
 C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from significant losses associated with turbines, compressors, and heat exchangers.
-The separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high temperature mass flow through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally $400^{\circ}$C.
+The separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high temperature mass flow through a circulator, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally $400^{\circ}$C.
 This is the most adoptable TES charging technique with a wide range of possible TES charging temperatures while transferring a majority of the heat from the LFR into the hot TES.
 Multiple temperatures for the cold TES are studied; $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C.
-Of these three temperatures, the highest efficiency is a cold TES temperature of $390^{\circ}$ with a heat storage efficiency of 100\%.
+Of these three temperatures, the highest efficiency is a cold TES temperature of $390^{\circ}$ with a heat storage efficiency of 100\% (not accounting for pressure drop losses, which will be small).
 The heat storage efficiency reduces as the temperature of the cold TES is increased; the $410^{\circ}$C case has an efficiency of 90\% while the $440^{\circ}$C case has an efficiency of 74\%.
 This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
-The non-charging cycle configuration that this charging cycle is implemented in requires further consideration.
+
+There is an interaction between the temperatures selected here and the non-charging cycle configuration.
 For C-LFR-CIRC, the highest efficiencies are achieved when the cold TES temperature is $10^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger.
-If the desired temperature of cold TES is $390^{\circ}$C, the non-charging cycle configurations with sCO$_2$ LFR inlet temperatures of $400^{\circ}$C are required for highest efficiency.
-A drawback of this TES charging technique is the additional components needed for the circulation loop, with an additional chiller and circulator component, adding cost.
-\bl{need to comment on how this interacts with the choice of cycle configuration.
-If the LFR temperature is 400C and cold TES is 390C then CSP inlet must be 380C and this requires 2HTR3T or separate cycles.
-If 1HTR1T is used, then 410C+ is needed which implies an efficiency penalty -BW}
+If the sCO$_2$ LFR inlet temperature is constrained to $400^{\circ}$C, then the desired cold TES temperature is $390^{\circ}$C to allow for the apporach temperature.
+If the cold TES is at a higher temperature, then the chiller is needed.
+This then implies that the sCO$_2$ inlet temperature in the salt-to-sCO2 heat exchanger is  $380^{\circ}$C.
+From the results of the previous section, this is clearly achievable for the C-2HTR3T-ON configuration and the separate cycle configuration, but for the C-1HTR1T-ON configuration the LFR and CSP inlet temperatures are constrained to be the same.
+In this case, the LFR and CSP inlet temperatures would then be $400^{\circ}$C, implying a cold TES temperature of  $410^{\circ}$C and hence a 90\% heat storage efficiency with a requirement for a chiller.
 
@@
 This paper analyzed contending sCO$_2$ Brayton cycle configurations for complimentary CSP and LFR cycles with non-charging cycle configurations focusing on electrical generation.
-An additional operating mode, hot TES charging, is considered where the CSP hot TES is charged when grid demand is low.
+An additional operating mode, hot TES charging, is considered where the CSP hot TES is charged by the LFR when grid demand is low.
 This operating mode positions the heat extraction point at different locations around the turbine in a sCO$_2$ Brayton recompression cycle.
@@
     \item	Two-cycle configuration C-LFR-ON and C-CSP-ON: Offers the highest cycle efficiency because of the freedom of the two cycles to operate independently when generating electrical power.
-The cycles individually are simple recompression but lead to redundancy in cycle components increasing cost and complexity.
+The cycles individually are simple recompression but there is a lack of component synergies.
     \item	C-1HTR1T-ON: Single cycle configuration that is the least complex, therefore cost efficient and compact, with heat additions from the CSP and LFR in parallel.
-This cycle has the lowest cycle efficiencies with constrained inlet temperatures to the LFR and CSP, limiting versatility.
+With both CSP and LFR discharging, combined cycle efficiency is reduced by ~0.8\% compared to the two cycle configuration.
     \item   C-2HTR3T-ON: Single cycle configuration that has dedicated turbines and HTRs for the LFR and CSP.
 This cycle makes a compromise between complexity with reduced cycle component redundancy, flexibility for dissimilar inlet temperatures on the CSP and LFR inlet, and median efficiency.
+The efficiency is only marginally higher than C-1HTR1T-ON, but heat storage efficiency when using the LFR to charge the salt is improved due to flexibility on setting the CSP and LFR inlet temperatures.
+As the additional turbines are likely present in practice anyway, this cycle is not anticipated to significantly increase cost and complexity over C-1HTR1T-ON.
+The relative merits of C-2HTR3T-ON and C-1HTR1T-ON are therefore similar.
 \end{itemize}
@@
 \begin{itemize}
+    \item    C-LFR-POST: Charging technique with the turbine subsequent to C2S heat exchanger. Infeasible due to lower thermodynamic efficiency. 
     \item	C-LFR-PRE: Charging technique with the turbine prior to C2S heat exchanger with a valve that bypasses the turbine, demands a high outlet temperature for the LFR to be effective.
-Due to LFR outlet temperature limitations, this configuration has the lowest heat storage efficiency.
-    \item	C-LFR-PAR: Charging technique that splits the flow directly after the LFR with the turbine and C2S heat exchanger in parallel.
-The heat storage efficiency is median of the tested charging techniques with a lower cold TES temperature having no effect other than increasing the solar salt mass flow rate increasing CSP component sizes.
+Due to LFR outlet temperature limitations, this configuration has the next lowest heat storage efficiency.
+    \item	C-LFR-PAR: Charging technique that splits the flow directly after the LFR with the turbine and C2S heat exchanger in parallel. The heat storage efficiency is higher than C-LFR-PRE.
     \item   C-LFR-CIRC: Flexible technique with a heat storage efficiency being highly dependent on cold TES temperature and LFR inlet temperature.
 Able to achieve heat storage efficiency to near 100\% by eliminating losses associated with the turbines and compressors.
+For C-1HTR1T-ON, the heat storage efficiency is limit to 90\% because the inlet temperatures to the LFR and CSP are constrained to be the same.
 The additional chiller and circulator components in the dedicated circulation loop increase complexity and cost.
 \end{itemize}
+
+C-LFR-PAR and C-LFR-CIRC are therefore options going forward, with a trade-off between heat storage efficiency and component costs, with the performance of C-LFR-CIRC also depending on the choise of charging configuration.
 

### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/backmatter.tex
tidy up figures, front and backmatter

\authorcontributions{Conceptualization, B.L., M.W., C.S. and T.N.; methodology, B.L., M.W., C.S., T.N. and B.L.; software, B.W.; validation, B.L and M.W.; formal analysis, B.W.; investigation, B.W.; resources, M.W. and B.L.; data curation, B.W.; writing---original draft preparation, B.W.; writing---review and editing, B.L. and M.W.; visualization, B.W.; supervision, M.W and B.L.; project administration, B.L.; funding acquisition, B.L, M.W, C.S and T.N. All authors have read and agreed to the published version of the manuscript.}

\funding{This work was supported by funding received from the DOE Office of Nuclear Energy’s Nuclear Energy University Program under contract number DE-NE0008988. }

% \institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.}

% \informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

% Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{Supporting data for this study is available on request.}

\acknowledgments{We would like to thank Josh McTigue (NREL) for useful technical discussions on the development of the cycle configurations.}

\conflictsofinterest{The authors declare no conflict of interest. The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results'.}

%% Optional
% \sampleavailability{Samples of the compounds ... are available from the authors.}

### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
tidy up figures, front and backmatter
some additional comments

--- 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 
-\mw{If mass is conserved, use a single $\dot{m}$ - BW}
+%\mw{If mass is conserved, use a single $\dot{m}$ - BW}
 
@@
 The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C.
-The outlet temperature of the LFR is specified because of high temperature material limits on the LFR lead side.
-The low temperature side is allowed to vary over a range of values with some considerations.
-The lead flow velocity is limited by the erosion of the fuel, the slower the lead flow velocity reduces fuel erosion and therefore leads to a more desirable compact design.
-Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.
-LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
-When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in LFR efficiency but a reduction in LFR power below $950$ MW.
-There is a compromise between high LFR efficiency and LFR power, therefore a temperature of $400^{\circ}$C for the sCO$_2$ inlet temperature is the optimal value provided by Westinghouse.
-
-\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
+%\mw{Make sure numbers are in math mode -BW}
+The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side.
+LFR sCO$_2$ inlet low temperature has a lower bound of $340^{\circ}$C and an optimal value of $400^{\circ}$C, as provided by Westinghouse.
+%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
 \bl{In an LFR, the outlet temperature is limited by materials considerations.
@@
 The trade-off gives 400C as a temperature that doesnt overly compromise core power while still providing reasonable efficiency.
-Raising this temperature higher would drop the core power below the 950 MW -BW}
+Raising this temperature higher would drop the core power below the 950 MW}
+Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.
 
@@
 \mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations.
-It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.-BW}
+It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.}
 %\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
@@
 Two temperatures are tested, $390^{\circ}$C and $440^{\circ}$C, to observe the impact of cold TES temperature on cycle efficiency.
-Efficiencies need to be combined to draw a comparison of the two-cycle configurations to the single cycle configurations; C-1HTR1T-ON and C-2HTR3T-ON.
-Equation \ref{eq-eta-2cycle} is used to calculate this combined two-cycle efficiency.
-
- \begin{equation}
-    \label{eq-eta-2cycle}
-    \eta_{combined} = \frac{\dot{W}_{A,C\text{-}LFR\text{-}ON}+\dot{W}_{A,C\text{-}CSP\text{-}ON}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
-\end{equation}
-
-Equation \ref{eq-eta-2cycle} is the ratio of total alternator power of C-LFR-ON, $\dot{W}_{A,C\text{-}LFR\text{-}ON}$, and C-CSP-ON, $\dot{W}_{A,C\text{-}CSP\text{-}ON}$, to the total heat input into the cycles from the LFR and CSP heat exchangers, $\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}$.
 
@@
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
-The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR.
+The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, \hl{HTR1}.
 %\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
@@
 To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
-\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
+%%\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
 
@@
 In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.
-\mw{not a full sentence -BW}
+%\mw{not a full sentence -BW}
 
@@
 
-The high temperature sCO$_2$ leaving the LFR HX flows through the LFR turbine converting thermal energy to usable work.
-The outlet temperature of the LFR turbine is at a temperature suitable to charge the hot TES, therefore the flow is passed through C2S exchanging heat to the cold solar salt.
+Flow leaving the turbine contains excess thermal energy that is not transformed into electrical energy.
+This excess thermal energy is stored in the hot CSP TES.
 The diagram outlining this process is C-LFR-PRE in Fig.
 \ref{c-lfr-pre}.
+
 \mw{Careful here.
@@
 Any fluid above absolute zero technically has excess thermal energy if the reference is zero.
-Depending on this definition, not all excess energy from the turbine is stored in TES.
--BW}
-\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations. -BW}
+Depending on this definition, not all excess energy from the turbine is stored in TES.}
+\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations.}
 
@@
 
-A problem arises with this salt charging configuration.
-The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $560^{\circ}$C when the turbine power is balanced with the compressor demand.
+Problems arise with this salt charging configuration.
+The temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $595^{\circ}$C.
 To raise the temperature, some of the high temperature flow before the turbine is redirected through a valve and combined after the turbine.
-Limiting the flow through the turbine reduces the turbine power and compressor power because of the balancing requirement.
-Due to the reduction in available compressor power, the LFR RC is effectively bypassed, and a large portion of usable heat is expelled in the LFR PC before the LFR MC.
-The thermal storage efficiency reduces as a result of the large amount of heat rejected in the LFR PC.
+Combining different temperature flows and reducing the flow through the turbine has a large impact on heat storage efficiency.
 
@@
 
-A sensitivity study \mw{this is one study with two parameter values, right?
--BW} with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency.
+Two sensitivity studies \mw{this is one study with two parameter values, right?} with varying cold CSP TES temperature are carried out to determine the impact on heat storage efficiency.
 The study considers two temperature values of $390^{\circ}$C and $440^{\circ}$C.
@@
 
-\hl{The values for the three non-charging cycle models with a focus on producing positive alternator power (provide electrical power to the grid), 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON,} are displayed in Table \ref{tab-noncharg}.
-
+The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.
+\mw{this sentence is hard to parse.
+What is meant by ``focus on electrical generation?''}
+
+The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
+Cycles that do not contain the listed component and omit the associated values.
+\clearpage 
+\mw{Check that the column breakdown and grouping is correct in what I've changed.}
 \end{paracol}
@@
 The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
-Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficiency perspective, but reduces the LFR thermal power.
+Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficency perspective, but reduces the LFR thermal power.
 This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power.
@@
 When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.
-
-C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because C2S is turned off and therefore the two cycles are not tethered during non-charging configuration.
-Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
+\bl{text revised}
+
+C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration.
+\bl{Provided that the charging configuration is suitably configured} Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C.
 A cold TES temperature of 410$^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values.
@@
 The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
-
-Combining the two-cycle efficiencies using Equation \ref{eq-eta-2cycle} gives a more direct comparison to the single cycle configurations; C-1HTR1T and C-2HTR3T.
-Two combined efficiencies are calculated for the two-cycle configuration combination.
-The first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low temperature and C-CSP-ON 440$^{\circ}$C cold TES cases.
-This combined efficiency yields a value of 46.05\%.
-The second combined configuration has a lower efficiency with favorable LFR characteristics and solar salt mass flow rate.
-This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON 390$^{\circ}$C cold TES cases with a combined efficiency of 45.05\%.
-\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination-BW}
+\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination}
 
@@
 
+\hl{should I include in table 3 important mass flow rates like solar salt mass flow and total mass flow in sCO2?}
+
 \subsection{Thermal Energy Storage Charging Techniques}
@@
 The results are presented in Table \ref{tab-charg}.
-
-\end{paracol}
-\begin{specialtable}[H] 
-    %[htbp]
-    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
-    \resizebox{\columnwidth}{!}{
-    \begin{tabular}{lccccccc}
-    \toprule
-     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
-    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
-    \midrule
-    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
-    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
-    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
-    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
-    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
-    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
-    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
-    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
-    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
-    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
-    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
-    \bottomrule
-    \end{tabular}
-    }
-\end{specialtable}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
 
@@
 
+% \end{paracol}
+
+\begin{specialtable}[H]  
+    %[htbp]
+    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
+    \resizebox{\columnwidth}{!}{
+    \begin{tabular}{lc|c|cc|ccc}
+    \toprule
+     &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
+    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
+    \midrule
+    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
+    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
+    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
+    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
+    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
+    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
+    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
+    \bottomrule
+    \end{tabular}
+    }
+\end{specialtable}
+% \begin{paracol}{2}
+% \linenumbers
+% \switchcolumn
+
 \subsubsection{C-LFR-PAR}
@@
 Both cycles have a heat storage efficiency of 45.30\%.
+\hl{Should I include solar salt mass flow also in table 4?}
 
@@
 C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from significant losses associated with turbines, compressors, and heat exchangers.
-The separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high temperature mass flow through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally 400$^{\circ}$C.
-This is the most adoptable TES charging technique with a wide range of possible TES charging temperatures while transferring a majority of the heat from the LFR into the hot TES.
+This is due to the fact that a separate recirculation cycle is modeled taking heat directly from the LFR, passing it through a recirculating pump, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, 400$^{\circ}$C.
+This is the most adoptable TES charging technique a wide range of possible TES charging temperatures with almost all of the heat from the LFR being transferred into the hot TES depending on the temperature.
 Multiple temperatures for the cold TES are studied; 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C.
 Of these three temperatures, the highest efficiency is a cold TES temperature of 390$^{\circ}$ with a heat storage efficiency of 100\%.
-The heat storage efficiency reduces as the temperature of the cold TES is increased; the 410$^{\circ}$C case has an efficiency of 90\% while the 440$^{\circ}$C case has an efficiency of 74\%.
-This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
-The non-charging cycle configuration that this charging cycle is implemented in requires further consideration.
-For C-LFR-CIRC, the highest efficiencies are achieved when the cold TES temperature is 10$^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger.
-If the desired temperature of cold TES is 390$^{\circ}$C, the non-charging cycle configurations with sCO$_2$ LFR inlet temperatures of 400$^{\circ}$C are required for highest efficiency.
+The heat storage efficiency reduces as the temperature of the cold TES is increased, the 410$^{\circ}$C case has an efficiency of 90\% while the 440$^{\circ}$C case has an efficiency of 74\%.
+This reduction in efficiency is due to the inlet temperature condition on the LFR, the higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore the more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet temperature.
 A drawback of this TES charging technique is the additional components needed for the circulation loop, with an additional chiller and circulator component, adding cost.
@@
 If the LFR temperature is 400C and cold TES is 390C then CSP inlet must be 380C and this requires 2HTR3T or separate cycles.
-If 1HTR1T is used, then 410C+ is needed which implies an efficiency penalty -BW}
+If 1HTR1T is used, then 410C+ is needed which implies an efficiency penalty}
 
@@
 
-This paper analyzed contending sCO$_2$ Brayton cycle configurations for complimentary CSP and LFR cycles with non-charging cycle configurations focusing on electrical generation.
-An additional operating mode, hot TES charging, is considered where the CSP hot TES is charged when grid demand is low.
-This operating mode positions the heat extraction point at different locations around the turbine in a sCO$_2$ Brayton recompression cycle.
-The performance parameters that are used for comparison of the cycles are cycle efficiency when the cycle is producing electricity and heat storage efficiency when the focus is on energy storage for later use in the charging mode.
-These efficiencies are maximized using flow splitter values at different values of cold TES temperature and constrained or unconstrained sCO$_2$ inlet LFR temperature.
-The conclusions drawn in this paper are as follows:
-
-\begin{itemize}
-    \item	x
-    \item	x
-    \item   x
-\end{itemize}
-
-The cycle configurations with the listed conclusions can be used as reference for future cycle design and proof of concept considerations.
-Further studies and cycle analysis must be done before these cycles are used for implementation into a physical plant.
-
 % This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
@@
 \end{paracol}
+
+% \subsection{Small Tables}
+% %--------------------------------------------------------------------------------------
+
+% Modeling the C-LFR-ON cycle in EES yielded the results in Table \ref{tab-c-lfr-on}.
+
+% \begin{specialtable}[H] 
+%     %[htbp]
+%     \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
+%     \begin{tabular}{lccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
+%     \midrule
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	395.1	&	400	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	678.9	&	626.4	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.9627	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% The EES model outputs for C-CSP-ON are listed in Table \ref{tab-c-csp-on}.
+
+% \begin{specialtable}[H] 
+%     %[htbp] 
+%     \caption{Calculated system parameters for non-charging C-CSP-ON cycle configuration with varied TES cold temperature. \label{tab-c-csp-on}}
+%     \begin{tabular}{lccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} &  &\\
+%     \midrule
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	45.58	&	45.93	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	339.1	&	340.6	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	418.5	&	420.2	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	95.73	&	96.13	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	97.22	&	97.71	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	532.1	&	534.5	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6996	&	0.6994	\\
+%     LTR UA Value (MW/$^{circ}$C)	&	$UA_{LTR}$	&	45.4	&	45.53	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9858	&	0.9854	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	548.3	&	551.4	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9201	&	0.9202	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	34.58	&	34.72	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8593	&	0.8594	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	665.4	&	667.7	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9436	&	0.9436	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	71.34	&	26.92	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9924	&	0.701	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	757.6	&	760.8	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.945	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %--------------------------------------------------------------------------------------
+
+% These values are displayed in Table \ref{tab-c-1htr1t-on}.
+
+% \begin{specialtable}[H] 
+%     %[htbp] 
+%     \caption{Calculated system parameters for non-charging C-1HTR1T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.
+Temperature of TES cold temperature is also varied.\label{tab-c-1htr1t-on}}
+%     \begin{tabular}{lcccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-1HTR1T-ON}\\
+%     & & \textit{U} & \textit{C} & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4C}$	&	380	&	400	&	400	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	44.9	&	44.22	&	44.22	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	763.9	&	752.3	&	752.6	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	937.4	&	949.2	&	949.3	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	214.5	&	194.8	&	194.8	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	217.4	&	285.7	&	285.7	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	1196	&	1233	&	1233	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.6333	&	0.6333	\\
+%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.4485	&	0.4928	&	0.4929	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	102	&	91.63	&	91.64	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.9066	&	0.9066	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	549.2	&	614.9	&	615.1	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.9485	&	0.9485	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	78.22	&	82.3	&	82.34	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8595	&	0.8754	&	0.8755	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	679.2	&	742.6	&	743	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9445	&	0.9441	&	0.9441	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	33.72	&	73.4	&	75.19	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8104	&	0.9957	&	0.8034	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.5	&	751.9	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.945	&	0.9381	&	0.9374	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %--------------------------------------------------------------------------------------
+
+% The calculated values from these studies are displayed in Table \ref{tab-c-2htr3t-on}.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for non-charging C-2HTR3T-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-2htr3t-on}}
+%     \begin{tabular}{lcccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} &\\
+%     & & \textit{U} & \textit{C} & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{5A}$	&	395.2	&	400	&	400	\\
+%     Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	46.10	&	44.34	&	44.35	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	783.7	&	753.7	&	754	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	917.6	&	947.6	&	947.9	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	209.9	&	216.8	&	216.9	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	213.5	&	140.8	&	140.8	\\
+%     T1 Power (MW)	&	$\dot{W}_{T1}$	&	679.3	&	626.3	&	626.3	\\
+%     T2 Power (MW)	&	$\dot{W}_{T2}$	&	527.8	&	485	&	485.4	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.6993	&	0.7846	&	0.7846	\\
+%     LFR Mass Flow Fraction (-)	&	$y_{2}$	&	0.5478	&	0.5486	&	5.48E-01	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	134.4	&	41.56	&	41.57	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9853	&	0.847	&	0.847	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	1204	&	667.1	&	667.3	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.9414	&	0.8741	&	0.8741	\\
+%     HTR1 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR1}$	&	48.32	&	42.69	&	42.69	\\
+%     HTR1 Capacitance Ratio (-)	&	$CR_{HTR1}$	&	0.8661	&	0.8142	&	0.8142	\\
+%     HTR1 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR1}$	&	545.7	&	636.8	&	636.6	\\
+%     HTR1 Effectiveness (-)	&	$\varepsilon_{HTR1}$	&	0.9542	&	0.9627	&	0.9627	\\
+%     HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	34.29	&	31.61	&	31.63	\\
+%     HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	0.8594	&	0.8074	&	0.8074	\\
+%     HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	298.1	&	363.4	&	363.8	\\
+%     HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	0.9436	&	0.9561	&	0.9561	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	70.88	&	44.92	&	23.13	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.9926	&	0.9138	&	0.6454	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	751.3	&	751.3	&	751.9	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9450	&	0.9493	&	0.9493	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %======================================================================================
+
+% %--------------------------------------------------------------------------------------
+
+% The calculations from this TES charging technique are shown in Table \ref{tab-c-lfr-pre}.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for salt charging C-LFR-PRE cycle configuration with TES cold storage set to 663.2 K.\label{tab-c-lfr-pre}}
+%     \begin{tabular}{lcc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-PRE}\\
+%     & & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	\\
+%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	\\
+%     Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	0.699	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	0.904	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.4735	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	328	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9368	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% \textbf{Discussion of Results}
+
+% %--------------------------------------------------------------------------------------
+
+% %--------------------------------------------------------------------------------------
+
+% The results from this study are displayed in Table \ref{tab-c-lfr-par}.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for salt charging C-LFR-PAR cycle configuration with TES cold storage varied and LFR low temperature set to 673.2 K.\label{tab-c-lfr-par}}
+%     \begin{tabular}{lccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-2HTR3T-ON} & \\
+%     & & \textit{C} & \textit{C}\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4}$	&	400	&	400	\\
+%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	45.30	&	45.30	\\
+%     Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	\\
+%     PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	519.6	&	519.6	\\
+%     MC Power (MW)	&	$\dot{W}_{MC}$	&	118.9	&	119	\\
+%     RC Power (MW)	&	$\dot{W}_{RC}$	&	77.28	&	77.28	\\
+%     Turbine Power (MW)	&	$\dot{W}_{T}$	&	196.2	&	196.2	\\
+%     MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7844	&	0.7844	\\
+%     SALT HX Mass Flow Fraction (-)	&	$y_{2}$	&	0.6867	&	0.6867	\\
+%     LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	22.83	&	22.83	\\
+%     LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.8473	&	0.8743	\\
+%     LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	366.4	&	366.4	\\
+%     LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.8742	&	0.8742	\\
+%     HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	42.69	&	42.69	\\
+%     HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8143	&	0.8143	\\
+%     HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1160	&	1160	\\
+%     HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9627	&	0.9627	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	8.037	&	14.24	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.7556	&	0.9339	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	430.4	&	430.4	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.8275	&	0.8307	\\
+%     CSPHX Approach Temperature ($^{\circ}$C)	&	$\delta_{CSPHX}$	&	35	&	26.27	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+% Changing the temperature of the cold CSP TES had little effect on the heat storage efficiency.
+The CSP salt mass flow rate and approach temperature of the SALT HX would adjust according to the temperature difference in the TES and keep the efficiency constant.
+
+% %--------------------------------------------------------------------------------------
+
+% Table \ref{tab-c-lfr-circ} to show cold thermal energy storage's affect on heat storage efficiency.
+
+% \begin{specialtable}[H]
+%     %[htbp]
+%     \caption{Calculated system parameters for charging C-LFR-CIRC subcycle configuration with constrained lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-circ}}
+%     \begin{tabular}{lcccc}
+%     \toprule
+%     \textbf{Definition} & \textbf{Variable} & \textbf{C-LFR-CIRC} &\\
+%     \midrule	
+%     Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	410	&	440	\\
+%     LFR Inlet Temperature ($^{\circ}$C)	&	$T_{1C}$	&	400	&	400	&	400	\\
+%     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	99.92	&	89.66	&	74.29	\\
+%     Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	0.7245	&	98.25	&	244.2	\\
+%     CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	48.29	&	43.16	&	35.63	\\
+%     CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	0.8755	&	0.8599	&	0.8294	\\
+%     CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	949.3	&	851.8	&	705.8	\\
+%     CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	0.9511	&	0.9459	&	0.9355	\\
+%     \bottomrule
+%     \end{tabular}\\
+% \end{specialtable}
+
+%This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Discussion}
+
+% Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
 

### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
SNL location corrected

--- 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}.
-Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Arvada, Colorado, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}.
+Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Albuquerque, NM, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}.
 In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.
@@
 \end{paracol}
-\begin{figure}[H] 
+\begin{figure}[h]
     \widefigure
@@
 
-\begin{figure}[H] 
+\begin{figure}[h] 
     %[htb]

### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

--- 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 
-\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from-BW}
+%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
 \mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
@@
 
+The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
+Cycles that do not contain the listed component and omit the associated values.
+\clearpage 
+\mw{Check that the column breakdown and grouping is correct in what I've changed.}
 \end{paracol}
@@
 
-\end{paracol}
+\subsubsection{C-LFR-PRE}
+The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
+The hot TES is at a temperature of 560$^{\circ}$C, with a 10$^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}$C.
+In cases where the turbine outlet temperature is less than 570$^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
+For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}$C.
+With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
+As the temperature of the hot TES is raised above a value of 540$^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
+The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$C to allow for operation of this cycle.
+With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
+This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.
+
+% \end{paracol}
+
 \begin{specialtable}[H]  
@@
     \resizebox{\columnwidth}{!}{
-    \begin{tabular}{lccccccc}
+    \begin{tabular}{lc|c|cc|ccc}
     \toprule
-     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
+     &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
     \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
@@
     Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
-    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
-    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
-    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
+    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
+    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
     C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
@@
 \end{specialtable}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-\subsubsection{C-LFR-PRE}
-The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
-The hot TES is at a temperature of $560^{\circ}$C, with a $10^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least $570^{\circ}$C.
-In cases where the turbine outlet temperature is less than $570^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
-For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of $595^{\circ}$C.
-With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
-As the temperature of the hot TES is raised above a value of $540^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
-The temperature in the hot TES is therefore set to a lower value of $540^{\circ}$C to allow for operation of this cycle.
-With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
-This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.
+% \begin{paracol}{2}
+% \linenumbers
+% \switchcolumn
 

### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Ty's comments

--- 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
@@
 
-Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
-High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
+Supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
 Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
+The literature shows that the recompression cycle can reach efficiencies of 50\% in some scenarios (with turbine inlet temperatures in the 650-700 $^{\circ}$C range) \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
 Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
-Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}.
+Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar award for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}.
 Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each.
@@
 Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}.
-Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Albuquerque, NM, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}.
-In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.
+Physical testing of simple sCO$_2$ Brayton cycles has been performed at Sandia National Laboratories \cite{wright_2011} and in Korea \cite{cha_2016}, with at least two commercial companies (Echogen, Net Power) having progressed to building pilot cycles  \cite{held_2015,fetvedt_2016}.
 
@@
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
-The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
+The molten salt loop for the CSP is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat exchangers.
 
@@
 The right hand side of the equation is heat leaving the black box heat exchanger with $\dot{m}$ and enthalpy of $h_{out}$.
-Black box energy balances are used in three situations, the receiver, LFR heat exchanger, and PC heat exchanger.
+Black box energy balances are used in three situations, the receiver, LFR heat exchanger, and pre-cooler heat exchanger.
 These heat exchangers are not exhaustively modeled because the state points on the inlet and outlet are defined by design parameters.
@@
 
-Counter-flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature.
+Counter-flow heat exchanger calculations require two known state points, fluid properties, mass flow rate of hot and cold side, and a specified approach temperature.
 In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers \cite{seidel_2010_model_development}.
@@
 
-Using values of effectiveness and capacitance ratio, the effectiveness-NTU method can be employed to find the number of transfer units, $NTU$, and the conductance, $UA$ \cite{klein_nellis_2011,nellis_klein_2008}.
-
 \subsubsection{Lead-Cooled Fast Reactor}
@@
 LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
-When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in LFR efficiency but a reduction in LFR power below $950$ MW.
+When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in power conversion cycle thermodynamic efficiency but a reduction in LFR power below $950$ MW.
 There is a compromise between high LFR efficiency and LFR power, therefore a temperature of $400^{\circ}$C for the sCO$_2$ inlet temperature is the optimal value provided by Westinghouse.
@@
 The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-salt counter-flow heat exchanger (C2S), and CSP counter-flow heat exchanger (CSP HX).
-The diagram for this CSP salt cycle is seen in Figure \ref{csp}.
+The diagram for this CSP salt loop is seen in Figure \ref{csp}.
 
@@
 Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C.
-Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to $720^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at $560^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}.
+Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to $720^{\circ}$C, but here the hot TES temperature is set at $560^{\circ}$C for all modeled cycles \cite{mehos2017concentrating} as this has been commercially proven.
 The cold TES temperature takes on three different values according to cycle configuration capabilities: $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C.
@@
 'Non-charging' cycle operating modes are characterized by operations wherein the CSP salt cycle is discharging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is dispatching heat directly to generate electricity.
-When electrical generation is occurring, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
+When electrical generation is occurring and solar resource is available, the heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field.
 The hot TES solar salt is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle through CSP HX to be converted into electricity.
@@
 
-The values displayed in Table \ref{tab-cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Company.
+The values displayed in Table \ref{tab-cycle-constants} are representative of CSP and the Westinghouse LFR.
 
@@
 
-Equation \ref{eq-eta-2cycle} is the ratio of total alternator power of C-LFR-ON, $\dot{W}_{A,C\text{-}LFR\text{-}ON}$, and C-CSP-ON, $\dot{W}_{A,C\text{-}CSP\text{-}ON}$, to the total heat input into the cycles from the LFR and CSP heat exchangers, $\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}$.
+Equation \ref{eq-eta-2cycle} is the ratio of total alternator (net) power of C-LFR-ON, $\dot{W}_{A,C\text{-}LFR\text{-}ON}$, and C-CSP-ON, $\dot{W}_{A,C\text{-}CSP\text{-}ON}$, to the total heat input into the cycles from the LFR and CSP heat exchangers, $\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}$.
 
@@
     \item	$440^{\circ}$C: Upper bound temperature on cold TES storage;
+    \item	$390^{\circ}$C: Unconstrained LFR cold inlet temperature allows a lower cold TES of $390^{\circ}$C to be achieved.
+This allows for a larger temperature drop across the CSP HX, increasing dispatchability.
 \end{itemize}
-
-Additionally a third test is conducted with the desired cold TES temperature of $390^{\circ}$C and the LFR low temperature unconstrained:
-
-\begin{itemize}
-    \item	$390^{\circ}$C: Unconstrained LFR cold inlet temperature allows for the desired cold TES to be achieved;
-\end{itemize}
-
-In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C.
-The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX, increasing dispatchability.
-\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets.
-Asp you will want to explain the criteria that go into cold storage temp.
-Lower = more delta T = more dispatchability -BW}
 
@@
 Another single cycle configuration is desired to allow dissimilar inlet temperatures for the CSP HX and LFR HX while additionally testing the effect that mixing flows downstream from the HTR has on cycle efficiency.
+
+In practice, sCO$_2$ cycles typically have 3 turbines, with 2 of these driving the compressor and recompressor.
+Therefore, this configuration will not in general require additional turbines compared to the C-1HTR1T-ON configuration.
+Furthermore, it is anticipated that the cost of the high temperature recuperator is likely most related to its volume, and hence having two smaller high temperature recuperators is unlikely to cost significantly more than one large one.
+
 This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines.
 The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR.
-The cycle with heat addition from the CSP also contains two separate turbines, diagrammatically shown as one turbine T2, while having a dedicated high temperature recuperator, HTR2.
+The cycle with heat addition from the CSP powers the other two turbines, which for modelling purposes are combined into a single turbine T2, while having a dedicated high temperature recuperator, HTR2.
 The two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine.
@@
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
-
-In practice, sCO$_2$ cycles typically have 3 turbines, with 2 of these driving the compressor and recompressor.
-Therefore, this configuration will not in general require additional turbines compared to the C-1HTR1T-ON configuration.
-Furthermore, it is anticipated that the cost of the high temperature recuperator is likely most related to its volume, and hence having two smaller high temperature recuperators is unlikely to cost significantly more than one large one.
 
@@
 The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually.
-C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%.
+C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8 percentage points.
 The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}.
@@
 A cold TES temperature of $410^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the $390^{\circ}$C and $440^{\circ}$C calculated values.
-Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the $440^{\circ}$C case gaining 0.35\%.
+Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the $440^{\circ}$C case gaining 0.35 percentage points.
 The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of $390^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.
@@
 The first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low temperature and C-CSP-ON $440^{\circ}$C cold TES cases.
-This combined efficiency yields a value of 46.05\%.
+This combined efficiency yields a value of 46.1\% (which is almost identical to the efficiency achieved by C-2HTR3T-ON shown in Table \ref{tab-noncharg}).
 The second combined configuration has a lower efficiency with favorable LFR characteristics and solar salt mass flow rate.
-This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON $390^{\circ}$C cold TES cases with a combined efficiency of 45.05\%.
+This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON $390^{\circ}$C cold TES cases with a combined efficiency of 45.1\%.
 
@@
 Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to $390^{\circ}$C.
-Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, $390^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases.
+Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, $390^{\circ}$C cold TES with an efficiency gain of 0.68 percentage points over the constrained cases.
 The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components.
@@
 Similarly to the studies done on C-1HTR1T-ON, the $440^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost.
-The $390^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases.
+The $390^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76 percentage points more than the constrained cases.
 Additionally, the sCO$_2$ LFR inlet temperature is $415.2^{\circ}$C, $15.2^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR efficiency.
@@
     \item	C-1HTR1T-ON: Single cycle configuration that is the least complex, therefore cost efficient and compact, with heat additions from the CSP and LFR in parallel.
-With both CSP and LFR discharging, combined cycle efficiency is reduced by ~0.8\% compared to the two cycle configuration.
+With both CSP and LFR discharging, combined cycle efficiency is reduced by ~0.8 percentage points compared to the two cycle configuration.
     \item   C-2HTR3T-ON: Single cycle configuration that has dedicated turbines and HTRs for the LFR and CSP.
@@
 The relative merits of C-2HTR3T-ON and C-1HTR1T-ON are therefore similar.
+It is noted that for the unconstrained case C-2HTR3T achieves almost identical performance to the two-cycle configuration, with an efficiency of 46.1\%, and hence the drop in performance relative to using separate cycles is attributable to the constraint on LFR inlet temperature being more limiting.
 \end{itemize}

### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
removed comments

@@
 Turbines and compressors are analyzed using isentropic efficiencies.
-Counter-flow heat exchangers are modelled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available.
+Counter-flow heat exchangers are modeled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available.
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
@@
 
-\mw{this is kind of an awkward way to describe what's happening. I think most readers are familiar with isentropic efficiencies and this can be omitted.-BW}
-
 \subsubsection{Black Box and Counter-Flow Heat Exchangers}
@@
 The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.
-
-\mw{This is for a single flow stream.
-Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream?
-Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$.
--BW}
 
@@
 
-\mw{If mass is conserved, use a single $\dot{m}$ - BW}
-
 Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$.
@@
 
-\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW}
-
 \subsubsection{Concentrating Solar Power Cycle}
@@
 The diagram for this CSP salt loop is seen in Figure \ref{csp}.
-
-\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}
 
@@
 Additionally, while the focus is on heat storage, and the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot TES.
-\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP?-BW}
 
@@
 %======================================================================================
-\mw{What do you mean by ``generalized?''-BW}
 
@@
 The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor.
-\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations.
-It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.-BW}
-\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
 The modeled cycles are summarized in Table \ref{tab-cycle_sum}.
@@
 The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.
-\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.-BW}
 
@@
 
-\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from-BW}
-\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page.
-I think it's a problem with the MDPI template.
-The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
 \end{paracol}
@@
 To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, is parametrically studied.
-\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
 Two cold TES temperatures are tested with constrained LFR low temperature of $400^{\circ}$C: 
@@
 The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR.
-The cycle with heat addition from the CSP powers the other two turbines, which for modelling purposes are combined into a single turbine T2, while having a dedicated high temperature recuperator, HTR2.
+The cycle with heat addition from the CSP powers the other two turbines, which for modeling purposes are combined into a single turbine T2, while having a dedicated high temperature recuperator, HTR2.
 The two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine.
@@
 Summing these power fractions together yields the total power of a singular turbine in the same position.
-\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.-BW} 
 After the high temperature recuperators, the two flows are combined and sent to the LTR hot side.
@@
 To quantify the effectiveness of TES charging techniques, Equation \ref{eq-eta-heatstorage} defines the heat storage efficiency, $\eta_{heatstorage}$.
-\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output -BW}
 
@@
 \ref{c-lfr-pre}.
-\mw{Careful here.
-Be precise about what ``excess'' means in this context.
-Any fluid above absolute zero technically has excess thermal energy if the reference is zero.
-Depending on this definition, not all excess energy from the turbine is stored in TES.
--BW}
-\mw{explain in a bit more detail what is happening that makes this configuration different from prior iterations. -BW}
 
@@
 
-A sensitivity study \mw{this is one study with two parameter values, right?
--BW} with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency.
+A sensitivity study with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency.
 The study considers two temperature values of $390^{\circ}$C and $440^{\circ}$C.
@@
 This subsection is encircled in blue and can be seen in Figure \ref{c-lfr-circ-sub}.
-
-\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}
 
@@
 The three non-charging cycle models have a focus on producing the highest positive alternator power to heat input, or cycle efficiency.
-The two-cycle configuration, composed of C-LFR-ON and C-CSP-ON, has independent recompression cycles with dedicated compressors, turbine, recuperators, and precooler for the LFR and CSP.
+The two-cycle configuration, composed of C-LFR-ON and C-CSP-ON, has independent recompression cycles with dedicated compressors, turbine, recuperators, and pre-cooler for the LFR and CSP.
 C-1HTR1T-ON, with the heat additions in parallel, and C-2HTR3T, with dedicated HTR for both heat additions, are cycles which incorporate the CSP and LFR in the same cycle.

### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

@@
 
-\end{paracol}
+% \end{paracol}
 \begin{figure}[H] 
@@
 
+A sensitivity study with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency.
+The study considers two temperature values of $390^{\circ}$C and $440^{\circ}$C.
+
+\clearpage
 \end{paracol}
@@
 
-A sensitivity study with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency.
-The study considers two temperature values of $390^{\circ}$C and $440^{\circ}$C.
-
 \subsubsection{C-LFR-CIRC} 
@@
 The full diagram for C-LFR-CIRC is shown in Figure \ref{c-lfr-circ}.
-
 \end{paracol}
@@
 
-\end{paracol}
+% \end{paracol}
 \begin{figure}[H]
     \widefigure
-    \includegraphics[width=8 cm]{Definitions/c-lfr-circ-sub.pdf}
+    \includegraphics[width=0.7\linewidth]{Definitions/c-lfr-circ-sub.pdf}
     \caption{Diagram for C-LFR-CIRC sub-cycle thermal energy storage charging orientation\label{c-lfr-circ-sub}}
 \end{figure}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
+% \begin{paracol}{2}
+% \linenumbers
+% \switchcolumn
 
@@
 
+The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
+Cycles that do not contain the listed component and omit the associated values.
+\clearpage 
+% \mw{Check that the column breakdown and grouping is correct in what I've changed.}
 \end{paracol}
@@
     %[htbp]
+
     \caption{Calculated system parameters for non-charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-noncharg}}
     \resizebox{\columnwidth}{!}{
-    \begin{tabular}{lccccccccccc}
+    \begin{tabular}{lc|cc|cc|ccc|ccc}
     \toprule
-     &  & \textbf{C-LFR-ON} & & \textbf{C-CSP-ON} &  &	\textbf{C-1HTR1T-ON} &	&	&	\textbf{C-2HTR3T-ON}	&	& \\
+     &  & \multicolumn{2}{c|}{\textbf{C-LFR-ON}} & \multicolumn{2}{c|}{\textbf{C-CSP-ON}}  &	\multicolumn{3}{c|}{\textbf{C-1HTR1T-ON}}	&	\multicolumn{3}{c}{\textbf{C-2HTR3T-ON}} \\
     \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C} & \textit{N/A} & \textit{N/A} &	\textit{U}	&	\textit{C}	&	\textit{C}	&	\textit{U}	&	\textit{C}	&	\textit{C}
@@
 \switchcolumn
-
-The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications.
-Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to $400^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
-Values listed in the Cold TES Temperature row are set to values of $390^{\circ}$C, $410^{\circ}$C, or $440^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
-Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.
 
@@
 
-\end{paracol}
+% \end{paracol}
+
 \begin{specialtable}[H]  
@@
     \resizebox{\columnwidth}{!}{
-    \begin{tabular}{lccccccc}
+        \begin{tabular}{lc|c|cc|ccc}
             \toprule
-     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
+            &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
             \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
@@
             Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
-    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
-    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
-    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
-    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
-    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
-    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
-    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
-    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
-    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
-    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
-    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
-    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
-    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
-    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
-    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
-    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
-    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
+            Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
+            MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
+            HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
             C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
@@
     \end{specialtable}
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
+    % \begin{paracol}{2}
+        % \linenumbers
+        % \switchcolumn
 
@@
 The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES.
-The hot TES is at a temperature of $560^{\circ}$C, with a $10^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least $570^{\circ}$C.
-In cases where the turbine outlet temperature is less than $570^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
-For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of $595^{\circ}$C.
+The hot TES is at a temperature of 560$^{\circ}$C, with a 10$^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}$C.
+In cases where the turbine outlet temperature is less than 570$^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger.
+For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}$C.
 With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
-As the temperature of the hot TES is raised above a value of $540^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
-The temperature in the hot TES is therefore set to a lower value of $540^{\circ}$C to allow for operation of this cycle.
+As the temperature of the hot TES is raised above a value of 540$^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
+The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$C to allow for operation of this cycle.
 With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.

### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/backmatter.tex
sort Ty's contribution and correct title (I think)

@@
 \authorcontributions{Conceptualization, B.L., M.W., C.S.
-and T.N.; methodology, B.L., M.W., C.S., T.N.
+and T.N.; methodology, B.W., M.W., C.S., T.N.
 and B.L.; software, B.W.; validation, B.L and M.W.; formal analysis, B.W.; investigation, B.W.; resources, M.W.
-and B.L.; data curation, B.W.; writing---original draft preparation, B.W.; writing---review and editing, B.L.
-and M.W.; visualization, B.W.; supervision, M.W and B.L.; project administration, B.L.; funding acquisition, B.L, M.W, C.S and T.N.
+and B.L.; data curation, B.W.; writing---original draft preparation, B.W.; writing---review and editing, B.L., M.W.
+and T.N.; visualization, B.W.; supervision, M.W and B.L.; project administration, B.L.; funding acquisition, B.L, M.W, C.S and T.N.
 All authors have read and agreed to the published version of the manuscript.}

### 2021-10-21 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
more minor formatting changes

@@
 
-\end{paracol}
+% \end{paracol}
 \begin{figure}[h]
@@
 
+The flow continues through a circulator which is assumed to have negligible pressure rise (i.e.
+there is assumed to be negligible pressure drop in this case).
+A heat exchanger, C2S, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
+Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of $400^{\circ}$C.
+Three different cold TES temperatures; $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C, are compared in a sensitivity study.
+
 % \end{paracol}
@@
 % \switchcolumn
-
-The flow continues through a circulator which is assumed to have negligible pressure rise (i.e.
-there is assumed to be negligible pressure drop in this case).
-A heat exchanger, C2S, extracts heat from the flow, storing the thermal energy in the hot TES for later use.
-Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of $400^{\circ}$C.
-Three different cold TES temperatures; $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C, are compared in a sensitivity study.
 
@@
     %[htbp]
-    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
+    \caption{Calculated system parameters for charging cycle configurations. All cases were evaluated with constrained (\textit{C}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
     \resizebox{\columnwidth}{!}{

### 2021-10-26 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
review edits on paper, word document in -> review response -> brian review is cover letter

@@
 
-Supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
+\replaced[comment={Abbreviation defined [4,1]}]{Supercritical carbon dioxide (sCO$_2$).}{Supercritical CO$_2$} Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid.
 Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.
@@
 Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}.
-Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar award for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}.
+Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar award for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated \replaced[comment={Abbreviations defined [4,1]}]{concentrating solar power (CSP) receiver, thermal energy storage (TES),.}{CSP receiver, TES,} and power block in one sCO$_2$ Brayton system \cite{seto_2015}.
 Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each.
-Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
-A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.
-Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}.
+\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR has a large system inertia on start-up and ramping while reducing strain on system components when consistently operating.}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
+A CSP has an array of mirrors concentrating solar rays towards a \replaced[comment={Furthering explanation of the CSP [3,1]}]{tower receiver, transferring the energy into a solar salt, and storing the solar salt in tanks.
+CSP systems require direct sunlight to operate at full power therefore causing variability based on weather conditions and time of day.}{receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.} Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}.
 Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases.
-With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch.
+With a comparable temperature to the hot TES, 560 $^{\circ}$C, a \replaced[comment={Abbreviation defined [4,1]}]{lead-cooled fast reactor (LFR).}{LFR} is capable of transferring heat to thermal storage for later dispatch.
 An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C.
@@
 %\end{quote}
+%\replaced[comment={better}]{asdf}{test}
 
@@
 Turbines and compressors are analyzed using isentropic efficiencies.
-Counter-flow heat exchangers are modeled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available.
+Counter-flow heat exchangers (HX) are modeled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data is available.
 The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
@@
 %--------------------------------------------------------------------------------------
-
 Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point and are modeled as a perfect heat transfer into or out of the cycle.
@@
 Counter-flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
-The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature.
-A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
+\replaced[comment={Improving counter-flow hx explanation [1,1]}]{The smallest temperature difference of the hot and cold flows on either the low or high end of the heat exchanger is defined as the approach temperature of the counter-flow heat exchanger.}{The temperatures of the hot and cold flows on either side of the heat exchanger have a temperature difference known as an approach temperature.} A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
 
@@
 In the modeled cases, the approach temperature is set to value of $10^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers \cite{seidel_2010_model_development}.
-The fluid libraries referenced are built into EES for Carbon Dioxide and Salt (60\% NaNO$_3$ 40\% KNO$_3$) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
+The fluid libraries referenced are built into \replaced[comment={Abbreviation defined [4,1]}]{Engineering Equation Solver (EES)}{EES} for Carbon Dioxide and Salt (60\% NaNO$_3$ 40\% KNO$_3$) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.
 
@@
 Knowing the state points on all inlets and outlets of the counter-flow heat exchanger allows for the heat exchanger performance metrics to be calculated.
-Performance metrics include effectiveness, capacitance ratio, UA, and NTU for heat exchangers.
-Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature.
+Performance metrics include \replaced[comment={Abbreviations defined [4,1]}]{effectiveness ($\varepsilon$), capacitance (CR), conductivity (UA), and number of transfer units (NTU).}{effectiveness, capacitance, UA, and NTU} for heat exchangers.
+Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, \replaced[comment={sentence proofread}]{a perfect heat exchanger has an effectiveness of one}{or a perfect heat exchanger} with no approach temperature.
 Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_{max}$ is found with the maximum enthalpy.
@@
 Where $C_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively.
-Specific heat is found using library correlations.
-Once both average capacitances are calculated for the hot and cold streams, one has a larger value, $\dot{C}_{max}$, and one has a smaller value,  $\dot{C}_{min}$.
+\replaced[comment={Improving counter-flow hx eplanation [1,1]}]{Specific heat is found using library correlations, with the average capacitance rate assumed to be constant during the analysis.
+Assuming constant average capacitance rate is suitable for most engineering purposes, especially when there is uncertainty associated with other parameters \cite{nellis_klein_2008}.}{Specific heat is found using library correlations.} Once both average capacitances are calculated for the hot and cold streams, one has a larger value, $\dot{C}_{max}$, and one has a smaller value,  $\dot{C}_{min}$.
 These maximum and minimum values are used to find the capacitance ratio, $CR$, in Equation \ref{cap_ratio}.
@@
 The lead flow velocity is limited by the erosion of the fuel, the slower the lead flow velocity reduces fuel erosion and therefore leads to a more desirable compact design.
-Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.
-LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
+\replaced[comment={Edited sentence for clarity [2,3]}]{Restricting the lead flow velocity, and therefore lead mass flow rate, while lowering the inlet sCO$_2$ temperature increases the temperature difference across the LFR HX allowing for a higher, more desirable, LFR power output.}{Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.} LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
 When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in power conversion cycle thermodynamic efficiency but a reduction in LFR power below $950$ MW.
@@
 
-The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-salt counter-flow heat exchanger (C2S), and CSP counter-flow heat exchanger (CSP HX).
+The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage \replaced[comment={Removed Abbreviation [4,1]}]{}{(TES)}, pumps, receiver, sCO$_2$-to-salt counter-flow heat exchanger (C2S), and CSP counter-flow heat exchanger (CSP HX).
 The diagram for this CSP salt loop is seen in Figure \ref{csp}.
@@
 This is achieved through the C2S being turned off for direct electrical production from the LFR and the hot TES is discharging heat through the CSP HX for electrical production in the sCO$_2$ Brayton cycle.
-As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.
-During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S.
+\replaced[comment={Edited sentence, CSP still charges the hot TES during low grid demand periods [2,4]}]{As grid demand diminishes, electrical generation is ramped down by decreasing heat input through the CSP HX.
+This continues until no heat is being dispatched from the solar salt to the sCO$_2$, and all produced thermal energy from the CSP is put into charging the hot TES.}{As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.} During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S.
 This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.
@@
 The values displayed in Table \ref{tab-cycle-constants} are representative of CSP and the Westinghouse LFR.
+\replaced[comment={Elaborated on table variable names [2,5]}]{In Table \ref{tab-cycle-constants}, variable names require further explanation.
+The high side pressure with the variable label $P_{2A}$, is the constant pressure outlet on the compressors and inlet to the turbines.
+In all models the value is set by the outlet of the main compressor and held constant with the assumption that there is no pressure drop across heat exchangers.
+In addition to this pressure, temperatures are also set.
+The inlet temperature of the main compressor, $T_{1A}$, is set to a value of $40^{\circ}$C in all models.
+The temperature of the sCO$_2$ on the outlet of the LFR HX has different variable names, T$_5$, T$_{2C}$, T$_{6A}$, and T$_{5C}$, according to the associated cycle configuration diagram.}{}.
 
 In addition to standardized parameters, all cycles have identical recompression sides.
-The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor.
+The recompression side contains a  \replaced[comment={Abbreviations defined [4,1]}]{precooler (PC), low temperature recuperator (LTR), and two compressors; main compressor (MC) and recompressor (RC)}{precooler, low temperature recuperator, and two compressors; main compressor and recompressor}.
 The modeled cycles are summarized in Table \ref{tab-cycle_sum}.
@@
 Therefore, this configuration will not in general require additional turbines compared to the C-1HTR1T-ON configuration.
-Furthermore, it is anticipated that the cost of the high temperature recuperator is likely most related to its volume, and hence having two smaller high temperature recuperators is unlikely to cost significantly more than one large one.
+Furthermore, it is anticipated that the cost of the high temperature recuperator (HTR) is likely most related to its volume, and hence having two smaller high temperature recuperators is unlikely to cost significantly more than one large one.
 
@@
 For all cycle configurations presented, with constrained or unconstrained LFR low temperature inlet and varied cold TES temperature, cycle and heat storage efficiencies are maximized using parametric studies on flow splitter fractions.
-These results are obtained using standardized values found in Table \ref{tab-cycle_sum} for a more direct comparison between cycles.
+\replaced[comment={Source of calculations defined [4,3]}]{All calculations were carried out using EES, with the results}{These results are} obtained using standardized values found in Table \ref{tab-cycle_sum} for a more direct comparison between cycles.
 Presentation and discussion of the results is fulfilled in the following section.
@@
 Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
-Cycles that do not contain the listed component and omit the associated values.
+\replaced[comment={Removed the conjunction 'and' in the sentence for clarity.
+[1,1]}]{Cycles that do not contain the listed component omit the associated values.}{Cycles that do not contain the listed component and omit the associated values.}
 \clearpage 

### 2021-10-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
backing up

@@
 Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each.
-\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR has a large system inertia on start-up and ramping while reducing strain on system components when consistently operating.}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
+\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does no incoporate thermal energy storage for meeting peak demand}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
 A CSP has an array of mirrors concentrating solar rays towards a \replaced[comment={Furthering explanation of the CSP [3,1]}]{tower receiver, transferring the energy into a solar salt, and storing the solar salt in tanks.
@@
 Counter-flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side.
-\replaced[comment={Improving counter-flow hx explanation [1,1]}]{The smallest temperature difference of the hot and cold flows on either the low or high end of the heat exchanger is defined as the approach temperature of the counter-flow heat exchanger.}{The temperatures of the hot and cold flows on either side of the heat exchanger have a temperature difference known as an approach temperature.} A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
+\replaced[comment={Improving counter-flow hx explanation [1,1]}]{The smallest temperature difference of the hot and cold flows on either the low or high end of the heat exchanger is defined as the approach temperature of the counter-flow heat exchanger and a calculation is performed to identify whether the hot end of cold end is limiting}{The temperatures of the hot and cold flows on either side of the heat exchanger have a temperature difference known as an approach temperature.} A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.
 
@@
 Where $C_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively.
-\replaced[comment={Improving counter-flow hx eplanation [1,1]}]{Specific heat is found using library correlations, with the average capacitance rate assumed to be constant during the analysis.
-Assuming constant average capacitance rate is suitable for most engineering purposes, especially when there is uncertainty associated with other parameters \cite{nellis_klein_2008}.}{Specific heat is found using library correlations.} Once both average capacitances are calculated for the hot and cold streams, one has a larger value, $\dot{C}_{max}$, and one has a smaller value,  $\dot{C}_{min}$.
+\replaced[comment={Improving counter-flow hx explanation [1,1]}]{Specific heat is found using library correlations, with the average capacitance rate assumed to be constant during the analysis.}{Specific heat is found using library correlations.} Once both average capacitances are calculated for the hot and cold streams, one has a larger value, $\dot{C}_{max}$, and one has a smaller value,  $\dot{C}_{min}$.
 These maximum and minimum values are used to find the capacitance ratio, $CR$, in Equation \ref{cap_ratio}.
@@
 \end{equation}
+
+\replaced[comment={Improving counter-flow hx explanation [1,1]}]{Assuming constant average capacitance rate is suitable for most engineering purposes, especially when there is uncertainty associated with other design parameters \cite{nellis_klein_2008}.
+To ensure that there is no internal pinch point, the temperatures of the hot and cold streams as a function of dimensionless length in the LTR and HTR are shown in Figure \ref{graph-t-vs-p-ltr} and Figure \ref{graph-t-vs-p-htr} respectively.
+Additionally, the specific heat as a function of dimensionless length of the hot and cold streams in the LTR and HTR are plotted in Figure \ref{graph-c-vs-p-ltr} and Figure \ref{graph-c-vs-p-htr} respectively.}{}
+
+\begin{figure*}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{Definitions/c-vs-p-ltr.pdf}
+        \caption[]%
+        {{\small Specific heat as a function of location for LTR}}
+        \label{graph-c-vs-p-ltr}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{Definitions/t-vs-p-ltr.pdf}
+        \caption[]%
+        {{\small Temperature as a function of location for LTR}}
+        \label{graph-t-vs-p-ltr}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{Definitions/c-vs-p-htr.pdf}
+        \caption[]%
+        {{\small Specific heat as a function of location for HTR}}
+        \label{graph-c-vs-p-htr}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{Definitions/t-vs-p-htr.pdf}
+        \caption[]%
+        {{\small Temperature as a function of location for HTR}}
+        \label{graph-t-vs-p-htr}
+    \end{subfigure}
+    \caption{Specific heats and temperatures of hot and cold streams as a function of dimensionless location for the low temperature recuperator and high temperature recuperator}
+    \label{graphs-t-c-vs-p} 
+\end{figure*}
+
+\replaced{The calculations used to discretize the counter-flow heat exchangers into sub-heat exchanger models is from JJ Dyreby's 2014 PhD thesis \cite{dyreby_2014}.}{}
 
@@
 The lead flow velocity is limited by the erosion of the fuel, the slower the lead flow velocity reduces fuel erosion and therefore leads to a more desirable compact design.
-\replaced[comment={Edited sentence for clarity [2,3]}]{Restricting the lead flow velocity, and therefore lead mass flow rate, while lowering the inlet sCO$_2$ temperature increases the temperature difference across the LFR HX allowing for a higher, more desirable, LFR power output.}{Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.} LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
+\replaced[comment={Edited sentence for clarity [2,3]}]{At constant lead velocity (and hence mass flow rate), reducing sCO$_2$ inlet temperature allows for a higher lead delta T in the LFR core and hence a higher thermal power output}{Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.} LFR sCO$_2$ inlet temperature has a lower bound of $340^{\circ}$C before the lead begins to freeze, which is operationally unacceptable.
 When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in power conversion cycle thermodynamic efficiency but a reduction in LFR power below $950$ MW.
@@
 This is achieved through the C2S being turned off for direct electrical production from the LFR and the hot TES is discharging heat through the CSP HX for electrical production in the sCO$_2$ Brayton cycle.
-\replaced[comment={Edited sentence, CSP still charges the hot TES during low grid demand periods [2,4]}]{As grid demand diminishes, electrical generation is ramped down by decreasing heat input through the CSP HX.
-This continues until no heat is being dispatched from the solar salt to the sCO$_2$, and all produced thermal energy from the CSP is put into charging the hot TES.}{As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.} During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S.
-This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.
+\replaced[comment={Edited sentence to clarify that the CSP charges the hot TES during low grid demand periods [2,4]}]{As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.
+During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S, supplementing the heat produced by the CSP which is also used to charge the TES.
+This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.}{As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging.
+During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S.
+This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.}
 

### 2021-10-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

@@
 \replaced[comment={Improving counter-flow hx explanation [1,1]}]{Assuming constant average capacitance rate is suitable for most engineering purposes, especially when there is uncertainty associated with other design parameters \cite{nellis_klein_2008}.
+To justify the assumption of constant average capacitance rate, two graphs for the LTR and HTR are plotted.
 To ensure that there is no internal pinch point, the temperatures of the hot and cold streams as a function of dimensionless length in the LTR and HTR are shown in Figure \ref{graph-t-vs-p-ltr} and Figure \ref{graph-t-vs-p-htr} respectively.
-Additionally, the specific heat as a function of dimensionless length of the hot and cold streams in the LTR and HTR are plotted in Figure \ref{graph-c-vs-p-ltr} and Figure \ref{graph-c-vs-p-htr} respectively.}{}
+Additionally, to confirm approximate linearity of specific heats at differential steps throughout the counter-flow heat exchanger, the specific heat as a function of dimensionless length of the hot and cold streams in the LTR and HTR are plotted in Figure \ref{graph-c-vs-p-ltr} and Figure \ref{graph-c-vs-p-htr} respectively.}{}
 
@@
 
-\replaced{The calculations used to discretize the counter-flow heat exchangers into sub-heat exchanger models is from JJ Dyreby's 2014 PhD thesis \cite{dyreby_2014}.}{}
+\replaced[comment={Improving counter-flow hx explanation [1,1]}]{The calculations used to discretize the counter-flow heat exchangers into a sub-heat exchanger model, shown in Figure \ref{graphs-t-c-vs-p}, is from JJ Dyreby's (2014) PhD thesis \cite{dyreby_2014}.
+The series of figures are constructed using extreme values experienced by the recuperators; the cold inlet temperature is lowest recorded value, and the hot inlet temperature is the highest recorded value.
+As seen in the presented graphs, the capacitance ratio determines the approach temperature, not an internal pinch point in the recuperator.
+All pinch points recorded are on the high end.}{}
 

### 2021-10-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
does no->does not

@@
 Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each.
-\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does no incoporate thermal energy storage for meeting peak demand}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
+\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does not incoporate thermal energy storage for meeting peak demand}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
 A CSP has an array of mirrors concentrating solar rays towards a \replaced[comment={Furthering explanation of the CSP [3,1]}]{tower receiver, transferring the energy into a solar salt, and storing the solar salt in tanks.

### 2021-11-08 simulations/scripts/PySAM_model1_sweep.py
cory value for extra bop cost. convert to Rankine cycle

@@ -36,11 +36,10 @@ dispatch_data=np.array(dispatch_data)
 # create empty dictionary for results
 results={}
 
-#two turbine max fractions
 p_refs=[465,525,600,700,800]
 cycle_max_fracs=[1.05]
 remove_tes_costs=[False]
-exaggerates=[1,1.5,2]
+exaggerates=[1]#,1.5,2] 
 for p_ref in p_refs:
     results[p_ref]={}
     
@@ -64,13 +63,12 @@ for p_ref in p_refs:
                 with open("../json/model1.json") as f:
                     base_sim = json.load(f)
                 
-                turbine_exponent = 0.83 #turbine cost vs size. Clara Lloyd thesis
-                turbine_cost = 100 #$/kWe Figure VI.2 of Clara Lloyd thesis. CHECK WITH CORY! Could be on low side from other referenes
-                ref_turbine_size = 950*base_sim["SSC_inputs"]["design_eff"]
-                turbine_premium = turbine_cost*((p_ref/ref_turbine_size)**turbine_exponent-1)
+                turbine_unit_cost = 225 #Cory email 8th Nov 2021
+                turbine_ref = 950*base_sim["SSC_inputs"]["design_eff"]
+                turbine_premium = turbine_unit_cost*(p_ref-turbine_ref)
                 
-                #add on the turbine premium !!!NO- but then scale down to ensure that plant cost is linked to reactor rating not turbine
-                base_sim["SSC_inputs"]["nuclear_spec_cost"]=(4500+turbine_premium)*(ref_turbine_size)/p_ref
+                #add on the turbine premium - but then scale down to ensure that plant cost is linked to reactor rating not turbine
+                base_sim["SSC_inputs"]["nuclear_spec_cost"]=(4500*turbine_ref+turbine_premium)/p_ref
                 print(base_sim["SSC_inputs"]["nuclear_spec_cost"])
                 
                 if remove_tes_cost:
@@ -91,7 +89,7 @@ for p_ref in p_refs:
                         f.write("{:.5f}\n".format(item))
                 
                 #sweep the TS Hours 
-                for tshours in range(6 if p_ref >465 else 1):
+                for tshours in range(1): #6 if p_ref >465 else 1):
                     
                     base_sim["SSC_inputs"]["tshours"]=tshours
                     
@@ -99,9 +97,12 @@ for p_ref in p_refs:
                     #Add on extra cost of big turbine and TES
                     yrs=4.0
                     rate=0.07
[…]

### 2021-11-09 papers/sustainability-1425053/sustainability-1425053-english.tex
added paper to repository from MDPI

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[sustainability,article,accept,moreauthors,pdftex]{Definitions/mdpi} 
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{mwe}
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, appliedchem, applmech, applmicrobiol, applnano, applsci, arts, asi, atmosphere, atoms, audiolres, automation, axioms, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomechanics, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, brainsci, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coatings, colloids, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, crops, cryptography, crystals, curroncol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forensicsci, forests, fractalfract, fuels, futureinternet, futuretransp, futurepharmacol, futurephys, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, land, languages, laws, life, liquids, literature, livers, logistics, lubricants, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, metabolites, metals, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, minerals, mining, modelling, molbank, molecules, mps, mti, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photochem, photonics, physchem, physics, physiolsci, plants, plasma, pollutants, polymers, polysaccharides, proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, systems, taxonomy, technologies, telecom, textiles, thermo, tourismhosp, toxics, toxins, transplantology, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wevj, women, world

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2021}
\externaleditor{Academic Editor: \hl{Firstname Lastname}} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{\hl{date}} 
\dateaccepted{\hl{date}} 
\datepublished{\hl{date}} 
\hreflink{https://doi.org/} % If needed use \linebreak
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Modeling of Combined Lead Fast Reactor and Concentrating Solar Power Supercritical Carbon Dioxide Cycles to Demonstrate Feasibility, Efficiency Gains, and Cost Reductions}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Modeling of Combined Lead Fast Reactor and Concentrating Solar Power Supercritical Carbon Dioxide Cycles to Demonstrate Feasibility, Efficiency Gains, and Cost Reductions}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-1015-7605} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-2128-4658} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
%\dagger -> adds dagger
%\ddagger -> adds double dagger
\Author{\hl{Brian White} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.
 $^{1}$, Michael Wagner~$^{1}$\orcidB{}, Ty Neises~$^{3}$, Cory Stansbury~$^{4}$ and Ben Lindley~$^{2,}$*\orcidA{}}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Brian White, Michael Wagner, Ty Neises, Cory Stansbury and Ben Lindley}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{White, B.; Wagner, M.; Neises, T.; Stansbury, C.; Lindley, B.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Mechanical Engineering, University of Wisconsin---Madison, 1415 University Drive, \mbox{Madison, WI 53706, USA;} bwhite24@wisc.edu (B.W.); mjwagner2@wisc.edu (M.W.)\\
$^{2}$ \quad Department of Engineering Physics, University of Wisconsin---Madison, 1500 Engineering Drive, \mbox{Madison, WI 53706, USA}\\
$^{3}$ \quad National Renewable Energy Laboratory, Thermal Systems Group, 15013 Denver West Parkway, \mbox{Golden, CO 80401, USA;} ty.neises@nrel.gov\\
$^{4}$ \quad Westinghouse Electric Company, Lead Fast Reactor Systems Development, 1000 Westinghouse Dr, \mbox{Cranberry Twp, PA 16066, USA;} stansbca@westinghouse.com}

% Contact information of the corresponding author
\corres{Correspondence: lindley2@wisc.edu; Tel.: +1-608-265-2001}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Solar power has innate issues with weather, grid demand and time of day, which can be mitigated through use of thermal energy storage for concentrating solar power (CSP). Nuclear reactors, including lead-cooled fast reactors (LFRs), can %\replaced[comment={Revised sentence for readability [2,1]}]
{adjust power output according to demand; but with high fixed costs and low operating costs, there may not be sufficient economic incentive to make this worthwhile.} %{load follow, but have high fixed and low operating costs which can make this economically unattractive.}  
We investigate potential synergies through coupling CSP and LFR together in a single supercritical CO$_2$ Brayton cycle and/or using the same thermal energy storage. Combining these cycles allows for the LFR to thermally charge the salt storage in the CSP cycle during low-demand periods to be dispatched when grid demand increases.  The LFR/CSP coupling into one cycle is modeled to find the preferred location of the LFR heat exchanger, CSP heat exchanger, sCO$_2$-to-salt heat exchanger (C2S), turbines, and recuperators within the supercritical CO$_2$ Brayton cycle. Three cycle configurations have been studied: two-cycle configuration, which uses CSP and LFR heat for dedicated turbocompressors, has the highest efficiencies but with less component synergies; a combined cycle with CSP and LFR heat sources in parallel is the simplest with the lowest efficiencies; and a combined cycle with separate high-temperature recuperators for both the CSP and LFR is a compromise between efficiency and component synergies. Additionally, four thermal energy storage charging techniques are studied: the turbine positioned before C2S, requiring a high LFR outlet temperature for viability; the turbine after the C2S, reducing turbine inlet temperature and therefore power; the turbine parallel to the C2S producing moderate efficiency; and a dedicated circulator loop. While all configurations have pros and cons, use of a single cycle offers component synergies with limited efficiency penalty. Using a turbine in parallel with the C2S heat exchanger is feasible but results in a low charging efficiency, while a dedicated circulator loop offers flexibility and near-perfect heat storage efficiency but increasing cost with additional cycle components.
}

%{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusion: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{supercritical carbon dioxide Brayton cycle; concentrating solar power (CSP); lead fast reactor (LFR); cogeneration; complimentary cycle; thermal energy storage (TES)} 
%List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Define fixed-width column types. Use as:
% \begin{tabular}{L{0.5\linewidth}cc}
% ... for example
\newcolumntype{L}[1]%
{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]%
{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]%
{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage[commentmarkup=uwave%
%,final%    <<< uncomment this line to render with changes and remove comments
]{changes}
\usepackage{xspace}
\usepackage{adjustbox}

\definechangesauthor[color=blue!80!black]{MW}
\definechangesauthor[color=red!80!black]{BL}
\newcommand{\mw}[1]{\comment[id=MW]{#1}}
\newcommand{\bl}[1]{\comment[id=BL]{#1}}

% \renewcommand{\added}[1]{\xspace{#1}\xspace}
% \renewcommand{\mw}[1]{\xspace}
% \renewcommand{\bl}[1]{\xspace}
% \renewcommand{\deleted}[1]{\xspace}
% \renewcommand{\replaced}[2]{\xspace{#1}\xspace}

\usepackage{subcaption}

\begin{document}

%\input{content.tex}

%\section{How to Use this Template}

%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.  %Please use the command \citep{} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%\replaced[comment={Abbreviation defined [4,1]}]
{Supercritical carbon dioxide (sCO$_2$).}
%{Supercritical CO$_2$} 
Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and~reduced turbomachinery cost while operating with non-toxic working fluid. Various sCO$_2$ Brayton cycles have been modeled, with the recompression cycle having efficiency advantages over other proposed cycle arrangements~\cite{turchi_2013,ahn_2014,wang_2018}. The~literature shows that the recompression cycle can reach efficiencies of 50\% in some scenarios (with turbine inlet temperatures in the 650--700 $~^{\circ}$C range) \cite{turchi_2013,wright_2009}, allowing these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures. Due to the benefits of sCO$_2$ Brayton cycles, the~United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar~\cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar award for demonstration and performance verification of a sCO$_2$ Brayton cycle~\cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated %\replaced[comment={Abbreviations defined [4,1]}]
{concentrating solar power (CSP) receiver, thermal energy storage (TES),}
%{CSP receiver, TES,} 
and power block in one sCO$_2$ Brayton system~\cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. %\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]
{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does not incoporate thermal energy storage for meeting peak demand}
Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and~thermal storage for high dispatchability during high-grid-demand periods. 
A CSP has an array of mirrors concentrating solar rays towards a %\replaced[comment={Furthering explanation of the CSP [3,1]}]
{tower receiver, transferring the energy into a solar salt, and~storing the solar salt in tanks. CSP systems require direct sunlight to operate at full power, therefore causing variability based on weather conditions and time of day.}
%{receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.}
 Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high-temperature thermal energy storage~\cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With~a comparable temperature to the hot TES, 560 $~^{\circ}$C, a~%\replaced[comment={Abbreviation defined [4,1]}]
{lead-cooled fast reactor (LFR).}
%{LFR} 
is capable of transferring heat toy thermal storage for later dispatch. An~LFR uses fission reactions to heat a heat transfer fluid, in~this case liquid lead, to~temperatures of 650 $~^{\circ}$C. Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles~\cite{dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles has been performed at Sandia National Laboratories~\cite{wright_2011} and in Korea~\cite{cha_2016}, with~at least two commercial companies (Echogen, Net Power) having progressed to building pilot cycles~\cite{held_2015,fetvedt_2016}.

Various studies on complimentary solar-nuclear systems have been accomplished with several reviewed as follows:

\begin{itemize}
    \item	Monnerie~et~al. (2011): In search of an alternative to the typical fossil fuel-based process, reports on synthesizing hydrogen with complimentary solar-nuclear technologies being utilized as consistent heat sources for chemical decomposition of sulphuric acid to aid in simple, low-temperature electrolysis~\cite{monnerie_2011}. 
    \item   Curtis J.D. (2015): Massachusetts Institute of Technology thesis reports cycle configuration, performance, and~development of complimentary solar-nuclear systems with a focus on shale oil extraction and production from kerogen deposits~\cite{curtis_2015}. 
    \item   Wang~et~al. (2020): Implements a combined solar and nuclear plant discussing a sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility~\cite{wang_2020}. 
\end{itemize}

The economic and physical feasibility of producing shale oil and hydrogen with complimentary solar-nuclear cycles, as~discussed in the Curtis J.D. (2015) thesis and Monnerie~et~al. (2011) article, is not within the scope of sCO$_2$ Brayton recompression cycle electrical generation and storage presented in this~paper.

The single-cycle configuration in Wang~et~al. (2020) has a higher-temperature operating salt, 67\%KCl\hl{--}33\%MgCl$_2$, as~the heat transfer fluid in the CSP which is capable of temperatures in the range of 450--1400 $~^{\circ}$C. The~lower operating point of the studied solar salt in this paper, 60\%NaNO$_3$\hl{--}40\%KNO$_3$ %does it should be en dash?
with a temperature range of 250--585 $~^{\circ}$C, is employed because the technology is more established when compared to KCl-MgCl$_2$ \cite{turchi_2018}. The~higher temperature salt requires preheating which is achieved prior to the CSP heat addition by a small modular lead-cooled fast reactor. The~small modular LFR operates at a low temperature and a fixed location when compared to the higher temperature lead and variable location that the Westinghouse LFR studied in this paper is capable of. Due to the similar operating temperatures of the CSP and LFR, multiple cycle configurations are studied that are not possible with the similar components in Wang~et~al. (2020). Specifically studied in this paper are the effects on cycle and heat storage efficiency of different cycle configurations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique. This paper provides an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle. Additionally, the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied with the results~discussed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and~Methods}

%Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

%Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

%Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
%\begin{quote}
%This is an example of a quote.
%\end{quote}
%\replaced[comment={better}]{asdf}{test}

% **************************************

\subsection{Cycle Component~Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques and are discussed in more detail below. Turbines and compressors are analyzed using isentropic efficiencies. Counter-flow heat exchangers (HX) are modeled using the effectiveness-NTU method while simplified ``black box'' heat exchangers that use a simple energy balance for state point calculations are used in lieu of more detailed component models where data are available. The~lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The~molten salt loop for the CSP is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat~exchangers.

\subsubsection{Turbines and~Compressors }
%--------------------------------------------------------------------------------------

Turbines and compressors are modeled for each cycle using constant isentropic efficiency values which are summarized in Table~\ref{tab-cycle-constants}. Turbines take the high-pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$. The~turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and~have single inlet and outlet streams. Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor are calculated~\cite{klein_nellis_2011}.

\subsubsection{Black Box and Counter-Flow Heat~Exchangers}
%--------------------------------------------------------------------------------------
Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point and are modeled as a perfect heat transfer into or out of the cycle. These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and~mass flow outlet energy. The~energy balance equation used for all black box heat exchangers is Equation~(\ref{eq-black}).
\begin{equation}
    \label{eq-black}
    \dot{m} \cdot h_{in} + \dot{Q}_{HX} = \dot{m} \cdot h_{out} ,
\end{equation}

In this equation, the energy input to the system is on the left hand side with $\dot{m}$ multiplied by $h_{in}$ being energy from the mass flow while $\dot{Q}_{HX}$ is heat transfer directly into, positive, or~out of, negative, the~flow from an outside source. The~right hand side of the equation is heat leaving the black box heat exchanger with $\dot{m}$ and enthalpy of $h_{out}$. Black box energy balances are used in three situations, the~receiver, LFR heat exchanger, and~pre-cooler heat exchanger. These heat exchangers are not exhaustively modeled because the state points on the inlet and outlet are defined by design~parameters.

Counter-flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side. %\replaced[comment={Improving counter-flow hx explanation [1,1]}]
{The smallest temperature difference of the hot and cold flows on either the low or high end of the heat exchanger is defined as the approach temperature of the counter-flow heat exchanger and a calculation is performed to identify whether the hot end of cold end is limiting}
%{The temperatures of the hot and cold flows on either side of the heat exchanger have a temperature difference known as an approach temperature.} 
A diagram showing a simplified counter-flow heat exchanger is illustrated in Figure~\ref{counter-flow-hx}.

% \end{paracol}
\begin{figure}[H]
    %\widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simplified counter-flow heat exchanger~diagram. \label{counter-flow-hx}}
\end{figure}
% \begin{paracol}{2}
% %\linenumbers
% \switchcolumn

Additional assumptions of the counter-flow heat exchanger model are: no heat loss to the surroundings, no pressure drops across the heat exchangers, and~no fouling resistances. In~Figure~\ref{counter-flow-hx}, the subscript 'out' denotes where the streams are leaving, 'in' denotes the entering streams, 'c' and 'h' signify cold and hot streams respectively, $\dot{Q}_{HX}$ is the total heat transfer from the hot to cold stream, and~$\dot{Q}_{surr}$ is the heat transfer to the~surroundings.

Counter-flow heat exchanger calculations require two known state points, fluid properties, mass flow rate of hot and cold side, and~a specified approach temperature. In~the modeled cases, the~approach temperature is set to value of $10~^{\circ}$C, based off prior model development of sCO$_{2}$ Brayton cycle heat exchangers~\cite{seidel_2010_model_development}. The~fluid libraries referenced are built into %\replaced[comment={Abbreviation defined [4,1]}]
{Engineering Equation Solver (EES)}
%{EES} 
for Carbon Dioxide and Salt (60\% NaNO$_3$ 40\% KNO$_3$) \cite{pacheco_1995_salt_properties,roland_1996_CO$_2$_properties}.

To analyze the counter-flow heat exchanger, a side is chosen, usually the high side, to~start the calculations. The~approach temperature is initially subtracted from the hot stream on the high-temperature side to find the missing cold temperature according to \mbox{Equation (\ref{temp_h}).}
\begin{equation}
   \label{temp_h}
    T_{out,c} = T_{in,h}-\Delta_{T},
\end{equation}
where T$_{out,c}$ is the cold stream outlet temperature and T$_{in,h}$ is the hot stream inlet temperature. Knowing the two state points allows for the enthalpy out to be found using correlations from the fluid property libraries. This enthalpy then allows for the heat transfer of the heat exchanger to be found with Equation~(\ref{heattrans_h}).
\begin{equation}
    \label{heattrans_h}
     \dot{Q}_{HX} = \dot{m}_{c}(h_{out,c}-h_{in,c}),
 \end{equation}
where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and~$h_{in,c}$ is the inlet of the cold side.
 The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is accomplished with Equation~(\ref{enthalpy_h}).
\begin{equation}
    \label{enthalpy_h}
     h_{out,h} = h_{in,h} - \frac{\dot{Q}_{HX}}{\dot{m}_{h}},
 \end{equation}

Knowing the hot stream enthalpy out allows for all states to be set on the outlets and inlets of the counter-flow heat exchanger. The~temperature difference of the low side is then checked to ensure that it is larger than the approach temperature, defined at $10~^\circ$C. If~the temperature difference on the low side is smaller than the approach temperature, the~same computations are carried with the low side as the starting~point.

Knowing the state points on all inlets and outlets of the counter-flow heat exchanger allows for the heat exchanger performance metrics to be calculated. Performance metrics include %\replaced[comment={Abbreviations defined [4,1]}]
{effectiveness ($\varepsilon$), capacitance (CR), conductivity (UA), and~number of transfer units (NTU).}
%{effectiveness, capacitance, UA, and NTU} 
for heat exchangers. Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, %\replaced[comment={sentence proofread}]
{a perfect heat exchanger has an effectiveness of one}
%{or a perfect heat exchanger} 
with no approach temperature. Assuming the approach temperature is on the high side, the~maximum heat transfer rate, $\dot{Q}_{max}$ is found with the maximum enthalpy. Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet. Using the maximum enthalpy, $h_{max}$, the~maximum heat transfer rate is calculated using Equation~(\ref{heattrans_max}).
\begin{equation}
    \label{heattrans_max}
    \dot{Q}_{max} = \dot{m}_{c}(h_{max}-h_{in,c}),
\end{equation}

Calculating the maximum heat transfer rate allows for effectiveness to be calculated using the ratio in Equation~(\ref{effective}).
\begin{equation}
    \label{effective}
    \varepsilon = \frac{\dot{Q}_{HX}}{\dot{Q}_{max}},
\end{equation}

All of the prior equations are carried out in a built-in function within EES. EES is an iterative solver, and therefore as long as there is a feasible solution, the~functions can take any of the four state points around the heat exchanger and converge on a~solution.

After the effectiveness is solved for, capacitance ratio is necessary. The~capacitance ratio is defined as the average minimum capacitance rate, $\dot{C}_{min}$, over~the average maximum capacitance rate, $\dot{C}_{max}$. Average capacitance rates for the hot and cold streams are found by multiplying the addition of the specific heat at the inlet and outlet of the stream by the mass flow and dividing by two as shown in Equation~(\ref{avg_cap}).
\begin{equation}
    \label{avg_cap}
    \dot{C}_{avg} = \frac{\dot{m}(c_{in}+c_{out})}{2},
\end{equation}
where $C_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively. %\replaced[comment={Improving counter-flow hx explanation [1,1]}]
{Specific heat is found using library correlations, with~the average capacitance rate assumed to be constant during the analysis.}
%{Specific heat is found using library correlations.} 
Once both average capacitances are calculated for the hot and cold streams, one has a larger value, $\dot{C}_{max}$, and~one has a smaller value,  $\dot{C}_{min}$. These maximum and minimum values are used to find the capacitance ratio, $CR$, in~Equation~(\ref{cap_ratio}).
\begin{equation}
    \label{cap_ratio}
    CR = \frac{\dot{C}_{min}}{\dot{C}_{max}},
\end{equation}

%\replaced[comment={Improving counter-flow hx explanation [1,1]}]
{Assuming constant average capacitance rate is suitable for most engineering purposes, especially when there is uncertainty associated with other design parameters~\cite{nellis_klein_2008}. To~justify the assumption of constant average capacitance rate, two graphs for the LTR and HTR are plotted. To~ensure that there is no internal pinch point, the~temperatures of the hot and cold streams as a function of dimensionless length in the LTR and HTR are shown in Figure~\ref{graphs-t-c-vs-p}b,d respectively. Additionally, to~confirm approximate linearity of specific heats at differential steps throughout the counter-flow heat exchanger, the~specific heat as a function of dimensionless length of the hot and cold streams in the LTR and HTR are plotted in Figure~\ref{graphs-t-c-vs-p}a,c respectively.}%{}

%\replaced[comment={Improving counter-flow hx explanation [1,1]}]
{The calculations used to discretize the counter-flow heat exchangers into a sub-heat exchanger model, shown in Figure~\ref{graphs-t-c-vs-p}, is from Dyreby~\cite{dyreby_2014}. Figure~\ref{graphs-t-c-vs-p} is constructed using the most extreme temperature values experienced by the recuperators---the cold inlet and hot outlet are the lowest and highest modeled temperature values, respectively. As~demonstrated, the~capacitance ratio determines the approach temperature instead of any possible internal pinch point within the recuperator. All pinch points recorded are on the high-temperature end.}{}
\end{paracol}

\clearpage
\begin{figure}[H]
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Definitions/c-vs-p-ltr.pdf}
        \caption[]%
        {{\small }}
        \label{graph-c-vs-p-ltr}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Definitions/t-vs-p-ltr.pdf}
        \caption[]%
        {{\small }}
        \label{graph-t-vs-p-ltr}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Definitions/c-vs-p-htr.pdf}
        \caption[]%
        {{\small }}
        \label{graph-c-vs-p-htr}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Definitions/t-vs-p-htr.pdf}
        \caption[]%
        {{\small }}
        \label{graph-t-vs-p-htr}
    \end{subfigure}
    \caption{Specific heats and temperatures of hot and cold streams as a function of dimensionless location for the low-temperature recuperator and high-temperature recuperator. (\textbf{a}) Specific heat as a function of location for LTR; (\textbf{b}) temperature as a function of location for LTR; (\textbf{c}) specific heat as a function of location for HTR; (\textbf{d}) temperature as a function of location for~HTR.}
    \label{graphs-t-c-vs-p} 
\end{figure}

\begin{paracol}{2}
  %%\linenumbers
    \switchcolumn

\vspace{-6pt}
\subsubsection{Lead-Cooled Fast~Reactor}
%--------------------------------------------------------------------------------------
Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead. This lead is used to cool the core and transfer heat into the sCO$_2$ Brayton power cycle~\cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}. The~lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX. The~inlet, outlet and heat transfer rates are provided by our industry partner, Westinghouse, making the black box simplification viable. The~energy balance for the black box assumption can be seen in Equation~(\ref{eq-lfr-black-box}).
\begin{equation}
    \label{eq-lfr-black-box}
    \dot{m} \cdot h_{inlet} + \dot{Q}_{LFRHX} = \dot{m} \cdot h_{outlet},
\end{equation}
where the left hand side, $\dot{m}$, $h_{inlet}$, and~$\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The~amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and~outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595~^{\circ}$C. The~outlet temperature of the LFR is specified because of high-temperature material limits on the LFR lead side. The~low-temperature side is allowed to vary over a range of values with some considerations. The~lead flow velocity is limited by the erosion of the fuel, the~slower the lead flow velocity reduces fuel erosion and therefore leads to a more desirable compact design. %\replaced[comment={Edited sentence for clarity [2,3]}]
{At constant lead velocity (and hence mass flow rate), reducing sCO$_2$ inlet temperature allows for a higher coolant temperature increase in the LFR core and hence a higher thermal power output}
%{Restricting the lead flow velocity, and therefore lead mass flow rate, leads to a higher LFR power output when the inlet sCO$_2$ temperature is reduced.} 
LFR sCO$_2$ inlet temperature has a lower bound of 340~$~^{\circ}$C before the lead begins to freeze, which is operationally unacceptable. When the inlet temperature of sCO$_2$ is increased the temperature difference across the LFR is decreased leading to an increase in power conversion cycle thermodynamic efficiency but a reduction in LFR power below $950$ MW. There is a compromise between high LFR efficiency and LFR power, and therefore a temperature of 400~$~^{\circ}$C for the sCO$_2$ inlet temperature is the optimal value provided by~Westinghouse.

\subsubsection{Concentrating Solar Power~Cycle}
%--------------------------------------------------------------------------------------

The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage, %\replaced[comment={Removed Abbreviation [4,1]}]
{}
%{(TES)}
pumps, receiver, sCO$_2$-to-salt counter-flow heat exchanger (C2S), and~CSP counter-flow heat exchanger (CSP HX). The~diagram for this CSP salt loop is shown in Figure~\ref{csp}.

% \end{paracol}

\begin{figure}[H] 
    %[htb]
    %\widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and~csp black box heat~input\label{csp}}
\end{figure}
% \begin{paracol}{2}
% %\linenumbers
% \switchcolumn

The CSP salt cycle uses 60\% sodium nitrate, NaNO$_3$, and~40\% potassium nitrate, KNO$_3$, 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$~^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to $720~^{\circ}$C, but~here the hot TES temperature is set at $560~^{\circ}$C for all modeled cycles~\cite{mehos2017concentrating} as this has been commercially proven. The~cold TES temperature takes on three different values according to cycle configuration capabilities: $390~^{\circ}$C, $410~^{\circ}$C, and~$440~^{\circ}$C. In~addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES~\cite{hamilton2020dispatch}. The~studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and~C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. While the hot TES is charging, the~receiver and LFR are storing heat for later use when grid demand increases. The~hot TES storage is not dispensing salt for use in the CSP cycle while~charging.

The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use. Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle. Additionally, while the focus is on heat storage, and~the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot~TES.

'Non-charging' cycle operating modes are characterized by operations wherein the CSP salt cycle is discharging the hot TES, the~C2S heat exchanger is not transferring heat, and~the LFR is dispatching heat directly to generate electricity. When electrical generation is occurring and solar resource is available, the~heat input in the CSP salt cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 750 MW from the heliostat field. The~hot TES solar salt is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle through CSP HX to be converted into electricity. The~cooled salt is stored in cold storage and moved through Pump 2, where the heat from the receiver is again transferred into the CSP~cycle.

When grid demand for electrical power increases, a~series of operating modes are activated. During~the highest demand times, cycle operation focuses on maximum electrical generation. This is achieved through the C2S being turned off for direct electrical production from the LFR and the hot TES is discharging heat through the CSP HX for electrical production in the sCO$_2$ Brayton cycle. %\replaced[comment={Edited sentence to clarify that the CSP charges the hot TES during low grid demand periods [2,4]}]
{As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging. During~this process, the~LFR gradually adds a larger fraction of heat input to the TES through C2S, supplementing the heat produced by the CSP which is also used to charge the TES. This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.}
%{As grid demand diminishes, CSP HX ramps down heat extraction until no power is being dispatched through the salt and the hot TES begins charging. During this process, the LFR gradually adds a larger fraction of heat input to the TES through C2S. This process continues until no electrical production is occurring in the cycle and all heat is stored in TES for later use.}

\subsection{Standardization of Cycle~Modeling}
%======================================================================================

In order to draw a more direct comparison, the~cycles are standardized in terms of isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and~pump constants. These values are summarized in Table~\ref{tab-cycle-constants}.

\begin{specialtable}[H] 
    %[htbp]
    \caption{Standardized constant cycle parameters with definition, variable and set~value. \label{tab-cycle-constants}}
    \begin{tabular}{L{0.52\linewidth}cc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{\hl{Efficiencies} %Is the italics necessary?
}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pumps 1--3 & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low-Temperature Recuperator & $\delta_{LTR}$		& 10 ($~^{\circ}$C)\\
    High-Temperature Recuperator & $\delta_{HTR}$		& 10 ($~^{\circ}$C)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 ($~^{\circ}$C)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 28.8 (MPa)\\
    \midrule
    \textit{Heat into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 950 (MW)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 750 (MW)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 40 ($~^{\circ}$C)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 595 ($~^{\circ}$C)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise across Pump & $\Delta_{P}$ & 3.726 (MPa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3 (MPa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

The values displayed in Table~\ref{tab-cycle-constants} are representative of CSP and the Westinghouse LFR. 
%\replaced[comment={Elaborated on table variable names [2,5]}]
{In Table~\ref{tab-cycle-constants}, variable names require further explanation. The~high side pressure with the variable label $P_{2A}$, is the constant pressure outlet on the compressors and inlet to the turbines. In~all models, the value is set by the outlet of the main compressor and held constant with the assumption that there is no pressure drop across heat exchangers. In~addition to this pressure, temperatures are also set. The~inlet temperature of the main compressor, $T_{1A}$, is set to a value of $40~^{\circ}$C in all models. The~temperature of the sCO$_2$ on the outlet of the LFR HX has different variable names, T$_5$, T$_{2C}$, T$_{6A}$, and~T$_{5C}$, according to the associated cycle configuration diagram.}{}.

In addition to standardized parameters, all cycles have identical recompression sides. The~recompression side contains a  %\replaced[comment={Abbreviations defined [4,1]}]
{precooler (PC), low-temperature recuperator (LTR), and~two compressors; main compressor (MC) and recompressor (RC)}
%{precooler, low-temperature recuperator, and two compressors; main compressor and recompressor}. 
The modeled cycles are summarized in Table~\ref{tab-cycle_sum}.

\begin{specialtable}[H] 
    \caption{Summary of all modeled non-charging and charging cycles with~descriptions. \label{tab-cycle_sum}}
    \begin{tabular}{lL{0.75\linewidth}}
    \toprule
    \textbf{Cycle Label} & \textbf{Description}\\
    \midrule
    \textit{Non-Charging}\\
    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
    C-2HTR3T-ON & CSP and LFR loops each with dedicated HTR and turbine.\\
    \midrule
    \textit{Charging}\\
    C-LFR-PRE & Turbine is prior to the C2S.\\
    C-LFR-POST & Turbine is after the C2S.\\
    C-LFR-PAR & Turbine is parallel to the C2S.\\
    C-LFR-CIRC & Circulator bridges the LFR and C2S.\\
    \bottomrule
    \end{tabular}
\end{specialtable}

\subsection{Non-Charging Cycle~Configurations} 
%======================================================================================

Various cycles are modeled to test their advantages and disadvantages. These cycle models fall into two categories: non-charging and charging. The~non-charging category is used to determine the configuration of the cycle with a focus on electricity generation. This includes the number and location of turbines, recuperators, and~heat input to the system by the CSP and LFR. To~quantify the effectiveness of the non-charging configurations, a~cycle efficiency, $\eta_{cycle}$, is defined in Equation~(\ref{eq-eta-cycle}).
\begin{equation}
    \label{eq-eta-cycle}
    \eta_{cycle} = \frac{\dot{W}_{T}-\dot{W}_{MC}-\dot{W}_{RC}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

The numerator in Equation~(\ref{eq-eta-cycle}) is the alternator power, or~the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The~denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and~CSP HX, $\dot{Q}_{CSPHX}$.

\subsubsection{Two-Cycle Configuration: C-LFR-ON and~C-CSP-ON} %--------------------------------------------------------------------------------------

The two-cycle configuration that is tested has independent sCO$_{2}$ loops that share a common CSP salt cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP. These two cycles individually operate when the focus of plant operation is primarily electricity~generation.

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure~\ref{c-lfr-on}.

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The~constrained study is calculated by setting the LFR inlet temperature to the design value of $400~^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits. In~addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency. The~unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency. In~Figure~\ref{c-lfr-on}, the~location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or~post.

% \end{paracol}
\begin{figure}[H] 
    %[!h] 
   % \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity~generation\label{c-lfr-on}}
\end{figure}
% \begin{paracol}{2}
% %\linenumbers
% \switchcolumn

The cycle that is using the CSP heat input in the two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure~\ref{c-csp-on}.

%\clearpage
\end{paracol}
\begin{figure}[H] 
    %[!h]
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-csp-on.pdf}
    \caption{Diagram for C-CSP-ON with focus on electricity~generation\label{c-csp-on}}
\end{figure}
\begin{paracol}{2}
%%\linenumbers
\switchcolumn

 Due to the individual operation while the cycles are generating electricity, C-CSP-ON is not directly impacted by the LFR low-end temperatures. Instead, a~sensitivity study is performed on the temperature of the cold TES. Two temperatures are tested, $390~^{\circ}$C and $440~^{\circ}$C, to~observe the impact of cold TES temperature on cycle efficiency. Efficiencies need to be combined to draw a comparison of the two-cycle configurations to the single-cycle configurations; C-1HTR1T-ON and C-2HTR3T-ON. Equation~(\ref{eq-eta-2cycle}) is used to calculate this combined two-cycle efficiency.
\begin{equation}
    \label{eq-eta-2cycle}
    \eta_{combined} = \frac{\dot{W}_{A,C\text{-}LFR\text{-}ON}+\dot{W}_{A,C\text{-}CSP\text{-}ON}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

Equation~(\ref{eq-eta-2cycle}) is the ratio of total alternator (net) power of C-LFR-ON, $\dot{W}_{A,C\text{-}LFR\text{-}ON}$, and~C-CSP-ON, $\dot{W}_{A,C\text{-}CSP\text{-}ON}$, to~the total heat input into the cycles from the LFR and CSP heat exchangers, $\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}$.

\subsubsection{C-1HTR1T-ON} 
%--------------------------------------------------------------------------------------

One drawback of having a two-cycle design, as~seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components. Combining the two cycles into one would reduce redundancy, complexity, and~cost. Heat addition from the CSP HX and LFR HX in parallel orientation is therefore studied in the C-1HTR1T-ON model. This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency. The~diagram for this cycle is illustrated in Figure~\ref{c-1htr1t-on}.
%\clearpage
\end{paracol}

\begin{figure}[H] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
    \caption{Diagram for C-1HTR1T-ON with focus on electricity~generation\label{c-1htr1t-on}}
\end{figure}

\begin{paracol}{2}
%%\linenumbers
\switchcolumn

The C2S is located around the turbine and LFR at state points 5 to 6 depending on the charging cycle configuration: pre, parallel, post or circulator. In~the C-1HTR1T-ON cycle, the~LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are performed on the model. The~initial two studies have the low LFR temperature constrained to the value of $400~^{\circ}$C with varied cold CSP TES temperature and maximized cycle efficiency. To~achieve a maximum cycle efficiency, the~split fraction amount of flow to the main compressor, $y_{1}$, is parametrically studied.
Two cold TES temperatures are tested with constrained LFR low temperature of $400~^{\circ}$C: 
\begin{itemize}
    \item	$410~^{\circ}$C: Lowest cold TES temperature possible due to the sCO$_2$ cold inlet constrained from the LFR to $400~^{\circ}$C and the addition of $10~^{\circ}$C approach temperature;
    \item	$440~^{\circ}$C: Upper bound temperature on cold TES storage;
    \item	$390~^{\circ}$C: Unconstrained LFR cold inlet temperature allows a lower cold TES of $390~^{\circ}$C to be achieved. This allows for a larger temperature drop across the CSP HX, increasing dispatchability.
\end{itemize}

\subsubsection{C-2HTR3T-ON} 
%--------------------------------------------------------------------------------------

The identical inlet temperatures due to the parallel configuration makes the C-1HTR1T-ON cycle configuration restricted. Another single-cycle configuration is desired to allow dissimilar inlet temperatures for the CSP HX and LFR HX while additionally testing the effect that mixing flows downstream from the HTR has on cycle~efficiency.

In practice, sCO$_2$ cycles typically have 3 turbines, with~2 of these driving the compressor and recompressor. Therefore, this configuration will not in general require additional turbines compared to the C-1HTR1T-ON configuration. Furthermore, it is anticipated that the cost of the high-temperature recuperator (HTR) is likely most related to its volume, and~hence having two smaller high-temperature recuperators is unlikely to cost significantly more than one large~one.

This cycle, C-2HTR3T-ON, can be seen in Figure~\ref{c-2htr3t-on} and has two high-temperature recuperators and three turbines. The~LFR is powering one turbine, T1, and~transferring unused heat to the flow entering LFR HX through a dedicated high-temperature recuperator, HTR. The~cycle with heat addition from the CSP powers the other two turbines, which for modeling purposes are combined into a single turbine T2, while having a dedicated high-temperature recuperator, HTR2. The~two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine. Additionally, the~power produced by the two turbines is proportional to mass flow rate, each receives a fraction of the mass flow rate, therefore producing the same fraction of power. Summing these power fractions together yields the total power of a singular turbine in the same position. After~the high-temperature recuperators, the~two flows are combined and sent to the LTR hot~side.

\end{paracol}
\begin{figure}[H]
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-2htr3t-on.pdf}
    \caption{Diagram for C-2HTR3T-ON with focus on electricity~generation\label{c-2htr3t-on}}
\end{figure}
\begin{paracol}{2}
%%\linenumbers
\switchcolumn

The C2S heat exchanger is located around the turbine and LFR at 7A to 8A depending on the charging configuration: pre, post, parallel or circulator. Three sensitivity studies are performed on the C-2HTR3T-ON model---two with the LFR low temperature constrained and one without this constraint. The~two constrained studies, with~an LFR temperature of $400^{\circ}$, have varied cold CSP TES temperature with the lowest temperature of $390~^{\circ}$C and highest temperature of $440~^{\circ}$C. The~unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390~^{\circ}$C.

\subsection{Thermal Energy Storage Charging~Techniques} 
%======================================================================================

Charging cycle configurations accommodate energy storage modes of operation. These configurations examine the location of LFR heat extraction via C2S. To~maximize the available heat for extraction, alternator net power is set to zero, therefore requiring the turbine power to balance with the compressors' demand. Despite the components being non-ideal and consuming power, the~recompression cycle continues to operate, ensuring that there is mass flow to transfer heat from the Brayton cycle to C2S. The~excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. Comparison of the heat extraction point in the cycle, C2S, is accomplished by implementing C2S in different locations around the turbine in the C-LFR-ON non-charging cycle configuration; C-LFR-PRE has the turbine prior to C2S, C-LFR-POST has the turbine after C2S, C-LFR-PAR has the turbine in parallel to C2S, and~C-LFR-CIRC uses a circulating loop instead of in-flow implementation. C-LFR-ON is the configuration used for these studies because during charging operation, flow through the CSP HX is deactivated, effectively making all non-charging cycles take the identical form of C-LFR-ON. To~quantify the effectiveness of TES charging techniques, Equation~(\ref{eq-eta-heatstorage}) defines the heat storage efficiency, $\eta_{heatstorage}$.
\begin{equation}
    \label{eq-eta-heatstorage}
    \eta_{heatstorage} = \frac{\dot{Q}_{C2S}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and~the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP~HX.

\subsubsection{C-LFR-PRE} 
%--------------------------------------------------------------------------------------

The high-temperature sCO$_2$ leaving the LFR HX flows through the LFR turbine converting thermal energy to usable work. The~outlet temperature of the LFR turbine is at a temperature suitable to charge the hot TES, and therefore the flow is passed through C2S exchanging heat to the cold solar salt. The~diagram outlining this process is C-LFR-PRE in Figure~\ref{c-lfr-pre}.

\end{paracol}
\begin{figure}[H]
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-pre.pdf}
    \caption{Diagram for C-LFR-PRE thermal energy storage charging orientation\label{c-lfr-pre}.}
\end{figure}
\begin{paracol}{2}
%%\linenumbers
\switchcolumn

A problem arises with this salt charging configuration. The~temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $560~^{\circ}$C when the turbine power is balanced with the compressor demand. To~raise the temperature, some of the high-temperature flow before the turbine is redirected through a valve and combined after the turbine. Limiting the flow through the turbine reduces the turbine power and compressor power because of the balancing requirement. Due to the reduction in available compressor power, the~LFR RC is effectively bypassed, and~a large portion of usable heat is expelled in the LFR PC before the LFR MC. The~thermal storage efficiency reduces as a result of the large amount of heat rejected in the LFR~PC.

\subsubsection{C-LFR-POST} 
%--------------------------------------------------------------------------------------

Moving the heat extraction prior to the turbine is analyzed in C-LFR-POST. This diagram is shown in Figure~\ref{c-lfr-post}.

\end{paracol}
\begin{figure}[H]
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-post.pdf}
    \caption{Diagram for C-LFR-POST thermal energy storage charging orientation\label{c-lfr-post}.}
\end{figure}
\begin{paracol}{2}
%%\linenumbers
\switchcolumn

This TES charging cycle extracts heat before the turbine and therefore has a large negative effect on the amount of work that the turbine is producing. The~turbine power offsets the requirements of both compressors, requiring the turbine inlet temperature to be high. The~amount of energy that is extracted before the turbine is small and therefore the heat storage efficiency is fractional compared to other charging techniques. There is no quantitative study performed on this case because, due to the efficiency losses, it is~non-viable.

\subsubsection{C-LFR-PAR} 
%--------------------------------------------------------------------------------------

The requirements of the turbine and CSP hot TES can be satisfied by splitting the flow before the turbine. The~flow through the salt heat exchanger in this cycle is therefore separate from the turbine. After~the salt heat exchanger, a~valve is needed to reduce the pressure, this TES charging cycle is C-LFR-PAR shown in Figure~\ref{c-lfr-par}.

A sensitivity study with varying cold CSP TES temperature is carried out to determine the impact on heat storage efficiency. The~study considers two temperature values of $390~^{\circ}$C and $440~^{\circ}$C.

\clearpage
\end{paracol}
\begin{figure}[H]
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-par.pdf}
    \caption{Diagram for C-LFR-PAR thermal energy storage charging orientation\label{c-lfr-par}.}
\end{figure}
\begin{paracol}{2}
%\linenumbers
\switchcolumn

\vspace{-6pt}
\subsubsection{C-LFR-CIRC} 
%--------------------------------------------------------------------------------------

The full diagram for C-LFR-CIRC is shown in Figure~\ref{c-lfr-circ}.
\end{paracol}
\begin{figure}[H]
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-circ.pdf}
    \caption{Full diagram for C-LFR-CIRC thermal energy storage charging orientation\label{c-lfr-circ}.}
\end{figure}
\begin{paracol}{2}
%\linenumbers
\switchcolumn

The charging subsection of this diagram is composed of a circulation cycle that has heat inputted through the LFR heat exchanger. A~separated circulation cycle has a loop which avoids the losses associated with compressor and turbine, therefore achieving higher heat storage efficiency than possible with full cycle operation. This subsection is encircled in blue and can be seen in Figure~\ref{c-lfr-circ-sub}.

The flow continues through a circulator which is assumed to have negligible pressure rise (i.e. there is assumed to be negligible pressure drop in this case). A~heat exchanger, C2S, extracts heat from the flow, storing the thermal energy in the hot TES for later use. Excess heat that is not extracted is then dumped into a reservoir through the chiller to bring the temperature of the flow down to LFR cool side operating temperature of $400~^{\circ}$C. Three different cold TES temperatures---$390~^{\circ}$C, $410~^{\circ}$C, and~$440~^{\circ}$C---are compared in a sensitivity~study.

% \end{paracol}
\begin{figure}[H]
   % \widefigure
    \includegraphics[width=0.7\linewidth]{Definitions/c-lfr-circ-sub.pdf}
    \caption{Diagram for C-LFR-CIRC sub-cycle thermal energy storage charging orientation\label{c-lfr-circ-sub}.}
\end{figure}
% \begin{paracol}{2}
% %\linenumbers
% \switchcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and~Discussion}

For all cycle configurations presented, with~constrained or unconstrained LFR low-temperature inlet and varied cold TES temperature, cycle and heat storage efficiencies are maximized using parametric studies on flow splitter fractions. %\replaced[comment={Source of calculations defined [4,3]}]
{All calculations were carried out using EES, with~the results}
%{These results are} 
obtained using standardized values found in \mbox{Table \ref{tab-cycle_sum}} for a more direct comparison between cycles. Presentation and discussion of the results is fulfilled in the following~section.

\subsection{Non-Charging Cycle~Configurations}
%======================================================================================

The three non-charging cycle models have a focus on producing the highest positive alternator power to heat input, or~cycle efficiency. The~two-cycle configuration, composed of C-LFR-ON and C-CSP-ON, has independent recompression cycles with dedicated compressors, turbine, recuperators, and~pre-cooler for the LFR and CSP. C-1HTR1T-ON, with~the heat additions in parallel, and~C-2HTR3T, with~dedicated HTR for both heat additions, are cycles which incorporate the CSP and LFR in the same cycle. The~results from studies performed on these cycles are displayed in Table~\ref{tab-noncharg}.

The calculated values reported in Table~\ref{tab-noncharg} are component power, mass flow fractions, and~counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$~^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$~^{\circ}$C, 410$~^{\circ}$C, or~440$~^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. %\replaced[comment={Removed the conjunction 'and' in the sentence for clarity. [1,1]}]
{Cycles that do not contain the listed component omit the associated values.}
%{Cycles that do not contain the listed component and omit the associated values.} 
\clearpage 
% \mw{Check that the column breakdown and grouping is correct in what I've changed.}
\end{paracol}
\begin{specialtable}[H] 
    %[htbp]

    \caption{\hl{Calculated} system parameters for non-charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-noncharg}}%is the Vertical line necessary?
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{lc|cc|cc|ccc|ccc}
    \toprule
     &  & \multicolumn{2}{c|}{\textbf{C-LFR-ON}} & \multicolumn{2}{c|}{\textbf{C-CSP-ON}}  &	\multicolumn{3}{c|}{\textbf{C-1HTR1T-ON}}	&	\multicolumn{3}{c}{\textbf{C-2HTR3T-ON}} \\
    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C} & \textit{N/A} & \textit{N/A} &	\textit{U}	&	\textit{C}	&	\textit{C}	&	\textit{U}	&	\textit{C}	&	\textit{C}
    \\
    \midrule
    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	47.08	&	45.28	&	45.58	&	45.93	&	44.9	&	44.22	&	44.22	&	46.10	&	44.34	&	44.35	\\
    LFR Inlet Temperature ($~^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	$\cdot$	&	$\cdot$	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
    Cold TES Temperature ($~^{\circ}$C)	&	$T_{CS}$	&	$\cdot$	&	$\cdot$	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\
    Alternator Power (MW)	&	$\dot{W}_{A}$	&	447.3	&	430.2	&	339.1	&	340.6	&	763.9	&	752.3	&	752.6	&	783.7	&	753.7	&	754	\\
    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	502.7	&	519.8	&	418.5	&	420.2	&	937.4	&	949.2	&	949.3	&	917.6	&	947.6	&	947.9	\\
    MC Power (MW)	&	$\dot{W}_{MC}$	&	115	&	118.9	&	95.73	&	96.13	&	214.5	&	194.8	&	194.8	&	209.9	&	216.8	&	216.9	\\
    RC Power (MW)	&	$\dot{W}_{RC}$	&	116.6	&	77.3	&	97.22	&	97.71	&	217.4	&	285.7	&	285.7	&	213.5	&	140.8	&	140.8	\\
    T1 Power (MW)	&	$\dot{W}_{T1}$	&	678.9	&	626.4	&	532.1	&	534.5	&	1196	&	1233	&	1233	&	679.3	&	626.3	&	626.3	\\
    T2 Power (MW)	&	$\dot{W}_{T2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	527.8	&	485	&	485.4	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.7	&	0.7844	&	0.6996	&	0.6994	&	0.7	&	0.6333	&	0.6333	&	0.6993	&	0.7846	&	0.7846	\\
    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\
    LTR UA Value (MW/$~^{\circ}$C)	&	$UA_{LTR}$	&	54.68	&	22.84	&	45.4	&	45.53	&	102	&	91.63	&	91.64	&	134.4	&	41.56	&	41.57	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.9867	&	0.8473	&	0.9858	&	0.9854	&	0.9867	&	0.9066	&	0.9066	&	0.9853	&	0.847	&	0.847	\\
    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	656.8	&	366.5	&	548.3	&	551.4	&	549.2	&	614.9	&	615.1	&	1204	&	667.1	&	667.3	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.92	&	0.8742	&	0.9201	&	0.9202	&	0.92	&	0.9485	&	0.9485	&	0.9414	&	0.8741	&	0.8741	\\
    HTR UA Value (MW/$~^{\circ}$C)	&	$UA_{HTR}$	&	48.29	&	42.71	&	34.58	&	34.72	&	78.22	&	82.3	&	82.34	&	48.32	&	42.69	&	42.69	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.8657	&	0.8143	&	0.8593	&	0.8594	&	0.8595	&	0.8754	&	0.8755	&	0.8661	&	0.8142	&	0.8142	\\
    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	998.1	&	1161	&	665.4	&	667.7	&	679.2	&	742.6	&	743	&	545.7	&	636.8	&	636.6	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9544	&	0.9627	&	0.9436	&	0.9436	&	0.9445	&	0.9441	&	0.9441	&	0.9542	&	0.9627	&	0.9627	\\
    HTR2 UA Value (MW/$~^{\circ}$C)	&	$UA_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	34.29	&	31.61	&	31.63	\\
    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.8594	&	0.8074	&	0.8074	\\
    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	298.1	&	363.4	&	363.8	\\
    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.9436	&	0.9561	&	0.9561	\\
    CSPHX UA Value (MW/$~^{\circ}$C)	&	$UA_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	757.6	&	760.8	&	751.3	&	751.5	&	751.9	&	751.3	&	751.3	&	751.9	\\
    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\
    \bottomrule
    \end{tabular}
    }
\end{specialtable}
\begin{paracol}{2}
%\linenumbers
\switchcolumn

\subsubsection{Two-Cycle Configuration: C-LFR-ON and~C-CSP-ON}

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, and therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8 percentage points. The~unconstrained case allows for smaller temperature gradient across the LFR, an~increase in recuperator effectiveness, and~an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle~\cite{klein_nellis_2011}. Increasing the LFR sCO$_2$ inlet temperature above the design value of $400~^{\circ}$C is favorable from a cycle efficiency perspective, but~reduces the LFR thermal power. This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power. In~principle, dropping the LFR inlet temperature further, to~as low as $340~^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed. When unconstrained, the~sCO$_2$ inlet temperature to the LFR increases by $15.1~^{\circ}$C to a value of $415.1~^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat~exchanger.

C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because C2S is turned off and therefore the two cycles are not tethered during non-charging configuration. Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of $390~^{\circ}$C and another with a higher value of $440~^{\circ}$C. A~cold TES temperature of $410~^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the $390~^{\circ}$C and $440~^{\circ}$C calculated values. Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with~the $440~^{\circ}$C case gaining 0.35 percentage points. The~component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, and therefore the lower temperature of $390~^{\circ}$C for cold TES temperature is ideal, increasing the performances of the heat~exchanger.

Combining the two-cycle efficiencies using Equation~(\ref{eq-eta-2cycle}) gives a more direct comparison to the single-cycle configurations; C-1HTR1T and C-2HTR3T. Two combined efficiencies are calculated for the two-cycle configuration combination. The~first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low-temperature and C-CSP-ON $440~^{\circ}$C cold TES cases. This combined efficiency yields a value of 46.1\% (which is almost identical to the efficiency achieved by C-2HTR3T-ON shown in Table~\ref{tab-noncharg}). The~second combined configuration has a lower efficiency with favorable LFR characteristics and solar salt mass flow rate. This combination has the constrained C-LFR-ON LFR low-temperature and C-CSP-ON $390~^{\circ}$C cold TES cases with a combined efficiency of 45.1\%.

\subsubsection{C-1HTR1T-ON}
The single-cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions. Due to the $10~^{\circ}$C approach temperature, the~identical inlet conditions lead to a lower bound of $410~^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to $400~^{\circ}$C. A~supplementary $440~^{\circ}$C cold TES study is run to test the effects that higher temperature storage has on cycle efficiency. Raising the temperature of the cold TES from $410~^{\circ}$C to $440~^{\circ}$C has no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side. Increasing the solar salt mass flow rate requires more storage for the same CSP heat input, a~reduction in dispatchability, and~larger pumps, increasing the cost of the system. Therefore, a~lower cold TES temperature is desirable. Without~the constraint on the sCO$_2$ LFR inlet temperature, a~study is additionally conducted with cold TES temperature set to $390~^{\circ}$C. Of~these three sensitivity studies, the~cycle that yielded the highest efficiency is the unconstrained, $390~^{\circ}$C cold TES with an efficiency gain of 0.68 percentage points over the constrained cases. The~high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components. The~sCO$_2$ LFR inlet temperature for the $390~^{\circ}$C cold TES study is $380~^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher core~power.

\subsubsection{C-2HTR3T-ON}
C-2HTR3T-ON has dedicated recuperators and turbines for the LFR and CSP, allowing for independent inlet temperatures. Three studies are conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions. The~constrained studies have cold TES temperatures of $390~^{\circ}$C and $440^{\circ}$, both of which have negligible efficiency differences. Similarly to the studies performed on C-1HTR1T-ON, the~$440~^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost. The~$390~^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76 percentage points more than the constrained cases. Additionally, the~sCO$_2$ LFR inlet temperature is $415.2~^{\circ}$C, $15.2~^{\circ}$C more than constrained cases, causing heat exchanger parameters to be less than ideal but increasing LFR~efficiency.

\subsection{Thermal Energy Storage Charging~Techniques}

When the focus of the cycles is thermal storage for later use, the~LFR charges the hot TES through the C2S heat exchanger. Studies performed on the charging techniques have constrained sCO$_2$ LFR inlet temperatures to $400~^{\circ}$C with set values of cold TES temperature of $390~^{\circ}$C, $410~^{\circ}$C, or~$440~^{\circ}$C. The~two charging techniques which run the full recompression cycle are C-LFR-PRE, with~the turbine before the heat extraction, and~C-LFR-PAR, with~heat extraction in parallel to the turbine. The~third charging technique, C-LFR-CIRC, has a dedicated circulation loop and additional chiller and circulator pump to avoid losses associated with the compressors and turbines. The~results are presented in Table~\ref{tab-charg}.

% \end{paracol}

\begin{specialtable}[H]  
    %[htbp]
    \caption{\hl{Calculated} system parameters for charging cycle configurations. All cases were evaluated with constrained (\textit{C}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}%is the Vertical line necessary?
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{lc|c|cc|ccc}
            \toprule
            &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
            \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
            \midrule
            Cold TES Temperature ($~^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
            LFR Inlet Temperature ($~^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
            Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
            Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
            MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR UA Value (MW/$~^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR UA Value (MW/$~^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            C2S UA Value (MW/$~^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
            C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
            C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
            C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
            C2S Approach Temperature ($~^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
            \bottomrule
        \end{tabular}
        }
    \end{specialtable}
    % \begin{paracol}{2}
        % %\linenumbers
        % \switchcolumn

\subsubsection{C-LFR-PRE}
The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES. The~hot TES is at a temperature of 560$~^{\circ}$C, with~a 10$~^{\circ}$C approach temperature, and therefore the inlet temperature to C2S is required to be at least 570$~^{\circ}$C. In~cases where the turbine outlet temperature is less than 570$~^{\circ}$C, a~isenthalpic valve bypasses flow from the high-temperature turbine inlet and mixes with the low-temperature turbine outlet raising the temperature prior to the C2S heat exchanger. For~the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$~^{\circ}$C. With~this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S. As~the temperature of the hot TES is raised above a value of 540$~^{\circ}$C, the~amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible. The~temperature in the hot TES is therefore set to a lower value of 540$~^{\circ}$C to allow for operation of this cycle. With~heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler. This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the~lowest of all tested TES charging~configurations.

\subsubsection{C-LFR-PAR}

To test the effects of splitting flow prior to the turbine, a~parallel configuration C-LFR-PAR is studied. To~reduce the pressure from 28.8 MPa to 8.8 MPa, an~isenthalpic valve is required after heat is extracted for storage through C2S. With~this configuration two different values for cold TES are studied, one with a cold TES storage of $390~^{\circ}$C the other with a temperature of $440~^{\circ}$C. A~noteworthy difference for this cycle is the C2S approach temperature is not set to $10~^{\circ}$C. Defining the approach temperature as $10~^{\circ}$C causes the energy balance governing combiner 2 to be over constrained. Therefore, this value is free and calculated to be $35~^{\circ}$C for the $390~^{\circ}$C case and $26.27~^{\circ}$C for the $440~^{\circ}$C case. Both of these different temperature cold TES studies do not change the cycle parameters because, as~seen in C-1HTR1T-ON and C-2HTR3T-ON, the~solar salt mass flow rate adjusts to accommodate for the temperature difference. The~higher cold TES temperature of $440~^{\circ}$C causes the mass flow rate in the CSP to increase by approximately 650 kg/s. Increasing the mass flow rate has a higher demand on system components but in this situation it allows for the salt to be charged at a higher rate, increasing the storage capabilities. Both cycles have a heat storage efficiency of 45.30\%.

\subsubsection{C-LFR-CIRC}

C-LFR-CIRC is a thermal energy storage charging technique which does not suffer from significant losses associated with turbines, compressors, and~heat exchangers. The~separate recirculation cycle is modeled extracting heat directly from the LFR, passes the high-temperature mass flow through a circulator, exchanges the heat into the hot TES through C2S, then removes heat in a chiller to bring the temperature of the flow down to the inlet temperature of the LFR, ideally $400~^{\circ}$C. This is the most adoptable TES charging technique with a wide range of possible TES charging temperatures while transferring a majority of the heat from the LFR into the hot TES. Multiple temperatures for the cold TES are studied; $390~^{\circ}$C, $410~^{\circ}$C, and~$440~^{\circ}$C. Of~these three temperatures, the~highest efficiency is a cold TES temperature of $390^{\circ}$ with a heat storage efficiency of 100\% (not accounting for pressure drop losses, which will be small). The~heat storage efficiency reduces as the temperature of the cold TES is increased; the $410~^{\circ}$C case has an efficiency of 90\% while the $440~^{\circ}$C case has an efficiency of 74\%. This reduction in efficiency is due to the inlet temperature condition on the LFR, the~higher the temperature of the cold TES the higher the temperature of the C2S outlet and therefore more heat is being extracted through the chiller to bring the flow temperature down to the LFR inlet~temperature.

There is an interaction between the temperatures selected here and the non-charging cycle configuration. For~C-LFR-CIRC, the~highest efficiencies are achieved when the cold TES temperature is $10~^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger. If~the sCO$_2$ LFR inlet temperature is constrained to $400~^{\circ}$C, then the desired cold TES temperature is $390~^{\circ}$C to allow for the apporach temperature. If~the cold TES is at a higher temperature, then the chiller is needed. This then implies that the sCO$_2$ inlet temperature in the salt-to-sCO$_2$ heat exchanger is  $380~^{\circ}$C. From~the results of the previous section, this is clearly achievable for the C-2HTR3T-ON configuration and the separate cycle configuration, but~for the C-1HTR1T-ON configuration the LFR and CSP inlet temperatures are constrained to be the same. In~this case, the~LFR and CSP inlet temperatures would then be $400~^{\circ}$C, implying a cold TES temperature of  $410~^{\circ}$C and hence a 90\% heat storage efficiency with a requirement for a~chiller.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This paper analyzed contending sCO$_2$ Brayton cycle configurations for complimentary CSP and LFR cycles with non-charging cycle configurations focusing on electrical generation. An~additional operating mode, hot TES charging, is considered where the CSP hot TES is charged by the LFR when grid demand is low. This operating mode positions the heat extraction point at different locations around the turbine in a sCO$_2$ Brayton recompression cycle. The~performance parameters that are used for comparison of the cycles are cycle efficiency when the cycle is producing electricity and heat storage efficiency when the focus is on energy storage for later use in the charging mode. These efficiencies are maximized using flow splitter values at different values of cold TES temperature and constrained or unconstrained sCO$_2$ inlet LFR temperature. The~conclusions drawn in this paper are as follows:

\textit{\hl{Non-charging configurations:}}%we recomended it can be format as~subsection
\begin{itemize}
    \item	Two-cycle configuration C-LFR-ON and C-CSP-ON: Offers the highest cycle efficiency because of the freedom of the two cycles to operate independently when generating electrical power. The~cycles individually are simple recompression but there is a lack of component synergies.
    \item	C-1HTR1T-ON: Single-cycle configuration that is the least complex, and therefore cost efficient and compact, with~heat additions from the CSP and LFR in parallel. With~both CSP and LFR discharging, combined cycle efficiency is reduced by ~0.8 percentage points compared to the two-cycle configuration. 
    \item   C-2HTR3T-ON: Single-cycle configuration that has dedicated turbines and HTRs for the LFR and CSP. This cycle makes a compromise between complexity with reduced cycle component redundancy, flexibility for dissimilar inlet temperatures on the CSP and LFR inlet, and~median efficiency. The~efficiency is only marginally higher than C-1HTR1T-ON, but~heat storage efficiency when using the LFR to charge the salt is improved due to flexibility on setting the CSP and LFR inlet temperatures. As~the additional turbines are likely present in practice anyway, this cycle is not anticipated to significantly increase cost and complexity over C-1HTR1T-ON. The~relative merits of C-2HTR3T-ON and C-1HTR1T-ON are therefore similar. It is noted that for the unconstrained case C-2HTR3T achieves almost identical performance to the two-cycle configuration, with~an efficiency of 46.1\%, and~hence the drop in performance relative to using separate cycles is attributable to the constraint on LFR inlet temperature being more limiting.
\end{itemize}

\textit{\hl{Thermal energy storage charging techniques:}}
\begin{itemize}
    \item    C-LFR-POST: Charging technique with the turbine subsequent to C2S heat exchanger. Infeasible due to lower thermodynamic efficiency. 
    \item	C-LFR-PRE: Charging technique with the turbine prior to C2S heat exchanger with a valve that bypasses the turbine, demands a high outlet temperature for the LFR to be effective. Due to LFR outlet temperature limitations, this configuration has the next lowest heat storage efficiency.
    \item	C-LFR-PAR: Charging technique that splits the flow directly after the LFR with the turbine and C2S heat exchanger in parallel. The~heat storage efficiency is higher than C-LFR-PRE.
    \item   C-LFR-CIRC: Flexible technique with a heat storage efficiency being highly dependent on cold TES temperature and LFR inlet temperature. Able to achieve heat storage efficiency to near 100\% by eliminating losses associated with the turbines and compressors. For~C-1HTR1T-ON, the~heat storage efficiency is limit to 90\% because the inlet temperatures to the LFR and CSP are constrained to be the same. The~additional chiller and circulator components in the dedicated circulation loop increase complexity and cost. 
\end{itemize}

C-LFR-PAR and C-LFR-CIRC are therefore options going forward, with~a trade-off between heat storage efficiency and component costs, with~the performance of C-LFR-CIRC also depending on the choise of charging~configuration.

The cycle configurations with the listed conclusions can be used as reference for future cycle design and proof of concept considerations. Further studies and cycle analysis must be performed before these cycles are used for implementation into a physical plant. 
\vspace{6pt}

\authorcontributions{Conceptualization, B.L., M.W., C.S. and T.N.; methodology, B.W., M.W., C.S., T.N. and B.L.; software, B.W.; validation, B.L. and M.W.; formal analysis, B.W.; investigation, B.W.; resources, M.W. and B.L.; data curation, B.W.; writing---original draft preparation, B.W.; writing---review and editing, B.L., M.W. and T.N.; visualization, B.W.; supervision, M.W. and B.L.; project administration, B.L.; funding acquisition, B.L., M.W., C.S. and T.N. All authors have read and agreed to the published version of the~manuscript.}

\funding{This work was supported by funding received from the DOE Office of Nuclear Energy’s Nuclear Energy University Program under contract number~DE-NE0008988. }

 \institutionalreview{\hl{x}}%In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and~approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or~animals.

 \informedconsent{\hl{x}}%Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve~humans.

% Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.

\dataavailability{Supporting data for this study is available on request.}

\acknowledgments{We would like to thank Josh McTigue (NREL) for useful technical discussions on the development of the cycle configurations.}

\conflictsofinterest{The authors declare no conflict of interest. The~funders had no role in the design of the study; in the collection, analyses, or~interpretation of data; in the writing of the manuscript, or~in the decision to publish the~results'.}

%% Optional
% \sampleavailability{Samples of the compounds ... are available from the authors.}
%% Optional
\abbreviations{Nomenclature}{
The following abbreviations and variables are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
\textbf{Abbreviations}\\
A & Alternator\\
CSP & Concentrating solar power\\
C2S & sCO$_2$-to-Salt heat exchanger\\
EES & Engineering Equation Solver\\
HTR & High-temperature recuperator\\
HX & Heat exchanger\\
LFR & Lead-fast reactor\\
LTR & Low-temperature recuperator\\
MC & Main compressor\\
NREL & National Renewable Energy Laboratory\\
P & Pump\\
PC & Pre-cooler\\
RC & Re-compressor\\
sCO$_2$ & Supercritical carbon dioxide\\
T & Turbine\\
TES & Thermal energy storage\\

 \\
\end{tabular}

\noindent 
\begin{tabular}{@{}ll}
\textbf{Variables [Units]}\\
$CR$ & Capacitance ratio [-]\\
$\dot{C}$ & Capacitance rate [MW/$~^{\circ}$C]\\
$\Delta$ & Temperature difference [$~^{\circ}$C]\\
$\delta$ & Approach temperature of heat exchanger [$~^{\circ}$C]\\
$\varepsilon$ & Effectiveness of heat exchanger [-]\\
$\eta$ & Isentropic efficiency [-]\\
$h$ & Enthalpy [J/kg]\\
$\dot{m}$ & Mass flow rate [kg/s]\\
$NTU$ & Number of transfer units [-]\\
$P$ & Pressure [MPa]\\
$\dot{Q}$ & Heat transfer rate [W]\\
$T$ & Temperature []$~^{\circ}$C]\\
$UA$ & Conductivity of heat exchanger [MW/$~^{\circ}$C]\\
$v$ & Volumetric flow rate [$m^3$/kg]\\
$\dot{W}$ & Power [MW]\\
$y$ & Splitter fraction [-]\\
\end{tabular}%
}

% overleaf.com/learn/latex/Code_listing
% \begin{lstlisting}[language=Python]
%     #My ees file
%     def myfunc():
%         return x
%     x = y

%     f = 8*y^2
% \end{lstlisting}

% % ------- new file

% \newcommand{\myeqnone}{%
% a^2 + b^2 = c^2
% }

% %---- back to the main file
% \begin{equation}
%     \myeqnone
%     \label{myeqnonelabel}
% \end{equation}

\end{paracol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{how to use}

%\subsection{Subsection}
%Citing a journal paper~\cite{wagner2017optimization} . Now citing a book reference~\cite{blair2005sam} or other reference types~\cite{hirsch2011standardization}. \cite{nellis_klein_2008}
%\subsubsection{Subsubsection}

%Bulleted lists look like this:
%\begin{itemize}
%\item	First bullet;
%\item	Second bullet;
%\item	Third bullet.
%\end{itemize}

%Numbered lists can be added as follows:
%\begin{enumerate}
%\item	First item; 
%\item	Second item;
%\item	Third item.
%\end{enumerate}

%The text continues here.

%\subsection{Figures, Tables and Schemes}

%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

%\begin{figure}[H]
%\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
%\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
%\end{figure}

% The MDPI table float is called specialtable
%\begin{specialtable}[htbp] 
%\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
%%% \tablesize{} %% You can specify the fontsize here, e.g.,~\tablesize{\footnotesize}. If commented out \small will be used.
%\begin{tabular}{ccc}
%\toprule
%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
%\midrule
%Entry 1		& Data			& Data\\
%Entry 2		& Data			& Data\\
%\bottomrule
%\end{tabular}
%\end{specialtable}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

%\subsection{Formatting of Mathematical Components}

%This is the example 1 of equation:
%\begin{equation}
%a = 1,
%\end{equation}

%the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

%This is the example 2 of equation:
%\end{paracol}
%\nointerlineskip
%\begin{eqnarray}
%a &=& b + c + d + e + f + g + h + i + j + k + l\nonumber \\
% &+& m + n + o + p + q + r + s + t + u + v + w + x + y + z %\nonumber
%\end{eqnarray}

% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, %\linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
%\begin{figure}[H]	
%\widefigure
%\includegraphics[width=15 cm]{Definitions/logo-mdpi}
%\caption{This is a wide figure.\label{fig2}}
%\end{figure}

%\begin{paracol}{2}
%%\linenumbers
%\switchcolumn
%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
%\begin{Theorem}
%Example text of a theorem.
%\end{Theorem}

%The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
%\begin{proof}[Proof of Theorem 1]
%Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
%\end{proof}
%The text continues here.

%\end{paracol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \setcounter{section}{-1} %% Remove this when starting to work on the template.
% \section{How to Use this Template}

% The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
% %The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

% \section{Introduction}

% The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper~\cite{ref-journal}. Now citing a book reference~\cite{ref-book1,ref-book2} or other reference types~\cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Materials and Methods}

% Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

% Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

% Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
% \begin{quote}
% This is an example of a quote.
% \end{quote}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Results}

% This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
% \subsection{Subsection}
% \subsubsection{Subsubsection}

% Bulleted lists look like this:
% \begin{itemize}
% \item	First bullet;
% \item	Second bullet;
% \item	Third bullet.
% \end{itemize}

% Numbered lists can be added as follows:
% \begin{enumerate}
% \item	First item; 
% \item	Second item;
% \item	Third item.
% \end{enumerate}

% The text continues here.

% \subsection{Figures, Tables and Schemes}

% All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

% \begin{figure}[H]
% \includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
% \caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
% \end{figure}

% % The MDPI table float is called specialtable
% \begin{specialtable}[H] 
% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
% %%% \tablesize{} %% You can specify the fontsize here, e.g.,~\tablesize{\footnotesize}. If commented out \small will be used.
% \begin{tabular}{ccc}
% \toprule
% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
% \midrule
% Entry 1		& Data			& Data\\
% Entry 2		& Data			& Data\\
% \bottomrule
% \end{tabular}
% \end{specialtable}

% %\begin{listing}[H]
% %\caption{Title of the listing}
% %\rule{\columnwidth}{1pt}
% %\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
% %\rule{\columnwidth}{1pt}
% %\end{listing}

% Text.

% Text.

% \subsection{Formatting of Mathematical Components}

% This is the example 1 of equation:
% \begin{equation}
% a = 1,
% \end{equation}
% the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
% %% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

% This is the example 2 of equation:
% \end{paracol}
% \nointerlineskip
% \begin{equation}
% a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
% \end{equation}

% % Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, %\linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
% \begin{figure}[H]	
% \widefigure
% \includegraphics[width=15 cm]{Definitions/logo-mdpi}
% \caption{This is a wide figure.\label{fig2}}
% \end{figure}  
% \begin{paracol}{2}
% %\linenumbers
% \switchcolumn

% Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
% %% Example of a theorem:
% \begin{Theorem}
% Example text of a theorem.
% \end{Theorem}

% The text continues here. Proofs must be formatted as follows:

% %% Example of a proof:
% \begin{proof}[Proof of Theorem 1]
% Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
% \end{proof}
% The text continues here.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Discussion}

% Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Conclusions}

% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Patents}

% This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\input{backmatter.tex}

% \authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

% \funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

% \institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.}

% \informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

% Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

% \dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. You might choose to exclude this statement if the study did not report any data.}

% \acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

% \conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

% %% Optional
% \sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{abbreviations.tex}
% %% Optional
% \abbreviations{Abbreviations}{
% The following abbreviations are used in this manuscript:\\

% \noindent 
% \begin{tabular}{@{}ll}
% MDPI & Multidisciplinary Digital Publishing Institute\\
% DOAJ & Directory of open access journals\\
% TLA & Three letter acronym\\
% LD & Linear dichroism
% \end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{variables.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
% \appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
% \appendixstart
% \appendix
% \section{}
% \subsection{}
% The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

% \begin{specialtable}[H] 
% %\tablesize{\scriptsize}
% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab2}}
% %\tablesize{} % You can specify the fontsize here, e.g.,~\tablesize{\footnotesize}. If commented out \small will be used.
% \begin{tabular}{ccc}
% \toprule
% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
% \midrule
% Entry 1		& Data			& Data\\
% Entry 2		& Data			& Data\\
% \bottomrule
% \end{tabular}
% \end{specialtable}

% \section{}
% All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \end{paracol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{bibliography}
\begin{thebibliography}{999}

\bibitem[Turchi \em{et~al.}(2013)Turchi, Ma, Neises, and Wagner]{turchi_2013}
Turchi, C.S.; Ma, Z.; Neises, T.W.; Wagner, M.J.
\newblock Thermodynamic study of advanced supercritical carbon dioxide power
  cycles for concentrating solar power systems.
\newblock {\em J. Sol. Energy Eng.} {\bf 2013}, {\em \hl{135}}.%please add page number or doi

\bibitem[Ahn \em{et~al.}(2014)Ahn, Bae, Kim, Cho, Baik, Lee, and Cha]{ahn_2014}
Ahn, Y.H.; Bae, S.J.; Kim, M.S.; Cho, S.K.; Baik, S.J.; Lee, J.I.; Cha, J.E.
\newblock Cycle layout studies of S-CO$_2$ cycle for the next generation nuclear
  system application.
\newblock  In Proceedings of the The Korean Nuclear Society Autumn Meeting, The Korean Nuclear
  Society,  \hl{2014.}%please add conference location and date, and the other highlighted part have the same problem, please revised

\bibitem[Wang \em{et~al.}(2018)Wang, Li, Guo, Li, and Liu]{wang_2018}
Wang, K.; Li, M.J.; Guo, J.Q.; Li, P.; Liu, Z.B.
\newblock A systematic comparison of different S-CO$_2$ Brayton cycle layouts
  based on multi-objective optimization for applications in solar power tower
  plants.
\newblock {\em Appl. Energy} {\bf 2018}, {\em 212},~109--121.
\newblock
  {\changeurlcolor{black}\href{https://doi.org/https://doi.org/10.1016/j.apenergy.2017.12.031}{\detokenize{https://doi.org/10.1016/j.apenergy.2017.12.031}}}.

\bibitem[wri(2009)]{wright_2009}
{{Supercritical CO$_2$ Brayton Cycle Power Generation Development Program and
  Initial Test Results}}.  In Proceedings of the  ASME Power
  Conference, \hl{2009.}
\newblock
  {\changeurlcolor{black}\href{https://doi.org/10.1115/POWER2009-81081}{\detokenize{10.1115/POWER2009-81081}}}.

\bibitem[doe(2012)]{doe_2012}
U.S. Department of Energy, Sunshot Vision Study.
\newblock  Available online: \url{http://www1.eere.energy.gov/solar/sunshot/vision_study.html}
  (accessed on 20 August 2021).

\bibitem[net(2016)]{netl_2016}
Supercritical Carbon Dioxide Pilot Plant Test Facility.
\newblock Avalaible online: \url{https://netl.doe.gov/project-information?p=FE0028979} (accessed
  on 30 August 2021).

\bibitem[set(2015)]{seto_2015}
Brayton Energy.
\newblock
 Avalaible online:  \url{https://www.energy.gov/eere/solar/project-profile-brayton-energy} (accessed
  on 30 August 2021).

\bibitem[Iverson \em{et~al.}(2013)Iverson, Conboy, Pasch, and
  Kruizenga]{iverson_2013}
Iverson, B.D.; Conboy, T.M.; Pasch, J.J.; Kruizenga, A.M.
\newblock Supercritical CO$_2$ Brayton cycles for solar-thermal energy.
\newblock {\em Appl. Energy} {\bf 2013}, {\em 111},~957--970.

\bibitem[ho_(2015)]{ho_2015}
{ {Cost and Performance Tradeoffs of Alternative Solar-Driven S-CO$_2$ Brayton
  Cycle Configurations}}. Volume 1: Advances in Solar Buildings and
  Conservation; Climate Control and the Environment; Alternate Fuels and
  Infrastructure; ARPA-E; Combined Energy Cycles, CHP, CCHP, and Smart Grids;
  Concentrating Solar Power; Economic, Environmental, and Policy Aspects of
  Alternate Energy; Geothermal Energy, Harvesting, Ocean Energy and Other
  Emerging Technologies; Hydrogen Energy Technologies; Low/Zero Emission Power
  Plants and Carbon Sequestration; Micro and Nano Technology Applications and
  Materials, {\em Energy Sustainability}  2015.  Available online: 
  \href{http://xxx.lanl.gov/abs/https://asmedigitalcollection.asme.org/ES/proceedings-pdf/ES2015/56840/V001T05A016/4448498/v001t05a016-es2015-49467.pdf}{{\normalfont
  https://asmedigitalcollection.asme.org/ES/proceedings-pdf/ES2015/56840/V001T05A016/4448498/v001t05a016-es2015-49467.pdf}} (accessed
  on 30 August 2021).

\bibitem[Neises(2020)]{neises_2020}
Neises, T.
\newblock Steady-state off-design modeling of the supercritical carbon dioxide
  recompression cycle for concentrating solar power applications with two-tank
  sensible-heat storage.
\newblock {\em Sol. Energy} {\bf 2020}, {\em 212},~19--33.

\bibitem[Dostal(2004)]{dostal_2004}
Dostal, V.
\newblock A Supercritical Carbon Dioxide Cycle for Next Generation Nuclear
  Reactors.
\newblock Ph.D. Thesis, Massachusetts Institute of Technology, Cambridge, MA, USA, 2004.

\bibitem[Luo and Huang(2020)]{luo_2020}
Luo, D.; Huang, D.
\newblock Thermodynamic and exergoeconomic investigation of various SCO$_2$
  Brayton cycles for next generation nuclear reactors.
\newblock {\em Energy Convers. Manag.} {\bf 2020}, {\em 209},~112649.
\newblock
  {\changeurlcolor{black}\href{https://doi.org/https://doi.org/10.1016/j.enconman.2020.112649}{\detokenize{https://doi.org/10.1016/j.enconman.2020.112649}}}.

\bibitem[Wright \em{et~al.}(2011)Wright, Conboy, and Rochau]{wright_2011}
Wright, S.A.; Conboy, T.M.; Rochau, G.E.
\newblock \emph{Break-even Power Transients for two Simple Recuperated S-CO$_2$ Brayton
  Cycle Test Configurations};
\newblock Technical Report; Sandia National Lab. (SNL-NM): Albuquerque, NM
USA,  2011.

\bibitem[Cha \em{et~al.}(2016)Cha, Bae, Lee, Cho, Lee, and Park]{cha_2016}
Cha, J.E.; Bae, S.W.; Lee, J.; Cho, S.K.; Lee, J.I.; Park, J.H.
\newblock Operation results of a closed supercritical CO$_2$ simple Brayton cycle.
\newblock In Proceedings of the 5th International Symposium-Supercritical CO$_2$
  Power Cycles, San Antonio, TX, USA, \hl{2016}; pp. 28--31.%please add conference date (day and month)

\bibitem[Held(2015)]{held_2015}
Held, T.J.
\newblock \emph{Suipercritical CO$_2$ Cycles for Gas Turbine Combined Cycle Power
  Plants};
\newblock  \hl{Power Gen International:} %Please add the location of the publisher.
 2015.

\bibitem[Fetvedt(2016)]{fetvedt_2016}
Fetvedt, J.
\newblock Development of the sCO$_2$ Allam Cycle.
\newblock  Supercritical CO$_2$ \hl{Power Cycles Symposium. 2016.}%please provide more information so we can confirm the type, such as weblink

\bibitem[Monnerie \em{et~al.}(2011)Monnerie, Schmitz, Roeb, Quantius, Graf,
  Sattler, and De~Lorenzo]{monnerie_2011}
Monnerie, N.; Schmitz, M.; Roeb, M.; Quantius, D.; Graf, D.; Sattler, C.;
  De~Lorenzo, D.
\newblock Potential of hybridisation of the thermochemical hybrid-sulphur cycle
  for the production of hydrogen by using nuclear and solar energy in the same
  plant.
\newblock {\em Int. J. Nucl. Hydrog. Prod. Appl.} {\bf 2011}, {\em 2},~178--201.

\bibitem[Curtis(2015)]{curtis_2015}
Curtis, D.J.
\newblock Nuclear Renewable Oil Shale Hybrid Energy Systems: Configuration,
  Performance, and Development Pathways.
\newblock Ph.D. thesis, Massachusetts Institute of Technology, Cambridge, MA, USA, 2015.

\bibitem[Wang \em{et~al.}(2020)Wang, Wang, Chen, and Hu]{wang_2020}
Wang, G.; Wang, C.; Chen, Z.; Hu, P.
\newblock Design and performance evaluation of an innovative solar-nuclear
  complementarity power system using the S–CO$_2$ Brayton cycle.
\newblock {\em Energy} {\bf 2020}, {\em 197},~117282.
\newblock
  {\changeurlcolor{black}\href{https://doi.org/https://doi.org/10.1016/j.energy.2020.117282}{\detokenize{https://doi.org/10.1016/j.energy.2020.117282}}}.

\bibitem[Turchi \em{et~al.}(2018)Turchi, Vidal, and Bauer]{turchi_2018}
Turchi, C.S.; Vidal, J.; Bauer, M.
\newblock Molten salt power towers operating at 600--650 C: Salt selection and
  cost benefits.
\newblock {\em Sol. Energy} {\bf 2018}, {\em 164},~38--46.

\bibitem[Klein and Nellis(2011)]{klein_nellis_2011}
Klein, S.; Nellis, G.
\newblock {\em Thermodynamics}; Cambridge University Press: Cambridge, MA, USA, 2011.
\newblock
  {\changeurlcolor{black}\href{https://doi.org/10.1017/CBO9780511994883}{\detokenize{10.1017/CBO9780511994883}}}.

\bibitem[Seidel(2010)]{seidel_2010_model_development}
Seidel, W.
\newblock Model Development and Annual Simulation of the Supercritical Carbon
  Dioxide Brayton Cycle for Concentrating Solar Power Applications.
\newblock Ph.D. Thesis, University of Wisconsin-Madison: Madison, WI, USA,  2010.

\bibitem[Pacheco \em{et~al.}(1995)Pacheco, Ralph, Chavez, Dunkin, Rush,
  Ghanbari, and Matthews]{pacheco_1995_salt_properties}
Pacheco, J.E.; Ralph, M.E.; Chavez, J.M.; Dunkin, S.R.; Rush, E.E.; Ghanbari,
  C.M.; Matthews, M.W.
\newblock Results of molten salt panel and component experiments for solar
  central receivers: Cold fill, freeze/thaw, thermal cycling and shock, and
  instrumentation tests {1995}. %%please add accessed date
 Available online: \url{https://www.osti.gov/servlets/purl/46671} (\hl{accessed on}).
\newblock
 % {\changeurlcolor{black}\href{https://doi.org/10.2172/46671}{\detokenize{10.2172/46671}}}.

\bibitem[Span and Wagner(1996)]{roland_1996_CO$_2$_properties}
Span, R.; Wagner, W.
\newblock A New Equation of State for Carbon Dioxide Covering the Fluid Region
  from the Triple‐Point Temperature to 1100 K at Pressures up to 800 MPa.
\newblock {\em J. Phys. Chem. Ref. Data} {\bf 1996},
  {\em 25},~1509--1596,
 % \href{http://xxx.lanl.gov/abs/https://doi.org/10.1063/1.555991}{{\normalfont
 % [https://doi.org/10.1063/1.555991]}}, doi:10.1063/1.555991.

\bibitem[Nellis and Klein(2008)]{nellis_klein_2008}
Nellis, G.; Klein, S.
\newblock {\em Heat Transfer}; Cambridge University Press: \hl{Cambridge, MA, USA,} %newly added information, please confirm
 2008, doi:10.1017/CBO9780511841606.

\bibitem[Dyreby(2014)]{dyreby_2014}
Dyreby, J.J.
\newblock Modeling the Supercritical Carbon Dioxide Brayton Cycle with
  Recompression.
\newblock Ph.D. Thesis, \hl{2014.}%please university and location
%\newblock Copyright - Database copyright ProQuest LLC; ProQuest does not claim
 % copyright in the individual underlying works; Last updated - 2021-10-26.

\bibitem[Smith and Cinotti(2016)]{smith_2016_lfr_background}
Smith, C.; Cinotti, L.
\newblock 6 - Lead-cooled fast reactor. In {\em Handbook of Generation IV
  Nuclear Reactors}; Pioro, I.L., Ed.; Woodhead Publishing Series in Energy,
  \hl{Woodhead Publishing:} %Please add the location of the publisher.
 2016; pp. 119--155.
\newblock
  {\changeurlcolor{black}\href{https://doi.org/https://doi.org/10.1016/B978-0-08-100149-3.00006-9}{\detokenize{https://doi.org/10.1016/B978-0-08-100149-3.00006-9}}}.

\bibitem[Alemberti \em{et~al.}(2014)Alemberti, Smirnov, Smith, and
  Takahashi]{alemberti_2013_lfr_overview}
Alemberti, A.; Smirnov, V.; Smith, C.F.; Takahashi, M.
\newblock Overview of lead-cooled fast reactor activities.
\newblock {\em Prog. Nucl. Energy} {\bf 2014}, {\em 77},~300--307.
\newblock
  {\changeurlcolor{black}\href{https://doi.org/https://doi.org/10.1016/j.pnucene.2013.11.011}{\detokenize{https://doi.org/10.1016/j.pnucene.2013.11.011}}}.

\bibitem[Mehos \em{et~al.}(2017)Mehos, Turchi, Vidal, Wagner, Ma, Ho, Kolb,
  Andraka, and Kruizenga]{mehos2017concentrating}
Mehos, M.; Turchi, C.; Vidal, J.; Wagner, M.; Ma, Z.; Ho, C.; Kolb, W.;
  Andraka, C.; Kruizenga, A.
\newblock \emph{Concentrating Solar Power Gen3 Demonstration Roadmap};
\newblock Technical Report; National Renewable Energy Lab. (NREL): Golden, CO,
 USA,  2017.

\bibitem[Hamilton \em{et~al.}(2020)Hamilton, Husted, Newman, Braun, and
  Wagner]{hamilton2020dispatch}
Hamilton, W.T.; Husted, M.A.; Newman, A.M.; Braun, R.J.; Wagner, M.J.
\newblock Dispatch optimization of concentrating solar power with utility-scale
  photovoltaics.
\newblock {\em Optim. Eng.} {\bf 2020}, {\em 21},~335--369.

\end{thebibliography}

%=====================================
% References, variant B: internal bibliography
%=====================================
% \begin{thebibliography}{999}
% % Reference 1
% \bibitem[Author1(year)]{ref-journal}
% Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% % Reference 2
% \bibitem[Author2(year)]{ref-book1}
% Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% % Reference 3
% \bibitem[Author3(year)]{ref-book2}
% Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% % Reference 4
% \bibitem[Author4(year)]{ref-unpublish}
% Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} stage of publication (under review; accepted; in~press).
% % Reference 5
% \bibitem[Author5(year)]{ref-communication}
% Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% % Reference 6
% \bibitem[Author6(year)]{ref-proceeding}
% Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of Presentation. In Title of the Collected Work (if available), Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference; Editor 1, Editor 2, Eds. (if available); Publisher: City, Country, Year (if available); Abstract Number (optional), Pagination (optional).
% % Reference 7
% \bibitem[Author7(year)]{ref-thesis}
% Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% % Reference 8
% \bibitem[Author8(year)]{ref-url}
% Title of Site. Available online: URL (accessed on Day Month Year).
% \end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2021-11-09 simulations/scripts/debugging__Model1_scripts/gen__PySAM_Pyomo_sweep_for_failures.py
adding line to update design point after perturbing Pref and tshours in sweep

@@ -39,7 +39,9 @@ print("PID = ", pid)
 
 # setting up arrays to cycle through
 tshours    = np.array([ 0, 2, 4, 6, 8, 10, 12, 14 ])
-p_cycle    = np.array([ 850, 800, 750, 700, 650, 600, 550, 500, 450, 400, 350, 300, 250, 200, 150, 100 ]) 
+# p_cycle    = np.array([ 850, 800, 750, 700, 650, 600, 550, 500, 450, 400, 350, 300, 250, 200, 150, 100 ]) 
+# p_cycle    = np.array([ 500, 450, 400, 350, 300, 250, 200, 150, 100 ]) 
+p_cycle    = np.array([ 850, 800, 750, 700, 650, 600, 550 ]) 
 
 # exceptions!
 # exceptions = {
@@ -89,9 +91,9 @@ op_modes_list = tmp_modes.operating_modes
 # =============================================================================
 # Double Loop
 # =============================================================================
-sscH = 12  # 12 # 24
-pyoH = 24  # 24 # 48
-json = "model1" # model1_CAISO # model1 # model1_noMin
+sscH = 24  # 12 # 24
+pyoH = 48  # 24 # 48
+json = "model1_CAISO" # model1_CAISO # model1 # model1_noMin
 dispatch = True # True # False
 run_loop = True
 
@@ -135,6 +137,7 @@ for i, th in enumerate(iterator1): #over tshours
         # update SSC dictionary parameters
         nuctes.SSC_dict['P_ref']   = float(pc)
         nuctes.SSC_dict['tshours'] = float(th)
+        nuctes.dispatch_wrap.set_design()
         
         # =========================================
         # exceptions we know don't work in SSC

### 2021-11-09 simulations/scripts/debugging__Model1_scripts/gen__PySSC_sweep_for_failures.py

@@ -91,7 +91,7 @@ op_modes_list = tmp_modes.operating_modes
 # =============================================================================
 sscH = 24  # 12 # 24
 pyoH = 48  # 24 # 48
-json = "model1" # model1_CAISO # model1 # model1_noMin
+json = "model1_CAISO" # model1_CAISO # model1 # model1_noMin
 dispatch = False # True # False
 run_loop = False
 

### 2021-11-09 simulations/scripts/debugging__Model1_scripts/run__PySAM_case.py

@@ -27,18 +27,18 @@ print("PID = ", pid)
 # =============================================================================
 
 # modifying inputs
-json = "model1"   # model1_CAISO # model1
+json = "model1_CAISO"   # model1_CAISO # model1
 dispatch = True
 run_loop = True
 sscH    = 24   # (hr)
 pyoH    = 48   # (hr)
-Pref    = 200  # (MW)
-tshours = 0    # (hr)
+Pref    = 850  # (MW)
+tshours = 2    # (hr)
 
 # ========================
 
 # defining directories
-nuctes = NuclearTES.NuclearTES(json_name=json, is_dispatch=dispatch, log_dispatch_targets=True) 
+nuctes = NuclearTES.NuclearTES(json_name=json, is_dispatch=dispatch, log_dispatch_targets=False) 
 output_file = 'output.csv'
 
 # horizons
@@ -53,6 +53,7 @@ nuctes.dispatch_wrap = nuctes.create_dispatch_wrapper( nuctes.PySAM_dict )
 # update SSC dictionary parameters
 nuctes.SSC_dict['P_ref'] = Pref
 nuctes.SSC_dict['tshours'] = tshours
+nuctes.dispatch_wrap.set_design()
 
 print("Pref    = {0}".format(nuctes.SSC_dict['P_ref'] ) )
 print("tshours = {0}".format(nuctes.SSC_dict['tshours'] ) )
@@ -133,7 +134,7 @@ upl.plot_SSC_massflow(ax3, plot_all_time=plt_allTime, start_hr=start, end_hr=end
 # retrieving the DispatchPlots class
 from util.PostProcessing import DispatchPlots
 # specifying dispatch model
-ind = 0
+ind = 160
 # extracting specific, solved dispatch model
 dm = nuctes.disp_models[str(ind)]
 # create Dispatch plotting object

### 2021-11-09 simulations/scripts/debugging__Model1_scripts/plot__PySSC_sweep_for_failures.py
updating list of filenames in plotting script

@@ -43,8 +43,15 @@ output_dir = FileMethods.output_dir
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_0__horizon_24_48__TES_[0,14]__PC_[100,850].nuctes'
 # filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[100,850].nuctes'
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[100,850].nuctes'
-filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,850].nuctes'
+# filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,850].nuctes'
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,850].nuctes'
+
+# filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[100,500].nuctes'
+# filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,500].nuctes'
+# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[100,500].nuctes'
+# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,500].nuctes'
+# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[550,850].nuctes'
+filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[550,850].nuctes'
 
 NTPath = os.path.join(output_dir, filename)
 

### 2021-11-10 papers/sustainability-1425053/sustainability-1425053-english.tex
Add files via upload
Make Brian's final changes. Comment out the unneeded statements at the end of the tex on consent statements

@@
 %\ddagger -> adds double dagger
-\Author{\hl{Brian White} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.
- $^{1}$, Michael Wagner~$^{1}$\orcidB{}, Ty Neises~$^{3}$, Cory Stansbury~$^{4}$ and Ben Lindley~$^{2,}$*\orcidA{}}
+\Author{\hl{Brian T. White} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.
+ $^{1}$, Michael J. Wagner~$^{1}$\orcidB{}, Ty Neises~$^{3}$, Cory Stansbury~$^{4}$ and Ben Lindley~$^{2,}$*\orcidA{}}
 
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Brian White, Michael Wagner, Ty Neises, Cory Stansbury and Ben Lindley}
+\AuthorNames{Brian T. White, Michael J. Wagner, Ty Neises, Cory Stansbury and Ben Lindley}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{White, B.; Wagner, M.; Neises, T.; Stansbury, C.; Lindley, B.}
+\AuthorCitation{White, B.T.; Wagner, M.J.; Neises, T.; Stansbury, C.; Lindley, B.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 The~lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided.
-The~molten salt loop for the CSP is modeled with necessary components including hot and cold TES, receiver, pumps and counter-flow heat~exchangers.
+The~molten salt loop for the CSP is modeled with necessary components including hot and cold TES, receiver, pumps, and counter-flow heat~exchangers.
 
@@
 All of the prior equations are carried out in a built-in function within EES.
-EES is an iterative solver, and therefore as long as there is a feasible solution, the~functions can take any of the four state points around the heat exchanger and converge on a~solution.
+EES is an iterative solver, and therefore if there is a feasible solution, the~functions can take any of the four state points around the heat exchanger and converge on a~solution.
 
@@
 The~inlet temperature of the main compressor, $T_{1A}$, is set to a value of $40~^{\circ}$C in all models.
-The~temperature of the sCO$_2$ on the outlet of the LFR HX has different variable names, T$_5$, T$_{2C}$, T$_{6A}$, and~T$_{5C}$, according to the associated cycle configuration diagram.}{}.
+The~temperature of the sCO$_2$ on the outlet of the LFR HX has different variable names, T$_5$, T$_{2C}$, T$_{6A}$, and~T$_{5C}$, according to the associated cycle configuration diagram.}{}
 
@@
     %[!h] 
-   % \widefigure
+   \widefigure
     \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
@@
 The calculated values reported in Table~\ref{tab-noncharg} are component power, mass flow fractions, and~counter-flow heat exchanger specifications.
-Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$~^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction.
+Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$~^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off a parametric study on the MC mass flow fraction.
 Values listed in the Cold TES Temperature row are set to values of 390$~^{\circ}$C, 410$~^{\circ}$C, or~440$~^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations.
@@
 For~C-LFR-CIRC, the~highest efficiencies are achieved when the cold TES temperature is $10~^{\circ}$C less than the inlet to the LFR, this is due to the approach temperature on the C2S heat exchanger.
-If~the sCO$_2$ LFR inlet temperature is constrained to $400~^{\circ}$C, then the desired cold TES temperature is $390~^{\circ}$C to allow for the apporach temperature.
+If~the sCO$_2$ LFR inlet temperature is constrained to $400~^{\circ}$C, then the desired cold TES temperature is $390~^{\circ}$C to allow for the approach temperature.
 If~the cold TES is at a higher temperature, then the chiller is needed.
@@
 
-C-LFR-PAR and C-LFR-CIRC are therefore options going forward, with~a trade-off between heat storage efficiency and component costs, with~the performance of C-LFR-CIRC also depending on the choise of charging~configuration.
+C-LFR-PAR and C-LFR-CIRC are therefore options going forward, with~a trade-off between heat storage efficiency and component costs, with~the performance of C-LFR-CIRC also depending on the choice of charging~configuration.
 
@@
 
- \institutionalreview{\hl{x}}%In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
+% \institutionalreview{\hl{x}}%In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
 Please note that the Editorial Office might ask you for further information.
@@
 
- \informedconsent{\hl{x}}%Any research article describing a study involving humans should contain this statement.
+ %\informedconsent{\hl{x}}%Any research article describing a study involving humans should contain this statement.
 Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.

### 2021-11-10 papers/sustainability-1425053/sustainability-1425053-english.tex
Add files via upload
Re-sized Fig. 4 (correct at 2nd attempt)
Add files via upload
Corrected the utter carnage previous change of figure did to the LaTeX so now it looks OK

@@
 
-% \end{paracol}
+ \end{paracol}
 \begin{figure}[H] 
     %[!h] 
-   \widefigure
+  % \widefigure
     \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
@@
 \end{figure}
-% \begin{paracol}{2}
+ \begin{paracol}{2}
 % %\linenumbers
-% \switchcolumn
+ \switchcolumn
 
@@
 $\dot{Q}$ & Heat transfer rate [W]\\
-$T$ & Temperature []$~^{\circ}$C]\\
+$T$ & Temperature [$~^{\circ}$C]\\
 $UA$ & Conductivity of heat exchanger [MW/$~^{\circ}$C]\\

### 2021-11-10 simulations/modules/GenericSSCModule.py
printing out SSC error message and saving it if one appears

@@ -562,6 +562,7 @@ class GenericSSCModule(ABC):
             Plant.execute()
         except Exception as err:
             exec_success = False
+            self.err_message = str(err)
             print("\n SSC error: {0}".format(err))
             
         return exec_success, Plant

### 2021-11-10 simulations/scripts/debugging__Model1_scripts/gen__PySAM_Pyomo_sweep_for_failures.py
fixing labels, titles, and SSC error messages when pgenerating and plotting

@@ -40,8 +40,8 @@ print("PID = ", pid)
 # setting up arrays to cycle through
 tshours    = np.array([ 0, 2, 4, 6, 8, 10, 12, 14 ])
 # p_cycle    = np.array([ 850, 800, 750, 700, 650, 600, 550, 500, 450, 400, 350, 300, 250, 200, 150, 100 ]) 
-# p_cycle    = np.array([ 500, 450, 400, 350, 300, 250, 200, 150, 100 ]) 
-p_cycle    = np.array([ 850, 800, 750, 700, 650, 600, 550 ]) 
+p_cycle    = np.array([ 500, 450, 400, 350, 300, 250, 200, 150, 100 ]) 
+# p_cycle    = np.array([ 850, 800, 750, 700, 650, 600, 550 ]) 
 
 # exceptions!
 # exceptions = {
@@ -73,7 +73,7 @@ qdot_nuc  = empty2D.copy()
 TES_CH    = empty.copy()
 TES_DC    = empty.copy()
 iter_log  = empty.copy()
-fail_log  = empty.copy() # 0 = No failure, 1 = SSC caused failure, 2 = Pyomo caused failure, 3 = Pyomo crash occurred, but sim continued
+fail_log  = empty.copy() # 0 = No failure, 1 = SSC caused failure, 2 = Pyomo caused failure, 3 = Pyomo crash occurred, but sim continued, 4 = SSC low mass flow error
 pyomo_bad_log     = empty.copy()
 pyomo_bad_idx_log = empty.copy()
 
@@ -248,6 +248,11 @@ for i, th in enumerate(iterator1): #over tshours
                     # Simulation ended because of SSC crash   == 1 
                     # Simulation ended because of Pyomo crash == 2 
                     fail_log[idx] = 1 if disp_success else 2 
+                
+                if hasattr(nuctes,'err_message'):
+                    if 'Mass flow rate too low' in nuctes.err_message:
+                        fail_log[idx] = 4
+                    
                 
                 dummy_val = -1
                 # log output means

### 2021-11-10 simulations/scripts/debugging__Model1_scripts/plot__PySSC_sweep_for_failures.py

@@ -50,8 +50,8 @@ output_dir = FileMethods.output_dir
 # filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,500].nuctes'
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[100,500].nuctes'
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,500].nuctes'
-# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[550,850].nuctes'
-filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[550,850].nuctes'
+filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[550,850].nuctes'
+# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[550,850].nuctes'
 
 NTPath = os.path.join(output_dir, filename)
 
@@ -114,7 +114,7 @@ x, y = np.meshgrid(x_series, y_series)
 for i, x_val in enumerate(x_series):
     for j, y_val in enumerate(y_series):
          condition = fail_log[i,j]
-         color = 'y' if condition == 1 else 'm' if condition == 2 else 'w' 
+         color = 'y' if condition == 1 else 'g' if condition == 2 else 'm' if condition == 4 else 'w' 
          color = 'c' if pyomo_bad_log[i,j] else color
          text = ax1.text(x_val, y_val, str(int(p_array[i,j])), color=color, fontsize=10, va='center', ha='center')
          text.set_path_effects([PathEffects.Stroke(linewidth=3, foreground='black'), PathEffects.Normal()])
@@ -145,7 +145,7 @@ cmap = cm.hot_r
 # ========== Arrays ==========
 p_array = copy.deepcopy( defocus[:,:,0] ) 
 array = copy.deepcopy( defocus[:,:,0] ) 
-mean_label = "% of simulation completed"
+mean_label = "defocus fraction"
 
 # ========== Figure ==========
 fig = plt.figure(figsize=(8,14))
[…]

### 2021-11-10 simulations/scripts/debugging__Model1_scripts/run__PySAM_case.py

@@ -32,8 +32,8 @@ dispatch = True
 run_loop = True
 sscH    = 24   # (hr)
 pyoH    = 48   # (hr)
-Pref    = 850  # (MW)
-tshours = 2    # (hr)
+Pref    = 650  # (MW)
+tshours = 0    # (hr)
 
 # ========================
 
@@ -117,7 +117,7 @@ ax2 = fig.add_subplot(312)
 ax3 = fig.add_subplot(313)
 
 plt_allTime = True
-title = 'SSC Results \nSSC horizon = {0}, Pyomo Horizon = {1} \nPref = {2:.2f} , tshours = {3}'.format( \
+title = 'SSC Results \nSSC horizon = {0} hr, Pyomo Horizon = {1} hr \nPref = {2:.2f} , tshours = {3}'.format( \
                                 sscH, pyoH, nuctes.SSC_dict['P_ref'], nuctes.SSC_dict['tshours'])
 start = 0
 end   = start + 3600
@@ -134,7 +134,7 @@ upl.plot_SSC_massflow(ax3, plot_all_time=plt_allTime, start_hr=start, end_hr=end
 # retrieving the DispatchPlots class
 from util.PostProcessing import DispatchPlots
 # specifying dispatch model
-ind = 160
+ind = 220
 # extracting specific, solved dispatch model
 dm = nuctes.disp_models[str(ind)]
 # create Dispatch plotting object
@@ -155,7 +155,10 @@ ax5 = fig.add_subplot(515)
 plt.subplots_adjust(hspace=0)
 # plt.gcf().subplots_adjust(bottom=0.1) # leaving room at the bottom
 
-dpl.plot_pyomo_energy(      ax1, x_legend=1.04, y_legend_L=1.0, hide_x=True )
+title_pyo = 'Pyomo Results \nTime after Sim Start = {0} d, Pyomo Horizon = {1} hr \nPref = {2:.2f} , tshours = {3}'.format( \
+                                (ind*sscH*u.hr).to('d').m, pyoH, nuctes.SSC_dict['P_ref'], nuctes.SSC_dict['tshours'])
+
+dpl.plot_pyomo_energy(      ax1, x_legend=1.04, y_legend_L=1.0, hide_x=True, title_label=title_pyo )
 dpl.plot_pyomo_power(       ax2, x_legend=1.15, y_legend_L=1.0, hide_x=True )
[…]

### 2021-11-10 simulations/dispatch/GeneralDispatch.py
fixing unit issue with delta w

@@ -161,10 +161,10 @@ class GeneralDispatch(ABC):
         #------- Variables ---------
         self.model.ucsu = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kWh)                             #u^{csu}: Cycle start-up energy inventory at period $t$ [kWt$\cdot$h]
         self.model.wdot = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW)                              #\dot{w}: Power cycle electricity generation at period $t$ [kWe]
-        self.model.wdot_delta_plus = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW)	                #\dot{w}^{\Delta+}: Power cycle ramp-up in period $t$ [kWe]
-        self.model.wdot_delta_minus = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW) 	                #\dot{w}^{\Delta-}: Power cycle ramp-down in period $t$ [kWe]
-        self.model.wdot_v_plus = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.W_v_plus), units=u.kW)      #\dot{w}^{v+}: Power cycle ramp-up beyond designed limit in period $t$ [kWe]
-        self.model.wdot_v_minus = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.W_v_minus), units=u.kW) 	 #\dot{w}^{v-}: Power cycle ramp-down beyond designed limit in period $t$ [kWe]
+        self.model.wdot_delta_plus = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW/u.hr)	                #\dot{w}^{\Delta+}: Power cycle ramp-up in period $t$ [kWe/hr]
+        self.model.wdot_delta_minus = pe.Var(self.model.T, domain=pe.NonNegativeReals, units=u.kW/u.hr) 	                #\dot{w}^{\Delta-}: Power cycle ramp-down in period $t$ [kWe/hr]
+        self.model.wdot_v_plus = pe.Var(self.model.T, domain=pe.NonNegativeReals, bounds = (0,self.model.W_v_plus), units=u.kW/u.hr)      #\dot{w}^{v+}: Power cycle ramp-up beyond designed limit in period $t$ [kWe/hr]
[…]

### 2021-11-15 simulations/dispatch/GeneralDispatch.py
if pyomo fails, now tries solving with simpler pivot method

@@ -454,7 +454,7 @@ class GeneralDispatch(ABC):
             return ineq
 
 
-    def solve_model(self, mipgap=0.7, tee=False):
+    def solve_model(self, mipgap=0.7, tee=False, run_simple=False):
         """ Method to solve the Pyomo model
         
         This method solves the Pyomo Concrete model that has been instantiated
@@ -481,6 +481,10 @@ class GeneralDispatch(ABC):
         
         # setting optimality condition
         opt.options["ratioGap"] = mipgap
+        
+        if run_simple:
+            opt.options["primalPivot"] = "dantzig"
+            opt.options["dualPivot"]   = "dantzig"
         
         # solving model
         results = opt.solve(self.model, tee=tee, keepfiles=False)

### 2021-11-15 simulations/scripts/debugging__Model1_scripts/plot__PySSC_sweep_for_failures.py
updating plots

@@ -50,8 +50,8 @@ output_dir = FileMethods.output_dir
 # filename   = 'failureModes_PySAM__model1_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,500].nuctes'
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[100,500].nuctes'
 # filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[100,500].nuctes'
-filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[550,850].nuctes'
-# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[550,850].nuctes'
+# filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_24_48__TES_[0,14]__PC_[550,850].nuctes'
+filename   = 'failureModes_PySAM__model1_CAISO_2021_11__pyomo_1__horizon_12_24__TES_[0,14]__PC_[550,850].nuctes'
 
 NTPath = os.path.join(output_dir, filename)
 
@@ -93,7 +93,7 @@ full_title = "PySSC - {0} tariffs {1} Pyomo - {2:.0f}/{3:.0f}hr horizons ".forma
 cmap = cm.hot_r
 
 # ========== Arrays ==========
-p_array = copy.deepcopy( iter_log ) 
+p_array = copy.deepcopy( iter_log ) / 24.
 array = copy.deepcopy( iter_log ) / 8760. * 100
 mean_label = "% of simulation completed"
 
@@ -116,7 +116,7 @@ for i, x_val in enumerate(x_series):
          condition = fail_log[i,j]
          color = 'y' if condition == 1 else 'g' if condition == 2 else 'm' if condition == 4 else 'w' 
          color = 'c' if pyomo_bad_log[i,j] else color
-         text = ax1.text(x_val, y_val, str(int(p_array[i,j])), color=color, fontsize=10, va='center', ha='center')
+         text = ax1.text(x_val, y_val, '{0:.1f}'.format(p_array[i,j]), color=color, fontsize=10, va='center', ha='center')
[…]

### 2021-11-15 simulations/scripts/debugging__Model1_scripts/run_PySSCWrap_DispatchTargets.py
script to run PySSC with pre-generated pyomo dispatch targets

@@ -1,0 +1,36 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon May 24 10:27:17 2021
+
+@author: gabrielsoto
+"""
+
+from util.PySSCWrapper import PySSCWrapper
+import os
+
+# print the PID of this script run
+pid = os.getpid()
+print("PID = ", pid)
+
+# initialize the PySSC Wrapper
+pw = PySSCWrapper(json_name='model1_CAISO',is_debug=True)
+
+# update SSC dictionary parameters
+pw.sscdict['tshours']   = 0
+pw.sscdict['P_ref']     = 400
+
+# run SSC through PySSC
+pw.run_sim(run_dispatch_targets=True)
+
+# get output arrays from the SSC run
+p_cycle       = pw.get_array('P_cycle')
+gen           = pw.get_array('gen') / 1e3
+p_cool        = pw.get_array('P_cooling_tower_tot')
+q_dot_rec_in  = pw.get_array('q_dot_rec_inc')
+m_dot         = pw.get_array('m_dot_rec')
+T_pc_in       = pw.get_array('T_pc_in')
+T_pc_out      = pw.get_array('T_pc_out')
+e_ch_tes      = pw.get_array('e_ch_tes')
+t_plot        = pw.get_array('time_hr') / 24
+op_mode_1     = pw.get_array('op_mode_1')

### 2021-11-15 simulations/modules/GenericSSCModule.py
fixing last log of dispatch targets if SSC fails

@@ -879,14 +879,13 @@ class GenericSSCModule(ABC):
         
         if self.log_dispatch_targets:
             if not self.hash_exists:
-                if not log_final:
-                    for l in self.Log_Target_Arrays.keys():
-                        # get what we have logged so far
-                        disp_targ = getattr(self.Plant.SystemControl, l )
-                        # grab and save corresponding slices to self (this should be some sort of pointer)
-                        self.Log_Target_Arrays[l][self.slice_ssc_currentH] = disp_targ[self.slice_ssc_firstH]
+                for l in self.Log_Target_Arrays.keys():
+                    # get what we have logged so far
+                    disp_targ = getattr(self.Plant.SystemControl, l )
+                    # grab and save corresponding slices to self (this should be some sort of pointer)
+                    self.Log_Target_Arrays[l][self.slice_ssc_currentH] = disp_targ[self.slice_ssc_firstH]
             
-                else:
+                if log_final:
                     with open(self.hash_filepath, "wb") as f:
                         pickle.dump(self.Log_Target_Arrays, f)
                     print("Dispatch Targets successfuly stored in {0}".format(self.hash_filepath))        

### 2021-11-15 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

@@
 Additionally, to confirm approximate linearity of specific heats at differential steps throughout the counter-flow heat exchanger, the specific heat as a function of dimensionless length of the hot and cold streams in the LTR and HTR are plotted in Figure \ref{graph-c-vs-p-ltr} and Figure \ref{graph-c-vs-p-htr} respectively.}{}
+\end{paracol}
 
 \begin{figure*}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Definitions/c-vs-p-ltr.pdf}
@@
     \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Definitions/t-vs-p-ltr.pdf}
@@
     \vskip\baselineskip
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Definitions/c-vs-p-htr.pdf}
@@
     \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Definitions/t-vs-p-htr.pdf}
@@
 
-\replaced[comment={Improving counter-flow hx explanation [1,1]}]{The calculations used to discretize the counter-flow heat exchangers into a sub-heat exchanger model, shown in Figure \ref{graphs-t-c-vs-p}, is from JJ Dyreby's (2014) PhD thesis \cite{dyreby_2014}.
-The series of figures are constructed using extreme values experienced by the recuperators; the cold inlet temperature is lowest recorded value, and the hot inlet temperature is the highest recorded value.
-As seen in the presented graphs, the capacitance ratio determines the approach temperature, not an internal pinch point in the recuperator.
-All pinch points recorded are on the high end.}{}
+\begin{paracol}{2}
+    \linenumbers
+    \switchcolumn
+
+\replaced[comment={Improving counter-flow hx explanation [1,1]}]{The calculations used to discretize the counter-flow heat exchangers into a sub-heat exchanger model, shown in Figure \ref{graphs-t-c-vs-p}, is from Dyreby \cite{dyreby_2014}.
+Figure~\ref{graphs-t-c-vs-p} is constructed using the most extreme temperature values experienced by the recuperators -- the cold inlet and hot outlet are the lowest and highest modeled temperature values, respectively.
+As demonstrated, the capacitance ratio determines the approach temperature instead of any possible internal pinch point within the recuperator.
+All pinch points recorded are on the high-temperature end.}{}
 

### 2021-11-15 simulations/scripts/PySAM_model1_sweep.py
update for CAISO data

@@ -25,6 +25,8 @@ u = pint.UnitRegistry()
 pid = os.getpid()
 print("PID = ", pid)
 
+turbine_source = "ud_ind_od.csv" #ud_ind_od.csv or had_slid_560.csv
+
 
 #parse the dispatch factors file
 dispatch_data = []
@@ -33,13 +35,19 @@ with open ("../data/dispatch_factors_ts.csv") as f:
         dispatch_data.append(float(line.strip()))
 dispatch_data=np.array(dispatch_data)
 
+caiso_dispatch_data=[]
+with open("../data/CAISO_dispatch_factors.csv") as f:
+    for line in f:
+        caiso_dispatch_data.append(float(line.strip()))
+caiso_dispatch_data=np.array(caiso_dispatch_data)
+
 # create empty dictionary for results
 results={}
 
 p_refs=[465,525,600,700,800]
 cycle_max_fracs=[1.05]
 remove_tes_costs=[False]
-exaggerates=[1]#,1.5,2] 
+exaggerates=["caiso"] #[1,1.5,2] 
 for p_ref in p_refs:
     results[p_ref]={}
     
@@ -63,6 +71,8 @@ for p_ref in p_refs:
                 with open("../json/model1.json") as f:
                     base_sim = json.load(f)
                 
+                base_sim["PySAM_inputs"]["ud_file"]="data/"+turbine_source
+                
                 turbine_unit_cost = 225 #Cory email 8th Nov 2021
                 turbine_ref = 950*base_sim["SSC_inputs"]["design_eff"]
                 turbine_premium = turbine_unit_cost*(p_ref-turbine_ref)
@@ -83,13 +93,16 @@ for p_ref in p_refs:
                 results[p_ref][cycle_max_frac][remove_tes_cost][exaggerate]=[]
                 
                 #increase the difference of the factors from unity
-                new_dispatch_data = list((dispatch_data-1)*exaggerate+1)
+                if exaggerate == "caiso":
+                    new_dispatch_data = caiso_dispatch_data
+                else:
+                    new_dispatch_data = list((dispatch_data-1)*exaggerate+1)
                 with open("../data/temp_dispatch_factors.csv","w") as f:
                     for item in new_dispatch_data:
                         f.write("{:.5f}\n".format(item))
                 
                 #sweep the TS Hours 
-                for tshours in range(1): #6 if p_ref >465 else 1):
+                for tshours in range(6 if p_ref >465 else 1):
[…]

### 2021-11-16 simulations/scripts/PySAM_model1_modified.py
fixing re-setting design point after modification

@@ -26,18 +26,18 @@ print("PID = ", pid)
 # =============================================================================
 
 # modifying inputs
-json = "model1"   # model1_CAISO # model1
+json = "model1_CAISO"   # model1_CAISO # model1
 dispatch = True
 run_loop = True
 sscH    = 24   # (hr)
 pyoH    = 48   # (hr)
 Pref    = 700  # (MW)
-tshours = 8    # (hr)
+tshours = 10    # (hr)
 
 # ========================
 
 # defining directories
-nuctes = NuclearTES.NuclearTES(json_name=json, is_dispatch=dispatch, log_dispatch_targets=True) 
+nuctes = NuclearTES.NuclearTES(json_name=json, is_dispatch=dispatch, log_dispatch_targets=False) 
 output_file = 'output.csv'
 
 # horizons
@@ -52,6 +52,7 @@ nuctes.dispatch_wrap = nuctes.create_dispatch_wrapper( nuctes.PySAM_dict )
 # update SSC dictionary parameters
 nuctes.SSC_dict['P_ref'] = Pref
 nuctes.SSC_dict['tshours'] = tshours
+nuctes.dispatch_wrap.set_design()
 
 print("Pref    = {0}".format(nuctes.SSC_dict['P_ref'] ) )
 print("tshours = {0}".format(nuctes.SSC_dict['tshours'] ) )

### 2022-02-21 papers/Review Response/Example Review/referee_responses_OPTE.tex

\documentclass[10pt]{article}

\usepackage{graphicx,amsmath,epsf, amssymb}
\usepackage{setspace, natbib, graphicx,amsmath,epsf}
\usepackage{color}
\usepackage{lineno}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{geometry}
\usepackage{pifont}
\usepackage{fleqn}
\usepackage{txfonts}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage[mathscr]{euscript}
\usepackage{natbib}

\linenumbers

\linespread{1.4}

\renewcommand{\baselinestretch}{1.0}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{9.in}
\renewcommand{\floatpagefraction}{.9}
\renewcommand{\topfraction}{.9}
\renewcommand{\bottomfraction}{.9}
\renewcommand{\textfraction}{.1}
%\input epsf
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\star$}
\renewcommand{\labelitemiii}{$\cdot$}
%\theoremstyle{break}
%\theoremstyle{plain}
\newtheorem{Thm}{Theorem}
\newtheorem{Cor}{Corollary}
\newtheorem{Obs}{Observation}
\newtheorem{Prop}{Proposition}
\newtheorem{Exa}{Example}[section]
\usepackage{color}
\usepackage{url}
\newtheorem{Def}{Definition}
%\newtheorem{Prop}[Cor]{Proposition}
%\theoremheadderfont{\scshape}
\newcommand{\dblon}{\addtolength{\baselineskip}{.1in}}
\newcommand{\dbloff}{\addtolength{\baselineskip}{-.1in}}
\newcommand{\tcm}{\textcolor{magenta}}
\newcommand{\tcga}{\textcolor{teal}}
\newcommand{\tcy}{\textcolor{yellow}}
\newcommand{\kw}[1]{$<${\it #1}$>$}

\input epsf
%\input{./packages_and_newcommands}
% Natbib setup for author-year style
\usepackage{natbib}
 \bibpunct[, ]{(}{)}{,}{a}{}{,}%
 \def\bibfont{\small}%
 \def\bibsep{\smallskipamount}%
 \def\bibhang{24pt}%
 \def\newblock{\ }%
 \def\BIBand{and}%

\begin{document}

\begin{center}
{\Large Referee responses, Paper \#OPTE-2021-2022:\\ Real-time Dispatch Optimization for Concentrating Solar Power with Thermal
Energy Storage}
\end{center}

\bigskip
%\noindent \hrulefill \vspace{-.05cm}

\noindent
\tcp{Alexandra}\\
\tco{John}\\
\tcc{Alex}\\
\tcg{Bill}\\
\tcr{Mike}\\
\tcb{Done}

\setcitestyle{citesep={;}} %use semicolon to seperate multiple citations
%\noindent \hrulefill \vspace{-.05cm}
\bigskip

{\bf  Editor}

{\bf Comments to the Author:}\\

Based on the feedback we received and my own review of your manuscript, I feel
that your manuscript is of interest to the journal and can be reassessed for
publication should you be prepared to incorporate major revisions. When
preparing your revised manuscript, please carefully consider the referee
comments attached, and submit an itemized list of responses and actions taken
to address these comments.

%\bigskip
\noindent \hrulefill \vspace{-.05cm}

\noindent

The authors thank the editor and reviewers for thoroughly reading the paper; we have done our best to address all the comments, have thoroughly proofread the paper, and hope that the paper is now improved. We provide the reviewers' comments in black font while our responses are given in \tcb{blue}.

\noindent \hrulefill \vspace{-.05cm}
\bigskip

{\bf Reviewer \#1}:

{\bf Comments to Author}\\

I have now completed a thorough review of your manuscript titled ``Real-time
Dispatch Optimization for Concentrating Solar Power with Thermal Energy
Storage." Your paper presents a very detailed model for operating a concentrating solar
power (CSP) plant with thermal energy storage (TES) to maximize profit.
Compared to previous models for this application, your paper's model includes
several novel features. Most importantly, you represent the receiver, storage,
and power cycle based on mass and temperature (rather than just energy), which
allows you to consider temperature-dependent efficiencies of processes within
the CSP plant. Since these features add more nonlinearities to the model, you
deploy several strategies to obtain near-optimal solutions in less than five
minutes, which would enable practical implementation in real time. Overall,
your model appears to be technically sound, and your paper is well written and
presented.

While I believe that your paper has the potential to become worthy of
publication in {\it Optimization and Engineering}, there are a number of issues (some
major, some minor) that I think you need to address before your paper can be
accepted. Therefore, my recommendation to the Editor is a {\bf Major Revision} to
address the following issues.

\begin{enumerate}

\item Your paper should do a better job clearly stating its main contributions at
the beginning, in the Introduction. First, what novel features does your model
of CSP plant operations include that have not been included in other models to
date (and why are these features important)? Second, what methodological
techniques do you develop and employ to allow you to solve the resulting
problem efficiently and to near-optimality? Actually, your sentence in Section
6 that begins with ``Our contributions include..." does a pretty good job of
answering my first question, but a clear statement like this should appear in
the Introduction and distinguish contributions to your specific CSP application
vs. contributions to methodology. In addition, you should specify your intended
audiences and your contributions that are of interest to them. Clearly, your
paper and its novel model features are relevant to other modelers who work on
CSP as an application, but this audience is quite small and niche. Are any of
your contributions relevant to a broader audience? Would any of your solution
strategies be useful for problems beyond CSP? Perhaps there are many other
energy and industrial processes that involve temperature-dependent efficiencies
with similar nonlinearities, and maybe your variable temporal resolution scheme
could help navigate tradeoffs between resolution and computational tractability
in many diverse settings. In short, your Introduction should more clearly
summarize your contributions and make a stronger effort to convince more of the
{\it Optimization and Engineering} readership that your paper is worth reading.

\tcb{The penultimate paragraph of \S1 now reads as follows:  ``The combination of the variable solar resource, the capability to defer electricity production, and the efficiency trade-off resulting from the temperature-limiting control policy creates challenging decisions for plant operators competing in the day-ahead utility energy market. The contributions of our paper entail the extension of an existing mixed-integer, linear programming model  which determines the optimal dispatch solution, maximizing plant revenue less estimated operating costs \citep{Wagner_2017}.
Specifically, we modify the model to allow real-time decision support by (i) increasing time fidelity in the near-term  horizon; (ii)  enforcing minimum up- and down-time requirements at the power cycle; (iii) improving the accuracy of the receiver and power cycle start-up processes; and, (iv) using explicit variables to represent mass and temperature  of the receiver, storage, and the power cycle. The resulting non-convex mixed-integer, quadratically-constrained program is computationally intractable with respect to supporting real-time decisions. Therefore, we present exact and inexact techniques to improve problem tractability, making it suitable for real-time decision support." That is, we state both the modeling and mathematical contributions upfront, before the paper organization (and literature review). We have additionally summarized our contributions towards the end of the \S2 Literature Review (see final two paragraphs) to contextualize our work.}
\tcr{Mike to address the second part starting with ``In addition, you should specify your intended
audiences and your contributions that are of interest to them...." by citing papers on grid storage with a thermal cycle or other cycle operations.}

\item Your model is very detailed and it is presented clearly in Section 3, but
this presentation is also quite long and tedious. Do you really need all of
these equations to appear in Section 3, or could you relegate more of them to
Appendix A? The way I would think about it is this: when you consider each of
your novel model features (such as the four identified on page 29, line 23), if
some equations are not relevant to these features specifically (i.e., they are
standard in existing CSP dispatch models), then they probably should not go in
Section 3. I would put the full, uninterrupted notation and model formulation
in Appendix A, and in Section 3, include only the notation and equations that
are needed to show how you represent your novel model features. It would also
be helpful to more clearly distinguish the linear and nonlinear versions of
various model elements. Right now, it is quite difficult for readers to do this
because the linear and nonlinear versions of constraints are included in the
same multi-equation blocks, and then on page 19 you have to include a
painstakingly detailed list of only the linear constraints that are included in
the linear version of the problem. When presenting the linear and nonlinear
representations of each model element, you could more clearly distinguish them
with labels, putting the two representations side-by-side in two columns, etc.
Overall, it needs to be easier for readers to focus their attention on the most
important model features and how your linear and nonlinear representations
differ.

\tcb{We have now placed the entire mathematical formulation in {\bf Appendix A} in a continuous fashion, with references after each ``subsection" of constraint to the paragraph following the formulation where the constraints are explained in English. These explanations mimic those given in the body of the paper (\S3 in the original draft, now \S4). Also please note the following about the math: (i) we have retained the table of notational definitions in \S4, corresponding to all the notation we use in that section; and (ii) \S4 remains unchanged from that in the original paper because every mathematical expression was either (a) new to the nonlinear model, or (b) necessary to understand the context in which the rest of the formulation exists. Unfortunately, all this detail is necessary to capture the real-time operations of the plant that depend on the ability to distinguish both the mass flow rates and temperatures in the hot and cold tanks for each time period in the relevant horizon.  Such a model is in direct contrast to  those pertaining to energy optimization   that characterizes occurrences over long periods of time, given in unit commitment models \citep{van2013unit} and regional capacity expansion models \citep{krishnan2016evaluating}.  }
\tcc{To explain the system operations in a simpler form prior to the detailed description, we have edited Figure 1 to relate the constraint sets in \S4 to the various subsystems of the CSP plant that they represent.  Additionally, Figure has been moved to what is now \S3, an overview of CSP plant operations, which we detail in our response to comment 6 below.}

\tcg{Try to construct a table with two columns that have the English associated with various attributes in the linear model and then how we handle them in the nonlinear model (e.g., omit, modify, replace).   }  \tcc{We could refer to Figure 1 when we go through the constraints and move some of the English up in addition to explaining why the organization is what it is.  The way the flow is currently set up is that we are following the energy through the system.}

\item Your model is quite detailed, so readers have to invest a considerable
amount of time and effort to understand it and make it to your Results section
on page 23. As it stands, I do not think that your Results section provides
enough findings and insights to justify all the work required to get to this
point in the paper. Specifically, you should run more scenarios where you
selectively include / exclude the various novel model features and solution
tactics that you developed and employed, so that by comparing their results, we
can understand the implications and advantages (hopefully) of your
methodological innovations. For example,  ``formulating mass and temperature
representations of the receiver, storage, and power cycle" to capture
temperature-dependent efficiencies is a novel model feature that you have
added, and one that introduces some computational challenges. So, what are the
benefits of adding this feature? How much additional profit can be earned with
a more sophisticated model like yours, and how is the CSP plant operated
differently when you account for temperature-dependent efficiencies? You can
answer these questions. For instance, derive the optimal dispatch decisions
without accounting for these features, then simulate how those decisions would
perform when efficiencies really do depend on temperatures, and you can
calculate how suboptimal they would be (relative to the true solution from your
more sophisticated model). Similarly, you could compare the solutions obtained
and the computational times required to obtain them when you do and do
not apply variable temporal resolution (and when you do apply it, you could
vary the resolutions, times for switching from one resolution to another,
etc.). In other words, your Results section should reveal the impacts of your
specific modeling and solution innovations on CSP plant operations, profits,
and computational times to obtain solutions.

\tco{One issue regarding addressing this request is that if we don't adhere to the mass and temperature balance, the model produces solutions that are simply flat infeasible, which is not very interesting.
Maybe we could see how quickly (in which time periods over the horizon) they go infeasible. We could also do everything on an hourly time fidelity and test the quality of those solutions.
I do not think we want to get too much into further analysis (beyond the new features of the model we present here) because some of that will belong to paper \#2. Try to create Figures 7 and 8 for the linear model as well to state how the nonlinear ones make a more compelling case. John to go back to the original 21 instances and look at how bad the performance was without the tuning tactics (and scaling) and then we will just report what John has readily available. We can also make the case that the linear model generally doesn't produce nonlinear-feasible solutions.}

\item I find it odd that you assume a single, constant price for grid electricity
sales and purchases in all of the numerical instances you consider. The way I
see it, dispatching energy storage optimally is far more important when prices
are time-varying, so that would be the more interesting case to consider and
could really amplify the advantages of your model's novel features.
Furthermore, it seems like it is the built-in TES capability that could
potentially make CSP competitive with solar PV, but with a single, constant
price, there is really no reason to value storage at your facility because you
can sell electricity for the same price whenever you send it to the grid. So, I
suggest that you consider at least some scenarios with time-varying prices,
especially as they might affect the differences in profits achieved using more
and less sophisticated formulations.

\tco{Can you find some time-varying price profiles for John to run? We wouldn't put those in paper \#2 because that's not the way things actually work right now, so these types of results are better relegated to this paper. Mike to find files from a node near Rice or try to find some on the CAISO database. Assume day-ahead market with hourly pricing. }

\item The content in Section 5 prior to Section 5.3 feels somewhat awkward
appearing under the section heading Results. Your descriptions of the hardware
and software, notional plant design, and problem instances are not results.
Normally, this information would appear in a section called something like
Scenarios, Numerical Case Study, Input Data, etc. The fact that only Sections
5.3  and 5.5 truly describe results is consistent with my comment (3), where I
explained that your Results section does not provide commensurate payoff to
readers who invest the time to get there.

\tcb{We have now entitled \S5 (now \S6) ``Scenario Descriptions and Results." Please see response to Comment 3 as well.}

\item In responding to my comment (2), you should consider removing the sporadic
descriptions of how different parts of a CSP plant work from Section 3, and
replacing them with a dedicated section that summarizes CSP plants and how they
work in a qualitative, intuitive manner. This could go a long way toward
helping all readers understand CSP well enough to appreciate your work. This
section could be called something like Background on Concentrating Solar Power,
Concentrating Solar Power: How It Works, or something like that, and appear
between Sections 1 and 2 or Sections 2 and 3.

\tcc{We have added what is now \S3, which we have titled ``CSP Plant Operations Overview,'' and moved Figure 1 to this section.  We added the following paragraph to introduce this section: ``Figure 1 depicts a notional CSP plant with TES in the power tower configuration, and relates sets of constraints in the mathematical formulation we present in Section~4 to the subsystems they represent.  The energy flow through the plant can be subdivided into two procedures.  In the first, which we call \textit{collection mode,} sunlight is absorbed as heat and transferred to thermal energy storage.  The second procedure, which we call \textit{production mode}, deploys the stored thermal energy is to generate electricity by transferring the thermal to electrical energy by driving a turbine and generator with the aid of HTF-to-steam heat exchangers.  Collected energy may be concurrently used in production mode or stored for later use; the presence of TES in this system allows for the two modes to run separately, allowing the plant to schedule production to maximize revenue.'' Then, we moved detailed information on the collection and production modes from the math in \S4 into this section.  We believe that this both (i) summarizes the ``big-picture'' operations of the plant, and (ii) provides a visualization of plant operations and energy flow as the reader proceeds through the formulation.  Please note that we restrict the constraint references in Figure 1 to those featured in the main body of the paper.}

\item On page 2, line 11, ``cost per Watt generated"  does not make sense. Plants
generate energy (e.g., MWh), not power. ``Cost per Watt" would only make
sense as the investment cost for installing capacity.

\tcb{We have now changed this to ``cost per Watt capacity."}

\end{enumerate}

\bibliographystyle{spbasic}   % outcomment this and next line in Case 1
\bibliography{real-time} % if more than one, comma separated

\end{document}

### 2022-02-21 papers/mdpi-default-latex/backmatter.tex

\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

% \institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.}

% \informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

% Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. You might choose to exclude this statement if the study did not report any data.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

%% Optional
% \sampleavailability{Samples of the compounds ... are available from the authors.}

### 2022-04-07 simulations/dispatch/SolarDispatch.py
CR startup parameter fix, now more prominent energy required

@@ -473,7 +473,7 @@ class SolarDispatchParamWrap(GeneralDispatchParamWrap):
         Drsu                    = self.SSC_dict['rec_su_delay']*u.hr
         heliostat_SU_energy     = self.SSC_dict['p_start']*u.kWh
         heliostat_track_energy  = self.SSC_dict['p_track']*u.kW
-        receiver_SU_ratio       = self.SSC_dict['rec_qf_delay'] * u.kWh / u.MW 
+        receiver_SU_ratio       = self.SSC_dict['rec_qf_delay'] * u.MWh / u.MW 
         TES_load_hrs            = self.SSC_dict['tshours']*u.hr
         min_massflow_td_frac    = self.SSC_dict['f_rec_min']
         

### 2022-04-07 simulations/util/DualPlots.py
new op modes for plotting and allowing plots if sim fails

@@ -353,22 +353,33 @@ class DualPlots(SolarPlots):
         # split strings by "__" and create dictionary of all subsystems (PC, TES, etc)
         op_modes_subsystem_splits = [op.split('__') for op in op_modes_labels]
         op_modes_dict = {subsys.split('_')[0]:[] for subsys in op_modes_subsystem_splits[0]}
+        if "ITER_START" in op_modes_labels:
+            op_modes_dict['ITER_START'] = []
         
         for op_mode in op_modes_subsystem_splits:
-            for subsys in op_mode:
-                op_modes_dict[subsys.split('_')[0]].append( subsys.split('_')[1] )
+            if 'ITER_START' in op_mode:
+                op_modes_dict['ITER_START'].append( op_mode[0].split('_')[1] )
+            else:
+                for subsys in op_mode:
+                    op_modes_dict[subsys.split('_')[0]].append( subsys.split('_')[1] )
         
         max_chars = np.array([ len( max(op_modes_dict[subsys], key=len) ) for subsys in op_modes_dict.keys()])
         new_tick_labels = []
         for label in op_modes_labels:
             formatted_label = ''
-            for i,(c,s) in enumerate( zip(max_chars, op_modes_dict.keys()) ):
-                subsys_mode = label.split('__')[i].split('_')[1:]
-                subsys_mode_label = '_'.join(subsys_mode)
-                subsys_mode_label = subsys_mode_label.ljust(c+2,'_')
-                
-                # subsys_op_mode_label = "{0}_{1}".format(s,subsys_mode_label )
-                formatted_label += "{0}_{1}".format(s,subsys_mode_label ) + '__'
+            
+            if label is "ITER_START":
+                formatted_label += label
+            else:
+                for i,(c,s) in enumerate( zip(max_chars, op_modes_dict.keys()) ):
+                    if s is not "ITER_START":
+                        subsys_mode = label.split('__')[i].split('_')[1:]
+                        subsys_mode_label = '_'.join(subsys_mode)
+                        subsys_mode_label = subsys_mode_label.ljust(c+2,'_')
+                        
[…]

### 2022-04-07 simulations/scripts/debugging__Model2_scripts/gen__PySAM_Pyomo_sweep_for_failures__model2.py
scripts to debug model 2

@@ -1,0 +1,349 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jan 19 13:14:51 2022
+
+@author: gabrielsoto
+"""
+
+
+import modules.DualPlantTES as DualPlantTES
+from util.DualPlots import DualOutputExtraction
+from util.FileMethods import FileMethods
+import os, pint, time, copy, pickle
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import matplotlib.patheffects as PathEffects
+import numpy as np
+from pylab import rc
+rc('axes', linewidth=2)
+rc('font', weight='bold',size=12)
+u = pint.UnitRegistry()
+
+# print the PID of this script run
+pid = os.getpid()
+print("PID = ", pid)
+
+# =============================================================================
+# set up
+# =============================================================================
+
+# possible different CSP design qdot 
+csp_qdot_ref = 500 # 500 # 400
+
+# array of successful P_cycle and tshours combinations
+# p_cycle_0     = np.array([ 700, 650, 600, 550,      450, 400, 350, 300, 250, 200, 150 ]) # Pref= 500, tshours=0
+# p_cycle_2     = np.array([ 700, 650, 600, 550, 500,      400, 350, 300, 250, 200, 150 ]) # Pref= 450, tshours=2
+# p_cycle_4     = np.array([ 700, 650, 600, 550, 500,                300, 250, 200, 150 ]) # Pref= [350,450], tshours=4
+# p_cycle_6     = np.array([ 700, 650, 600, 550, 500,      400,      300, 250, 200, 150 ]) # Pref= {350,450}, tshours=6
+# p_cycle_8     = np.array([ 700, 650, 600, 550, 500,           350, 300, 250,      150 ]) # Pref= {200,400,450}, tshours=8
+# p_cycle_10    = np.array([ 700, 650, 600, 550, 500,      400, 350, 300, 250, 200, 150 ]) # Pref= 450, tshours=10
+# p_cycle_12    = np.array([ 700, 650, 600, 550, 500,           350, 300, 250,      150 ]) # Pref= {200,400,450}, tshours=12
+# p_cycle_14    = np.array([ 700, 650, 600, 550, 500,      400, 350, 300, 250, 200, 150 ]) # Pref= 450, tshours=14
+
[…]

### 2022-04-07 simulations/scripts/debugging__Model2_scripts/plot__PySAM_Pyomo_sweep_for_failures__model2.py

@@ -1,0 +1,314 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jan 19 16:55:39 2022
+
+@author: gabrielsoto
+"""
+
+
+from util.PySSCWrapper import PySSCWrapper
+from util.FileMethods import FileMethods
+import os, pint, time, copy, pickle
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import matplotlib.patheffects as PathEffects
+import numpy as np
+from pylab import rc
+rc('axes', linewidth=2)
+rc('font', weight='bold',size=12)
+u = pint.UnitRegistry()
+
+# print the PID of this script run
+pid = os.getpid()
+print("PID = ", pid)
+
+
+# =============================================================================
+# Retrieving Data
+# =============================================================================
+
+# locating output directory
+output_dir = FileMethods.output_dir
+
+start_name     = 'failureModesNoCSPSB' # testDefocus # failureModes # failureModesNoCSPSB
+PySAM_name     = 'PySAM'  # PySAM  # ''
+add_extra_Name = True
+extra_name    = '2022_04'  # 2021_10  # 2021_11 # 2021_12
+json_name     = 'model2_Hamilton_560_tariffx1'   # model2_CAISO_Hamilton  # model2_Hamilton_560_TwoPeaks_x1 # model2_Hamilton_560_tariffx1
+dispatch      = True # True # False
+sscH          = 24   # 12 # 24
+pyoH          = 48   # 24 # 48
+q_dot_CSP     = 500
+TES_min       = 2    # 0  # 2
+TES_max       = 12   # 14
+PC_min        = 600  # 100 # 300 # 400 # 550 # 600 # 900
+PC_max        = 850  # 500 # 850 # 1150
+
+# generate name of file
+filename = '{0}_{1}__{2}__{3}__pyomo_{4:.0f}__horizon_{5:.0f}_{6:.0f}__TES_[{7},{8}]__PC_[{9},{10}]__CSP_{11}.nuctes'.format(
+                start_name,
+                PySAM_name,
+                json_name,
+                extra_name if add_extra_Name else '',
+                dispatch, sscH, pyoH,
+                TES_min, TES_max,
+                PC_min, PC_max, q_dot_CSP )
+
+
+# generate full path to file
+NTPath = os.path.join(output_dir, filename)
+
+if os.path.exists( NTPath ):
[…]

### 2022-04-07 simulations/scripts/debugging__Model2_scripts/run_PySAM_case.py

@@ -1,0 +1,127 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Feb  4 11:23:19 2022
+
+@author: gabrielsoto
+"""
+
+import os, sys
+sys.path.append('..')
+import modules.DualPlantTES as DualPlantTES
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import pint
+import numpy as np
+from pylab import rc
+rc('axes', linewidth=2)
+rc('font', weight='bold',size=12)
+u = pint.UnitRegistry()
+
+pid = os.getpid()
+print("PID = ", pid)
+
+# =============================================================================
+#     Run Simulation
+# =============================================================================
+
+# modifying inputs
+json = "model2_Hamilton_560_TwoPeaks_x1"  # model2_Hamilton_560_tariffx1 # model2_Hamilton_560_TwoPeaks_x1
+dispatch = True
+run_loop = True
+sscH    = 24   # (hr)
+pyoH    = 48   # (hr)
+Pref    = 800  # (MW)
+tshours = 2    # (hr)
+qdotrec = 500  # (MW)
+
+# defining NE2 module
+dptes = DualPlantTES.DualPlantTES(json_name=json, is_dispatch=dispatch, log_dispatch_targets=True) 
+
+# horizons
+dptes.PySAM_dict['ssc_horizon']   = sscH
+dptes.ssc_horizon   = sscH * dptes.u.hr
+dptes.PySAM_dict['pyomo_horizon'] = pyoH
+dptes.pyomo_horizon = pyoH * dptes.u.hr
+
+# saving/updating PYSAM dict to nuctes
+dptes.dispatch_wrap = dptes.create_dispatch_wrapper( dptes.PySAM_dict )
+
+# update SSC dictionary parameters
+dptes.SSC_dict['P_ref'] = Pref
+dptes.SSC_dict['tshours'] = tshours
+dptes.SSC_dict['q_dot_rec_des'] = qdotrec
+
+dptes.dispatch_wrap.set_design()
+
+print("Pref    = {0}".format(dptes.SSC_dict['P_ref'] ) )
+print("tshours = {0}".format(dptes.SSC_dict['tshours'] ) )
+print("QdotRec = {0}".format(dptes.SSC_dict['q_dot_rec_des'] ) )
+# ========================
+
[…]

### 2022-04-07 papers/sustainability-1425053/sustainability-1425053-english.tex

@@
 \address{%
-$^{1}$ \quad Department of Mechanical Engineering, University of Wisconsin---Madison, 1415 University Drive, \mbox{Madison, WI 53706, USA;} bwhite24@wisc.edu (B.W.); mjwagner2@wisc.edu (M.W.)\\
+$^{1}$ \quad Department of Mechanical Engineering, University of Wisconsin---Madison, 1415 Engineering Drive, \mbox{Madison, WI 53706, USA;} bwhite24@wisc.edu (B.W.); mjwagner2@wisc.edu (M.W.)\\
 $^{2}$ \quad Department of Engineering Physics, University of Wisconsin---Madison, 1500 Engineering Drive, \mbox{Madison, WI 53706, USA}\\
@@
 %\replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]
-{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does not incoporate thermal energy storage for meeting peak demand}
+{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does not incorporate thermal energy storage for meeting peak demand.}
 Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and~thermal storage for high dispatchability during high-grid-demand periods.
-A CSP has an array of mirrors concentrating solar rays towards a %\replaced[comment={Furthering explanation of the CSP [3,1]}]
+A CSP \hl{plant} has an array of mirrors concentrating solar rays towards a %\replaced[comment={Furthering explanation of the CSP [3,1]}]
 {tower receiver, transferring the energy into a solar salt, and~storing the solar salt in tanks.
@@
 The~higher temperature salt requires preheating which is achieved prior to the CSP heat addition by a small modular lead-cooled fast reactor.
-The~small modular LFR operates at a low temperature and a fixed location when compared to the higher temperature lead and variable location that the Westinghouse LFR studied in this paper is capable of.
+The~small modular LFR operates at a \hl{relatively low temperature and at a fixed configuration in contrast to the Westinghouse LFR studied in this paper, which is capable of higher temperature and variable configuration}.
 Due to the similar operating temperatures of the CSP and LFR, multiple cycle configurations are studied that are not possible with the similar components in Wang~et~al.
@@
 \end{equation}
-where $C_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively.
+where $\dot{C}_{avg}$ is the average capacitance rate across the hot or cold stream and $c_{in}$ and $c_{out}$ is the specific heat at the inlet and outlet respectively.
 %\replaced[comment={Improving counter-flow hx explanation [1,1]}]
@@
 The~cycle with heat addition from the CSP powers the other two turbines, which for modeling purposes are combined into a single turbine T2, while having a dedicated high-temperature recuperator, HTR2.
-The~two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine.
-Additionally, the~power produced by the two turbines is proportional to mass flow rate, each receives a fraction of the mass flow rate, therefore producing the same fraction of power.
-Summing these power fractions together yields the total power of a singular turbine in the same position.
-After~the high-temperature recuperators, the~two flows are combined and sent to the LTR hot~side.
 
@@
   \switchcolumn
+
+  The~two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine.
+Additionally, the~power produced by the two turbines is proportional to mass flow rate, each receives a fraction of the mass flow rate, therefore producing the same fraction of power.
+Summing these power fractions together yields the total power of a singular turbine in the same position.
+After~the high-temperature recuperators, the~two flows are combined and sent to the LTR hot~side.
 
@@
 
+A problem arises with this salt charging configuration.
+The~temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $560~^{\circ}$C when the turbine power is balanced with the compressor demand.
+To~raise the temperature, some of the high-temperature flow before the turbine is redirected through a valve and combined after the turbine.
+Limiting the flow through the turbine reduces the turbine power and compressor power because of the balancing requirement.
+Due to the reduction in available compressor power, the~LFR RC is effectively bypassed, and~a large portion of usable heat is expelled in the LFR PC before the LFR MC.
+The~thermal storage efficiency reduces as a result of the large amount of heat rejected in the LFR~PC.
+
 \end{paracol}
@@
 \switchcolumn
-
-A problem arises with this salt charging configuration.
-The~temperature out of the turbine is not high enough to charge the hot CSP TES to the required value of $560~^{\circ}$C when the turbine power is balanced with the compressor demand.
-To~raise the temperature, some of the high-temperature flow before the turbine is redirected through a valve and combined after the turbine.
-Limiting the flow through the turbine reduces the turbine power and compressor power because of the balancing requirement.
-Due to the reduction in available compressor power, the~LFR RC is effectively bypassed, and~a large portion of usable heat is expelled in the LFR PC before the LFR MC.
-The~thermal storage efficiency reduces as a result of the large amount of heat rejected in the LFR~PC.
 
@@
 For~the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$~^{\circ}$C.
-With~this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
+With~this low of a LFR outlet temperature, \hl{73.8}\% of the flow is redirected around the turbine to raise the temperature prior to C2S.
 As~the temperature of the hot TES is raised above a value of 540$~^{\circ}$C, the~amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible.
 The~temperature in the hot TES is therefore set to a lower value of 540$~^{\circ}$C to allow for operation of this cycle.
-With~heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
-This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the~lowest of all tested TES charging~configurations.
+With~heat storage efficiency maximized, \hl{93.9}\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler.
+This amount of rejected heat is reflected in a heat storage efficiency of \hl{34.5}\%, the~lowest of all tested TES charging~configurations.
 
@@
 Defining the approach temperature as $10~^{\circ}$C causes the energy balance governing combiner 2 to be over constrained.
-Therefore, this value is free and calculated to be $35~^{\circ}$C for the $390~^{\circ}$C case and $26.27~^{\circ}$C for the $440~^{\circ}$C case.
+Therefore, this value is free and calculated to be $35~^{\circ}$C for the $390~^{\circ}$C case and $26.3~^{\circ}$C for the $440~^{\circ}$C case.
 Both of these different temperature cold TES studies do not change the cycle parameters because, as~seen in C-1HTR1T-ON and C-2HTR3T-ON, the~solar salt mass flow rate adjusts to accommodate for the temperature difference.
@@
 Increasing the mass flow rate has a higher demand on system components but in this situation it allows for the salt to be charged at a higher rate, increasing the storage capabilities.
-Both cycles have a heat storage efficiency of 45.30\%.
+Both cycles have a heat storage efficiency of \hl{45.3}\%.
 
